### 2019-09-10 conclusion.tex
first step from osama

\section{Conclusion}

In the present paper, five different types of initial fissile materials have been studied for transitioning to thorium fuel cycle in the \gls{SD-TMSR}. The molar composition of startup fuel for all five cases is listed in Table~\ref{tab:table4}, as well, the inventories in Table~\ref{tab:table5}. We adopted two different feed mechanisms; thorium feed mechanism and non-thorium feed mechanism. The whole-core of the SD-TMSR was simulated with Pu reactor-grade, TRU, and $^{233}$U as initial fissile materials. Besides, the variation of the effective multiplication factor $k_{eff}$, inventory, and other neutronic parameters have been investigated. Results demonstrated that continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U startup fuel. Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U. in addition, the Pu proportion in fuel salt has been calculated and found to be below the solubility limit. Finally, the neutron flux spectrum for the three selected cases has been described.

\section{Future work}

%The authors intend to compare the present results and results from SaltProc batch-wise code \cite{rykhlevskii2019modeling} in future work. Moreover, they will consider the delayed neutron precursor drift. Future work will also consider the benchmark study based on other codes and models. The authors intend to conduct a sensitivity study to evaluate the impact of the radial reflector material and its thickness. In addition, they will study the impact of \gls{FPs} removal (i.e. only reprocessing without refueling) on reactivity and neutron economy.

\section{Conflict of interest}

The authors declare no conflict of interest.

### 2019-09-10 introduction.tex
first step from osama

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation nuclear systems. These goals are; safety and reliability, economics, sustainability, and non-proliferation and physical protection \cite{doe2002technology}. \glspl{MSR} have many advantages that consistent with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online reprocessing and refueling, excellent neutron economy and operation under ambient pressure \cite{siemer2015molten,rosenthal1970molten}. Therefore, in 2002 the \gls{MSR} has been chosen as one of the promising reactors by this forum \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel supposed to be in the form of liquid dissolved in molten salt (e.g., LiF or NaCl). This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly circulates through the core and allows transferring fission heat.

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 MWth) was introduced by the \gls{CAS} \cite{li_optimization_2018}. The SD-TMSR is a graphite-moderated thermal-spectrum MSR. In the SD-TMSR the fissile and fertile elements are integrated into the same salt. In addition, the active core is divided into two zones, the radius of the fuel channels in the outer zone is modified to be larger than the radius of the fuel channels in the inner zone to improve the breeding ratio \cite{nuttin2005potential,li_optimization_2018}.

Basically, the \gls{MSR} has been designed to apply the Th/$^{233}$U fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,merle2004scenarios,rosenthal1970molten}. Hence, the fertile isotope $^{232}$Th is converted to the fissile isotope $^{233}$U, an isotope that is not exist in nature. Therefore it is required to examine available fissile materials (e.g., $^{235}$U and Pu) to replace the $^{233}$U in the startup fuel \cite{betzler2016modeling,zou2018transition}. The thorium fuel cycle transition can be achieved after reaching the doubling time\footnote{Time required to produce enough amount of $^{233}$U to trigger a new SD-TMSR.} of $^{233}$U.

Betzler, et al. discussed the simulation of the start-up of a MSBR unit cell with LEU (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial fissile materials \cite{betzler2016modeling}. They concluded that the plutonium vector extracted from LWR SF serves as the best alternative source to $^{233}$U thanks to the highest ratio of fissile isotopes \cite{betzler2016modeling}. Zou, et al. introduced two ways for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition. In the former way, the TMSR is launched with existing fissile material and thorium as a fertile material, then the bred $^{233}$U from thorium is rerouted into the core for criticality. In contrast, the latter way tends to store the bred $^{233}$U out of the core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Meanwhile, Zou, et al. studied the transitioning to thorium fuel cycle in a small modular Th-based molten salt reactor (smTMSR) using TRUs as startup fuel. They concluded that the transition to thorium fuel cycle can be achieved in thermal smTMSR with a proper fuel fraction \cite{zou2018preliminary}.
Heuer, et al., discussed the transition characteristics of the \gls{MSFR} under different launching scenarios (e.g., enriched uranium and TRU) \cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the MSRs with fissile materials alternative to $^{233}$U. Many of these researches focus on the fast-spectrum MSRs \cite{ashraf2019modeling,ashraf2018nuclear,heuer2014towards,fiorina2013investigation}, while little focus on thermal-spectrum MSRs \cite{betzler2016modeling,zou2018preliminary,zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other fissile materials (except $^{233}$U) not found in the literature. Therefore, the present paper discusses the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition. To do that, we investigate five types of initial fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF \cite{de2000scenarios}. Moreover, two different feed mechanisms are used: \\
(1)Th + $^{233}$U from Pa-decay tank (i.e. removal mass rate (Pa-233) = feed mass rate ($^{233}$U)) \cite{betzler2016modeling}.\\
(2)continuous feed flow of (HM except for Th) + some or all $^{233}$U from Pa-decay tank.\\
This present paper is organized as follows: after an introduction on \gls{MSR} systems, the model description is discussed in section 2. Methodology and tools is descried in section 3. Extraction and feed mechanisms are addressed in section 4. Section 5 focuses on the results and discussion. Finally, section 6 highlights the conclusions.

%produce enough amount of $^{233}$U to start a new \gls{SD-TMSR}. 
%Therefore, the aim of this paper is to operate the \gls{SD-TMSR} for a long period of time with different initial fissile materials without external feed of $^{233}$U (that does not exist anywhere) to produce enough amount of $^{233}$U that is required to start a new \gls{SD-TMSR}.

%The \gls{MSR} is the only liquid-fueled reactor that the \gls{GIF} has chosen as one of the six promising concepts \cite{doe2002technology,pioro2016handbook}. The reactor's liquid fuel distinguishes it from other nuclear reactors. \glspl{MSR} can operate extended time without shutdown for refueling with a superior neutron economy \cite{doe2002technology}. Introducing online reprocessing and refueling systems would ensure sustainability. In a \gls{MSR}, liquid fuel salt (e.g. a mixture of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) circulates through the core and transports fission heat to the \glspl{IHX}. Finally, this type of reactor has a high conversion efficiency and a negative temperature coefficient.

%Both thermal and fast \gls{MSR} concepts exist in the literature \cite{pioro2016handbook,engel1979development}. For thermal \glspl{MSR}, hexagonal graphite prisms act as moderators. In contrast, fast spectrum \glspl{MSR} lack moderators. A \gls{MSR} can breed in both cases, making them optimal for realizing a desirable Thorium-Uranium fuel cycle \cite{hargraves2010liquid}.

%In the 1950s, \gls{ORNL} performed experiments that provided a basis for \gls{MSR} feasibility. In 1958, a 5 MW$_{th}$ homogeneous reactor experiment called HRE-2 utilized water-based liquid fuel to illustrate the intrinsic stability of homogeneous reactors. In the 1960s, \gls{ORNL} performed the \gls{MSRE} \cite{engel1979development,haubenreich1970experience,fiorinibasis,robertson1965msre}. These experiments demonstrated the capability of circulating a liquid fluoride mixture without significant corrosion problems. Researchers used a nickel-based alloy (Hastelloy N) as structural material and controlled the fuel's oxidation by using a U$^{3+}$/U$^{4+}$ buffer. The experiment also tested the continuous reprocessing of liquid fuel. The results showed that introducing a noble gas system (i.e. gas bubbling system) during the fuel cycle helps extract gaseous fission products \cite{pioro2016handbook}.

%\gls{ORNL} later researched the \gls{MSBR} \cite{rosenthal1970molten}. There were two types of \gls{MSBR}: the single-fluid molten salt reactor and the two-fluid molten salt reactor. While the single-fluid MSR dissolves fertile and fissile materials in the same salt, the two-fluid MSR physically separates them. The two-fluid MSR had a higher breeding performance than the single-fluid MSR. However, the single-fluid MSR can operate as an iso-breeding reactor as long as there is an efficient reprocessing system for the fuel salt \cite{rosenthal1970molten}.

%Despite the success of the \gls{MSRE}, \gls{ORNL} halted work on the \gls{MSBR} in 1976. The \gls{Euratom} later revived the project. To enhance the breeding performance of the \gls{MSBR}, \gls{Euratom} introduced the idea of dividing the core into multiple zones of fuel channels with different radii \cite{nuttin2005potential}. The results showed that increasing the radii of the outer fuel channels relative to the inner radii improved the reactor's breeding and allowed it to out-perform the reactor with a single-zone core and large fuel channels \cite{nuttin2005potential}.

%Later, fast spectrum MSRs were introduced. Several fast MSR designs include: \gls{MSFR}, \gls{EVOL} \cite{serp2014molten}, \gls{MOSART} \cite{boussier2012molten}, REBUS-3700 \cite{mourogov2006potentialities} and Molten Chloride Salt Fast Reactor \cite{taube1978fast}. \gls{GIF} has elected to further research \gls{MSFR} and \gls{MOSART} \cite{serp2014molten,boussier2012molten,locatelli2013generation,pettersen2016coupled}. Both designs feature the fast-spectrum, Th-based fuel, and liquid fuel circulation. The \gls{MSFR} concept initially gained momentum at \gls{CNRS} in France, and the \gls{MOSART} concept is in progress in Russia.

%Indeed, several challenges interfere with the commercial adoption of \gls{MSFR}. For example, large initial inventory of $^{233}$U and relatively long doubling time for $^{233}$U production. Moreover, material scientists must identify or create structural materials which have reasonable lifespan in extreme operational conditions (high temperature, large neutron flux, chemically aggressive salt). Finally, breeding of high-quiality fissile material in the \gls{MSFR} blanket rises significant nuclear non-proliferation concerns \cite{pettersen2016coupled,merle2009minimizing}.

%The thermal MSR has priority due to the low inventory of initial fissile $^{233}$U and short doubling time for its production \cite{ZOU2015114}. 
%Nagy et al. studied the effect of core zoning on the breeding performance and graphite lifespan of a graphite-moderated MSR \cite{nagy2011new,nagy2012effects}. Li et al. divided the active core into two zones to improve the breeding performance \cite{li_optimization_2018}. The central zone is moderated, while the unmoderated outer zone acts as a subcritical fast spectrum zone \cite{li_optimization_2018}.

%In 2011, the \gls{CAS} established the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)". Since then, several studies aimed to improve the \gls{TMSR} to efficiently utilize the Th-U fuel cycle \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}.
%Separately, we can highlight the issue of a closed Th-U fuel cycle in the thermal spectrum. A number of studies have shown the fundamental possibility of organizing such a cycle in a heavy-water reactor and referred to the limitation of the burn-up of solid fuels due to the accumulation of the fission products (FPs) \cite{dastur1995thorium,bergel2004mode,bergelson2008op}. The question of feasibility and parameters of a closed U-Th fuel cycle in a \gls{TMSR} reactor is relevant.

%Liquid-fueled systems require specific neutron transport and depletion tools that capture online fuel reprocessing and refueling. Specifically, the circulation of the liquid fuel and the continuous feed or removal of elements (e.g. fissile material injection into and Fission Products (FPs) extraction from the fuel salt) are out-of-scope for most contemporary nuclear reactor physics software, which was originally written primarily to simulate solid-fueled reactors. The SERPENT-2 \cite{leppanen2014serpent} code extension takes into account the online fuel reprocessing and its effects on depletion calculations \cite{aufiero2013extended}.

%The present paper aims to analyze the fuel depletion of the \gls{SD-TMSR} during 60 years reactor operation time using SERPENT-2. This work investigates the inventory of isotopes in the core to establish the advantages of the \gls{TMSR} concept applied to energy production (based on the thorium fuel cycle). All calculations presented in the present work were implemented using SERPENT-2 version 2.1.30. We adopted the built-in SERPENT-2 subroutine to simulate continuous online reprocessing and refueling in contrast with other batch-wise codes \footnote{In the batch-wise technique, the simulation stops at a certain time and restarts after removing of poisoning isotopes and addition of fissile and/or fertile materials.} (e.g. SaltProc \cite{rykhlevskii2019modeling} and MCNP6-PYTHON \cite{Jeong2016}). 
%SERPENT-2 allowed us to conduct burn-up calculations on computer clusters with multiple cores using distributed-memory MPI parallelization. The drift of the delayed neutron precursors is not examined in this paper.

%The present paper is organized as follows: after a general introduction about \gls{MSR} systems, section 2 briefly presents the \gls{SD-TMSR}. Section 3 focuses on the methodology and calculation tools used in this work. Fission products extraction modeling is described in section 4. Section 5 highlights the results and discussion. Finally, section 6 summarizes the conclusions.

% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.

### 2019-09-10 acks.tex

\section{Acknowledgments}

Osama Ashraf would like to thank the Egyptian Ministry of Higher Education (MoHE), as well as MEPhI's Competitiveness Program for providing financial support for this research. The facility and tools needed to conduct this work were supported by MEPhI.

The authors contributed to this work as described below.

Osama Ashraf conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, and reviewed drafts of the paper.

Andrei Rykhlevskii conceived and designed the simulations, wrote the paper, prepared figures 
and/or tables, performed the computation work, and reviewed drafts of the paper. Andrei Rykhlevskii 
is supported by  DOE ARPA-E MEITNER program award DE-AR0000983.

G. V. Tikhomirov directed and supervised the work, conceived and designed the simulations and reviewed drafts of the paper. Prof. Tikhomirov is supported by Rosatom, he is Deputy Director of the Institute of Nuclear Physics and Engineering MEPhI. Board member of Nuclear society of Russia.

Kathryn D. Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.  Prof. Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the NNSA Office of Defense Nuclear Nonproliferation R\&D through the Consortium for Verfication Technologies and the Consortium for Nonproliferation Enabling Capabilities,  the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

This research is part of the Blue Waters sustained-petascale computing project, 
which is supported by the National Science Foundation (awards OCI-0725070 and 
ACI-1238993) and the state of Illinois. Blue Waters is a joint effort of the 
University of Illinois at Urbana-Champaign and its National Center for 
Supercomputing Applications

### 2019-09-10 acros.tex

\newacronym{<++>}{<++>}{<++>}
\newacronym[longplural={metric tons of heavy metal}]{MTHM}{MTHM}{metric ton of heavy metal}
\newacronym{ABM}{ABM}{agent-based modeling}
\newacronym{TRU}{TRU}{Transuranic elements}
\newacronym{LEU}{LEU}{Low-enriched uranium}
\newacronym{ACDIS}{ACDIS}{Program in Arms Control \& Domestic and International Security}
\newacronym{AHTR}{AHTR}{Advanced High Temperature Reactor}
\newacronym{ANDRA}{ANDRA}{Agence Nationale pour la gestion des D\'echets RAdioactifs, the French National Agency for Radioactive Waste Management}
\newacronym{ANL}{ANL}{Argonne National Laboratory}
\newacronym{ANS}{ANS}{American Nuclear Society}
\newacronym{API}{API}{application programming interface}
\newacronym{ARE}{ARE}{Aircraft Reactor Experiment}
\newacronym{ARFC}{ARFC}{Advanced Reactors and Fuel Cycles}
\newacronym{ASME}{ASME}{American Society of Mechanical Engineers}
\newacronym{ATWS}{ATWS}{Anticipated Transient Without Scram}
\newacronym{BDBE}{BDBE}{Beyond Design Basis Event}
\newacronym{BIDS}{BIDS}{Berkeley Institute for Data Science}
\newacronym{BR}{BR}{Breeding Ratio}
\newacronym{CAFCA}{CAFCA}{ Code for Advanced Fuel Cycles Assessment }
\newacronym{CAS}{CAS}{Chinese Academy of Sciences} 
\newacronym{CDTN}{CDTN}{Centro de Desenvolvimento da Tecnologia Nuclear}
\newacronym{CEA}{CEA}{Commissariat \`a l'\'Energie Atomique et aux \'Energies Alternatives}
\newacronym{CFD}{CFD}{Computational Fluid Dynamics}
\newacronym{CI}{CI}{continuous integration}
\newacronym{CNEN}{CNEN}{Comiss\~{a}o Nacional de Energia Nuclear}
\newacronym{CNERG}{CNERG}{Computational Nuclear Engineering Research Group}
\newacronym{COSI}{COSI}{Commelini-Sicard}
\newacronym{COTS}{COTS}{commercial, off-the-shelf}
\newacronym{CSNF}{CSNF}{commercial spent nuclear fuel}
\newacronym{CTAH}{CTAHs}{Coiled Tube Air Heaters}
\newacronym{CUBIT}{CUBIT}{CUBIT Geometry and Mesh Generation Toolkit}
\newacronym{CURIE}{CURIE}{Centralized Used Fuel Resource for Information Exchange}
\newacronym{DAG}{DAG}{directed acyclic graph}
\newacronym{DANESS}{DANESS}{Dynamic Analysis of Nuclear Energy System Strategies}
\newacronym{DBE}{DBE}{Design Basis Event}
\newacronym{DESAE}{DESAE}{Dynamic Analysis of Nuclear Energy Systems Strategies}
\newacronym{DHS}{DHS}{Department of Homeland Security}
\newacronym{DOE}{DOE}{Department of Energy}
\newacronym{DRACS}{DRACS}{Direct Reactor Auxiliary Cooling System}
\newacronym{DRE}{DRE}{dynamic resource exchange}
\newacronym{DSNF}{DSNF}{DOE spent nuclear fuel}
\newacronym{DYMOND}{DYMOND}{Dynamic Model of Nuclear Development }
\newacronym{EBS}{EBS}{Engineered Barrier System}
\newacronym{EDF}{EDF}{Électricité de France}
\newacronym{EDZ}{EDZ}{Excavation Disturbed Zone}
\newacronym{EFPY}{EFPY}{Effective Full-Power Years}
\newacronym{EIA}{EIA}{U.S. Energy Information Administration}
\newacronym{EPA}{EPA}{Environmental Protection Agency}
\newacronym{EPR}{EPR}{European Pressurized Reactors}
\newacronym{EP}{EP}{Engineering Physics}
\newacronym{EU}{EU}{European Union}
\newacronym{FCO}{FCO}{Fuel Cycle Options}
\newacronym{FCT}{FCT}{Fuel Cycle Technology}
\newacronym{FEHM}{FEHM}{Finite Element Heat and Mass Transfer}
\newacronym{FEPs}{FEPs}{Features, Events, and Processes}
\newacronym{FHR}{FHR}{Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{FLiBe}{FLiBe}{Fluoride-Lithium-Beryllium}
\newacronym{FP}{FP}{Fission Product}
\newacronym{FTC}{FTC}{Fuel Temperature Coefficient}
\newacronym{GDSE}{GDSE}{Generic Disposal System Environment}
\newacronym{GDSM}{GDSM}{Generic Disposal System Model}
\newacronym{GENIUSv1}{GENIUSv1}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 1}
\newacronym{GENIUSv2}{GENIUSv2}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios, Version 2}
\newacronym{GENIUS}{GENIUS}{Global Evaluation of Nuclear Infrastructure Utilization Scenarios}
\newacronym{GIF}{GIF}{Generation IV International Forum}
\newacronym{GPAM}{GPAM}{Generic Performance Assessment Model}
\newacronym{GRSAC}{GRSAC}{Graphite Reactor Severe Accident Code}
\newacronym{GUI}{GUI}{graphical user interface}
\newacronym{HLW}{HLW}{high level waste}
\newacronym{HPC}{HPC}{high-performance computing}
\newacronym{HTC}{HTC}{high-throughput computing}
\newacronym{HTGR}{HTGR}{High Temperature Gas-Cooled Reactor}
\newacronym{IAEA}{IAEA}{International Atomic Energy Agency}
\newacronym{IEMA}{IEMA}{Illinois Emergency Mangament Agency}
\newacronym{IHLRWM}{IHLRWM}{International High Level Radioactive Waste Management}
\newacronym{INL}{INL}{Idaho National Laboratory}
\newacronym{IHX}{IHX}{Intermediate Heat Exchanger}
\newacronym{IPRR1}{IRP-R1}{Instituto de Pesquisas Radioativas Reator 1}
\newacronym{IRP}{IRP}{Integrated Research Project}
\newacronym{ISFSI}{ISFSI}{Independent Spent Fuel Storage Installation}
\newacronym{ISRG}{ISRG}{Independent Student Research Group}
\newacronym{JFNK}{JFNK}{Jacobian-Free Newton Krylov}
\newacronym{LANL}{LANL}{Los Alamos National Laboratory}
\newacronym{LBNL}{LBNL}{Lawrence Berkeley National Laboratory}
\newacronym{LCOE}{LCOE}{levelized cost of electricity}
\newacronym{LDRD}{LDRD}{laboratory directed research and development}
\newacronym{LFR}{LFR}{Lead-Cooled Fast Reactor}
\newacronym{LLNL}{LLNL}{Lawrence Livermore National Laboratory}
\newacronym{LMFBR}{LMFBR}{Liquid Metal Fast Breeder Reactor}
\newacronym{LOFC}{LOFC}{Loss of Forced Cooling}
\newacronym{LOHS}{LOHS}{Loss of Heat Sink}
\newacronym{LOLA}{LOLA}{Loss of Large Area}
\newacronym{LP}{LP}{linear program}
\newacronym{LWR}{LWR}{Light Water Reactor}
\newacronym{MAGNOX}{MAGNOX}{Magnesium Alloy Graphie Moderated Gas Cooled Uranium Oxide Reactor}
\newacronym{MA}{MA}{minor actinide}
\newacronym{MCNP}{MCNP}{Monte Carlo N-Particle code}
\newacronym{MILP}{MILP}{mixed-integer linear program}
\newacronym{MIT}{MIT}{the Massachusetts Institute of Technology}
\newacronym{MOAB}{MOAB}{Mesh-Oriented datABase}
\newacronym{MOOSE}{MOOSE}{Multiphysics Object-Oriented Simulation Environment}
\newacronym{MOSART}{MOSART}{MOlten Salt Actinide Recycler and Transmuter}
\newacronym{MOX}{MOX}{mixed oxide}
\newacronym{MPI}{MPI}{Message Passing Interface}
\newacronym{MRPP}{MRPP}{Multiregion Processing Plant}
\newacronym{MSBR}{MSBR}{Molten Salt Breeder Reactor}
\newacronym{MSFR}{MSFR}{Molten Salt Fast Reactor}
\newacronym{MSRE}{MSRE}{Molten Salt Reactor Experiment}
\newacronym{MSR}{MSR}{Molten Salt Reactor}
\newacronym{MTC}{MTC}{Moderator Temperature Coefficient}
\newacronym{NAGRA}{NAGRA}{National Cooperative for the Disposal of Radioactive Waste}
\newacronym{NEAMS}{NEAMS}{Nuclear Engineering Advanced Modeling and Simulation}
\newacronym{NEUP}{NEUP}{Nuclear Energy University Programs}
\newacronym{NFCSim}{NFCSim}{Nuclear Fuel Cycle Simulator}
\newacronym{NGNP}{NGNP}{Next Generation Nuclear Plant}
\newacronym{NMWPC}{NMWPC}{Nuclear MW Per Capita}
\newacronym{NNSA}{NNSA}{National Nuclear Security Administration}
\newacronym{NPP}{NPP}{Nuclear Power Plant}
\newacronym{NPRE}{NPRE}{Department of Nuclear, Plasma, and Radiological Engineering}
\newacronym{NQA1}{NQA-1}{Nuclear Quality Assurance - 1}
\newacronym{NRC}{NRC}{Nuclear Regulatory Commission}
\newacronym{NSF}{NSF}{National Science Foundation}
\newacronym{NSSC}{NSSC}{Nuclear Science and Security Consortium}
\newacronym{NUWASTE}{NUWASTE}{Nuclear Waste Assessment System for Technical Evaluation}
\newacronym{NWF}{NWF}{Nuclear Waste Fund}
\newacronym{NWTRB}{NWTRB}{Nuclear Waste Technical Review Board}
\newacronym{OCRWM}{OCRWM}{Office of Civilian Radioactive Waste Management}
\newacronym{ORION}{ORION}{ORION}
\newacronym{ORNL}{ORNL}{Oak Ridge National Laboratory}
\newacronym{PARCS}{PARCS}{Purdue Advanced Reactor Core Simulator}
\newacronym{PBAHTR}{PB-AHTR}{Pebble Bed Advanced High Temperature Reactor}
\newacronym{PBFHR}{PB-FHR}{Pebble-Bed Fluoride-Salt-Cooled High-Temperature Reactor}
\newacronym{PEI}{PEI}{Peak Environmental Impact}
\newacronym{PH}{PRONGHORN}{PRONGHORN}
\newacronym{PRIS}{PRIS}{Power Reactor Information System}
\newacronym{PRKE}{PRKE}{Point Reactor Kinetics Equations}
\newacronym{PSPG}{PSPG}{Pressure-Stabilizing/Petrov-Galerkin}
\newacronym{PWAR}{PWAR}{Pratt and Whitney Aircraft Reactor}
\newacronym{PWR}{PWR}{Pressurized Water Reactor}
\newacronym{PyNE}{PyNE}{Python toolkit for Nuclear Engineering}
\newacronym{PyRK}{PyRK}{Python for Reactor Kinetics}
\newacronym{QA}{QA}{quality assurance}
\newacronym{RDD}{RD\&D}{Research Development and Demonstration}
\newacronym{RD}{R\&D}{Research and Development}
\newacronym{REE}{REE}{rare earth element}
\newacronym{RELAP}{RELAP}{Reactor Excursion and Leak Analysis Program}
\newacronym{RIA}{RIA}{Reactivity Insertion Accident}
\newacronym{RIF}{RIF}{Region-Institution-Facility}
\newacronym{ROD}{ROD}{Reactor Optimum Design}
\newacronym{SD-TMSR}{SD-TMSR}{Single-fluid Double-zone Thorium-based Molten Salt Reactor}	
\newacronym{SFR}{SFR}{Sodium-Cooled Fast Reactor}
\newacronym{SINDAG}{SINDA{\textbackslash}G}{Systems Improved Numerical Differencing Analyzer $\backslash$ Gaski}
\newacronym{SKB}{SKB}{Svensk K\"{a}rnbr\"{a}nslehantering AB}
\newacronym{SNF}{SNF}{spent nuclear fuel}
\newacronym{SNL}{SNL}{Sandia National Laboratory}
\newacronym{STC}{STC}{specific temperature change}
\newacronym{SUPG}{SUPG}{Streamline-Upwind/Petrov-Galerkin}
\newacronym{SWF}{SWF}{Separations and Waste Forms}
\newacronym{SWU}{SWU}{Separative Work Unit}
\newacronym{TRIGA}{TRIGA}{Training Research Isotope General Atomic}
\newacronym{TRISO}{TRISO}{Tristructural Isotropic}
\newacronym{TSM}{TSM}{Total System Model}
\newacronym{TSPA}{TSPA}{Total System Performance Assessment for the Yucca Mountain License Application}
\newacronym{ThOX}{ThOX}{thorium oxide}
\newacronym{UFD}{UFD}{Used Fuel Disposition}
\newacronym{UML}{UML}{Unified Modeling Language}
\newacronym{UOX}{UOX}{uranium oxide}
\newacronym{UQ}{UQ}{uncertainty quantification}
\newacronym{US}{US}{United States}
\newacronym{UW}{UW}{University of Wisconsin}
\newacronym{VISION}{VISION}{the Verifiable Fuel Cycle Simulation Model}
\newacronym{VVER}{VVER}{Voda-Vodyanoi Energetichesky Reaktor (Russian Pressurized Water Reactor)}
\newacronym{VV}{V\&V}{verification and validation}
\newacronym{WIPP}{WIPP}{Waste Isolation Pilot Plant}
\newacronym{YMR}{YMR}{Yucca Mountain Repository Site}
\newacronym{CNRS}{CNRS}{National Center for Scientific Research}		
\newacronym{CRAM}{CRAM}{Chebyshev Rational Approximation Method}
\newacronym{DT}{DT}{Doubling Time}		
\newacronym{Euratom}{Euratom}{European Atomic Energy Community}
\newacronym{FPs}{FPs}{Fission Products} 
\newacronym{HM}{HM}{Heavy Metal}
\newacronym{MAs}{MAs}{Minor Actinides}
\newacronym{OpenMP}{OpenMP}{Open Multi-Processing}
\newacronym{TCR}{TCR}{Temperature Coefficient of Reactivity}
\newacronym{3D}{3D}{Three Dimensions}			
\newacronym{TS-MSR}{TS-MSR}{Thermal-Spectrum Molten Salt Reactor}
\newacronym{FS-MSR}{FS-MSR}{Fast-Spectrum Molten Salt Reactor}
\newacronym{EVOL}{EVOL}{Evaluation and Viability of Liquid Fuel Fast Reactor System}
\newacronym{TMSR}{TMSR}{Thorium-based Molten Salt Reactor}

### 2019-09-11 paper/abstract.tex
add paper and Scenarios folders

\begin{abstract}
Liquid-fueled Molten Salt Reactor (MSR) systems represent advances in safety, economics, sustainability, and proliferation-resistance. Therefore, \gls{MSR} has been selected as one of the promising reactors by the \gls{GIF}. Basically, the \gls{MSR} has been designed to operate based on Th/$^{233}$U fuel cycle. Since $^{233}$U does not exist in nature, it is required to examine available fissile materials to replace the $^{233}$U in the startup fuel. Here, five different types of initial fissile materials are proposed for transitioning to thorium fuel cycle in the \gls{SD-TMSR}. Plutonium mixed with \gls{LEU} (19.79\%), \gls{LEU} (19.79\%), Plutonium reactor-grade, \gls{TRU} from LWR spent fuel (SF) and finally $^{233}$U for comparison purpose are investigated. In the present paper, two different feed mechanisms are applied. Consequently, the multiplication factor, inventories of important nuclides and net production of $^{233}$U are studied. Moreover, the molten salt Temperature Coefficient of Reactivity $(\alpha$$_{T}$) is negative for startup and equilibrium states. The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U startup fuel. Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U. 
\end{abstract}

%The SD-TMSR (2,250 MW$_{th}$) is a Single-fluid Double-zone Thorium-based Molten Salt Reactor. The active core of the SD-TMSR is divided into the inner zone (486 fuel tubes) and the outer zone (522 fuel tubes) to improve the Th-U breeding performance. The lack of computational reactor analysis software that deal with MSR cores prevents improvement. This work adopted the SERPENT-2 Monte Carlo code to analyze the whole core model of the SD-TMSR. Built-in SERPENT-2 capabilities simulated online reprocessing and refueling and calculated the multiplication factor and Breeding Ratio (BR). We found that the molten salt Temperature Coefficient of Reactivity $(\alpha$$_{T}$) was negative for initial and equilibrium states. This study investigated the variation of the multiplication factor, BR, and build-up of important nuclides in the core as a function of burn-up time. Under online reprocessing and refueling, we studied the variation of the reactivity during 60 years of reactor operation. The present work has introduced a feasible reprocessing scheme. In addition, it has investigated the neutron flux energy spectrum at initial and equilibrium state.
%In conclusion, the full core of SD-TMSR was modeled and the net production of $^{233}$U was found to be positive.

### 2019-09-11 paper/methods.tex
add paper and Scenarios folders

\section{Model description}
\subsection{Geometry}
The \gls{SD-TMSR} design model was introduced by the \gls{CAS} during the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)" in 2011 \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The design of \gls{SD-TMSR} is inspired by \gls{MSBR} \cite{robertson_conceptual_1971} after some modification in the geometry to control the positive temperature coefficient in MSBR. The \gls{SD-TMSR} model is described deeply in \cite{li_optimization_2018}.
Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the \gls{SD-TMSR}. The active zone is a right cylinder with height and diameter equal to 460 cm. Assemblies of graphite\footnote{Density of graphite 2.3 g/cm$^3$.} hexagonal prisms fill the core. The side length of the graphite hexagonal prism was optimized in \cite{li_optimization_2018} and found to be 7.5 cm. The liquid fuel circulates continuously through the fuel channels that pierces the graphite hexagonal prisms. The active zone is divided into two different zones to enhance Th-U breeding performance. The radius of the fuel tubes in the outer zone is 5 cm and the radius of the fuel tubes in the inner zone is 3.5 cm. Moreover, axial and radial reflectors from graphite surround the active zone to maximize neutron flux. The core is surrounded by B${_4}$C cylinder that acts as a shield against heat and neutrons radiation. 
Another Ni-based (hastelloy N) cylinder surrounds the whole core and provides structure and heat protection. The main characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.

\begin{figure} % replace 't' with 'b' to \centering [hbp!]
	\includegraphics[width=\textwidth]{ff.jpg}
	\caption{The quarter-core model configuration of the SD-TMSR a) Longitudinal view b) cross-sectional view at the horizontal midplane.}
	\label{fig:ff}
\end{figure}

\begin{table}  %[!ht]
	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{l | l}
		\hline
		Thermal power, MW$_{th}$          				&  2,250  \\ 
		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_4$ \\
		Fuel composition, mole\%                        & 70-17.5-12.5    \\
		$^7$Li enrichment, \%        				& 99.995   \\
		Fuel temperature, K 							& 900  \\
		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
		Fuel dilatation coefficient, g/(cm$^3$ $.$K)  &  -6.7$\times$10$^{-4}$ \\
		Graphite density, g/cm$^3$             	    & 2.3	\\  
		B$_4$C density, g/cm$^3$					& 2.52  \\
		$^{10}$B enrichment, \%						&  18.4  \\
		Core diameter, cm								& 460  \\
		Core height, cm									& 460  \\
		Side length of the graphite hexagonal prism, cm   & 7.5 \\
		Inner radius, cm							& 3.5  \\
		Outer radius, cm							& 5  \\
		Ratio of molten salt and graphite in the inner zone	&  0.357  \\
		Ratio of molten salt and graphite in the outer zone &  1.162  \\
		Fuel volume, m$^3$  &	52.9 \\
		\hline
	\end{tabularx}
	\label{tab:table1}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{figure}[t!] % replace 't' with 'b' to \centering
%	\hspace{+0.65in}
%	\includegraphics[width=\textwidth]{core.png}
%	\caption{Plan view of SD-TMSR core.}
%	\label{fig:core}
%\end{figure}

\subsection{Fuel composition}
The general composition of the liquid fuel salt in this work is 70LiF - 17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (i.e. thorium + different fissile materials).
As previously mentioned, the aim of this paper is to simulate the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U. Therefore, five different types of initial fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF are investigated as follows:\\
	(1)low-enriched uranium (LEU) (19.79\%);\\
	(2)Pu mixed with LEU (19.79\%);\\
	(3)Pu reactor-grade \cite{marka1993explosive};\\
	(4)transuranic (TRU) elements from LWR SF \cite{de2000scenarios};\\
	(5)and $^{233}$U for comparison purpose.\\

The reactor-grade plutonium and \gls{TRU} vector (\%) are summarized in Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.

\begin{table}  %[!ht]
	\caption{Reactor-grade plutonium vector \cite{marka1993explosive}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s}
		\hline
		$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu \\
		\hline
		 1.3&60.3&24.3&9.1&5 \\
		\hline
	\end{tabularx}
	\label{tab:table2}
\end{table}

\begin{table}  %[!ht]
	\caption{\gls{TRU} vector (\%) \cite{de2000scenarios}}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s s s s s}
		\hline
		$^{237}$Np&$^{238}$Pu & $^{239}$Pu & $^{240}$Pu & $^{241}$Pu & $^{242}$Pu&$^{241}$Am &$^{243}$Am&$^{244}$Cm &$^{245}$Cm\\
		\hline
		6.3&2.7&45.9&21.5&10.7&6.7&3.4&1.9&0.8&0.1 \\
		\hline
	\end{tabularx}
	\label{tab:table3}
\end{table}

The isotopic compositions of plutonium recovered from the spent fuel composition of commercial LEU \gls{PWR} that has released $33$ $GWd/t$ fission energy and has been cooled for $10$ $years$ before reprocessing \cite{oecd1989probabilistic,marka1993explosive}. As well, the isotopic compositions of \gls{TRU} have been taken from the SF of UOX \gls{PWR} (after one use and without multi-recycling) with $60$ $GWd/t$ burnup, and after $5$ $years$ cooling \cite{de2000scenarios}. 
The molar composition of startup fuel for all five cases is listed in Table~\ref{tab:table4}. Meanwhile, the corresponding initial nuclei inventories with different types of fuel are tabulated in Table~\ref{tab:table5}.

\begin{table}  %[!ht]
	\caption{Composition of startup fuel mole\%}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s}
		\hline
		Molecule& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79 wt-\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		LiF&70&70&70&70&70\\
		BeF$_2$&17.5&17.5&17.5&17.5&17.5\\
		ThF$_4$&8.25&7.5&10.75&	8.65&12.3		\\
		UF$_4$&4.25&4.75&&&	0.2		\\
		PuF$_3$&&0.25&1.75&&		\\
		TRUF$_3$&&&	&3.85	&\\
		\hline
	\end{tabularx}
	\label{tab:table4}
\end{table}

\begin{table}  %[!ht]
	\caption{Initial nuclei inventories (in grams) of the SD-TMSR with different types of fuel.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s}
		\hline
		\vspace{0.1in}
		Molecule& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		$^{232}$Th       &6.24E+07 & 4.67E+07 &   6.75E+07			& 5.44E+07	& 7.69E+07    \\ 
		$^{233}$U        &         & &        &       &  1.30E+06 \\
		$^{235}$U        & 3.17E+06 &6.01E+06	&            &   & \\
		$^{238}$U      	 &1.28E+07  &2.43E+07 &	&  &\\
		$^{237}$Np	  	 &         && &1.58E+06	&    \\
		$^{238}$Pu	  	 &         &1.60E+04	& 1.13E+05 & 6.78E+05	&   \\
		$^{239}$Pu       &         &9.59E+05&6.76E+06& 1.15E+07&    \\
		$^{240}$Pu       &         &3.99E+05& 2.82E+06&5.40E+06&  	\\  
		$^{241}$Pu		 &         &1.60E+05&1.13E+06&2.69E+06&   \\
		$^{242}$Pu		 &         &6.39E+04	&4.51E+05	& 1.68E+06& \\
		$^{241}$Am		 &         &&& 8.53E+05 & \\
		$^{242}$Am		 &         &&&  &\\
		$^{243}$Am       &        & &&4.77E+05&\\
		$^{244}$Cm		 &        & &&2.01E+05&  \\
		$^{245}$Cm		 &        & &&			2.51E+04	&   \\
		&         &&		&		&\\
		Total mass \\of HM without $^{232}$Th	& 1.60E+07& 3.20E+07&1.13E+07&  2.51E+07&   1.30E+06  \\
		\hline
	\end{tabularx}
\label{tab:table5}
\end{table}

\section{Methodology and tools}

Simulation of Liquid-fueled Molten Salt Reactor (MSR) systems requires computational software that must support online fuel salt reprocessing and refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 beta\footnote{SERPENT-2 is a \gls{3D} continuous energy Monte Carlo neutron transport and burn-up code.} \cite{leppanen2014serpent} is used to simulate the full-core of the SD-TMSR with different types of initial fuel. The extension of SERPENT code accounts for continuous online reprocessing and refueling \cite{aufiero2013extended}. Meanwhile, ENDF-VII.0 cross-section library is adopted for all calculations. The results demonstrate full-core runs of 12.5E+06 neutron history per depletion step. The full burnup time of the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ $36$ $pcm$. The online extraction of \gls{FPs} and noble gases  provides many benefits for MSRs. For example, it would reduce the fissile inventory required to achieve criticality and improve the breeding ratio.
Figure~\ref{fig:flow} shows a flow chart of the calculation steps.

\begin{figure}[t!] % replace 't' with 'b' to \centering
	\includegraphics[width=\textwidth]{flowch.png}
	\caption{Flow chart of the calculation procedures.}
	\label{fig:flow}
\end{figure}

As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced matrix exponential solution based on the Chebyshev Rational Approximation Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. Then, the system extracted gaseous \gls{FPs} and other materials (non-dissolved metals, lanthanides, and soluble metals except Pu) in a proper time\footnote{The extraction time depends on the type of material and its impact on the neutron economy, for instance, the extraction time of the gaseous \gls{FPs} is 30 seconds and for lanthanides and other soluble metals is $\approx$10.59 days in this work.}. This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the gas-tank\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}. Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, pa-tank\footnote{An imaginary tank used to store protactinium extracted from the core.}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel and the residual $^{233}$U is the net production of $^{233}$U. SERPENT-2 subroutine allows changes the flow rates of the isotopes during reactor operation \cite{aufiero2013extended}. The mass of the fissile and fertile materials needed to achieve criticality is calculated at the end of the cycle (i.e. 1 year). Then, this mass is added to the core at the beginning of the cycle by a certain flow rate.

\section{Feed and extraction rates}
In the present work, two different feed mechanisms are used. The first mechanism allows continuous feed flow of thorium and $^{233}$U from Pa-decay tank. In contrast, the second mechanism adopts continuous feed flow of $^{233}$U from Pa-decay tank and the same composition of the initial fuel except for thorium. \\
The fission products act as poisons in the MSRs; they negatively impacting the reactivity. Therefore, \gls{FPs} must be extracted during reactor operation. Consider $T_{r}$ as the time during which the total fuel salt is reprocessed and $dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that the \gls{MSR} extracts during time $dt$; thus \cite{nuttin2005potential}

\begin{equation}
\label{Equ:1}
\dfrac{dN_{e}}{dt} = N_{e}\dfrac{\varepsilon_{e}}{T_{r}},	
\end{equation}

where $\varepsilon_{e}$ is the removal efficiency. Equation \ref{Equ:1} gives the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material is removed), where $\lambda_{e}=\varepsilon_{e}/T_{r}$. The removal constant $\lambda_{e}$ of gaseous and other fission products is precisely calculated and summarized in Table~\ref{tab:table6}.
The effective reprocessing time for the gaseous \gls{FPs} and non-dissolved metals was set to 30 seconds (removal constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be extract promptly and continuously via He bubbling system. In contrast, extracting the soluble \gls{FPs}, lanthanides, and protactinium can be done by the chemical reprocessing (i.e. fluorination and reduction reaction). Therefore, the system reprocesses a specific amount of fuel salt daily. In the present work, the effective extraction time for soluble \gls{FPs} is $\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is equivalent to 5 m$^3$/d of chemical reprocessing rate \cite{nuttin2005potential,li_optimization_2018}. The effective feed rates of the heavy metals (HM) are changed during reactor operation to conserve the total fuel mass and criticality.

\begin{table}[ht!]
	\centering
	\caption{The reprocessing table.} 
	\vspace{1ex}
	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4.5cm}|s|p{2cm}|}
		\hline
		\textbf{Reprocessing group}  & \textbf{Element} & \textbf{Reproc- essing time} & \textbf{Removal constant} $\lambda_{e}$ $[s^{-1}]$ \\
		\hline
		Gaseous \gls{FPs} and non-dissolved metals  &  Atomic number (Z) = 1, 2, 7, 8,10, 18, 36, 41, 42, 43, 44, 45, 46, 47, 51, 52, 54, 71, 72, 73, 74, 75, 76,77, 78, 79 and 86.			&	30s	&  -3.333E-02 \\
		\hline
		Lanthanides and other soluble \gls{FPs}     & Atomic number (Z) = 30, 31,32, 33, 34, 35, 37, 38, 39, 40, 48, 49, 50, 53, 55, 56, 57, 58, 59, 60, 61,62, 63, 64, 65, 66, 67, 68, 69 and 70. & 10.599 d (5 m$^3$/d) &  -1.092E-06 \\
		\hline
		Protactinium   & Pa  &  10.599 d (5 m$^3$/d)  &  -1.092E-06 \\
		\hline
	\end{tabularx}
	\label{tab:table6}
\end{table}

%\begin{table}[ht!]
%	\centering
%	\caption{The refueling table.} 
%	\vspace{1ex}
%	\begin{tabularx}{\textwidth}{|p{1.5cm}|b|p{1.9cm}|}
%		\hline
%		\textbf{Nuclide} & \textbf{Feed rate} & \textbf{Feed constant$^{\star}$} $\lambda_{e}$ $[s^{-1}]$ \\
%		\hline
%		$^{232}$Th        &  1.842 [Kg/day], first 90 [d] & 1.500E-09 \\
%		&  2.511 [Kg/day], from 90 to 1550 [d] & 		2.045E-09 \\
%		&  2.456 [Kg/day], from 1550 to 3010 [d] & 		2.000E-09 \\
%		&  2.321 [Kg/day], from 3010 to 5930 [d]& 		1.890E-09	\\
%		&  2.241 [Kg/day], from 5930 to 7390 [d] &		1.825E-09	\\
%		&  2.186 [Kg/day], from 7390 to 12500 [d] &		1.780E-09	\\
%		&  2.118 [Kg/day], from 12500 to 15420 [d] &	1.725E-09	\\
%		&  2.136 [Kg/day], from 15420 to 18340 [d]&		1.740E-09		\\
%		&  2.063 [Kg/day], from 18340 to 21900 [d]&		1.680E-09	 \\ 
%		\hline
%		$^{233}$U & 2.619 [Kg/day], first 90 [d]	&   6.400E-09  \\
%		& 2.009 [Kg/day],  form 90 to 1550 [d] &	4.910E-09 \\
%		& 1.944 [Kg/day], from 1550 to 3010 [d] &	4.750E-09 \\
%		& 1.826 [Kg/day],  from 3010 to 5930 [d] &	4.460E-09 \\
%		& 1.811 [Kg/day],  from 5930 to 7390[d] &	4.425E-09 \\
%		& 1.744 [Kg/day], from 7390 to 12500 [d] &	4.260E-09 \\
%		& 1.699 [Kg/day], from 12500 to 18340 [d]	& 4.150E-09 \\
%		& 1.657 [Kg/day], from 18340 to 21900 [d]	& 4.050E-09 \\
%		\hline
%	\end{tabularx}
%	\begin{tablenotes}
%		\small
%		\item  $^{\star}$ Feed constant is the mass fraction of fissile nuclide ($^{232}$Th or $^{233}$U) transferred from the external storage to the core per second.
%	\end{tablenotes}
%	\label{tab:table3}
%\end{table}

### 2019-09-11 paper/results.tex
add paper and Scenarios folders

\section{Results and discussion}

\subsection{Thorium feed mechanism}

The first mechanism adopts continuous feed flow of external thorium and $^{233}$U from Pa-decay tank. Hereinafter the first mechanism will be mentioned as the thorium feed mechanism. The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. Besides, the initial fissile material fraction was increased for the five fuel salt compositions until the SD-TMS reactor was sufficiently critical at the Beginning Of Life (BOL). 
Figure~\ref{fig:keff1} illustrates the change of the effective multiplication with \gls{EFPY} for the thorium feed mechanism.
As shown in Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) decreases sharply during the first 25 years of reactor operation for the first four cases. $k_{eff}$ decreases as a result of depletion of the initial fissile materials and generation of the neutron poisons (FPs). Thus, the reactor becomes subcritical within a relatively short time ($\approx$ $4$ $years$ in the \gls{TRU} case and $\approx$ $12$ $years$ in the Pu reactor-grade case). The amount of $^{233}$U generated in the \gls{SD-TMSR} is not enough to conserve the reactor criticality and overcome the neutron absorption in the initial fertile isotopes.
Nevertheless, the continuous feed flow of thorium and $^{233}$U helps to operate the \gls{SD-TMSR} for a long period of time (the U-233 case). Besides, the initial molar fraction of LEU and Pu reactor-grade was increased more (Figure~\ref{fig:keff1}) to counteract the absorption of neutrons in the non-fissile heavy metals added with the initial fuel salt. But $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff1.png}
	\caption{The change of the effective multiplication factor during 60 \gls{EFPY} of reactor operation for thorium feed mechanism (confidence interval $\pm\sigma$ is shaded).} 
	\label{fig:keff1}
\end{figure}

\subsection{Non-thorium feed mechanism}

The second mechanism allows continuous feed flow of $^{233}$U only from Pa-decay tank and the same composition of the initial fuel except for thorium. Hereinafter the second mechanism will be mentioned as the non-thorium feed mechanism. Figure~\ref{fig:keff2} shows the change of the effective multiplication during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism.
As shown in Figure~\ref{fig:keff2}, the SD-TMS reactor was sufficiently critical at the Beginning Of Life (BOL). Both Pu reactor-grade and TRU case show good results relative to the other two cases (i.e. LEU and Pu+LEU). For the Pu reactor-grade fuel salt, the amount of $^{233}$U generated in the \gls{SD-TMSR} in addition to the external feed flow of Pu are sufficient to maintain the reactor criticality and overcome the neutron absorption in the initial non-fissile isotopes. This may be attributed to the fact that the spectrum in the Pu reactor-grade initial core is hardened that is more thorium is being converted to $^{233}$U. For the \gls{TRU} fuel salt, the amount of $^{233}$U and the external feed flow of TRU is barely enough to operate the reactor for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U. Nevertheless, $k_{eff}$ decreases with the burnup time because the minor actinides accumulating in the core as a result of continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU fuel are less attractive for non-thorium feed mechanism. The continuous LEU feed increases the amount of fertile $^{238}$U and consequently, reduces the feasibility of such fissile materials. The continuous feed of $^{233}$U without $^{232}$Th will lead to supercritical reactor, thus the $^{233}$U case is excluded from non-thorium feed mechanism.\\
According to the $k_{eff}$ results, Pu reactor-grade and TRU fissile materials are selected and discussed in the following. 
\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{keff2.png}
	\caption{The change of the effective multiplication factor during 60 \gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence interval $\pm\sigma$ is shaded).} 
	\label{fig:keff2}
\end{figure}

\subsection{Pu reactor-grade, TRU, and $^{233}$U initial fuel}

In this section, the simulation of the SD-TMSR with Pu reactor-grade and TRU fissile materials is discussed. Besides, the $^{233}$U case is listed for comparison.\\
Figure~\ref{fig:refillCCC} demonstrates the dynamics of heavy metal refill rate during 60 \gls{EFPY} of SD-TMSR operation. The heavy metal refill rate was adjusted to maintain; the reactor criticality and total fuel mass almost constant (less than $0.1\%$) during the reactor operation. In $^{233}$U case, the mean values of $^{233}$U and $^{232}$Th refill rate are $1.77$ and $2.21$ $kg/d$, respectively. As well, in the Pu reactor-grade case, the mean values of $^{233}$U and Pu refill rate are $0.75$ and $2.75$ $kg/d$, respectively. In the TRU case, the mean values of $^{233}$U and TRU refill rate are $0.90$ and $2.0$ $kg/d$, respectively.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{refillCCC.png}
	\caption{Dynamics of heavy metal refill rate during 60 \gls{EFPY} of reactor operation. Solid lines for $^{233}$U case, dashed lines for Pu reactor-grade case, and dotted lines for TRU case.}
	\label{fig:refillCCC}
\end{figure}

Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC} describe the evolution of important isotopes for $^{233}$U, Pu and TRU cases respectively.
From Figure~\ref{fig:inventoryCCCC}, The mass of Pa in the fuel salt is almost constant and reaches $17.8$ $kg$ at the end of the operation time. In addition, the mass of Minor Actinides\footnote{In the present work, the Minor Actinides (MA) include Np, Am and Cm.} (MA) increases with time; however, by applying online reprocessing, its value remains relatively low. As well, the total mass of Pu increases with burnup time. The level of Pu in the fuel correlates with the mass of the MA, and Pu. MA need more time to reach equilibrium. The total mass of U increases with burnup time and reaches equilibrium after $\approx$ $27$ $years$. As shown in Figure~\ref{fig:inventoryCCCC}, refueling the core with Th helps maintain an almost constant inventory throughout the full operation time.\\
The Pa extraction time was adjusted to be 30 seconds for Pu and TRU cases to avoid poisoning the core. Therefore, Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel for Pu and TRU cases is relatively low when compared to the $^{233}$U case.
Major isotopes for the three cases reaches the equilibrium state after $\approx$ $30$ $years$ (see Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC}).

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryCCCC.png}
	\caption{Evolution of the important nuclides inventories for $^{233}$U case ($^{\star}$MA involves Np, Am, Cm).}
	\label{fig:inventoryCCCC}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{inventoryPu_TRUCCC.png}
	\caption{Evolution of the important nuclides inventories for Pu reactor-grade case (solid lines) and for TRU case (dashed lines).}
	\label{fig:inventoryPu_TRUCCC}
\end{figure}

Figure~\ref{fig:Th232CC} illustrates the variation of thorium mass in the fuel salt for $^{233}$U, Pu reactor-grade and TRU cases, respectively. In $^{233}$U case, we apply the thorium feed mechanism, thus thorium mass decreases by only $3.2$ $\%$ at the end of operation time (60 years). In contrast, thorium mass decreases significantly in Pu and TRU cases according to the non-thorium feed mechanism. Thorium mass decreases by $39.2$ $\%$ and $37.96$ $\%$ in Pu reactor-grade and TRU cases, respectively. The maximum decreasing in thorium mass refer to the effective utilization of thorium fuel cycle. Consequently, the Pu reactor-grade initial fuel may help to utilize thorium fuel cycle more effective.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{Th232CC.png}
	\caption{The variation of thorium mass in the fuel salt for $^{233}$U, Pu reactor-grade and TRU cases, respectively.}
	\label{fig:Th232CC}
\end{figure}

Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for $^{233}$U, Pu reactor-grade and TRU cases, respectively. One can see that the mass of the $^{233}$U reaches the equilibrium state after $\approx$ $30$ $years$. Meanwhile, the amount of $^{233}$U is sufficient to maintain criticality in the three cases.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{U233CC.png}
	\caption{Mass of $^{233}$U in the fuel salt for $^{233}$U, Pu reactor-grade and TRU case, respectively.}
	\label{fig:U233CC}
\end{figure}

In the non-thorium feed mechanism, the SD-TMSR is continuously refueled for criticality, which increases the Pu proportion in the molten salt. According to the literature, the limit of Pu solubility in the FLiBe salt is $\approx$ $4.0$ $\%$ \cite{ignatiev2012progress,sood1975plutonium}. Figure~\ref{fig:PusolubilityCC} represents the Pu proportion in the fuel salt (mole\%). In $^{233}$U and Pu reactor-grade cases, the Pu proportion increases slightly but still below its solubility limit. On the other hand, the Pu proportion in the molten salt loaded by TRU increases with operation time and exceeds the Pu solubility limit.
This issue may be solved by increasing the reactor operation temperature and or reducing the HM initial inventory \cite{zou2018transition}.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{PusolubilityCC.png}
	\caption{The Pu proportion in the fuel salt (mole\%).}
	\label{fig:PusolubilityCC}
\end{figure}

Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U as a function of burnup time. In TRU case, the net production of $^{233}$U is almost zero, nevertheless, the reactor becomes subcritical after 40 years of operation. In $^{233}$U and Pu reactor-grade cases, the net production of $^{233}$U increases with burnup time and reaches about $1.77$ $t$ and $10$ $t$, respectively at the end of operation lifetime. It worth noting that thorium feed mechanism is applied in $^{233}$U case, while, non-thorium feed mechanism is adopted in Pu reactor-grade cases.
As shown in Figure~\ref{fig:NetCC}, after 26 years the net production of $^{233}$U reaches $1.3$ $t$; this is sufficient to start-up another \gls{SD-TMSR}. Similarly, one can see that the same amount of $^{233}$U (i.e. $1.3$ $t$) can be achieved after $\approx$ $4.5$ $years$ if we applied the non-thorium feed mechanism on the SD-TMSR that initially loaded by Pu reactor-grade alternative to $^{233}$U. In addition, Figure~\ref{fig:NetCC} also shows that the net production of $^{233}$U during the first 455 days is negative, thus about $175.28$ $kg$ of $^{233}$U must be added during this period. In conclusion, the thorium fuel cycle transition can be achieved by selecting the proper feed mechanism and initial fissile material.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{NetCC.png}
	\caption{Net production of $^{233}$U during burn-up period (60 \gls{EFPY}).}
	\label{fig:NetCC}
\end{figure}

\subsection{Neutron spectrum}

Figure~\ref{fig:spectrumFLUX110vC} represents the normalized neutron flux spectrum for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 MeV for the $^{233}$U, Pu reactor-grade, and TRU started case. In $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due to the accumulation of the Pu and other strong thermal neutron absorbers in the fuel salt. In Pu reactor-grade and TRU cases and during the reactor operation, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope, the neutron spectrum softens and becomes similar to a thermal spectrum of the TMSR.

\begin{figure}
 	\centering
 	\includegraphics[width=\textwidth]{spectrumFLUX110vC.png}
 	\caption{The neutron flux energy spectrum at different BOL (solid lines) and EOL (dashed lines).}
 	\label{fig:spectrumFLUX110vC}
\end{figure}

The comparison of the two feed mechanisms based on five different types of initial fuel is listed in Table~\ref{tab:table7}.

\begin{table} % [!ht]
	\centering
	\caption{Comparison of the two feed mechanisms based on five different types of initial fuel.}
	\vspace{0.1in}
	\begin{tabularx}{\textwidth}{s s s s s s }  %{\textwidth}
		\hline
		\backslashbox{Feed mechanism}{Initial fuel}& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79 wt-\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
		\hline
		Thorium feed mechanism&Not work&Not work&Not work&Not work& Work\\
		Non-thorium feed mechanism &Not work&Not work&Work well with positive net production of $^{233}$U &Work for 40 years with net production of $^{233}$U = zero & Not examine (supercritical reactor)\\
		\hline
	\end{tabularx}
	\label{tab:table7}
\end{table}

### 2019-09-11 Scenarios/Pu-with non-thorium feed mechanism/TMSRPu_det0.m

@@ -1,0 +1,2007 @@
+
+DET1 = [
+    1    1    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    2    2    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    3    3    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    4    4    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    5    5    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    6    6    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    7    7    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    8    8    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    9    9    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   10   10    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   11   11    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   12   12    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   13   13    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   14   14    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   15   15    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   16   16    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   17   17    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   18   18    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   19   19    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   20   20    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   21   21    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   22   22    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   23   23    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   24   24    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   25   25    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   26   26    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
[…]

### 2019-09-11 Scenarios/Pu-with non-thorium feed mechanism/TMSRPu_det60.m

@@ -1,0 +1,2007 @@
+
+DET1 = [
+    1    1    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    2    2    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    3    3    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    4    4    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    5    5    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    6    6    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    7    7    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    8    8    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    9    9    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   10   10    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   11   11    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   12   12    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   13   13    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   14   14    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   15   15    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   16   16    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   17   17    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   18   18    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   19   19    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   20   20    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   21   21    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   22   22    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   23   23    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   24   24    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   25   25    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   26   26    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
[…]

### 2019-09-11 Scenarios/TRU-with non-thorium feed mechanism/TMSRTRU_det0.m

@@ -1,0 +1,2007 @@
+
+DET1 = [
+    1    1    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    2    2    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    3    3    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    4    4    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    5    5    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    6    6    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    7    7    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    8    8    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    9    9    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   10   10    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   11   11    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   12   12    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   13   13    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   14   14    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   15   15    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   16   16    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   17   17    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   18   18    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   19   19    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   20   20    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   21   21    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   22   22    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   23   23    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   24   24    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   25   25    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   26   26    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
[…]

### 2019-09-11 Scenarios/TRU-with non-thorium feed mechanism/TMSRTRU_det60.m

@@ -1,0 +1,2007 @@
+
+DET1 = [
+    1    1    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    2    2    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    3    3    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    4    4    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    5    5    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    6    6    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    7    7    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    8    8    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    9    9    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   10   10    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   11   11    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   12   12    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   13   13    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   14   14    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   15   15    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   16   16    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   17   17    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   18   18    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   19   19    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   20   20    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   21   21    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   22   22    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   23   23    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   24   24    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   25   25    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   26   26    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
[…]

### 2019-09-11 Scenarios/U233-with thorium feed mechanism/TMSR_det0.m

@@ -1,0 +1,1007 @@
+
+DET1 = [
+    1    1    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    2    2    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    3    3    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    4    4    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    5    5    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    6    6    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    7    7    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    8    8    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    9    9    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   10   10    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   11   11    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   12   12    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   13   13    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   14   14    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   15   15    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   16   16    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   17   17    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   18   18    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   19   19    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   20   20    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   21   21    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   22   22    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   23   23    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   24   24    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   25   25    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   26   26    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
[…]

### 2019-09-11 Scenarios/U233-with thorium feed mechanism/TMSR_det60.m

@@ -1,0 +1,1007 @@
+
+DET1 = [
+    1    1    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    2    2    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    3    3    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    4    4    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    5    5    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    6    6    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    7    7    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    8    8    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+    9    9    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   10   10    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   11   11    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   12   12    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   13   13    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   14   14    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   15   15    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   16   16    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   17   17    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   18   18    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   19   19    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   20   20    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   21   21    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   22   22    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   23   23    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   24   24    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   25   25    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
+   26   26    1    1    1    1    1    1    1    1  0.00000E+00 0.00000 
[…]

### 2019-09-27 paper/conclusion.tex
Revised based on reviewer's comments

--- 2019-09-10 conclusion.tex
@@
 In the present paper, five different types of initial fissile materials have been studied for transitioning to thorium fuel cycle in the \gls{SD-TMSR}.
-The molar composition of startup fuel for all five cases is listed in Table~\ref{tab:table4}, as well, the inventories in Table~\ref{tab:table5}.
+The molar composition of start-up fuel for all five cases is listed in Table~\ref{tab:table4}, as well, the inventories in Table~\ref{tab:table5}.
 We adopted two different feed mechanisms; thorium feed mechanism and non-thorium feed mechanism.
 The whole-core of the SD-TMSR was simulated with Pu reactor-grade, TRU, and $^{233}$U as initial fissile materials.
-Besides, the variation of the effective multiplication factor $k_{eff}$, inventory, and other neutronic parameters have been investigated.
-Results demonstrated that continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U startup fuel.
+Additionally, the variation of the effective multiplication factor $k_{eff}$, inventory, and other neutronic parameters have been investigated.
+Results demonstrated that continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U start-up fuel.
 Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U.
 in addition, the Pu proportion in fuel salt has been calculated and found to be below the solubility limit.
-Finally, the neutron flux spectrum for the three selected cases has been described.
+Finally, the neutron spectrum shift during the reactor operation for the three selected cases has been calculated.
 

### 2019-09-27 paper/introduction.tex
Revised based on reviewer's comments

--- 2019-09-10 introduction.tex
@@
 The \gls{GIF} has defined eight technology goals for the next generation nuclear systems.
-These goals are; safety and reliability, economics, sustainability, and non-proliferation and physical protection \cite{doe2002technology}.
+These goals are; safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}.
 \glspl{MSR} have many advantages that consistent with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online reprocessing and refueling, excellent neutron economy and operation under ambient pressure \cite{siemer2015molten,rosenthal1970molten}.
@@
 Zou, et al.
-introduced two ways for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition.
+introduced two approaches for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition.
 In the former way, the TMSR is launched with existing fissile material and thorium as a fertile material, then the bred $^{233}$U from thorium is rerouted into the core for criticality.
@@
 Nevertheless, starting the \gls{SD-TMSR} with other fissile materials (except $^{233}$U) not found in the literature.
-Therefore, the present paper discusses the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition.
+Therefore, the main object of the present paper is to discuss the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition.
 To do that, we investigate five types of initial fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF \cite{de2000scenarios}.
-Moreover, two different feed mechanisms are used: \\
-(1)Th + $^{233}$U from Pa-decay tank (i.e. removal mass rate (Pa-233) = feed mass rate ($^{233}$U)) \cite{betzler2016modeling}.\\
-(2)continuous feed flow of (HM except for Th) + some or all $^{233}$U from Pa-decay tank.\\
-This present paper is organized as follows: after an introduction on \gls{MSR} systems, the model description is discussed in section 2.
+Moreover, two different feed mechanisms are used as follows:
+\begin{itemize}
+	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
+	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.
+\end{itemize}
+This present paper is organized as follows: after an introduction about \gls{MSR} systems, the model description is discussed in section 2.
 Methodology and tools is descried in section 3.

### 2019-09-27 paper/methods.tex
Revised based on reviewer's comments

@@
 The active zone is a right cylinder with height and diameter equal to 460 cm.
-Assemblies of graphite\footnote{Density of graphite 2.3 g/cm$^3$.} hexagonal prisms fill the core.
+Assemblies of graphite\footnote{We choose graphite density of $2.3$ g/cm$^3$, to validate our results against results in the literature \cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the core.
 The side length of the graphite hexagonal prism was optimized in \cite{li_optimization_2018} and found to be 7.5 cm.
@@
 \begin{figure} % replace 't' with 'b' to \centering [hbp!]
-	\includegraphics[width=\textwidth]{ff.jpg}
-	\caption{The quarter-core model configuration of the SD-TMSR a) Longitudinal view b) cross-sectional view at the horizontal midplane.}
+	\includegraphics[width=\textwidth]{ff.png}
+	\caption{The quarter-core model configuration of the SD-TMSR a) Longitudinal view b) Cross-sectional view at the horizontal midplane.}
 	\label{fig:ff}
@@
 Meanwhile, ENDF-VII.0 cross-section library is adopted for all calculations.
-The results demonstrate full-core runs of 12.5E+06 neutron history per depletion step.
+The results demonstrate full-core runs of $12.5E+06$ neutron history per depletion step.
 The full burnup time of the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ $36$ $pcm$.
@@
 As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced matrix exponential solution based on the Chebyshev Rational Approximation Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation.
-Then, the system extracted gaseous \gls{FPs} and other materials (non-dissolved metals, lanthanides, and soluble metals except Pu) in a proper time\footnote{The extraction time depends on the type of material and its impact on the neutron economy, for instance, the extraction time of the gaseous \gls{FPs} is 30 seconds and for lanthanides and other soluble metals is $\approx$10.59 days in this work.}.
-This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the gas-tank\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}.
-Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, pa-tank\footnote{An imaginary tank used to store protactinium extracted from the core.}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}.
+Then, the system extracted gaseous \gls{FPs} and other materials (non-dissolved metals, lanthanides, and soluble metals except Pu) in a proper time.
+This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the \texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}.
+Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, \texttt{pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}.
 The produced $^{233}$U is used as a fresh fissile fuel and the residual $^{233}$U is the net production of $^{233}$U.
-SERPENT-2 subroutine allows changes the flow rates of the isotopes during reactor operation \cite{aufiero2013extended}.
-The mass of the fissile and fertile materials needed to achieve criticality is calculated at the end of the cycle (i.e.
-1 year).
+The MSR burnup routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the isotopes during reactor operation \cite{aufiero2013extended}.
+The mass of the fissile and fertile materials needed to achieve criticality is calculated at the end of the cycle.
 Then, this mass is added to the core at the beginning of the cycle by a certain flow rate.
@@
 In the present work, two different feed mechanisms are used.
-The first mechanism allows continuous feed flow of thorium and $^{233}$U from Pa-decay tank.
-In contrast, the second mechanism adopts continuous feed flow of $^{233}$U from Pa-decay tank and the same composition of the initial fuel except for thorium.
-\\
+The first mechanism allows continuous feed flow of thorium and $^{233}$U from \texttt{pa-decay tank}.
+In contrast, the second mechanism adopts continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.\\
 The fission products act as poisons in the MSRs; they negatively impacting the reactivity.
@@
 			\hline
-		Gaseous \gls{FPs} and non-dissolved metals  &  Atomic number (Z) = 1, 2, 7, 8,10, 18, 36, 41, 42, 43, 44, 45, 46, 47, 51, 52, 54, 71, 72, 73, 74, 75, 76,77, 78, 79 and 86.			&	30s	&  -3.333E-02 \\
+			Gaseous \gls{FPs} and non-dissolved metals  &  H, He, N, O, Ne, Ar, Kr, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te, Xe, Lu, Hf, Ta, W, Re, Os, Ir, Pt, Au and Rn.		&	30s	&  -3.333E-02 \\
 			\hline
-		Lanthanides and other soluble \gls{FPs}     & Atomic number (Z) = 30, 31,32, 33, 34, 35, 37, 38, 39, 40, 48, 49, 50, 53, 55, 56, 57, 58, 59, 60, 61,62, 63, 64, 65, 66, 67, 68, 69 and 70.
-& 10.599 d (5 m$^3$/d) &  -1.092E-06 \\
+			Lanthanides and other soluble \gls{FPs}     & 
+			Zn, Ga, Ge, As, Se, Br, Rb, Sr, Y, Zr, Cd, In, Sn, I, Cs, Ba, La, Ce, Pr, Nd, Pm, Sm, Eu, Gd, Tb, Dy, Ho, Er, Tm and Yb. & 10.599 d (5 m$^3$/d) &  -1.092E-06 \\
 			\hline

### 2019-09-27 paper/results.tex
Revised based on reviewer's comments

@@
 
-The first mechanism adopts continuous feed flow of external thorium and $^{233}$U from Pa-decay tank.
+The first mechanism adopts continuous feed flow of external thorium and $^{233}$U from \texttt{Pa-decay tank}.
 Hereinafter the first mechanism will be mentioned as the thorium feed mechanism.
@@
 Nevertheless, the continuous feed flow of thorium and $^{233}$U helps to operate the \gls{SD-TMSR} for a long period of time (the U-233 case).
-Besides, the initial molar fraction of LEU and Pu reactor-grade was increased more (Figure~\ref{fig:keff1}) to counteract the absorption of neutrons in the non-fissile heavy metals added with the initial fuel salt.
+Additionally, the initial molar fraction in the LEU and Pu reactor-grade cases was increased more (see Figure~\ref{fig:keff1}) to counteract the absorption of neutrons in the non-fissile heavy metals added with the initial fuel salt.
 But $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.
@@
 
-The second mechanism allows continuous feed flow of $^{233}$U only from Pa-decay tank and the same composition of the initial fuel except for thorium.
+The second mechanism allows continuous feed flow of $^{233}$U from \texttt{Pa-decay tank} and Heavy Metal except for Th.
 Hereinafter the second mechanism will be mentioned as the non-thorium feed mechanism.
@@
 As shown in Figure~\ref{fig:keff2}, the SD-TMS reactor was sufficiently critical at the Beginning Of Life (BOL).
-Both Pu reactor-grade and TRU case show good results relative to the other two cases (i.e.
+Both Pu reactor-grade and TRU case show promising results relative to the other two cases (i.e.
 LEU and Pu+LEU).
@@
 For the \gls{TRU} fuel salt, the amount of $^{233}$U and the external feed flow of TRU is barely enough to operate the reactor for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U.
-Nevertheless, $k_{eff}$ decreases with the burnup time because the minor actinides accumulating in the core as a result of continuous TRU feed.
+Nevertheless, $k_{eff}$ decreases with the burnup because the Minor Actinides\footnote{In the present work, the Minor Actinides (MA) include Np, Am and Cm.} (MA) accumulating in the core as a result of continuous TRU feed.
 As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU fuel are less attractive for non-thorium feed mechanism.
@@
 Figure~\ref{fig:refillCCC} demonstrates the dynamics of heavy metal refill rate during 60 \gls{EFPY} of SD-TMSR operation.
-The heavy metal refill rate was adjusted to maintain; the reactor criticality and total fuel mass almost constant (less than $0.1\%$) during the reactor operation.
+The heavy metal refill rate was adjusted to maintain; the reactor criticality and total fuel mass almost constant\footnote{The variation of the total fuel mass is less than $0.1\%$} during the reactor operation.
 In $^{233}$U case, the mean values of $^{233}$U and $^{232}$Th refill rate are $1.77$ and $2.21$ $kg/d$, respectively.
@@
 Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC} describe the evolution of important isotopes for $^{233}$U, Pu and TRU cases respectively.
-From Figure~\ref{fig:inventoryCCCC}, The mass of Pa in the fuel salt is almost constant and reaches $17.8$ $kg$ at the end of the operation time.
-In addition, the mass of Minor Actinides\footnote{In the present work, the Minor Actinides (MA) include Np, Am and Cm.} (MA) increases with time; however, by applying online reprocessing, its value remains relatively low.
-As well, the total mass of Pu increases with burnup time.
+From Figure~\ref{fig:inventoryCCCC}, the mass of Pa in the fuel salt is almost constant and reaches $17.8$  $kg$ at the end of the operation time.
+In addition, the mass of Minor Actinides (MA) increases with time; however, by applying online reprocessing, its value remains relatively low.
+As well, the total mass of Pu increases with burnup.
 The level of Pu in the fuel correlates with the mass of the MA, and Pu.
 MA need more time to reach equilibrium.
-The total mass of U increases with burnup time and reaches equilibrium after $\approx$ $27$ $years$.
+The total mass of U increases with burnup and reaches equilibrium after $\approx$ $27$ $years$.
 As shown in Figure~\ref{fig:inventoryCCCC}, refueling the core with Th helps maintain an almost constant inventory throughout the full operation time.\\
@@
 	\includegraphics[width=\textwidth]{inventoryCCCC.png}
-	\caption{Evolution of the important nuclides inventories for $^{233}$U case ($^{\star}$MA involves Np, Am, Cm).}
+	\caption{Evolution of the important nuclides inventories for $^{233}$U case (MA involves Np, Am, Cm).}
 	\label{fig:inventoryCCCC}
@@
 Thorium mass decreases by $39.2$ $\%$ and $37.96$ $\%$ in Pu reactor-grade and TRU cases, respectively.
-The maximum decreasing in thorium mass refer to the effective utilization of thorium fuel cycle.
+The more decreasing in thorium mass, the more effective utilization of thorium fuel cycle.
 Consequently, the Pu reactor-grade initial fuel may help to utilize thorium fuel cycle more effective.
@@
 In $^{233}$U and Pu reactor-grade cases, the Pu proportion increases slightly but still below its solubility limit.
-On the other hand, the Pu proportion in the molten salt loaded by TRU increases with operation time and exceeds the Pu solubility limit.
+On the other hand, the Pu proportion in the molten salt loaded by TRU increases with operation time and reaches the Pu solubility limit after $\approx$ $40$ $years$.
 This issue may be solved by increasing the reactor operation temperature and or reducing the HM initial inventory \cite{zou2018transition}.
@@
 
-Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U as a function of burnup time.
-In TRU case, the net production of $^{233}$U is almost zero, nevertheless, the reactor becomes subcritical after 40 years of operation.
-In $^{233}$U and Pu reactor-grade cases, the net production of $^{233}$U increases with burnup time and reaches about $1.77$ $t$ and $10$ $t$, respectively at the end of operation lifetime.
+Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U as a function of burnup.
+In TRU case, the net production of $^{233}$U is almost zero, nevertheless, the reactor becomes subcritical after $40$ $years$ of operation.
+In $^{233}$U and Pu reactor-grade cases, the net production of $^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$, respectively at the end of operation lifetime.
 It worth noting that thorium feed mechanism is applied in $^{233}$U case, while, non-thorium feed mechanism is adopted in Pu reactor-grade cases.
@@
 
-Figure~\ref{fig:spectrumFLUX110vC} represents the normalized neutron flux spectrum for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 MeV for the $^{233}$U, Pu reactor-grade, and TRU started case.
+Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit lethargy for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 MeV for the $^{233}$U, Pu reactor-grade, and TRU started case.
 In $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due to the accumulation of the Pu and other strong thermal neutron absorbers in the fuel salt.
-In Pu reactor-grade and TRU cases and during the reactor operation, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope, the neutron spectrum softens and becomes similar to a thermal spectrum of the TMSR.
+For Pu reactor-grade and TRU cases, during the reactor operation, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope (see Figure~\ref{fig:U233CC}), the neutron spectrum softens and becomes similar to a thermal spectrum of the TMSR.
 
@@
  	\includegraphics[width=\textwidth]{spectrumFLUX110vC.png}
- 	\caption{The neutron flux energy spectrum at different BOL (solid lines) and EOL (dashed lines).}
+ 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for $^{233}$U, Pu reactor-grade, and TRU case.}
  	\label{fig:spectrumFLUX110vC}
@@
 
-The comparison of the two feed mechanisms based on five different types of initial fuel is listed in Table~\ref{tab:table7}.
+The comparison between the two feed mechanisms with different types of initial fuel is listed in Table~\ref{tab:table7}.
 
@@
 	\centering
-	\caption{Comparison of the two feed mechanisms based on five different types of initial fuel.}
+	\caption{Comparison between the two feed mechanisms for the five different types of initial fuel.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{s s s s s s }  %{\textwidth}
+	\begin{tabularx}{\textwidth}{l s s s s s }  %{\textwidth}
 		\hline
-		\backslashbox{Feed mechanism}{Initial fuel}& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79 wt-\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
+		\backslashbox{Feed\\ mechanism}{Initial\\ fuel}& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79 wt-\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
 		\hline
 		Thorium feed mechanism&Not work&Not work&Not work&Not work& Work\\
-		Non-thorium feed mechanism &Not work&Not work&Work well with positive net production of $^{233}$U &Work for 40 years with net production of $^{233}$U = zero & Not examine (supercritical reactor)\\
+		Non-thorium feed mechanism &Not work&Not work&Work well with positive net production of $^{233}$U &Work for $40$ $years$ with net production of $^{233}$U = zero & Not examine (supercritical reactor)\\
 		\hline

### 2019-10-07 paper/results.tex
Flux added, text ofsusbsection added

@@
 \end{table}
+\FloatBarrier
+
+\subsection{Neutron flux}
+Figures~\ref{fig:fast_flux}, \ref{fig:thermal_flux} show the radial 
+distribution of fast (energy range between 0.625 eV and 20 MeV) and thermal 
+(energy range between 10$^{-5}$ eV and 0.625 eV) neutron flux for three 
+different initial fissile materials in the fuel salt ($^{233}$U, reactor-grade 
+plutonium, TRU) at startup and at equilibrium (after $\approx 30$ years of 
+operation). Actinides evolution and poisonous fission products accumulation 
+for various initial fissile compositions demonstrated different effect on the 
+SD-TMSR neutronics performance. For the Th/$^{233}$U, thermal neutron flux is 
+suppressed at the equilibrium state because fissile $^{233}$U in the core is 
+being substituted with heavier fissile actinides: $^{235}$U, $^{239}$Pu, and 
+$^{241}$Pu which is in a good agreement with results the literature 
+\cite{rykhlevskii2019modeling, ashraf2019whole_core}.
+\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
+	\includegraphics[width=\textwidth]{radial_fast_flux_init_vs_eq.png} 
+	\caption{Radial fast neutron flux distribution for 3 different initial 
+		fuel salt compositions at startup and equilibrium (the fast flux 
+		confidence interval $\pm\sigma<2.5$\% for all cases).}
+	\label{fig:fast_flux}
+\end{figure}
+
+Opposite observation has been made for reactor-grade Pu and TRU cases. For 
+these cases, thermal neutron flux is increasing during operation while fast 
+neutron flux is decreasing. The fissile Pu (generates relatively hard 
+spectrum) from initial fuel salt composition is gradually substituted with the 
+$^{233}$U (generates relatively soft spectrum), produced from the fertile 
+$^{232}$Th. During reactor operation, the $^{233}$U becomes primary fissile 
+isotope which leads to the neutron spectrum softening of the reactor. 
+\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
+	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
+	\caption{Radial thermal neutron flux distribution for 3 different initial 
+		fuel salt compositions at startup and equilibrium for initial and 
+		equilibrium fuel salt composition (the thermal flux confidence 
+		interval 
+		$\pm\sigma<1.6$\% for all cases).}
+	\label{fig:thermal_flux}
+\end{figure}
+
+Notably, more changes in thermal neutron flux shape and magnitude for  
+$^{233}$U case were observed in the inner core zone ($R\lesssim150$) than 
+in the outer core zone. In contrast, for Pu reactor-grade and TRU case, large 
+changes were observed for thermal neutron flux in the outer core zone and 
+reflector. Additionally, Figure~\ref{fig:thermal_flux} shows relatively large 
+changes in thermal flux leakage from the core for Pu case. Overall, the 
+SD-TMSR core design was optimized for $^{233}$U fissile isotope 
+\cite{li_optimization_2018}, hence, the core geometry (e.g., fuel channels  
+lattice pitch) must be re-optimized for another type of fuel to obtain better 
+neutronics performance.
+
+\subsection{Temperature coefficient of reactivity}
+To determine 
+the temperature coefficients, the cross-section temperatures for the fuel and 
+moderator were changed from 900 K to 1000 K. This study considered three 
+different cases:
+\begin{enumerate}
+	\item Fuel salt temperature rising from 900 K to 1000 K.
+	\item Graphite temperature rising from 900 K to 1000 K.
+	\item Whole reactor temperature rising from 900 K to 1000 K.
+\end{enumerate}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table} [b!]
+	\caption{Temperature coefficients of reactivity for 3 different initial 
+		fuel salt compositions at startup and equilibrium. Confidence interval 
+		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
+	\begin{tabularx}{\textwidth}{ p{0.255\textwidth} | X X  X X  X X } \hline
+		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
+		& 
+		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
+		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
+		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
+		\space  & Initial & Equil. & Initial & Equil. & Initial & 
+		Equil. \\ \hline
+		Fuel temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ \\ 
+		Fuel density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
+		Total fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ \hline
+		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
+		\\	\hline
+		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
+	\end{tabularx}
+	\label{tab:tcoe}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Six Factor analysis}
+The effective multiplication factor can be expressed using the following 
+formula:
+\begin{align*}
+k_{eff} = k_{inf} P_f  P_t = \eta \epsilon p f P_f P_t
+\end{align*}
+
+Table~\ref{tab:six_factor} summarizes the six factors for both initial and 
+equilibrium 
+fuel salt composition. Using SERPENT-2 built-in online reprocessing 
+capabilities all six 
+factors and their statistical uncertainties have been calculated at the 
+beginning of 
+operation and after 20 years of operation. The fast and thermal non-leakage 
+probabilities 
+and the thermal utilization factor (f)
+remain constant regardless of neutron spectrum hardening during operation. In 
+contrast, the 
+neutron reproduction factor ($\eta$), resonance escape probability ($p$), and 
+fast fission 
+factor ($\epsilon$) differ notably between initial and equilibrium state. The 
+neutron 
+spectrum is soft at the beginning of reactor life (Figure~\ref{fig:spectrum}), 
+but 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table} %[hb!]
+	\caption{Six factors for the SD-TMSR model for 3 different initial 
+		fuel salt compositions at startup and equilibrium.}
+	\begin{tabularx}{\textwidth}{ X | X X | X X | X X } \hline
+		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
+		material} \\ 
+		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
+		\multicolumn{2}{c}{TRU} \\
+		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
+		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.57 & 1.31 \\ 
+		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
+	    p       & 0.54 & 0.43 & 0.26 & 1.60 & 0.17 & 0.15 \\
+		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
+		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
+        P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
+	\end{tabularx}
+	\label{tab:six_factor}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+neutron 
+spectrum hardening causes the fast fission factor to grow throughout the 
+core's lifetime. Conversely, 
+the resonance escape probability decreases during reactor operation. The 
+neutron reproduction factor increases during reactor operation due to 
+accumulation of fissile plutonium 
+isotopes, which produce more neutrons per fission ($\nu$). This six factors' 
+evolution agrees with 
+previously determined evolution parameters for a similar single-fluid 
+double-zone \gls{MSBR} \cite{rykhlevskii2019modeling, park_whole_2015}.

### 2019-10-08 paper/results.tex
Andrei's contribution after Grammarly check

--- 2019-09-27 paper/results.tex
@@
 \end{table}
+\FloatBarrier
+
+\subsection{Neutron flux}
+Figures~\ref{fig:fast_flux}, \ref{fig:thermal_flux} show the radial 
+distribution of fast (energy range between 0.625 eV and 20 MeV) and thermal 
+(energy range between 10$^{-5}$ eV and 0.625 eV) neutron flux for three 
+different initial fissile materials in the fuel salt ($^{233}$U, reactor-grade 
+plutonium, TRU) at startup and at equilibrium (after $\approx 30$ years of 
+operation). Actinides evolution and poisonous fission product accumulation 
+for various initial fissile compositions demonstrated the different effects on 
+the SD-TMSR neutronics performance. For the Th/$^{233}$U, the thermal neutron 
+flux is suppressed at the equilibrium because fissile $^{233}$U in the core is 
+being substituted with heavier fissile actinides: $^{235}$U, $^{239}$Pu, and 
+$^{241}$Pu. This is in good agreement with results in the literature 
+\cite{rykhlevskii2019modeling, ashraf2019whole_core}.
+\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
+	\includegraphics[width=\textwidth]{radial_fast_flux_init_vs_eq.png} 
+	\caption{Radial fast neutron flux distribution for 3 different initial 
+		fuel salt compositions at startup and equilibrium (the fast flux 
+		confidence interval $\pm\sigma<2.5$\% for all cases).}
+	\label{fig:fast_flux}
+\end{figure}
+
+Opposite observation has been made for the Pu reactor-grade and TRU cases. For 
+these cases, the thermal neutron flux is increasing during operation while 
+fast neutron flux is decreasing. Fissile plutonium nuclides (generate 
+relatively hard spectrum) from initial fuel salt composition is gradually 
+substituted with the $^{233}$U (generates relatively soft spectrum), produced 
+from the fertile $^{232}$Th. During reactor operation, the $^{233}$U becomes 
+primary fissile isotope, which leads to the neutron spectrum softening of the 
+reactor. 
+\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
+	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
+	\caption{Radial thermal neutron flux distribution for 3 different initial 
+		fuel salt compositions at startup and equilibrium for initial and 
+		equilibrium fuel salt composition (the thermal flux confidence 
+		interval 
+		$\pm\sigma<1.6$\% for all cases).}
+	\label{fig:thermal_flux}
+\end{figure}
+
+Notably, more changes in thermal neutron flux shape and magnitude for  
+$^{233}$U case were observed in the inner core zone ($R\lesssim150$) than 
+in the outer core zone. In contrast, for Pu reactor-grade and TRU cases, 
+significant changes were observed for thermal neutron flux in the outer core 
+zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
+relatively large changes in thermal flux leakage from the core for the Pu and 
+TRU cases. Overall, the SD-TMSR core design was optimized for $^{233}$U 
+fissile isotope \cite{li_optimization_2018}; hence, the core geometry (e.g., 
+fuel channels lattice pitch) must be re-optimized for another type of fuel to 
+obtain better neutronics performance.
+
+\subsection{Temperature coefficient of reactivity}
+The temperature coefficient of reactivity quantifies reactivity changes due to 
+temperature increase in the core and was calculated in this work as follows:
+\begin{align}
+\alpha &= \frac{k_{eff}(T_{i+1}) - k_{eff}(T_i)}{k_{eff}(T_{i+1}) 
+	k_{eff}(T_{i}) (T_{i+1} - T_i)}
+\intertext{where}
+k_{eff} &= \mbox{effective multiplication factor} \nonumber \\
+T_i &= \mbox{fuel salt temperature in (900K, 1000K).} \nonumber
+\end{align}
+
+Table~\ref{tab:tcoe} summarizes temperature coefficients calculated for three 
+different initial fissile loads at the startup and at the equilibrium. By 
+propagating the $k_{eff}$ statistical error provided by SERPENT-2, 
+uncertainty for each temperature coefficient was calculated using formula:
+\begin{align}
+\delta\alpha &= \abs{\frac{1}{T_{i+1} - T_i}} \sqrt{\frac{\delta 
+		k_{eff}^2(T_{i+1})}{k_{eff}^4(T_{i+1})}  
+	+ \frac{\delta k_{eff}^2(T_i)}{k_{eff}^4(T_i)}}
+\intertext{where}
+\delta k_{eff} &= \mbox{statistical error for $k_{eff}$ from SERPENT-2 
+output.} 
+\nonumber
+\end{align}
+Notably, other sources of uncertainty are neglected, such as cross-section 
+measurement error and approximations inherent in the density dependence on 
+temperature.
+
+When the fuel salt temperature increases, the density of the salt decreases, 
+but at the same time, the total volume of fuel salt in the 
+core remains constant because it
+is bounded by the vessel. When the graphite 
+temperature increases, the density of
+graphite decreases, creating additional 
+space for the salt. The cross-section temperatures for the fuel and moderator 
+were changed from 900 to 1000 K to determine the temperature coefficients. 
+This work considered five different cases:
+\begin{enumerate}
+	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 
+	(first row  in Table ~\ref{tab:tcoe}).
+	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 
+	(density change caused by temperature increase from	900 to 1000 K).
+	\item Total fuel salt temperature (Doppler+density) rising from 900 to 
+	1000 K.	
+	\item Graphite temperature (Doppler Effect) rising from 900 to 1000 K.
+	\item Whole reactor temperature rising from 900 K to 1000 K.
+\end{enumerate}
+
+In the first case, the fuel temperature change only impacts cross-section 
+temperature. In the second case, changes in the fuel temperature only impact 
+density, and the third case takes into account both effects. The geometry for 
+these three cases is unchanged because the fuel is a liquid. However, when 
+the graphite blocks heat up, both the density and the geometry changing due 
+to the thermal expansion of solid graphite. The graphite linear thermal 
+expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
+we focus only on Doppler Effect for the moderator temperature coefficient.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table} [b!]
+	\caption{Temperature coefficients of reactivity for 3 different initial 
+		fuel salt compositions at startup and equilibrium. Confidence interval 
+		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
+	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
+		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
+		& 
+		\multicolumn{6}{c}{Startup fissile material} \\ \cline{2-7}
+		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
+		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
+		\space  & Initial & Equil. & Initial & Equil. & Initial & 
+		Equil. \\ \hline
+		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
+		\\ 
+		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
+		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
+		\hline
+		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
+		\\	\hline
+		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
+	\end{tabularx}
+	\label{tab:tcoe}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The \gls{FTC} is negative for all considered fuel compositions due to thermal 
+Doppler broadening of the resonance capture cross-sections in the thorium. For 
+$^{233}$U case, the \gls{FTC} decreases in magnitude by $-25\%$ due to neutron 
+spectrum hardening during the reactor operation. For Pu reactor-grade and TRU 
+cases, the \gls{FTC} becomes more negative at the equilibrium, by $+31\%$ and 
+$+14\%$, respectively. Spectrum softening for these fueling cases positively 
+affects the \gls{FTC} magnitude, and this effect seems to be proportional to 
+the spectrum shift.
+
+The \gls{MTC} for the $^{233}$U case is positive and decreases during reactor 
+operation because of spectrum hardening with fuel depletion. For other cases, 
+the \gls{MTC} is negative and also decreasing in magnitude during the reactor 
+operation. Finally, the total temperature coefficient of reactivity is 
+strongly negative for all considered scenarios but decreases in magnitude 
+during reactor operation due to spectral shift. Notably, the total temperature 
+coefficient is the most negative for the Pu reactor-grade case at startup, 
+which has the hardest neutron spectrum (Figure~\ref{fig:spectrumFLUX110vC}). 
+These coefficients agree with earlier estimates for SD-TMSR 
+\cite{li_optimization_2018,Ashraf2019Whole} and \gls{MSBR} 
+\cite{rykhlevskii2019modeling, 
+rykhlevskii_full-core_2017,robertson_conceptual_1971}.
+
+Even after 30 years of operation, the total temperature coefficient of 
+reactivity remains relatively large and negative (in the range between $-2.59$ 
+and $-5.06$ pcm/K) comparing with the conventional \gls{PWR}, which has 
+temperature coefficient of about $-1.71$ $pcm/^{\circ}F\approx -3.08$ $pcm/K$ 
+\cite{forget_integral_2018}), and allows excellent reactor stability and 
+control. The additional analysis must be performed taking graphite moderator 
+density change and linear thermal expansion into account, but material 
+properties for the SD-TMSR graphite are not available in published literature. 
+Alternatively, relatively well-studied reactor graphite (e.g., AXQ graphite 
+\cite{robertson_conceptual_1971}) can be considered as a candidate for the 
+SD-TMSR concept.
+
+\subsection{Six Factor analysis}
+The effective multiplication factor can be expressed as follows:
+\begin{align}
+k_{eff} &= k_{inf} P_f  P_t = \eta f p \epsilon P_f P_t
+\intertext{where}
+\eta     &= \mbox{thermal fission factor} \nonumber \\
+f        &= \mbox{thermal utilization factor} \nonumber \\
+p        &= \mbox{resonance escape probability} \nonumber \\
+\epsilon &= \mbox{fast fission factor} \nonumber \\
+P_f      &= \mbox{fast non-leakage probability} \nonumber \\
+P_t      &= \mbox{thermal non-leakage probability.} \nonumber
+\end{align}
+
+Table~\ref{tab:six_factor} summarizes the six factors for 3 different initial 
+fuel salt compositions at startup and equilibrium. Using SERPENT-2 built-in 
+online reprocessing capabilities, all six factors have been calculated at the 
+beginning of the operation and after 30 years of operation. Neutron population 
+and number of active/inactive cycles were selected to obtain $k_{eff}$ 
+statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
+probabilities  remain constant regardless of initial fissile material and 
+neutron spectrum shift during operation. The thermal utilization factor (f) 
+remains almost constant during operation for $^{233}$U and TRU cases but 
+considerably declines for Pu case due to significant neutron spectrum 
+softening.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table} [ht!]
+	\caption{Six factors for the SD-TMSR model for 3 different initial 
+		fuel salt compositions at startup and equilibrium.}
+	\begin{tabularx}{\textwidth}{ X | X X  X X  X X } \hline
+		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
+			material} \\ \cline{2-7}
+		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
+		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
+		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
+		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31 \\ 
+		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
+		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15 \\
+		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
+		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
+		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
+	\end{tabularx}
+	\label{tab:six_factor}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In contrast, the neutron reproduction factor ($\eta$), resonance escape 
+probability ($p$), and fast fission factor ($\epsilon$) differ notably between 
+initial and equilibrium state for all three initial fissile materials. The 
+fast fission factor ($\epsilon$) is much larger at startup for Pu and TRU 
+cases because these initial fissile materials provided a much harder neutron 
+spectrum than $^{233}$U, and $\epsilon$ grows throughout the core's lifetime. 
+Conversely, the resonance escape probability decreases during reactor 
+operation. The thermal fission factor increases during reactor operation for 
+the $^{233}$U as initial fuel due to the accumulation of fissile plutonium 
+isotopes, which produce more neutrons per fission ($\nu$). The other two 
+scenarios demonstrated opposite behavior: plutonium isotopes with large 
+neutrons per fission production ($\nu$) are gradually substituted with the 
+$^{233}$U, which has lower $\nu$ \cite{sjostrand_cross_1960}. This six 
+factors' evolution agrees with previously determined evolution parameters for 
+a similar single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
+rykhlevskii2019modeling, park_whole_2015}.

### 2019-10-09 paper/results.tex
Osama's comments impelemented

@@
 
-Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U as a function of burnup.
-In TRU case, the net production of $^{233}$U is almost zero, nevertheless, the reactor becomes subcritical after $40$ $years$ of operation.
-In $^{233}$U and Pu reactor-grade cases, the net production of $^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$, respectively at the end of operation lifetime.
-It worth noting that thorium feed mechanism is applied in $^{233}$U case, while, non-thorium feed mechanism is adopted in Pu reactor-grade cases.
+Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U as a 
+function of burnup. In TRU case, the net production of $^{233}$U is almost 
+zero, nevertheless, the reactor becomes subcritical after $40$ $years$ of 
+operation. In $^{233}$U and Pu reactor-grade cases, the net production of 
+$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$, 
+respectively at the end of operation lifetime. It worth noting that thorium 
+feed mechanism is applied in $^{233}$U case, while, non-thorium feed mechanism 
+is adopted in Pu reactor-grade cases.
 As shown in Figure~\ref{fig:NetCC}, after 26 years the net production of $^{233}$U reaches $1.3$ $t$; this is sufficient to start-up another \gls{SD-TMSR}.
@@
 
-Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit lethargy for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 MeV for the $^{233}$U, Pu reactor-grade, and TRU started case.
-In $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due to the accumulation of the Pu and other strong thermal neutron absorbers in the fuel salt.
-For Pu reactor-grade and TRU cases, during the reactor operation, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope (see Figure~\ref{fig:U233CC}), the neutron spectrum softens and becomes similar to a thermal spectrum of the TMSR.
+Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
+lethargy for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
+MeV for the $^{233}$U, Pu reactor-grade, and TRU started case. In $^{233}$U 
+case, at the EOL, the neutron spectrum is harder than at BOL due to the 
+accumulation of the Pu and other strong thermal neutron absorbers in the fuel 
+salt. For Pu reactor-grade and TRU cases, during the reactor operation, the 
+fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
+(see Figure~\ref{fig:U233CC}), the neutron spectrum softens and becomes 
+similar to a thermal spectrum of the TMSR.
 
@@
 
-Opposite observation has been made for the Pu reactor-grade and TRU cases. For 
+Opposite behavior was observed for the Pu reactor-grade and TRU cases. For 
 these cases, the thermal neutron flux is increasing during operation while 
@@
 	\caption{Radial thermal neutron flux distribution for 3 different initial 
-		fuel salt compositions at startup and equilibrium for initial and 
-		equilibrium fuel salt composition (the thermal flux confidence 
-		interval 
-		$\pm\sigma<1.6$\% for all cases).}
+		fuel salt compositions at startup and equilibrium (the thermal flux 
+		confidence interval $\pm\sigma<1.6$\% for all cases).}
 	\label{fig:thermal_flux}
@@
 TRU cases. Overall, the SD-TMSR core design was optimized for $^{233}$U 
-fissile isotope \cite{li_optimization_2018}; hence, the core geometry (e.g., 
+fissile isotope \cite{li_optimization_2018}; thus, the core geometry (e.g., 
 fuel channels lattice pitch) must be re-optimized for another type of fuel to 
@@
 k_{eff} &= \mbox{effective multiplication factor} \nonumber \\
-T_i &= \mbox{fuel salt temperature in (900K, 1000K).} \nonumber
+T_i &= \mbox{fuel salt temperature in (900 K, 1000 K).} \nonumber
 \end{align}
@@
 These coefficients agree with earlier estimates for SD-TMSR 
-\cite{li_optimization_2018,Ashraf2019Whole} and \gls{MSBR} 
+\cite{li_optimization_2018, ashraf2019whole_core} and \gls{MSBR} 
 \cite{rykhlevskii2019modeling,  
@@
 Table~\ref{tab:six_factor} summarizes the six factors for 3 different initial 
-fuel salt compositions at startup and equilibrium. Using SERPENT-2 built-in 
+fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
 online reprocessing capabilities, all six factors have been calculated at the 

### 2019-10-10 paper/introduction.tex
Andrei's minor changes in the  Introduction

@@
 \section{Introduction}
-The \gls{GIF} has defined eight technology goals for the next generation nuclear systems.
-These goals are; safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}.
-\glspl{MSR} have many advantages that consistent with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online reprocessing and refueling, excellent neutron economy and operation under ambient pressure \cite{siemer2015molten,rosenthal1970molten}.
-Therefore, in 2002 the \gls{MSR} has been chosen as one of the promising reactors by this forum \cite{doe2002technology,pioro2016handbook}.
-In the \gls{MSR}, the fuel supposed to be in the form of liquid dissolved in molten salt (e.g., LiF or NaCl).
-This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly circulates through the core and allows transferring fission heat.
+The \gls{GIF} has defined eight technology goals for the next generation 
+nuclear systems. These goals are: safety and reliability, economics, 
+sustainability, non-proliferation and physical protection 
+\cite{doe2002technology}. The \gls{MSR} has many advantages that consistent 
+with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online 
+reprocessing and refueling, excellent neutron economy and near atmospheric 
+pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}. 
+Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV 
+reactors \cite{doe2002technology,pioro2016handbook}.
+In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl). 
+This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly 
+circulates through the core and allows transferring fission heat from reactor 
+core to heat exchanger.
 
-The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 MWth) was introduced by the \gls{CAS} \cite{li_optimization_2018}.
-The SD-TMSR is a graphite-moderated thermal-spectrum MSR.
-In the SD-TMSR the fissile and fertile elements are integrated into the same salt.
-In addition, the active core is divided into two zones, the radius of the fuel channels in the outer zone is modified to be larger than the radius of the fuel channels in the inner zone to improve the breeding ratio \cite{nuttin2005potential,li_optimization_2018}.
+The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 
+MW$_{th}$) was introduced by the \gls{CAS} \cite{li_optimization_2018}. The 
+SD-TMSR 
+is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U 
+fuel cycle. In the SD-TMSR the fissile and fertile elements are integrated 
+into the same salt. In addition, the active core is divided into two zones, 
+the radius of the fuel channels in the outer zone is modified to be larger 
+than the radius of the fuel channels in the inner zone to improve the breeding 
+ratio \cite{nuttin2005potential,li_optimization_2018}.
 
-Basically, the \gls{MSR} has been designed to apply the Th/$^{233}$U fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,merle2004scenarios,rosenthal1970molten}.
-Hence, the fertile isotope $^{232}$Th is converted to the fissile isotope $^{233}$U, an isotope that is not exist in nature.
-Therefore it is required to examine available fissile materials (e.g., $^{235}$U and Pu) to replace the $^{233}$U in the startup fuel \cite{betzler2016modeling,zou2018transition}.
-The thorium fuel cycle transition can be achieved after reaching the doubling time\footnote{Time required to produce enough amount of $^{233}$U to trigger a new SD-TMSR.} of $^{233}$U.
+Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U 
+fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
+merle2004scenarios,rosenthal1970molten}. This design assumes that we have 
+fissile $^{233}$U inventory to startup new \glspl{MSR}. But $^{233}$U does not 
+exist in the Earth's crust and can be produced from fertile $^{232}$Th only in 
+the nuclear reactor. Therefore, it is required to examine alternative fissile 
+materials (e.g., $^{235}$U) to replace the $^{233}$U in the startup fuel 
+composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel 
+cycle transition can be achieved after reaching the doubling 
+time\footnote{Time required to produce enough amount of $^{233}$U to trigger a 
+new SD-TMSR.} of $^{233}$U because in this case all startup fissile material 
+is being substituted by newly produced $^{233}$U.
 
-Betzler, et al.
-discussed the simulation of the start-up of a MSBR unit cell with LEU (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial fissile materials \cite{betzler2016modeling}.
-They concluded that the plutonium vector extracted from LWR SF serves as the best alternative source to $^{233}$U thanks to the highest ratio of fissile isotopes \cite{betzler2016modeling}.
-Zou, et al.
-introduced two approaches for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition.
-In the former way, the TMSR is launched with existing fissile material and thorium as a fertile material, then the bred $^{233}$U from thorium is rerouted into the core for criticality.
-In contrast, the latter way tends to store the bred $^{233}$U out of the core until there is enough amount to start a new TMSR \cite{zou2018transition}.
-Meanwhile, Zou, et al.
-studied the transitioning to thorium fuel cycle in a small modular Th-based molten salt reactor (smTMSR) using TRUs as startup fuel.
-They concluded that the transition to thorium fuel cycle can be achieved in thermal smTMSR with a proper fuel fraction \cite{zou2018preliminary}.
-Heuer, et al., discussed the transition characteristics of the \gls{MSFR} under different launching scenarios (e.g., enriched uranium and TRU) \cite{heuer2014towards}.
+Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit 
+cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial 
+fissile materials \cite{betzler2016modeling}. They concluded that the 
+plutonium vector extracted from LWR SF is the best alternative source 
+to $^{233}$U because it has the highest ratio of fissile isotopes 
+\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for 
+the thorium fuel cycle transition in \gls{TMSR}: in-core transition and 
+ex-core transition. Historically, the TMSR is launched with existing fissile 
+material and thorium as a fertile material; then the $^{233}$U bred from 
+thorium is rerouted into the core to maintain criticality. In contrast, the 
+new approaches tends to store produced $^{233}$U out of the core until there 
+is enough amount to start a new TMSR \cite{zou2018transition}.
+Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel 
+cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU} 
+as startup fuel. They concluded that the transition to thorium fuel cycle can 
+be achieved in thermal smTMSR with a proper fuel fraction 
+\cite{zou2018preliminary}.
+Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR} 
+under different launching scenarios (e.g., enriched uranium and TRU) 
+\cite{heuer2014towards}.
 
-Indeed, there are various researches that revolve around starting the MSRs with fissile materials alternative to $^{233}$U.
-Many of these researches focus on the fast-spectrum MSRs \cite{ashraf2019modeling,ashraf2018nuclear,heuer2014towards,fiorina2013investigation}, while little focus on thermal-spectrum MSRs \cite{betzler2016modeling,zou2018preliminary,zou2018transition}.
-Nevertheless, starting the \gls{SD-TMSR} with other fissile materials (except $^{233}$U) not found in the literature.
-Therefore, the main object of the present paper is to discuss the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition.
-To do that, we investigate five types of initial fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF \cite{de2000scenarios}.
-Moreover, two different feed mechanisms are used as follows:
+Indeed, there are various researches that revolve around starting the 
+\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these 
+researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling, 
+ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019, 
+heuer2014towards,fiorina2013investigation}, while little focus on 
+thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary, 
+zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other 
+fissile materials (except $^{233}$U) was not studied before. Therefore, 
+the main object of the present paper is to discuss the simulation of the 
+\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with 
+different initial fissile materials and without any external feed of $^{233}$U 
+to achieve the thorium fuel cycle transition. We investigated five different  
+initial fissile materials: \gls{LEU}, Pu, and \gls{TRU} from LWR SF 
+\cite{de2000scenarios}. Moreover, two different feed scenarios were selected:
 \begin{itemize}

### 2019-10-10 paper/introduction.tex
After Osama's comments

@@
 with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online
-reprocessing and refueling, excellent neutron economy and near atmospheric 
+reprocessing and refueling, excellent neutron economy and operation near
+atmospheric
 pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
@@
 fissile materials \cite{betzler2016modeling}. They concluded that the 
-plutonium vector extracted from LWR SF is the best alternative source 
-to $^{233}$U because it has the highest ratio of fissile isotopes 
+plutonium vector extracted from LWR SF is the best alternative source to 
+$^{233}$U because it has the highest ratio of fissile isotopes
 \cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for
-the thorium fuel cycle transition in \gls{TMSR}: in-core transition and 
-ex-core transition. Historically, the TMSR is launched with existing fissile 
-material and thorium as a fertile material; then the $^{233}$U bred from 
-thorium is rerouted into the core to maintain criticality. In contrast, the 
-new approaches tends to store produced $^{233}$U out of the core until there 
-is enough amount to start a new TMSR \cite{zou2018transition}.
+the thorium fuel cycle transition in \gls{TMSR}: (1) in-core transition and 
+(2) ex-core transition. In the first approach, the TMSR is launched with 
+existing fissile material and thorium as a fertile material; then the 
+$^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
+In contrast, the second approache tends to store produced $^{233}$U out of the 
+core until there is enough amount to start a new TMSR \cite{zou2018transition}.
 Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel
@@
 \cite{zou2018preliminary}.
+
 Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR}

### 2019-10-10 paper/introduction.tex
Resolving conflicts

@@
 \begin{itemize}
-	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
-	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.
+	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay 
+	tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. 
+	\cite{betzler2016modeling}.
+	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or 
+	part of $^{233}$U from \texttt{Pa-decay tank}.
 \end{itemize}
-This present paper is organized as follows: after an introduction about \gls{MSR} systems, the model description is discussed in section 2.
-Methodology and tools is descried in section 3.
-Extraction and feed mechanisms are addressed in section 4.
-Section 5 focuses on the results and discussion.
+This present paper is organized as follows: after an introduction about 
+\gls{MSR} systems, the model description is discussed in section 2. 
+Methodology and tools is descried in section 3. Extraction and feed mechanisms 
+are addressed in section 4. Section 5 focuses on the results and discussion. 
 Finally, section 6 highlights the conclusions.
@@
 %produce enough amount of $^{233}$U to start a new \gls{SD-TMSR}.
-%Therefore, the aim of this paper is to operate the \gls{SD-TMSR} for a long period of time with different initial fissile materials without external feed of $^{233}$U (that does not exist anywhere) to produce enough amount of $^{233}$U that is required to start a new \gls{SD-TMSR}.
+%Therefore, the aim of this paper is to operate the \gls{SD-TMSR} for a long 
+%period of time with different initial fissile materials without external feed 
+%of $^{233}$U (that does not exist anywhere) to produce enough amount of 
+%$^{233}$U that is required to start a new \gls{SD-TMSR}.
 
-%The \gls{MSR} is the only liquid-fueled reactor that the \gls{GIF} has chosen as one of the six promising concepts \cite{doe2002technology,pioro2016handbook}.
-The reactor's liquid fuel distinguishes it from other nuclear reactors.
-\glspl{MSR} can operate extended time without shutdown for refueling with a superior neutron economy \cite{doe2002technology}.
-Introducing online reprocessing and refueling systems would ensure sustainability.
-In a \gls{MSR}, liquid fuel salt (e.g.
-a mixture of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) circulates through the core and transports fission heat to the \glspl{IHX}.
-Finally, this type of reactor has a high conversion efficiency and a negative temperature coefficient.
+%The \gls{MSR} is the only liquid-fueled reactor that the \gls{GIF} has chosen 
+%as one of the six promising concepts 
+%\cite{doe2002technology,pioro2016handbook}. The reactor's liquid fuel 
+%distinguishes it from other nuclear reactors. \glspl{MSR} can operate 
+%extended 
+%time without shutdown for refueling with a superior neutron economy 
+%\cite{doe2002technology}. Introducing online reprocessing and refueling 
+%systems would ensure sustainability. In a \gls{MSR}, liquid fuel salt (e.g. a 
+%mixture of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) circulates through the core 
+%and 
+%transports fission heat to the \glspl{IHX}. Finally, this type of reactor has 
+%a high conversion efficiency and a negative temperature coefficient.
 
-%Both thermal and fast \gls{MSR} concepts exist in the literature \cite{pioro2016handbook,engel1979development}.
-For thermal \glspl{MSR}, hexagonal graphite prisms act as moderators.
-In contrast, fast spectrum \glspl{MSR} lack moderators.
-A \gls{MSR} can breed in both cases, making them optimal for realizing a desirable Thorium-Uranium fuel cycle \cite{hargraves2010liquid}.
+%Both thermal and fast \gls{MSR} concepts exist in the literature 
+%\cite{pioro2016handbook,engel1979development}. For thermal \glspl{MSR}, 
+%hexagonal graphite prisms act as moderators. In contrast, fast spectrum 
+%\glspl{MSR} lack moderators. A \gls{MSR} can breed in both cases, making them 
+%optimal for realizing a desirable Thorium-Uranium fuel cycle 
+%\cite{hargraves2010liquid}.
 
-%In the 1950s, \gls{ORNL} performed experiments that provided a basis for \gls{MSR} feasibility.
-In 1958, a 5 MW$_{th}$ homogeneous reactor experiment called HRE-2 utilized water-based liquid fuel to illustrate the intrinsic stability of homogeneous reactors.
-In the 1960s, \gls{ORNL} performed the \gls{MSRE} \cite{engel1979development,haubenreich1970experience,fiorinibasis,robertson1965msre}.
-These experiments demonstrated the capability of circulating a liquid fluoride mixture without significant corrosion problems.
-Researchers used a nickel-based alloy (Hastelloy N) as structural material and controlled the fuel's oxidation by using a U$^{3+}$/U$^{4+}$ buffer.
-The experiment also tested the continuous reprocessing of liquid fuel.
-The results showed that introducing a noble gas system (i.e.
-gas bubbling system) during the fuel cycle helps extract gaseous fission products \cite{pioro2016handbook}.
+%In the 1950s, \gls{ORNL} performed experiments that provided a basis for 
+%\gls{MSR} feasibility. In 1958, a 5 MW$_{th}$ homogeneous reactor experiment 
+%called HRE-2 utilized water-based liquid fuel to illustrate the intrinsic 
+%stability of homogeneous reactors. In the 1960s, \gls{ORNL} performed the 
+%\gls{MSRE} 
+%\cite{engel1979development,haubenreich1970experience,fiorinibasis,robertson1965msre}.
+% These experiments demonstrated the capability of circulating a liquid 
+%fluoride mixture without significant corrosion problems. Researchers used a 
+%nickel-based alloy (Hastelloy N) as structural material and controlled the 
+%fuel's oxidation by using a U$^{3+}$/U$^{4+}$ buffer. The experiment also 
+%tested the continuous reprocessing of liquid fuel. The results showed that 
+%introducing a noble gas system (i.e. gas bubbling system) during the fuel 
+%cycle helps extract gaseous fission products \cite{pioro2016handbook}.
 
-%\gls{ORNL} later researched the \gls{MSBR} \cite{rosenthal1970molten}.
-There were two types of \gls{MSBR}: the single-fluid molten salt reactor and the two-fluid molten salt reactor.
-While the single-fluid MSR dissolves fertile and fissile materials in the same salt, the two-fluid MSR physically separates them.
-The two-fluid MSR had a higher breeding performance than the single-fluid MSR.
-However, the single-fluid MSR can operate as an iso-breeding reactor as long as there is an efficient reprocessing system for the fuel salt \cite{rosenthal1970molten}.
+%\gls{ORNL} later researched the \gls{MSBR} \cite{rosenthal1970molten}. There 
+%were two types of \gls{MSBR}: the single-fluid molten salt reactor and the 
+%two-fluid molten salt reactor. While the single-fluid MSR dissolves fertile 
+%and fissile materials in the same salt, the two-fluid MSR physically 
+%separates 
+%them. The two-fluid MSR had a higher breeding performance than the 
+%single-fluid MSR. However, the single-fluid MSR can operate as an 
+%iso-breeding 
+%reactor as long as there is an efficient reprocessing system for the fuel 
+%salt 
+%\cite{rosenthal1970molten}.
 
-%Despite the success of the \gls{MSRE}, \gls{ORNL} halted work on the \gls{MSBR} in 1976.
-The \gls{Euratom} later revived the project.
-To enhance the breeding performance of the \gls{MSBR}, \gls{Euratom} introduced the idea of dividing the core into multiple zones of fuel channels with different radii \cite{nuttin2005potential}.
-The results showed that increasing the radii of the outer fuel channels relative to the inner radii improved the reactor's breeding and allowed it to out-perform the reactor with a single-zone core and large fuel channels \cite{nuttin2005potential}.
+%Despite the success of the \gls{MSRE}, \gls{ORNL} halted work on the 
+%\gls{MSBR} in 1976. The \gls{Euratom} later revived the project. To enhance 
+%the breeding performance of the \gls{MSBR}, \gls{Euratom} introduced the idea 
+%of dividing the core into multiple zones of fuel channels with different 
+%radii 
+%\cite{nuttin2005potential}. The results showed that increasing the radii of 
+%the outer fuel channels relative to the inner radii improved the reactor's 
+%breeding and allowed it to out-perform the reactor with a single-zone core 
+%and 
+%large fuel channels \cite{nuttin2005potential}.
 
-%Later, fast spectrum MSRs were introduced.
-Several fast MSR designs include: \gls{MSFR}, \gls{EVOL} \cite{serp2014molten}, \gls{MOSART} \cite{boussier2012molten}, REBUS-3700 \cite{mourogov2006potentialities} and Molten Chloride Salt Fast Reactor \cite{taube1978fast}.
-\gls{GIF} has elected to further research \gls{MSFR} and \gls{MOSART} \cite{serp2014molten,boussier2012molten,locatelli2013generation,pettersen2016coupled}.
-Both designs feature the fast-spectrum, Th-based fuel, and liquid fuel circulation.
-The \gls{MSFR} concept initially gained momentum at \gls{CNRS} in France, and the \gls{MOSART} concept is in progress in Russia.
+%Later, fast spectrum MSRs were introduced. Several fast MSR designs include: 
+%\gls{MSFR}, \gls{EVOL} \cite{serp2014molten}, \gls{MOSART} 
+%\cite{boussier2012molten}, REBUS-3700 \cite{mourogov2006potentialities} and 
+%Molten Chloride Salt Fast Reactor \cite{taube1978fast}. \gls{GIF} has elected 
+%to further research \gls{MSFR} and \gls{MOSART} 
+%\cite{serp2014molten,boussier2012molten,locatelli2013generation,pettersen2016coupled}.
+% Both designs feature the fast-spectrum, Th-based fuel, and liquid fuel 
+%circulation. The \gls{MSFR} concept initially gained momentum at \gls{CNRS} 
+%in 
+%France, and the \gls{MOSART} concept is in progress in Russia.
 
-%Indeed, several challenges interfere with the commercial adoption of \gls{MSFR}.
-For example, large initial inventory of $^{233}$U and relatively long doubling time for $^{233}$U production.
-Moreover, material scientists must identify or create structural materials which have reasonable lifespan in extreme operational conditions (high temperature, large neutron flux, chemically aggressive salt).
-Finally, breeding of high-quiality fissile material in the \gls{MSFR} blanket rises significant nuclear non-proliferation concerns \cite{pettersen2016coupled,merle2009minimizing}.
+%Indeed, several challenges interfere with the commercial adoption of 
+%\gls{MSFR}. For example, large initial inventory of $^{233}$U and relatively 
+%long doubling time for $^{233}$U production. Moreover, material scientists 
+%must identify or create structural materials which have reasonable lifespan 
+%in 
+%extreme operational conditions (high temperature, large neutron flux, 
+%chemically aggressive salt). Finally, breeding of high-quiality fissile 
+%material in the \gls{MSFR} blanket rises significant nuclear 
+%non-proliferation 
+%concerns \cite{pettersen2016coupled,merle2009minimizing}.
 
-%The thermal MSR has priority due to the low inventory of initial fissile $^{233}$U and short doubling time for its production \cite{ZOU2015114}.
-%Nagy et al.
-studied the effect of core zoning on the breeding performance and graphite lifespan of a graphite-moderated MSR \cite{nagy2011new,nagy2012effects}.
-Li et al.
-divided the active core into two zones to improve the breeding performance \cite{li_optimization_2018}.
-The central zone is moderated, while the unmoderated outer zone acts as a subcritical fast spectrum zone \cite{li_optimization_2018}.
+%The thermal MSR has priority due to the low inventory of initial fissile 
+%$^{233}$U and short doubling time for its production \cite{ZOU2015114}.
+%Nagy et al. studied the effect of core zoning on the breeding performance and 
+%graphite lifespan of a graphite-moderated MSR 
+%\cite{nagy2011new,nagy2012effects}. Li et al. divided the active core into 
+%two 
+%zones to improve the breeding performance \cite{li_optimization_2018}. The 
+%central zone is moderated, while the unmoderated outer zone acts as a 
+%subcritical fast spectrum zone \cite{li_optimization_2018}.
 
-%In 2011, the \gls{CAS} established the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)".
-Since then, several studies aimed to improve the \gls{TMSR} to efficiently utilize the Th-U fuel cycle \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}.
-%Separately, we can highlight the issue of a closed Th-U fuel cycle in the thermal spectrum.
-A number of studies have shown the fundamental possibility of organizing such a cycle in a heavy-water reactor and referred to the limitation of the burn-up of solid fuels due to the accumulation of the fission products (FPs) \cite{dastur1995thorium,bergel2004mode,bergelson2008op}.
-The question of feasibility and parameters of a closed U-Th fuel cycle in a \gls{TMSR} reactor is relevant.
+%In 2011, the \gls{CAS} established the strategic project ``Future Advanced 
+%Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)". Since 
+%then, several studies aimed to improve the \gls{TMSR} to efficiently utilize 
+%the Th-U fuel cycle 
+%\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}.
+%Separately, we can highlight the issue of a closed Th-U fuel cycle in the 
+%thermal spectrum. A number of studies have shown the fundamental possibility 
+%of organizing such a cycle in a heavy-water reactor and referred to the 
+%limitation of the burn-up of solid fuels due to the accumulation of the 
+%fission products (FPs) 
+%\cite{dastur1995thorium,bergel2004mode,bergelson2008op}. The question of 
+%feasibility and parameters of a closed U-Th fuel cycle in a \gls{TMSR} 
+%reactor 
+%is relevant.
 
-%Liquid-fueled systems require specific neutron transport and depletion tools that capture online fuel reprocessing and refueling.
-Specifically, the circulation of the liquid fuel and the continuous feed or removal of elements (e.g.
-fissile material injection into and Fission Products (FPs) extraction from the fuel salt) are out-of-scope for most contemporary nuclear reactor physics software, which was originally written primarily to simulate solid-fueled reactors.
-The SERPENT-2 \cite{leppanen2014serpent} code extension takes into account the online fuel reprocessing and its effects on depletion calculations \cite{aufiero2013extended}.
+%Liquid-fueled systems require specific neutron transport and depletion tools 
+%that capture online fuel reprocessing and refueling. Specifically, the 
+%circulation of the liquid fuel and the continuous feed or removal of elements 
+%(e.g. fissile material injection into and Fission Products (FPs) extraction 
+%from the fuel salt) are out-of-scope for most contemporary nuclear reactor 
+%physics software, which was originally written primarily to simulate 
+%solid-fueled reactors. The SERPENT-2 \cite{leppanen2014serpent} code 
+%extension 
+%takes into account the online fuel reprocessing and its effects on depletion 
+%calculations \cite{aufiero2013extended}.
 
-%The present paper aims to analyze the fuel depletion of the \gls{SD-TMSR} during 60 years reactor operation time using SERPENT-2.
-This work investigates the inventory of isotopes in the core to establish the advantages of the \gls{TMSR} concept applied to energy production (based on the thorium fuel cycle).
-All calculations presented in the present work were implemented using SERPENT-2 version 2.1.30.
-We adopted the built-in SERPENT-2 subroutine to simulate continuous online reprocessing and refueling in contrast with other batch-wise codes \footnote{In the batch-wise technique, the simulation stops at a certain time and restarts after removing of poisoning isotopes and addition of fissile and/or fertile materials.} (e.g.
-SaltProc \cite{rykhlevskii2019modeling} and MCNP6-PYTHON \cite{Jeong2016}).
-%SERPENT-2 allowed us to conduct burn-up calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.
-The drift of the delayed neutron precursors is not examined in this paper.
+%The present paper aims to analyze the fuel depletion of the \gls{SD-TMSR} 
+%during 60 years reactor operation time using SERPENT-2. This work 
+%investigates 
+%the inventory of isotopes in the core to establish the advantages of the 
+%\gls{TMSR} concept applied to energy production (based on the thorium fuel 
+%cycle). All calculations presented in the present work were implemented using 
+%SERPENT-2 version 2.1.30. We adopted the built-in SERPENT-2 subroutine to 
+%simulate continuous online reprocessing and refueling in contrast with other 
+%batch-wise codes \footnote{In the batch-wise technique, the simulation stops 
+%at a certain time and restarts after removing of poisoning isotopes and 
+%addition of fissile and/or fertile materials.} (e.g. SaltProc 
+%\cite{rykhlevskii2019modeling} and MCNP6-PYTHON \cite{Jeong2016}).
+%SERPENT-2 allowed us to conduct burn-up calculations on computer clusters 
+%with multiple cores using distributed-memory MPI parallelization. The drift 
+%of 
+%the delayed neutron precursors is not examined in this paper.
 
-%The present paper is organized as follows: after a general introduction about \gls{MSR} systems, section 2 briefly presents the \gls{SD-TMSR}.
-Section 3 focuses on the methodology and calculation tools used in this work.
-Fission products extraction modeling is described in section 4.
-Section 5 highlights the results and discussion.
-Finally, section 6 summarizes the conclusions.
+%The present paper is organized as follows: after a general introduction about 
+%\gls{MSR} systems, section 2 briefly presents the \gls{SD-TMSR}. Section 3 
+%focuses on the methodology and calculation tools used in this work. Fission 
+%products extraction modeling is described in section 4. Section 5 highlights 
+%the results and discussion. Finally, section 6 summarizes the conclusions.
 

### 2019-10-10 paper/methods.tex

@@
 \subsection{Geometry}
-The \gls{SD-TMSR} design model was introduced by the \gls{CAS} during the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)" in 2011 \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}.
-The design of \gls{SD-TMSR} is inspired by \gls{MSBR} \cite{robertson_conceptual_1971} after some modification in the geometry to control the positive temperature coefficient in MSBR.
-The \gls{SD-TMSR} model is described deeply in \cite{li_optimization_2018}.
-Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the \gls{SD-TMSR}.
-The active zone is a right cylinder with height and diameter equal to 460 cm.
-Assemblies of graphite\footnote{We choose graphite density of $2.3$ g/cm$^3$, to validate our results against results in the literature \cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the core.
-The side length of the graphite hexagonal prism was optimized in \cite{li_optimization_2018} and found to be 7.5 cm.
-The liquid fuel circulates continuously through the fuel channels that pierces the graphite hexagonal prisms.
-The active zone is divided into two different zones to enhance Th-U breeding performance.
-The radius of the fuel tubes in the outer zone is 5 cm and the radius of the fuel tubes in the inner zone is 3.5 cm.
-Moreover, axial and radial reflectors from graphite surround the active zone to maximize neutron flux.
-The core is surrounded by B${_4}$C cylinder that acts as a shield against heat and neutrons radiation.
-Another Ni-based (hastelloy N) cylinder surrounds the whole core and provides structure and heat protection. The main characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.
+The \gls{SD-TMSR} design model was introduced by the \gls{CAS} as a part of  
+the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based 
+Molten Salt Reactor System (TMSR)" in 2011 
+\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
+design of \gls{SD-TMSR} is inspired by \gls{MSBR} 
+\cite{robertson_conceptual_1971} after some modification in the geometry to 
+control the positive temperature coefficient in MSBR. The \gls{SD-TMSR} core 
+geometry was described in details by Li \emph{et al.} 
+\cite{li_optimization_2018}.
+Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the 
+\gls{SD-TMSR}. The active zone is a right cylinder with height and diameter 
+equal to 460 cm. Assemblies of graphite\footnote{We choose graphite density of 
+$2.3$ g/cm$^3$, to validate our results against results in the literature 
+\cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the 
+core. The side length of the graphite hexagonal prism was optimized in 
+\cite{li_optimization_2018} and found to be 7.5 cm. The liquid fuel circulates 
+continuously through the fuel channels that pierces the graphite hexagonal 
+prisms. The core is divided into two different zones to enhance 
+Th/$^{233}$U breeding performance. The radius of the fuel channels in the 
+outer and inner zone are 5 and 3.5 cm, respectively. The axial and radial 
+graphite reflectors surround the core to minimize neutron leakage and 
+maximize flux in the core. The reflectors are surrounded by B${_4}$C cylinder 
+that acts as a radiation shielding. The \gls{SD-TMSR} pressure vessel holds 
+the fuel salt, graphite elements, reflector, shielding, intermediate heat 
+exchanger (IHX) and made of Ni-based (hastelloy N) alloy. The main 
+characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.
 
@@
 	\includegraphics[width=\textwidth]{ff.png}
-	\caption{The quarter-core model configuration of the SD-TMSR a) Longitudinal view b) Cross-sectional view at the horizontal midplane.}
+	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
+	SD-TMSR.}
 	\label{fig:ff}
@@
 \subsection{Fuel composition}
-The general composition of the liquid fuel salt in this work is 70LiF - 17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (i.e. thorium + different fissile materials).
-As previously mentioned, the aim of this paper is to simulate the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U.
-Therefore, five different types of initial fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF are investigated as follows:\\
-	(1)low-enriched uranium (LEU) (19.79\%);\\
-	(2)Pu mixed with LEU (19.79\%);\\
-	(3)Pu reactor-grade \cite{marka1993explosive};\\
-	(4)transuranic (TRU) elements from LWR SF \cite{de2000scenarios};\\
-	(5)and $^{233}$U for comparison purpose.\\
+The general composition of the liquid fuel salt in this work is 70LiF - 
+17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (misture of 
+thorium and other actinides). The aim of this paper is to simulate the  
+operation of \gls{SD-TMSR} for 60 years with different startup fissile 
+compositions and without any external feed of fissile $^{233}$U which we 
+assumed is unavailable. For that reason, five different types of initial 
+fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF were 
+considered:
+\begin{enumerate}[label=(\alph*)]
+	\item low-enriched uranium (LEU) (19.79\%);
+	\item Pu mixed with \gls{LEU} (19.79\%);
+	\item Pu reactor-grade \cite{marka1993explosive};
+	\item transuranic (TRU) elements from LWR SF \cite{de2000scenarios};
+	\item $^{233}$U for comparison purpose \cite{ashraf2019whole_core}.
+\end{enumerate}
 
-The reactor-grade plutonium and \gls{TRU} vector (\%) are summarized in Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.
+The reactor-grade plutonium and \gls{TRU} composition are summarized in 
+Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.
 
@@
 
-The isotopic compositions of plutonium recovered from the spent fuel composition of commercial LEU \gls{PWR} that has released $33$ $GWd/t$ fission energy and has been cooled for $10$ $years$ before reprocessing \cite{oecd1989probabilistic,marka1993explosive}.
-As well, the isotopic compositions of \gls{TRU} have been taken from the SF of UOX \gls{PWR} (after one use and without multi-recycling) with $60$ $GWd/t$ burnup, and after $5$ $years$ cooling \cite{de2000scenarios}.
-The molar composition of startup fuel for all five cases is listed in Table~\ref{tab:table4}.
-Meanwhile, the corresponding initial nuclei inventories with different types of fuel are tabulated in Table~\ref{tab:table5}.
-
+For reactor-grade plutonium case, the composition was taken for plutonium 
+recovered from the spent fuel composition of commercial \gls{PWR} with the 
+average discharge burnup $33$ $GWd/t$ and after $10$ years of cooling before 
+reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
+isotopic compositions of \gls{TRU} was taken for the SF of UOX \gls{PWR} 
+(after one use, no multi-recycling) with the average discharge $60$ 
+$GWd/t$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
+The molar composition of startup fuel for all five cases is listed in 
+Table~\ref{tab:table4}. Meanwhile, the corresponding initial nuclei 
+inventories with different types of fuel are summarized in 
+Table~\ref{tab:table5}.
 \begin{table}  %[!ht]
-	\caption{Composition of startup fuel mole\%}
+	\caption{Composition of startup fuel (mole\%)}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{s s s s s s}
+	\begin{tabularx}{\textwidth}{p{0.16\textwidth} X p{0.17\textwidth} 
+	p{0.14\textwidth} X X}
 		\hline
-		Molecule& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79 wt-\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
+		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt\%) 
+		& Pu reactor-grade & \gls{TRU}& $^{233}$U \\
 		\hline
@@
 		PuF$_3$&&0.25&1.75&&		\\
-		TRUF$_3$&&&	&3.85	&\\
+		(TRU)F$_3$&&&	&3.85	&\\
 		\hline
@@
 
-Simulation of Liquid-fueled Molten Salt Reactor (MSR) systems requires computational software that must support online fuel salt reprocessing and refueling \cite{serp2014molten}.
-In this work, SERPENT-2 version 2.1.31 beta\footnote{SERPENT-2 is a \gls{3D} continuous energy Monte Carlo neutron transport and burn-up code.} \cite{leppanen2014serpent} is used to simulate the full-core of the SD-TMSR with different types of initial fuel.
-The extension of SERPENT code accounts for continuous online reprocessing and refueling \cite{aufiero2013extended}.
-Meanwhile, ENDF-VII.0 cross-section library is adopted for all calculations.
-The results demonstrate full-core runs of $12.5E+06$ neutron history per depletion step.
-The full burnup time of the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ $36$ $pcm$.
-The online extraction of \gls{FPs} and noble gases  provides many benefits for MSRs.
-For example, it would reduce the fissile inventory required to achieve criticality and improve the breeding ratio.
-Figure~\ref{fig:flow} shows a flow chart of the calculation steps.
+Simulation of Liquid-fueled Molten Salt Reactor (MSR) systems requires 
+computational software that must support online fuel salt reprocessing and 
+refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 
+beta\footnote{SERPENT-2 is a 3D continuous energy Monte Carlo neutron 
+transport and burnup code.} \cite{leppanen2014serpent} is used to simulate the 
+full-core of the SD-TMSR with different types of initial fuel. The extension 
+of SERPENT accounts for continuous online reprocessing and refueling 
+\cite{aufiero2013extended}. ENDF-VII.0 cross-section library was used for all 
+calculations in this work. The results demonstrate full-core runs of 
+$1.25\times 10^7$ neutron history per depletion step. The full burnup time of 
+the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
+$36$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
+provides many benefits for MSRs. For example, it would reduce the initial 
+fissile material inventory required to achieve criticality and improve the 
+breeding ratio. Figure~\ref{fig:flow} shows a flow chart of the calculation 
+steps.
 
@@
 
-As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced matrix exponential solution based on the Chebyshev Rational Approximation Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation.
-Then, the system extracted gaseous \gls{FPs} and other materials (non-dissolved metals, lanthanides, and soluble metals except Pu) in a proper time.
-This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the \texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}.
-Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, \texttt{pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}.
-The produced $^{233}$U is used as a fresh fissile fuel and the residual $^{233}$U is the net production of $^{233}$U.
-The MSR burnup routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the isotopes during reactor operation \cite{aufiero2013extended}.
-The mass of the fissile and fertile materials needed to achieve criticality is calculated at the end of the cycle.
-Then, this mass is added to the core at the beginning of the cycle by a certain flow rate.
+As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced 
+matrix exponential solution based on the Chebyshev Rational Approximation 
+Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. 
+Then, the system extracted gaseous \gls{FPs} and other materials 
+(non-dissolved metals, lanthanides, and soluble metals except Pu) with 
+suitable removal rate\footnote{The extraction rate depends on the type of 
+poison and its impact on the neutron
+economy.}. This can be done by set the 
+flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
+\texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous 
+\gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
+soluble metals except protactinium).}. Specifically, protactinium was removed 
+from the fuel with a certain flow rate into the external tank, 
+\texttt{pa-decay tank}\footnote{An imaginary tank used to store protactinium 
+extracted from the core.}, to decay and produce $^{233}$U\footnote{The 
+$^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
+$\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
+and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup 
+routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the 
+isotopes during reactor operation \cite{aufiero2013extended}. The mass of the 
+fissile and fertile materials needed to achieve criticality is calculated at 
+the end of the cycle. Then, this mass is added to the core at the beginning of 
+the cycle by a certain flow rate.
 
 \section{Feed and extraction rates}
-In the present work, two different feed mechanisms are used.
-The first mechanism allows continuous feed flow of thorium and $^{233}$U from \texttt{pa-decay tank}.
-In contrast, the second mechanism adopts continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.\\
-The fission products act as poisons in the MSRs; they negatively impacting the reactivity.
-Therefore, \gls{FPs} must be extracted during reactor operation.
-Consider $T_{r}$ as the time during which the total fuel salt is reprocessed and $dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that the \gls{MSR} extracts during time $dt$; thus \cite{nuttin2005potential}
+In the present work, two different feed mechanisms are used. The first 
+mechanism allows continuous feed flow of thorium from Th stockpile, and 
+$^{233}$U from \texttt{pa-decay tank}. In contrast, the second mechanism 
+continuously injects Heavy Metal (HM) (excluding Th) and simultaneously feeds  
+all or part of produced $^{233}$U from \texttt{Pa-decay tank}. The fission 
+products act as poisons in the MSRs; they negatively impacting the reactivity. 
+Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
+$T_{r}$ as the time during which the total fuel salt is reprocessed and 
+$dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that 
+the \gls{MSR} extracts during time $dt$; thus \cite{nuttin2005potential}
 
@@
 
-where $\varepsilon_{e}$ is the removal efficiency.
-Equation \ref{Equ:1} gives the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material is removed), where $\lambda_{e}=\varepsilon_{e}/T_{r}$.
-The removal constant $\lambda_{e}$ of gaseous and other fission products is precisely calculated and summarized in Table~\ref{tab:table6}.
-The effective reprocessing time for the gaseous \gls{FPs} and non-dissolved metals was set to 30 seconds (removal constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be extract promptly and continuously via He bubbling system.
-In contrast, extracting the soluble \gls{FPs}, lanthanides, and protactinium can be done by the chemical reprocessing (i.e.
-fluorination and reduction reaction).
-Therefore, the system reprocesses a specific amount of fuel salt daily.
-In the present work, the effective extraction time for soluble \gls{FPs} is $\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is equivalent to 5 m$^3$/d of chemical reprocessing rate \cite{nuttin2005potential,li_optimization_2018}.
-The effective feed rates of the heavy metals (HM) are changed during reactor operation to conserve the total fuel mass and criticality.
+where $\varepsilon_{e}$ is the removal efficiency. Equation \ref{Equ:1} gives 
+the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
+is removed), where $\lambda_{e}=\varepsilon_{e}/T_{r}$. The removal constant 
+$\lambda_{e}$ of gaseous and other fission products is precisely calculated 
+and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
+the gaseous \gls{FPs} and non-dissolved metals was set to 30 seconds (removal 
+constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
+extracted promptly and continuously via gas removal system. In contrast, 
+extracting the soluble \gls{FPs}, lanthanides, and protactinium can be done by 
+the chemical reprocessing (i.e. fluorination and reduction reaction). 
+Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
+present work, the effective extraction time for soluble \gls{FPs} is 
+$\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
+equivalent to 5 m$^3$/d of chemical reprocessing rate 
+\cite{nuttin2005potential,li_optimization_2018}. The effective feed rates of 
+the heavy metals (HM) are changed during reactor operation to conserve the 
+total fuel mass and criticality.
 

### 2019-10-10 paper/abstract.tex
Andrei's comments impelemented Abstract & introduction

@@
 \begin{abstract}
-Liquid-fueled Molten Salt Reactor (MSR) systems represent advances in safety, economics, sustainability, and proliferation-resistance.
-Therefore, \gls{MSR} has been selected as one of the promising reactors by the \gls{GIF}.
-Basically, the \gls{MSR} has been designed to operate based on Th/$^{233}$U fuel cycle.
-Since $^{233}$U does not exist in nature, it is required to examine available fissile materials to replace the $^{233}$U in the startup fuel.
-Here, five different types of initial fissile materials are proposed for transitioning to thorium fuel cycle in the \gls{SD-TMSR}.
-Plutonium mixed with \gls{LEU} (19.79\%), \gls{LEU} (19.79\%), Plutonium reactor-grade, \gls{TRU} from LWR spent fuel (SF) and finally $^{233}$U for comparison purpose are investigated.
-In the present paper, two different feed mechanisms are applied.
-Consequently, the multiplication factor, inventories of important nuclides and net production of $^{233}$U are studied.
-Moreover, the molten salt Temperature Coefficient of Reactivity $(\alpha$$_{T}$) is negative for startup and equilibrium states.
-The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U startup fuel.
-Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U.
+Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance.
+The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as start-up fissile material.
+Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials.
+This work investigated the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at start-up: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} spent fuel with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF} and finally $^{233}$U.
+The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}.
+The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work.
+The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for $^{233}$U start-up fuel.
+Finally, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
 \end{abstract}
@@
 %In conclusion, the full core of SD-TMSR was modeled and the net production of $^{233}$U was found to be positive.
+
+%Therefore, \gls{MSR} has been selected as one of the promising reactors by the \gls{GIF}.

### 2019-10-10 paper/introduction.tex
Andrei's comments impelemented Abstract & introduction

--- 2019-10-10 paper/introduction.tex
@@
 \section{Introduction}
-The \gls{GIF} has defined eight technology goals for the next generation 
-nuclear systems. These goals are: safety and reliability, economics, 
-sustainability, non-proliferation and physical protection 
-\cite{doe2002technology}. The \gls{MSR} has many advantages that consistent 
-with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online 
-reprocessing and refueling, excellent neutron economy and near atmospheric 
-pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}. 
-Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV 
-reactors \cite{doe2002technology,pioro2016handbook}.
-In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl). 
-This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly 
-circulates through the core and allows transferring fission heat from reactor 
-core to heat exchanger.
+The \gls{GIF} has defined eight technology goals for the next generation nuclear systems.
+These goals have been defined in four broad areas: safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}.
+\glspl{MSR} have many advantages that consistent with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online reprocessing and refueling, excellent neutron economy and operation under ambient pressure \cite{siemer2015molten,rosenthal1970molten}.
+Therefore, in 2002 the \gls{MSR} has been chosen as one of the promising reactors by this forum \cite{doe2002technology,pioro2016handbook}.
+In the \gls{MSR}, the fuel supposed to be in the form of liquid dissolved in molten salt (e.g., LiF or NaCl).
+This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly circulates through the core and allows transferring fission heat.
 
-The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 
-MW$_{th}$) was introduced by the \gls{CAS} \cite{li_optimization_2018}. The 
-SD-TMSR 
-is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U 
-fuel cycle. In the SD-TMSR the fissile and fertile elements are integrated 
-into the same salt. In addition, the active core is divided into two zones, 
-the radius of the fuel channels in the outer zone is modified to be larger 
-than the radius of the fuel channels in the inner zone to improve the breeding 
-ratio \cite{nuttin2005potential,li_optimization_2018}.
+The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 MWth) was introduced by the \gls{CAS} \cite{li_optimization_2018}.
+The SD-TMSR is a graphite-moderated thermal-spectrum MSR.
+In the SD-TMSR the fissile and fertile elements are integrated into the same salt.
+In addition, the active core is divided into two zones, the radius of the fuel channels in the outer zone is modified to be larger than the radius of the fuel channels in the inner zone to improve the breeding ratio \cite{nuttin2005potential,li_optimization_2018}.
 
-Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U 
-fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
-merle2004scenarios,rosenthal1970molten}. This design assumes that we have 
-fissile $^{233}$U inventory to startup new \glspl{MSR}. But $^{233}$U does not 
-exist in the Earth's crust and can be produced from fertile $^{232}$Th only in 
-the nuclear reactor. Therefore, it is required to examine alternative fissile 
-materials (e.g., $^{235}$U) to replace the $^{233}$U in the startup fuel 
-composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel 
-cycle transition can be achieved after reaching the doubling 
-time\footnote{Time required to produce enough amount of $^{233}$U to trigger a 
-new SD-TMSR.} of $^{233}$U because in this case all startup fissile material 
-is being substituted by newly produced $^{233}$U.
+Basically, the \gls{MSR} has been designed to apply the Th/$^{233}$U fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,merle2004scenarios,rosenthal1970molten}.
+Hence, the fertile isotope $^{232}$Th is converted to the fissile isotope $^{233}$U, an isotope that is not exist in nature.
+Therefore it is required to examine available fissile materials (e.g., $^{235}$U and Pu) to replace the $^{233}$U in the startup fuel \cite{betzler2016modeling,zou2018transition}.
+The thorium fuel cycle transition can be achieved after reaching the doubling time\footnote{Time required to produce enough amount of $^{233}$U to trigger a new SD-TMSR.} of $^{233}$U.
 
-Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit 
-cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial 
-fissile materials \cite{betzler2016modeling}. They concluded that the 
-plutonium vector extracted from LWR SF is the best alternative source 
-to $^{233}$U because it has the highest ratio of fissile isotopes 
-\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for 
-the thorium fuel cycle transition in \gls{TMSR}: in-core transition and 
-ex-core transition. Historically, the TMSR is launched with existing fissile 
-material and thorium as a fertile material; then the $^{233}$U bred from 
-thorium is rerouted into the core to maintain criticality. In contrast, the 
-new approaches tends to store produced $^{233}$U out of the core until there 
-is enough amount to start a new TMSR \cite{zou2018transition}.
-Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel 
-cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU} 
-as startup fuel. They concluded that the transition to thorium fuel cycle can 
-be achieved in thermal smTMSR with a proper fuel fraction 
-\cite{zou2018preliminary}.
-Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR} 
-under different launching scenarios (e.g., enriched uranium and TRU) 
-\cite{heuer2014towards}.
+Betzler, et al.
+discussed the simulation of the start-up of a MSBR unit cell with LEU (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial fissile materials \cite{betzler2016modeling}.
+They concluded that the plutonium vector extracted from LWR SF serves as the best alternative source to $^{233}$U thanks to the highest ratio of fissile isotopes \cite{betzler2016modeling}.
+Zou, et al.
+introduced two approaches for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition.
+In the former way, the TMSR is launched with existing fissile material and thorium as a fertile material, then the bred $^{233}$U from thorium is rerouted into the core for criticality.
+In contrast, the latter way tends to store the bred $^{233}$U out of the core until there is enough amount to start a new TMSR \cite{zou2018transition}.
+Meanwhile, Zou, et al.
+studied the transitioning to thorium fuel cycle in a small modular Th-based molten salt reactor (smTMSR) using TRUs as startup fuel.
+They concluded that the transition to thorium fuel cycle can be achieved in thermal smTMSR with a proper fuel fraction \cite{zou2018preliminary}.
+Heuer, et al., discussed the transition characteristics of the \gls{MSFR} under different launching scenarios (e.g., enriched uranium and TRU), they concluded that starting the Thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.
 
-Indeed, there are various researches that revolve around starting the 
-\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these 
-researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling, 
-ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019, 
-heuer2014towards,fiorina2013investigation}, while little focus on 
-thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary, 
-zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other 
-fissile materials (except $^{233}$U) was not studied before. Therefore, 
-the main object of the present paper is to discuss the simulation of the 
-\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with 
-different initial fissile materials and without any external feed of $^{233}$U 
-to achieve the thorium fuel cycle transition. We investigated five different  
-initial fissile materials: \gls{LEU}, Pu, and \gls{TRU} from LWR SF 
-\cite{de2000scenarios}. Moreover, two different feed scenarios were selected:
+Indeed, there are various researches that revolve around starting the MSRs with fissile materials alternative to $^{233}$U.
+Many of these researches focus on the fast-spectrum MSRs \cite{ashraf2019modeling,ashraf2018nuclear,heuer2014towards,fiorina2013investigation}, while little focus on thermal-spectrum MSRs \cite{betzler2016modeling,zou2018preliminary,zou2018transition}.
+Nevertheless, starting the \gls{SD-TMSR} with other fissile materials (except $^{233}$U) not found in the literature.
+Therefore, the main object of the present paper is to discuss the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition.
+To do that, we investigate five types of initial fissile materials based on \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SF and $^{233}$U \cite{de2000scenarios}.
+Moreover, two different feed mechanisms are used as follows:
+
 \begin{itemize}
-	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
-	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.
+	\item Continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
+\cite{betzler2016modeling}.
+	\item Continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
 \end{itemize}
+
+All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30.
+We used the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling.
+SERPENT-2 uses an internal calculation routine for solving the set of Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}.
+Additionally, SERPENT-2 allows us to conduct the burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.
+
 This present paper is organized as follows: after an introduction about \gls{MSR} systems, the model description is discussed in section 2.

### 2019-10-10 paper/methods.tex
Andrei's comments impelemented Abstract & introduction

--- 2019-09-27 paper/methods.tex
@@
 This can be done by set the flow rate of gaseous \gls{FPs} and other materials from the fuel to the \texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and soluble metals except protactinium).}.
-Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, \texttt{pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}.
+Specifically, protactinium was removed from the fuel with a certain flow rate into the external tank, \texttt{pa-decay tank}, to decay and produce $^{233}$U\footnote{The $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ $\approx$ $27$ $d$.}.
 The produced $^{233}$U is used as a fresh fissile fuel and the residual $^{233}$U is the net production of $^{233}$U.

### 2019-10-11 paper/introduction.tex
introduction & method
Abstract, introduction & method after Andrei's revision

--- 2019-10-10 paper/introduction.tex
@@
 The \gls{GIF} has defined eight technology goals for the next generation
-nuclear systems. These goals are: safety and reliability, economics,
-sustainability, non-proliferation and physical protection
-\cite{doe2002technology}. The \gls{MSR} has many advantages that consistent
+nuclear systems.
+These goals have been defined in four broad areas: safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}.
+The \gls{MSR} has many advantages that consistent
 with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online
@@
 Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR}
-under different launching scenarios (e.g., enriched uranium and TRU)
-\cite{heuer2014towards}.
+under different launching scenarios (e.g., enriched uranium and TRU) they concluded that starting the Thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.
 
@@
 to achieve the thorium fuel cycle transition. We investigated five different
-initial fissile materials: \gls{LEU}, Pu, and \gls{TRU} from LWR SF
-\cite{de2000scenarios}. Moreover, two different feed scenarios were selected:
+initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed scenarios were selected:
+
 \begin{itemize}
-	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay 
-	tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. 
+	\item Continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
 \cite{betzler2016modeling}.
-	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or 
-	part of $^{233}$U from \texttt{Pa-decay tank}.
+	\item Continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
 \end{itemize}
+
+All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30.
+We used the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling.
+SERPENT-2 uses an internal calculation routine for solving the set of Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}.
+Additionally, SERPENT-2 allows us to conduct the burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.
+
 This present paper is organized as follows: after an introduction about 
@@
 %the results and discussion. Finally, section 6 summarizes the conclusions.
-
-% State the objectives of the work and provide an adequate background, avoiding
-% a detailed literature survey or a summary of the results.

### 2019-10-11 paper/methods.tex

--- 2019-10-10 paper/methods.tex
@@
 The general composition of the liquid fuel salt in this work is 70LiF - 
-17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (misture of 
+17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (mixture of 
 thorium and other actinides). The aim of this paper is to simulate the  

### 2019-10-11 paper/methods.tex

@@
 \begin{table}  %[!ht]
-	\caption{Reactor-grade plutonium vector \cite{marka1993explosive}}
+	\caption{Reactor-grade plutonium vector (Mass fraction \%) \cite{marka1993explosive}}
 	\vspace{0.1in}
@@
 \begin{table}  %[!ht]
-	\caption{\gls{TRU} vector (\%) \cite{de2000scenarios}}
+	\caption{\gls{TRU} vector (Mass fraction \%) \cite{de2000scenarios}}
 	\vspace{0.1in}
@@
 from the fuel with a certain flow rate into the external tank, 
-\texttt{pa-decay tank}\footnote{An imaginary tank used to store protactinium 
-extracted from the core.}, to decay and produce $^{233}$U\footnote{The 
+\texttt{pa-decay tank}, to decay and produce $^{233}$U\footnote{The 
 $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
@@
 routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the 
-isotopes during reactor operation \cite{aufiero2013extended}. The mass of the 
-fissile and fertile materials needed to achieve criticality is calculated at 
-the end of the cycle. Then, this mass is added to the core at the beginning of 
-the cycle by a certain flow rate.
+isotopes during reactor operation \cite{aufiero2013extended}. Specifically, we have to determine the mass flow ($mflow$), which is the rate by 
+which elements or nuclides are transferred between materials. After that, the 
+transfer rates should be connected to materials with a reprocessing scheme. 
+Finally, we have to link the reprocessing schemes to depletion histories. In 
+the present work, we adjusted the transfer rates of fresh fuel to maintain core 
+criticality and to keep fuel salt inventory constant during burnup. The feed constant calculation procedures are summarized as follows:
+\begin{enumerate}
+	\item The simulation started without any injection of refueling materials (i.e. with only removing of FPs and Pa).
+	\item After first depletion calculation step, we checked the total mass density of FPs and Pa in \texttt{FP-waste tank} and \texttt{pa-tank}, respectively.
+	\item A simple calculation yields the amount of Th and $^{233}$U that must be added during this cycle (mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa).
+	\item Dividing this mass by time and inventory of refueling material gave the corresponding feed constant.
+\end{enumerate}
+The cycle calculation ran iteratively until the burnup reached the desired worth.
 

### 2019-10-11 paper/methods.tex
adding refueling tables in the Appendix

@@
-\section{Model description}
+\section{Model description} \label{Model-description}
 \subsection{Geometry}
@@
 thorium and other actinides). The aim of this paper is to simulate the  
-operation of \gls{SD-TMSR} for 60 years with different startup fissile 
+operation of \gls{SD-TMSR} for 60 years with different start-up fissile 
 compositions and without any external feed of fissile $^{233}$U which we 
@@
 $GWd/t$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
-The molar composition of startup fuel for all five cases is listed in 
+The molar composition of start-up fuel for all five cases is listed in 
 Table~\ref{tab:table4}. Meanwhile, the corresponding initial nuclei 
@@
 \begin{table}  %[!ht]
-	\caption{Composition of startup fuel (mole\%)}
+	\caption{Composition of start-up fuel (mole\%)}
 	\vspace{0.1in}
@@
 
-\section{Methodology and tools}
+\section{Methodology and tools} \label{Methodology-and-tools}
 
@@
 
-\section{Feed and extraction rates}
+\section{Feed and extraction rates} \label{Feed-and-extraction-rates}
 In the present work, two different feed mechanisms are used. The first 
@@
 the heavy metals (HM) are changed during reactor operation to conserve the 
-total fuel mass and criticality.
+total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, Pu reactor-grade and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9} and \ref{tab:table10} in Appendix.
 

### 2019-10-11 paper/introduction.tex

@@
 	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
-fissile $^{233}$U inventory to startup new \glspl{MSR}. But $^{233}$U does not
+fissile $^{233}$U inventory to start-up new \glspl{MSR}. But $^{233}$U does not
 exist in the Earth's crust and can be produced from fertile $^{232}$Th only in
 the nuclear reactor. Therefore, it is required to examine alternative fissile
-materials (e.g., $^{235}$U) to replace the $^{233}$U in the startup fuel
+materials (e.g., $^{235}$U) to replace the $^{233}$U in the start-up fuel
 composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
@@
 time\footnote{Time required to produce enough amount of $^{233}$U to trigger a
-new SD-TMSR.} of $^{233}$U because in this case all startup fissile material
+	new SD-TMSR.} of $^{233}$U because in this case all start-up fissile material
 is being substituted by newly produced $^{233}$U.
 
-Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit
+Betzler \emph{et al.} discussed the simulation of the start-up of a MSBR unit
 cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial
@@
 cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU}
-as startup fuel. They concluded that the transition to thorium fuel cycle can
+as start-up fuel. They concluded that the transition to thorium fuel cycle can
 be achieved in thermal smTMSR with a proper fuel fraction 
@@
 thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary,
-zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other
+	zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} specifically with other
 fissile materials (except $^{233}$U) was not studied before. Therefore,
@@
 This present paper is organized as follows: after an introduction about 
-\gls{MSR} systems, the model description is discussed in section 2. 
-Methodology and tools is descried in section 3. Extraction and feed mechanisms 
-are addressed in section 4. Section 5 focuses on the results and discussion. 
-Finally, section 6 highlights the conclusions.
+\gls{MSR} systems, the model description is discussed in section \ref{Model-description}. 
+Methodology and tools is descried in section \ref{Methodology-and-tools}. Extraction and feed mechanisms 
+are addressed in section  \ref{Feed-and-extraction-rates}. Section \ref{Results-and-discussion} focuses on the results and discussion. 
+Finally, section \ref{Conclusion} highlights the conclusions.
 

### 2019-10-11 paper/results.tex
Appendix section and table numbers fixed.Minor table fixes in methods.

@@
-\section{Results and discussion}
+\section{Results and discussion} \label{Results-and-discussion}
 
@@
 
-The first mechanism adopts continuous feed flow of external thorium and $^{233}$U from \texttt{Pa-decay tank}.
-Hereinafter the first mechanism will be mentioned as the thorium feed mechanism.
-The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases.
-Besides, the initial fissile material fraction was increased for the five fuel salt compositions until the SD-TMS reactor was sufficiently critical at the Beginning Of Life (BOL).
+The first mechanism adopts continuous feed flow of external thorium and 
+$^{233}$U from \texttt{Pa-decay tank}. Hereinafter the first mechanism will be 
+mentioned as the thorium feed mechanism. The molar fraction of the heavy metal 
+in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
+Besides, the initial fissile material fraction was increased for the five fuel 
+salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
+the Beginning Of Life (BOL). 
 Figure~\ref{fig:keff1} illustrates the change of the effective multiplication with \gls{EFPY} for the thorium feed mechanism.

### 2019-10-11 paper/results.tex
Andrei's all changes after review.

@@
 the Beginning Of Life (BOL). 
-Figure~\ref{fig:keff1} illustrates the change of the effective multiplication with \gls{EFPY} for the thorium feed mechanism.
-As shown in Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) decreases sharply during the first 25 years of reactor operation for the first four cases.
-$k_{eff}$ decreases as a result of depletion of the initial fissile materials and generation of the neutron poisons (FPs).
-Thus, the reactor becomes subcritical within a relatively short time ($\approx$ $4$ $years$ in the \gls{TRU} case and $\approx$ $12$ $years$ in the Pu reactor-grade case).
-The amount of $^{233}$U generated in the \gls{SD-TMSR} is not enough to conserve the reactor criticality and overcome the neutron absorption in the initial fertile isotopes.
-Nevertheless, the continuous feed flow of thorium and $^{233}$U helps to operate the \gls{SD-TMSR} for a long period of time (the U-233 case).
-Additionally, the initial molar fraction in the LEU and Pu reactor-grade cases was increased more (see Figure~\ref{fig:keff1}) to counteract the absorption of neutrons in the non-fissile heavy metals added with the initial fuel salt.
-But $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.
-
+Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
+dynamics during reactor operation for the thorium feed mechanism. As shown in 
+Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
+decreases sharply during the first 25 years of reactor operation for the first 
+four cases. $k_{eff}$ decreases as a result of depletion of the initial 
+fissile materials and production of poisonous fission products. Thus, the 
+reactor becomes subcritical relatively quickly for alternative startup 
+compositions ($\approx$ $4$ $years$ in the \gls{TRU} case and $\approx$ $12$ 
+$years$ in the Pu reactor-grade case). The amount of $^{233}$U generated in 
+the \gls{SD-TMSR} is not enough to maintain the reactor criticality and 
+overcome parasitic neutron absorption. Nevertheless, 
+the continuous feed flow of thorium and $^{233}$U helps to operate the 
+\gls{SD-TMSR} for a long period of time (the U-233 case). Additionally, the 
+initial molar fraction in the LEU and Pu reactor-grade cases was increased 
+more (see Figure~\ref{fig:keff1}) to counteract the absorption of neutrons in 
+the non-fissile heavy metals added with the initial fuel salt. But $k_{eff}$ 
+still decreases below 1.0, as a result of increasing the non-fissile heavy 
+metals in the initial fuel \cite{betzler2016modeling}.
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{keff1.png}
+		\vspace{-0.5in}
 	\caption{The change of the effective multiplication factor during 60 \gls{EFPY} of reactor operation for thorium feed mechanism (confidence interval $\pm\sigma$ is shaded).} 
@@
 
-The second mechanism allows continuous feed flow of $^{233}$U from \texttt{Pa-decay tank} and Heavy Metal except for Th.
-Hereinafter the second mechanism will be mentioned as the non-thorium feed mechanism.
-Figure~\ref{fig:keff2} shows the change of the effective multiplication during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism.
-As shown in Figure~\ref{fig:keff2}, the SD-TMS reactor was sufficiently critical at the Beginning Of Life (BOL).
-Both Pu reactor-grade and TRU case show promising results relative to the other two cases (i.e.
-LEU and Pu+LEU).
-For the Pu reactor-grade fuel salt, the amount of $^{233}$U generated in the \gls{SD-TMSR} in addition to the external feed flow of Pu are sufficient to maintain the reactor criticality and overcome the neutron absorption in the initial non-fissile isotopes.
-This may be attributed to the fact that the spectrum in the Pu reactor-grade initial core is hardened that is more thorium is being converted to $^{233}$U.
-For the \gls{TRU} fuel salt, the amount of $^{233}$U and the external feed flow of TRU is barely enough to operate the reactor for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U.
-Nevertheless, $k_{eff}$ decreases with the burnup because the Minor Actinides\footnote{In the present work, the Minor Actinides (MA) include Np, Am and Cm.} (MA) accumulating in the core as a result of continuous TRU feed.
-As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU fuel are less attractive for non-thorium feed mechanism.
-The continuous LEU feed increases the amount of fertile $^{238}$U and consequently, reduces the feasibility of such fissile materials.
-The continuous feed of $^{233}$U without $^{232}$Th will lead to supercritical reactor, thus the $^{233}$U case is excluded from non-thorium feed mechanism.\\
-According to the $k_{eff}$ results, Pu reactor-grade and TRU fissile materials are selected and discussed in the following. 
+The second mechanism (non-thorium feed) allows continuous feed flow of 
+$^{233}$U from \texttt{Pa-decay tank} and external Heavy Metal (excluding Th). 
+Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
+during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism.
+As shown in Figure~\ref{fig:keff2}, the \gls{SD-TMSR} reactor was sufficiently 
+critical at the Beginning Of Life (BOL). Both Pu reactor-grade and TRU case 
+show promising results relative to the other two cases (LEU and Pu+LEU). 
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{keff2.png}
-	\caption{The change of the effective multiplication factor during 60 \gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence interval $\pm\sigma$ is shaded).} 
+			\vspace{-0.5in}
+	\caption{The change of the effective multiplication factor during 60 
+	\gls{EFPY} of reactor operation for non-thorium feed mechanism (confidence 
+	interval $\pm\sigma$ is shaded).} 
 	\label{fig:keff2}
@@
 
+For the Pu reactor-grade initial loading, the amount of $^{233}$U generated in 
+the \gls{SD-TMSR} in addition to the external feed flow of Pu is sufficient to 
+maintain the reactor criticality and overcome the neutron absorption in the 
+initial non-fissile isotopes. This may be attributed to the fact that the 
+spectrum in the Pu reactor-grade initial core is hardened that is more thorium 
+is being converted to $^{233}$U.
+
+For the \gls{TRU} fuel salt, the amount of 
+$^{233}$U and the external feed flow of TRU is barely enough to operate the 
+reactor for a long period of time ($\approx$ $40$ $years$) without any 
+external feed of $^{233}$U. Nevertheless, $k_{eff}$ decreases with the burnup 
+because the \glspl{MA}\footnote{In the present work, the Minor Actinides 
+(MA) include Np, Am and Cm.} accumulating in the core as a result of 
+continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU 
+fuel are less attractive for non-thorium feed mechanism. The continuous LEU 
+feed increases the amount of fertile $^{238}$U and consequently, reduces the 
+feasibility of such fissile materials. The continuous feed of $^{233}$U 
+without $^{232}$Th will lead to supercritical reactor, thus the $^{233}$U case 
+is excluded from non-thorium feed mechanism study. According to the $k_{eff}$ 
+results, Pu reactor-grade and TRU are only alternative fissile materials that  
+can be used to startup and maintain operation of the \gls{SD-TMSR}.
+
 \subsection{Pu reactor-grade, TRU, and $^{233}$U initial fuel}
-
-In this section, the simulation of the SD-TMSR with Pu reactor-grade and TRU fissile materials is discussed. Besides, the $^{233}$U case is listed for comparison.\\
-Figure~\ref{fig:refillCCC} demonstrates the dynamics of heavy metal refill rate during 60 \gls{EFPY} of SD-TMSR operation.
-The heavy metal refill rate was adjusted to maintain; the reactor criticality and total fuel mass almost constant\footnote{The variation of the total fuel mass is less than $0.1\%$} during the reactor operation.
-In $^{233}$U case, the mean values of $^{233}$U and $^{232}$Th refill rate are $1.77$ and $2.21$ $kg/d$, respectively.
-As well, in the Pu reactor-grade case, the mean values of $^{233}$U and Pu refill rate are $0.75$ and $2.75$ $kg/d$, respectively.
-In the TRU case, the mean values of $^{233}$U and TRU refill rate are $0.90$ and $2.0$ $kg/d$, respectively.
-
+In this section, the simulation of the SD-TMSR with Pu reactor-grade and TRU 
+fissile materials is discussed. Additionally, previously studied the $^{233}$U 
+case is listed for comparison \cite{ashraf2019whole_core}. 
+Figure~\ref{fig:refillCCC} demonstrates the dynamics of heavy metal refill 
+rate during 60 \gls{EFPY} of the SD-TMSR operation. The heavy metal refill 
+rate was adjusted to maintain the reactor critical and the total fuel mass 
+almost constant\footnote{The variation of the total fuel mass is less than 
+$0.1\%$} during the reactor operation. In $^{233}$U case, the mean values of 
+$^{233}$U and $^{232}$Th refill rate are $1.77$ and $2.21$ $kg/d$, 
+respectively. Similarly, in the Pu reactor-grade case, the mean values of 
+$^{233}$U and Pu refill rate are $0.75$ and $2.75$ $kg/d$, respectively. For  
+the TRU case, the mean values of $^{233}$U and TRU refill rate are $0.90$ and 
+$2.0$ $kg/d$, respectively.
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{refillCCC.png}
-	\caption{Dynamics of heavy metal refill rate during 60 \gls{EFPY} of reactor operation. Solid lines for $^{233}$U case, dashed lines for Pu reactor-grade case, and dotted lines for TRU case.}
+			\vspace{-0.5in}
+	\caption{Dynamics of heavy metal refill rate during 60 \gls{EFPY} of 
+		reactor operation. Solid lines for $^{233}$U case, dashed lines for Pu 
+		reactor-grade case, and dotted lines for TRU case.}
 	\label{fig:refillCCC}
@@
 
-Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC} describe the evolution of important isotopes for $^{233}$U, Pu and TRU cases respectively.
-From Figure~\ref{fig:inventoryCCCC}, the mass of Pa in the fuel salt is almost constant and reaches $17.8$  $kg$ at the end of the operation time.
-In addition, the mass of Minor Actinides (MA) increases with time; however, by applying online reprocessing, its value remains relatively low.
-As well, the total mass of Pu increases with burnup.
-The level of Pu in the fuel correlates with the mass of the MA, and Pu.
-MA need more time to reach equilibrium.
-The total mass of U increases with burnup and reaches equilibrium after $\approx$ $27$ $years$.
-As shown in Figure~\ref{fig:inventoryCCCC}, refueling the core with Th helps maintain an almost constant inventory throughout the full operation time.\\
-The Pa extraction time was adjusted to be 30 seconds for Pu and TRU cases to avoid poisoning the core.
-Therefore, Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel for Pu and TRU cases is relatively low when compared to the $^{233}$U case.
-Major isotopes for the three cases reaches the equilibrium state after $\approx$ $30$ $years$ (see Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC}).
+Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC} demonstrate 
+the evolution of important isotopes for $^{233}$U, Pu and TRU cases 
+respectively. The mass of Pa in the fuel salt is almost constant and reaches 
+$17.8$  $kg$ at the end of the operation time 
+(Figure~\ref{fig:inventoryCCCC}). In addition, the mass of Minor Actinides 
+(MA) increases with time; however, by applying online reprocessing, its value 
+remains relatively low. Notably, the total mass of Pu increases with burnup. 
+The level of Pu in the fuel correlates with the mass of the MA, and Pu. MA 
+need more time to reach equilibrium. Uranium inventory increases during 
+operation and reaches equilibrium after $\approx$ $27$ $years$. 
+Figure~\ref{fig:inventoryCCCC} shows that refueling the core with Th helps 
+maintain an almost constant inventory throughout the full operation time.
 
+The protactinium extraction time was selected equal 30 seconds for Pu and TRU 
+cases to avoid poisoning the core. Therefore, 
+Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel for 
+Pu and TRU cases is relatively low when compared to the $^{233}$U case. Major 
+isotopes for all three cases reach the equilibrium state after $\approx$ $30$ 
+years (see Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC}).
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{inventoryCCCC.png}
-	\caption{Evolution of the important nuclides inventories for $^{233}$U case (MA involves Np, Am, Cm).}
+	\vspace{-0.4in}
+	\caption{Evolution of the important nuclides inventories for $^{233}$U 
+		case (MA involves Np, Am, Cm).}
 	\label{fig:inventoryCCCC}
 \end{figure}
-
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{inventoryPu_TRUCCC.png}
-	\caption{Evolution of the important nuclides inventories for Pu reactor-grade case (solid lines) and for TRU case (dashed lines).}
+	\vspace{-0.5in}
+	\caption{Evolution of the important nuclides inventories for Pu 
+		reactor-grade case (solid lines) and for TRU case (dashed lines).}
 	\label{fig:inventoryPu_TRUCCC}
@@
 
-Figure~\ref{fig:Th232CC} illustrates the variation of thorium mass in the fuel salt for $^{233}$U, Pu reactor-grade and TRU cases, respectively.
-In $^{233}$U case, we apply the thorium feed mechanism, thus thorium mass decreases by only $3.2$ $\%$ at the end of operation time (60 years).
-In contrast, thorium mass decreases significantly in Pu and TRU cases according to the non-thorium feed mechanism.
-Thorium mass decreases by $39.2$ $\%$ and $37.96$ $\%$ in Pu reactor-grade and TRU cases, respectively.
-The more decreasing in thorium mass, the more effective utilization of thorium fuel cycle.
-Consequently, the Pu reactor-grade initial fuel may help to utilize thorium fuel cycle more effective.
-
+Figure~\ref{fig:Th232CC} illustrates the variation of thorium inventory in the 
+fuel salt for $^{233}$U, Pu reactor-grade and TRU cases. For the  
+$^{233}$U case and the thorium feed mechanism, thorium inventory 
+decreases by only $3.2$\% at the end of life (EOL). In contrast, thorium 
+total mass decreases significantly in Pu and TRU cases when the non-thorium 
+feed mechanism was applied. Thus, thorium mass decreases by $39.2$\% and 
+$37.96$\% for Pu reactor-grade and TRU cases, respectively. The more   
+decreasing in thorium mass, the more effective utilization of thorium fuel 
+cycle. Consequently, the Pu reactor-grade initial fuel may help to utilize 
+thorium fuel cycle more effectively.
 \begin{figure}
@@
 
-Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for $^{233}$U, Pu reactor-grade and TRU cases, respectively.
-One can see that the mass of the $^{233}$U reaches the equilibrium state after $\approx$ $30$ $years$.
-Meanwhile, the amount of $^{233}$U is sufficient to maintain criticality in the three cases.
-
+Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt 
+for $^{233}$U, Pu reactor-grade and TRU cases. Notably, the mass of the 
+$^{233}$U reaches the equilibrium after $\approx$ $30$ $years$. Overall, the 
+amount of $^{233}$U is sufficient to maintain criticality in 
+the three cases.
 \begin{figure}
@@
 
-In the non-thorium feed mechanism, the SD-TMSR is continuously refueled for criticality, which increases the Pu proportion in the molten salt.
-According to the literature, the limit of Pu solubility in the FLiBe salt is $\approx$ $4.0$ $\%$ \cite{ignatiev2012progress,sood1975plutonium}.
-Figure~\ref{fig:PusolubilityCC} represents the Pu proportion in the fuel salt (mole\%).
-In $^{233}$U and Pu reactor-grade cases, the Pu proportion increases slightly but still below its solubility limit.
-On the other hand, the Pu proportion in the molten salt loaded by TRU increases with operation time and reaches the Pu solubility limit after $\approx$ $40$ $years$.
-This issue may be solved by increasing the reactor operation temperature and or reducing the HM initial inventory \cite{zou2018transition}.
-
+In the non-thorium feed mechanism, the SD-TMSR is continuously refueled for 
+criticality, which increases the Pu weight fraction in the molten salt. 
+According to the literature, the limit of Pu solubility in the FLiBe salt is 
+$\approx$$4.0$\% \cite{ignatiev2012progress,sood1975plutonium}. 
+Figure~\ref{fig:PusolubilityCC} represents the Pu fraction in the fuel salt 
+(mole\%). In $^{233}$U and Pu reactor-grade cases, the Pu fraction increases 
+slightly but still below its solubility limit. On the other hand, the Pu 
+fraction in the molten salt loaded by TRU increases during operation and 
+reaches the Pu solubility limit after $\approx$ $40$ years. This issue may 
+be solved by increasing the reactor operation temperature or reducing the 
+HM initial inventory \cite{zou2018transition}.
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{PusolubilityCC.png}
-	\caption{The Pu proportion in the fuel salt (mole\%).}
+	\caption{The Pu fraction in the fuel salt (mole\%).}
 	\label{fig:PusolubilityCC}
 \end{figure}
+\FloatBarrier
 
-Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U as a 
-function of burnup. In TRU case, the net production of $^{233}$U is almost 
+Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
+operation. For the TRU case, the net production of $^{233}$U is almost 
 zero, nevertheless, the reactor becomes subcritical after $40$ $years$ of 
 operation. In $^{233}$U and Pu reactor-grade cases, the net production of 
-$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$, 
-respectively at the end of operation lifetime. It worth noting that thorium 
-feed mechanism is applied in $^{233}$U case, while, non-thorium feed mechanism 
-is adopted in Pu reactor-grade cases.
-As shown in Figure~\ref{fig:NetCC}, after 26 years the net production of $^{233}$U reaches $1.3$ $t$; this is sufficient to start-up another \gls{SD-TMSR}.
-Similarly, one can see that the same amount of $^{233}$U (i.e.
-$1.3$ $t$) can be achieved after $\approx$ $4.5$ $years$ if we applied the non-thorium feed mechanism on the SD-TMSR that initially loaded by Pu reactor-grade alternative to $^{233}$U.
-In addition, Figure~\ref{fig:NetCC} also shows that the net production of $^{233}$U during the first 455 days is negative, thus about $175.28$ $kg$ of $^{233}$U must be added during this period.
-In conclusion, the thorium fuel cycle transition can be achieved by selecting the proper feed mechanism and initial fissile material.
-
+$^{233}$U increases with burnup and reaches at the end of operation lifetime 
+about $1.77$ $t$ and $10$ $t$, respectively. As shown in 
+Figure~\ref{fig:NetCC}, after 26 years the net production of $^{233}$U reaches 
+$1.3$ $t$; this is sufficient to start-up another \gls{SD-TMSR}. Similarly, 
+one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
+after $\approx$ $4.5$ $years$ if we applied the non-thorium feed mechanism on 
+the SD-TMSR that initially loaded by Pu reactor-grade alternative to 
+$^{233}$U. In addition, Figure~\ref{fig:NetCC} also shows that for $^{233}$U 
+case the net production of $^{233}$U during the first 455 days is negative, 
+thus about $175.28$ $kg$ of $^{233}$U must be added during this period. In 
+conclusion, the thorium fuel cycle transition can be achieved by selecting the 
+proper feed mechanism and initial fissile material. 
 \begin{figure}
@@
 \subsection{Neutron spectrum}
-
 Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
 lethargy for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
-MeV for the $^{233}$U, Pu reactor-grade, and TRU started case. In $^{233}$U 
+MeV for the $^{233}$U, Pu reactor-grade, and TRU startup cases. In $^{233}$U 
 case, at the EOL, the neutron spectrum is harder than at BOL due to the 
@@
 (see Figure~\ref{fig:U233CC}), the neutron spectrum softens and becomes 
-similar to a thermal spectrum of the TMSR.
-
+similar to a initial thermal spectrum of $^{233}$U fueled \gls{SD-TMSR}. The 
+comparison between the two feed mechanisms with different types of initial 
+fuel is listed in Table~\ref{tab:comp_feeds}. 
  \begin{figure}
  	\centering
- 	\includegraphics[width=\textwidth]{spectrumFLUX110vC.png}
+ 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
+ 			\vspace{-0.4in}
  	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for $^{233}$U, Pu reactor-grade, and TRU case.}
@@
 \end{figure}
-
-The comparison between the two feed mechanisms with different types of initial fuel is listed in Table~\ref{tab:table7}.
-
-\begin{table} % [!ht]
-	\centering
-	\caption{Comparison between the two feed mechanisms for the five different types of initial fuel.}
+\begin{table}  [!hb]
+	\begin{minipage}{\linewidth}
+		\renewcommand\footnoterule{}
+		\renewcommand{\thefootnote}{\alph{footnote}}
+	\caption{Comparison between the two feed mechanisms for the five different 
+	types of initial fuel.}
+		\label{tab:comp_feeds}
 		\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{l s s s s s }  %{\textwidth}
+	\begin{tabularx}{\textwidth}{p{0.22\textwidth} X p{0.18\textwidth} 
+	p{0.14\textwidth} X X 
+	}  %{\textwidth}
 		\hline
-		\backslashbox{Feed\\ mechanism}{Initial\\ fuel}& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79 wt-\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
+		Feed mechanism & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) & Pu 
+		reactor-grade & \gls{TRU}& $^{233}$U \\
 		\hline
-		Thorium feed mechanism&Not work&Not work&Not work&Not work& Work\\
-		Non-thorium feed mechanism &Not work&Not work&Work well with positive net production of $^{233}$U &Work for $40$ $years$ with net production of $^{233}$U = zero & Not examine (supercritical reactor)\\
+		Thorium feed\\ mechanism&\xmark&\xmark&\xmark&\xmark& \cmark \\
+		Non-thorium feed\\ mechanism &\xmark&\xmark&\cmark\footnotemark[1] 
+		&\cmark\footnotemark[2] & \xmark\footnotemark[3] \\
 		\hline
 	\end{tabularx}
-	\label{tab:table7}
+			\vspace{-1.5ex}%
+		\footnotetext[1]{Positive $^{233}$U net production and critical 
+		configuration for 60 years of operation.}
+		\footnotetext[2]{Zero $^{233}$U net production and critical 
+		configuration for 40 years of operation.}		
+		\footnotetext[3]{Too large and increasing $k_{eff}$ during 
+		lifetime.}		
+	\end{minipage}
 \end{table}

### 2019-10-11 paper/conclusion.tex

--- 2019-09-10 conclusion.tex
@@
-\section{Conclusion}
+\section{Conclusion} \label{Conclusion}
 
-In the present paper, five different types of initial fissile materials have been studied for transitioning to thorium fuel cycle in the \gls{SD-TMSR}.
-The molar composition of startup fuel for all five cases is listed in Table~\ref{tab:table4}, as well, the inventories in Table~\ref{tab:table5}.
-We adopted two different feed mechanisms; thorium feed mechanism and non-thorium feed mechanism.
-The whole-core of the SD-TMSR was simulated with Pu reactor-grade, TRU, and $^{233}$U as initial fissile materials.
-Besides, the variation of the effective multiplication factor $k_{eff}$, inventory, and other neutronic parameters have been investigated.
-Results demonstrated that continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for Th/$^{233}$U startup fuel.
-Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ $years$) without any external feed of $^{233}$U.
-in addition, the Pu proportion in fuel salt has been calculated and found to be below the solubility limit.
-Finally, the neutron flux spectrum for the three selected cases has been described.
+Five different types of initial fissile loadings have been studied for 
+transitioning to the thorium fuel cycle in the \gls{SD-TMSR}. We 
+adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
+feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
+performed with Pu reactor-grade, TRU, and $^{233}$U as initial fissile 
+materials. Additionally, the dynamics of the effective multiplication factor 
+$k_{eff}$, major isotopes mass, neutron energy spectrum, and essential safety 
+parameters have been investigated.
+
+Results demonstrated that continuous flow of Pu reactor-grade allows the 
+transition to the thorium fuel cycle in a relatively short time ($\approx$ 
+$4.5$ years) compared to $26$ $years$ for Th/$^{233}$U startup fuel. 
+Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility 
+of operating the SD-TMSR for an extended time ($\approx$ $40$ $years$) 
+without any external feed of $^{233}$U. Notably, the Pu mass fraction in 
+fuel salt was calculated and found to be below the solubility limit.
+
+Additionally, the neutron energy spectrum shift during the reactor operation 
+for the Pu and TRU cases is different from the $^{233}$U fueling scenario. 
+Indeed, the spectrum hardening for $^{233}$U initial fissile isotope during 
+operation, but softening for the Pu and TRU cases. Notably, the most 
+significant neutron energy spectrum shift was obtained for reactor-grade Pu 
+startup loading.
+
+We compared the operational and safety parameters of the \gls{SD-TMSR} for all 
+three startup fuels at both initial and equilibrium states. The total 
+temperature coefficient of reactivity is negative and relatively large in all 
+cases. For TRU case, the coefficient remained almost constant during 
+operation: $-4.79\pm0.12$ $pcm/K$ and $-4.76\pm0.11$ $pcm/K$ for the initial 
+and equilibrium states, respectively. For reactor-grade Pu, the coefficient 
+absolute value decreased from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
+60 years of operation. Finally, the six factors evolution during the operation 
+were calculated for all three cases, and these parameters can be used to 
+design the reactivity control system of the \gls{SD-TMSR}.
 
 \section{Future work}
+The authors intend to verify obtained results using another tool: batch-wise 
+code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
+Moreover, in further simulations, we intend to take into account the delayed 
+neutron precursor drift. The \gls{SD-TMSR} reactivity control system has not 
+been introduced in the literature yet. Thus, the control rods design and 
+configuration might be suggested in the nearest future.
 
-%The authors intend to compare the present results and results from SaltProc batch-wise code \cite{rykhlevskii2019modeling} in future work.
-Moreover, they will consider the delayed neutron precursor drift.
-Future work will also consider the benchmark study based on other codes and models.
-The authors intend to conduct a sensitivity study to evaluate the impact of the radial reflector material and its thickness.
-In addition, they will study the impact of \gls{FPs} removal (i.e.
-only reprocessing without refueling) on reactivity and neutron economy.
+Lastly, an additional area to explore is the accident safety analysis which 
+requires high-fidelity multi-physics model of the \gls{SD-TMSR} with the 
+coupled neutronics/thermal-hydraulics software, Moltres 
+\cite{lindsay_introduction_2018}. The full-core SERPENT-2 model of the 
+\gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in this work, 
+would be employed to generate problem-oriented nuclear data libraries for 
+Moltres. The ultimate goal of this effort is to develop a 
+fast-running computational model for studying the dynamics behavior of generic 
+\glspl{MSR}, performing safety analysis for different accident scenarios and 
+optimizing design of various reactor concepts.
 

### 2019-10-11 paper/methods.tex

@@
 \begin{table}  %[!ht]
-	\caption{Reactor-grade plutonium vector (Mass fraction \%) \cite{marka1993explosive}}
+	\caption{Reactor-grade plutonium vector (wt.\%) \cite{marka1993explosive}}
 	\vspace{0.1in}
@@
 \begin{table}  %[!ht]
-	\caption{\gls{TRU} vector (Mass fraction \%) \cite{de2000scenarios}}
+	\caption{\gls{TRU} vector (wt.\%) \cite{de2000scenarios}}
 	\vspace{0.1in}
@@
 \begin{table}  %[!ht]
-	\caption{Composition of start-up fuel (mole\%)}
+	\caption{Composition of startup fuel (mole\%).}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{p{0.16\textwidth} X p{0.17\textwidth} 
+	\begin{tabularx}{\textwidth}{p{0.13\textwidth} X p{0.18\textwidth} 
 	p{0.14\textwidth} X X}
 		\hline
-		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt\%) 
+		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) 
 		& Pu reactor-grade & \gls{TRU}& $^{233}$U \\
@@
 \begin{table}  %[!ht]
-	\caption{Initial nuclei inventories (in grams) of the SD-TMSR with different types of fuel.}
+	\caption{Initial heavy metal inventories (excluding $^{232}$Th) for 
+	different initial fissile loadings (g).}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{s s s s s s}
+	\begin{tabularx}{\textwidth}{X X p{0.18\textwidth} 
+	p{0.14\textwidth} X X}
 		\hline
-		\vspace{0.1in}
-		Molecule& \gls{LEU} (19.79\%) & Pu mixed with enriched U (19.79\%) & Pu reactor-grade & \gls{TRU}& $^{233}$U \\
-		\hline
+		Nuclide & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) & Pu 
+		reactor-grade & \gls{TRU}& $^{233}$U \\	\hline
 		$^{232}$Th       &6.24E+07 & 4.67E+07 &   6.75E+07			& 5.44E+07	& 7.69E+07    \\ 
@@
 		$^{244}$Cm		 &        & &&2.01E+05&  \\
-		$^{245}$Cm		 &        & &&			2.51E+04	&   \\
-		&         &&		&		&\\
-		Total mass \\of HM without $^{232}$Th	& 1.60E+07& 3.20E+07&1.13E+07&  2.51E+07&   1.30E+06  \\
+		$^{245}$Cm		 &        & &&			2.51E+04	&   \\ \hline
+		Total            & 1.60E+07& 3.20E+07&1.13E+07&  2.51E+07&   1.30E+06  
+		\\
 		\hline

### 2019-10-14 paper/abstract.tex
Osama's changes after whole manuscript review including answers #13

@@
 Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance.
-The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as start-up fissile material.
+The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material.
 Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials.
-This work investigated the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at start-up: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} spent fuel with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF} and finally $^{233}$U.
+This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF} and finally $^{233}$U.
 The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}.
 The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work.
-The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ $years$) compared to $26$ $years$ for $^{233}$U start-up fuel.
+Additionally, the neutron spectrum shift during the reactor operation was calculated.
+The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel.
 Finally, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.

### 2019-10-14 paper/introduction.tex
Osama's changes after whole manuscript review including answers #13

--- 2019-10-11 paper/introduction.tex
@@
 circulates through the core and allows transferring fission heat from reactor
-core to heat exchanger.
+core to \glspl{IHX}.
 
@@
 
-Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit
-cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial
+Betzler \emph{et al.} (2016), discussed the simulation of the startup of a MSBR unit
+cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent nuclear fuel (SNF) as initial
 fissile materials \cite{betzler2016modeling}. They concluded that the 
-plutonium vector extracted from LWR SF is the best alternative source to 
-$^{233}$U because it has the highest ratio of fissile isotopes
-\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for
+plutonium vector extracted from LWR SNF is the best alternative source to 
+$^{233}$U because it has high ratio of fissile isotopes
+\cite{betzler2016modeling}. Zou \emph{et al.} (2018), introduced two approaches for
 the thorium fuel cycle transition in \gls{TMSR}: (1) in-core transition and 
@@
 core until there is enough amount to start a new TMSR \cite{zou2018transition}.
-Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel
+Additionally, Zou \emph{et al.} (2018), studied the transitioning to thorium fuel
 cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU}
@@
 
-Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR}
-under different launching scenarios (e.g., enriched uranium and TRU) they concluded that starting the Thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.
+Heuer \emph{et al.} (2014), discussed the transition characteristics of the \gls{MSFR}
+under different launching scenarios (e.g., enriched uranium and TRU) they concluded that starting the thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.
 
@@
 \glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
-researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling,
+researches focus on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
 	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
-heuer2014towards,fiorina2013investigation}, while little focus on
-thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary,
-zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other
+	fiorina2013investigation}, while little focus on
+thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
+	zou2018transition,zou2018preliminary}. Nevertheless, simulating the operation of the \gls{SD-TMSR} concept with other
 fissile materials (except $^{233}$U) was not studied before. Therefore,
@@
 to achieve the thorium fuel cycle transition. We investigated five different
-initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed scenarios were selected:
+initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SNF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed mechanisms were selected:
 
 \begin{itemize}
-	\item Continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
+	\item Thorium feed mechanism: continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
 \cite{betzler2016modeling}.
-	\item Continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
+	\item Non-thorium feed mechanism: continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
 \end{itemize}
 
-All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30.
+All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30 \cite{leppanen2014serpent}.
 We used the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling.

### 2019-10-14 paper/results.tex
Osama's changes after whole manuscript review including answers #13

@@
 
-The first mechanism adopts continuous feed flow of external thorium and 
-$^{233}$U from \texttt{Pa-decay tank}. Hereinafter the first mechanism will be 
-mentioned as the thorium feed mechanism. The molar fraction of the heavy metal 
+The thorium feed mechanism adopts continuous feed flow of external thorium (from Th stockpile) and 
+$^{233}$U from \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
 in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
-Besides, the initial fissile material fraction was increased for the five fuel 
+Additionally, the initial fissile material fraction was increased for the five fuel 
 salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
@@
 reactor becomes subcritical relatively quickly for alternative startup 
-compositions ($\approx$ $4$ $years$ in the \gls{TRU} case and $\approx$ $12$ 
-$years$ in the Pu reactor-grade case). The amount of $^{233}$U generated in 
+compositions ($\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
+years in the Pu reactor-grade case). The amount of $^{233}$U generated in 
 the \gls{SD-TMSR} is not enough to maintain the reactor criticality and 
-overcome parasitic neutron absorption. Nevertheless, 
+counteract parasitic neutron absorption. Nevertheless, 
 the continuous feed flow of thorium and $^{233}$U helps to operate the 
-\gls{SD-TMSR} for a long period of time (the U-233 case). Additionally, the 
-initial molar fraction in the LEU and Pu reactor-grade cases was increased 
-more (see Figure~\ref{fig:keff1}) to counteract the absorption of neutrons in 
-the non-fissile heavy metals added with the initial fuel salt. But $k_{eff}$ 
-still decreases below 1.0, as a result of increasing the non-fissile heavy 
-metals in the initial fuel \cite{betzler2016modeling}.
+\gls{SD-TMSR} for a lifetime-long period of time (Figure~\ref{fig:keff1} (U-233 case)). 
+Additionally, the molar fraction of the LEU and Pu reactor-grade in the initial fuel composition was increased
+more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and Pu reactor-grade cases)).
+Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.
+
 \begin{figure}
@@
 
-The second mechanism (non-thorium feed) allows continuous feed flow of 
+The non-thorium feed mechanism allows continuous feed flow of 
 $^{233}$U from \texttt{Pa-decay tank} and external Heavy Metal (excluding Th). 
+Under the non-thorium feed mechanism, four different initial fissile materials were studied: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, and \gls{TRU}. The continuous feed of $^{233}$U 
+without $^{232}$Th will lead to supercritical reactor, thus the $^{233}$U case 
+is excluded from non-thorium feed mechanism study.
+The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
+Additionally, the initial fissile material fraction was increased for the four fuel 
+salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
+the Beginning Of Life (BOL). 
 Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
-during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism.
-As shown in Figure~\ref{fig:keff2}, the \gls{SD-TMSR} reactor was sufficiently 
-critical at the Beginning Of Life (BOL). Both Pu reactor-grade and TRU case 
-show promising results relative to the other two cases (LEU and Pu+LEU). 
+during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both Pu reactor-grade and TRU case 
+show promising results relative to the other two cases (LEU and Pu+LEU) (see Figure~\ref{fig:keff2}). 
 \begin{figure}
@@
 
-For the Pu reactor-grade initial loading, the amount of $^{233}$U generated in 
-the \gls{SD-TMSR} in addition to the external feed flow of Pu is sufficient to 
-maintain the reactor criticality and overcome the neutron absorption in the 
-initial non-fissile isotopes. This may be attributed to the fact that the 
-spectrum in the Pu reactor-grade initial core is hardened that is more thorium 
-is being converted to $^{233}$U.
-
+For the Pu reactor-grade case, the amount of $^{233}$U generated in the \gls{SD-TMSR} in addition to the external feed flow of Pu is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs.
 For the \gls{TRU} fuel salt, the amount of 
 $^{233}$U and the external feed flow of TRU is barely enough to operate the 
-reactor for a long period of time ($\approx$ $40$ $years$) without any 
-external feed of $^{233}$U. Nevertheless, $k_{eff}$ decreases with the burnup 
+reactor for a long period of time ($\approx$ $40$ years) without any 
+external feed of $^{233}$U ($^{233}$U used only from \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
 because the \glspl{MA}\footnote{In the present work, the Minor Actinides 
@@
 feed increases the amount of fertile $^{238}$U and consequently, reduces the 
-feasibility of such fissile materials. The continuous feed of $^{233}$U 
-without $^{232}$Th will lead to supercritical reactor, thus the $^{233}$U case 
-is excluded from non-thorium feed mechanism study. According to the $k_{eff}$ 
+feasibility of such fissile materials. According to the $k_{eff}$ 
 results, Pu reactor-grade and TRU are only alternative fissile materials that  
@@
 almost constant\footnote{The variation of the total fuel mass is less than 
-$0.1\%$} during the reactor operation. In $^{233}$U case, the mean values of 
+$0.1\%$} during the reactor operation. In the $^{233}$U case, the mean values of 
 $^{233}$U and $^{232}$Th refill rate are $1.77$ and $2.21$ $kg/d$, 
@@
 the evolution of important isotopes for $^{233}$U, Pu and TRU cases 
-respectively. The mass of Pa in the fuel salt is almost constant and reaches 
-$17.8$  $kg$ at the end of the operation time 
-(Figure~\ref{fig:inventoryCCCC}). In addition, the mass of Minor Actinides 
-(MA) increases with time; however, by applying online reprocessing, its value 
-remains relatively low. Notably, the total mass of Pu increases with burnup. 
-The level of Pu in the fuel correlates with the mass of the MA, and Pu. MA 
-need more time to reach equilibrium. Uranium inventory increases during 
-operation and reaches equilibrium after $\approx$ $27$ $years$. 
-Figure~\ref{fig:inventoryCCCC} shows that refueling the core with Th helps 
+respectively. For the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}), the mass of Pa in the fuel salt is almost constant and reaches 
+$17.8$  $kg$ at the end of the operation time. 
+Additionally, the mass of Minor Actinides (MA) and Pu increases with time.
+The level of Pu in the fuel salt correlates with the mass of the MA.
+Moreover, MA needs more time to reach equilibrium than Pu.
+Uranium inventory increases during
+operation and reaches equilibrium after $\approx$ $27$ years. Figure~\ref{fig:inventoryCCCC} shows that refueling the core with Th helps 
 maintain an almost constant inventory throughout the full operation time. 
-
-The protactinium extraction time was selected equal 30 seconds for Pu and TRU 
-cases to avoid poisoning the core. Therefore, 
-Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel for 
-Pu and TRU cases is relatively low when compared to the $^{233}$U case. Major 
+For Pu and TRU cases (Figure~\ref{fig:inventoryPu_TRUCCC}), the protactinium extraction time was selected equal 30s 
+to avoid poisoning the core. Therefore, 
+Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
+is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
 isotopes for all three cases reach the equilibrium state after $\approx$ $30$ 
@@
 	\caption{Evolution of the important nuclides inventories for $^{233}$U 
-		case (MA involves Np, Am, Cm).}
+		case (MA involves Np, Am, Cm) \cite{ashraf2019whole_core}.}
 	\label{fig:inventoryCCCC}
@@
 Figure~\ref{fig:Th232CC} illustrates the variation of thorium inventory in the 
-fuel salt for $^{233}$U, Pu reactor-grade and TRU cases. For the  
-$^{233}$U case and the thorium feed mechanism, thorium inventory 
-decreases by only $3.2$\% at the end of life (EOL). In contrast, thorium 
-total mass decreases significantly in Pu and TRU cases when the non-thorium 
+fuel salt for $^{233}$U, Pu reactor-grade and TRU cases. The thorium inventory 
+decreases in the $^{233}$U case by only $3.2$\% at the End Of Life (EOL) when the thorium 
+feed mechanism was applied. 
+In contrast, thorium total mass decreases significantly in Pu and TRU cases when the non-thorium 
 feed mechanism was applied. Thus, thorium mass decreases by $39.2$\% and 
-$37.96$\% for Pu reactor-grade and TRU cases, respectively. The more   
-decreasing in thorium mass, the more effective utilization of thorium fuel 
-cycle. Consequently, the Pu reactor-grade initial fuel may help to utilize 
-thorium fuel cycle more effectively.
+$37.96$\% for Pu reactor-grade and TRU cases, respectively.
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{Th232CC.png}
-	\caption{The variation of thorium mass in the fuel salt for $^{233}$U, Pu reactor-grade and TRU cases, respectively.}
+	\caption{The variation of thorium mass in the fuel salt for $^{233}$U, Pu reactor-grade, and TRU cases.}
 	\label{fig:Th232CC}
@@
 for $^{233}$U, Pu reactor-grade and TRU cases. Notably, the mass of the 
-$^{233}$U reaches the equilibrium after $\approx$ $30$ $years$. Overall, the 
+$^{233}$U reaches the equilibrium after $\approx$ $30$ years. Overall, the 
 amount of $^{233}$U is sufficient to maintain criticality in 
@@
 	\includegraphics[width=\textwidth]{U233CC.png}
-	\caption{Mass of $^{233}$U in the fuel salt for $^{233}$U, Pu reactor-grade and TRU case, respectively.}
+	\caption{Mass of $^{233}$U in the fuel salt for $^{233}$U, Pu reactor-grade, and TRU cases.}
 	\label{fig:U233CC}
@@
 
-In the non-thorium feed mechanism, the SD-TMSR is continuously refueled for 
-criticality, which increases the Pu weight fraction in the molten salt. 
+In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by HM (Pu and TRU) for 
+criticality, which increases the Pu molar fraction (mole\%) in the molten salt. 
 According to the literature, the limit of Pu solubility in the FLiBe salt is 
-$\approx$$4.0$\% \cite{ignatiev2012progress,sood1975plutonium}. 
+$\approx$ $4.0$ mole\% \cite{ignatiev2012progress,sood1975plutonium}. 
 Figure~\ref{fig:PusolubilityCC} represents the Pu fraction in the fuel salt 
-(mole\%). In $^{233}$U and Pu reactor-grade cases, the Pu fraction increases 
+(mole\%) for $^{233}$U, Pu reactor-grade and TRU cases, respectively. In $^{233}$U and Pu reactor-grade cases, the Pu fraction increases 
 slightly but still below its solubility limit. On the other hand, the Pu 
@@
 	\includegraphics[width=\textwidth]{PusolubilityCC.png}
-	\caption{The Pu fraction in the fuel salt (mole\%).}
+	\caption{The Pu fraction in the fuel salt (mole\%) for $^{233}$U, Pu reactor-grade, and TRU cases.}
 	\label{fig:PusolubilityCC}
@@
 Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
-operation. For the TRU case, the net production of $^{233}$U is almost 
-zero, nevertheless, the reactor becomes subcritical after $40$ $years$ of 
-operation. In $^{233}$U and Pu reactor-grade cases, the net production of 
+operation for $^{233}$U, Pu reactor-grade and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
+zero. 
+Although all produced $^{233}$U was used to refuel the core, the reactor was subcritical after $40$ years of operation (Figure~\ref{fig:keff2}).
+In $^{233}$U and Pu reactor-grade cases, the net production of 
 $^{233}$U increases with burnup and reaches at the end of operation lifetime 
 about $1.77$ $t$ and $10$ $t$, respectively. As shown in 
-Figure~\ref{fig:NetCC}, after 26 years the net production of $^{233}$U reaches 
-$1.3$ $t$; this is sufficient to start-up another \gls{SD-TMSR}. Similarly, 
+Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
+$1.3$ $t$; this is sufficient to startup another \gls{SD-TMSR}. Similarly, 
 one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
-after $\approx$ $4.5$ $years$ if we applied the non-thorium feed mechanism on 
+after $\approx$ $4.5$ years if we applied the non-thorium feed mechanism on 
 the SD-TMSR that initially loaded by Pu reactor-grade alternative to 
@@
 case the net production of $^{233}$U during the first 455 days is negative, 
-thus about $175.28$ $kg$ of $^{233}$U must be added during this period. In 
-conclusion, the thorium fuel cycle transition can be achieved by selecting the 
+thus about $175.28$ $kg$ of $^{233}$U must be added during this period. 
+In conclusion, the thorium fuel cycle transition can be achieved by selecting the 
 proper feed mechanism and initial fissile material. 
+Specifically, applied non-thorium feed mechanism on 
+the SD-TMSR loaded by Pu reactor-grade allows the 
+transition to the thorium fuel cycle after $\approx$ 
+$4.5$ years. Additionally, applied thorium feed mechanism on 
+the SD-TMSR loaded by $^{233}$U allows the 
+transition to the thorium fuel cycle after $26$ years of operation. 
+The comparison between the two feed mechanisms with different types of initial 
+fuel is listed in Table~\ref{tab:comp_feeds}.
+
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{NetCC.png}
-	\caption{Net production of $^{233}$U during burn-up period (60 \gls{EFPY}).}
+	\caption{Net production of $^{233}$U during burnup period (60 \gls{EFPY}) for $^{233}$U, Pu reactor-grade, and TRU cases.}
 	\label{fig:NetCC}
@@
 
-\subsection{Neutron spectrum}
-Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
-lethargy for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
-MeV for the $^{233}$U, Pu reactor-grade, and TRU startup cases. In $^{233}$U 
-case, at the EOL, the neutron spectrum is harder than at BOL due to the 
-accumulation of the Pu and other strong thermal neutron absorbers in the fuel 
-salt. For Pu reactor-grade and TRU cases, during the reactor operation, the 
-fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
-(see Figure~\ref{fig:U233CC}), the neutron spectrum softens and becomes 
-similar to a initial thermal spectrum of $^{233}$U fueled \gls{SD-TMSR}. The 
-comparison between the two feed mechanisms with different types of initial 
-fuel is listed in Table~\ref{tab:comp_feeds}. 
- \begin{figure}
- 	\centering
- 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
- 			\vspace{-0.4in}
- 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for $^{233}$U, Pu reactor-grade, and TRU case.}
- 	\label{fig:spectrumFLUX110vC}
-\end{figure}
-\begin{table}  [!hb]
+\begin{table}  [!h]
 	\begin{minipage}{\linewidth}
@@
 
+\subsection{Neutron spectrum}
+Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
+lethargy for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
+MeV for the $^{233}$U, Pu reactor-grade, and TRU cases at BOL and EOL. In $^{233}$U 
+case, at the EOL, the neutron spectrum is harder than at BOL due to the 
+accumulation of the Pu and other strong thermal neutron absorbers in the fuel 
+salt. For Pu reactor-grade and TRU cases, during the reactor operation, the 
+fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
+(see Figure~\ref{fig:U233CC}), the neutron spectrum softens and becomes 
+similar to a initial thermal spectrum of $^{233}$U fueled \gls{SD-TMSR}.
+ \begin{figure}
+ 	\centering
+ 	\includegraphics[width=1.01\textwidth]{spectrumFLUX110vC.png}
+ 			\vspace{-0.4in}
+ 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for $^{233}$U, Pu reactor-grade, and TRU cases.}
+ 	\label{fig:spectrumFLUX110vC}
+\end{figure}
+
 \subsection{Neutron flux}
@@
 for various initial fissile compositions demonstrated the different effects on 
-the SD-TMSR neutronics performance. For the Th/$^{233}$U, the thermal neutron 
+the SD-TMSR neutronics performance. For the $^{233}$U case, the thermal neutron 
 flux is suppressed at the equilibrium because fissile $^{233}$U in the core is 
@@
 
-Notably, more changes in thermal neutron flux shape and magnitude for  
+Notably, more changes in thermal neutron flux shape and magnitude for the 
 $^{233}$U case were observed in the inner core zone ($R\lesssim150$) than 
@@
 The \gls{FTC} is negative for all considered fuel compositions due to thermal 
-Doppler broadening of the resonance capture cross-sections in the thorium. For 
+Doppler broadening of the resonance capture cross-sections in the thorium. For the 
 $^{233}$U case, the \gls{FTC} decreases in magnitude by $-25\%$ due to neutron 
@@
 
-\subsection{Six Factor analysis}
+\subsection{Six factor analysis}
 The effective multiplication factor can be expressed as follows:

### 2019-10-14 paper/abstract.tex
Last edits in abstract.tex
Just a few minor grammar mistakes.

@@
 Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials.
-This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF} and finally $^{233}$U.
+This work investigated the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
 The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}.
@@
 Additionally, the neutron spectrum shift during the reactor operation was calculated.
-The results show that the continuous flow of Pu reactor-grade helps in transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel.
-Finally, using \gls{TRU} as initial fissile materials shows the possibility of operating the SD-TMSR for a long period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
+The results showed that the continuous flow of Pu reactor-grade helps transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel.
+Finally, using \gls{TRU} as initial fissile materials proved the possibility of operating the SD-TMSR for a extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
 \end{abstract}

### 2019-10-14 paper/abstract.tex
After Osama's comments

@@
 The results showed that the continuous flow of Pu reactor-grade helps transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel.
-Finally, using \gls{TRU} as initial fissile materials proved the possibility of operating the SD-TMSR for a extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
+Finally, using \gls{TRU} as initial fissile materials offers the possibility of operating the SD-TMSR for an extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
 \end{abstract}

### 2019-10-14 paper/introduction.tex
Minor changes before proofreading

@@
 fissile materials (except $^{233}$U) was not studied before. Therefore,
-the main object of the present paper is to discuss the simulation of the
+the main objective of the present paper is to discuss the simulation of the
 \gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
@@
 \cite{betzler2016modeling}.
-	\item Non-thorium feed mechanism: continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or part of produced $^{233}$U from \texttt{Pa-decay tank}.
+	\item Non-thorium feed mechanism: continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or fraction of $^{233}$U from \texttt{Pa-decay tank}.
 \end{itemize}

### 2019-10-14 paper/conclusion.tex

@@
 transition to the thorium fuel cycle in a relatively short time ($\approx$ 
-$4.5$ years) compared to $26$ $years$ for Th/$^{233}$U startup fuel. 
+$4.5$ years) compared to $26$ years for Th/$^{233}$U startup fuel. 
 Meanwhile, using \gls{TRU} as initial fissile materials shows the possibility 
-of operating the SD-TMSR for an extended time ($\approx$ $40$ $years$) 
-without any external feed of $^{233}$U. Notably, the Pu mass fraction in 
+of operating the SD-TMSR for an extended time ($\approx$ $40$ years) 
+without any external feed of $^{233}$U. Notably, the Pu molar fraction (mole\%) in 
 fuel salt was calculated and found to be below the solubility limit.
@@
 
-\section{Conflict of interest}
+\section{Declaration of Competing Interest}
 
-The authors declare no conflict of interest.
+The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

### 2019-10-14 paper/methods.tex

@@
 that acts as a radiation shielding. The \gls{SD-TMSR} pressure vessel holds 
-the fuel salt, graphite elements, reflector, shielding, intermediate heat 
-exchanger (IHX) and made of Ni-based (hastelloy N) alloy. The main 
+the fuel salt, graphite elements, reflector, shielding, \gls{IHX} and made of Ni-based (hastelloy N) alloy. The main 
 characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.
@@
 	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
-	SD-TMSR.}
+	SD-TMSR \cite{ashraf2019Preliminary}.}
 	\label{fig:ff}
@@
 thorium and other actinides). The aim of this paper is to simulate the  
-operation of \gls{SD-TMSR} for 60 years with different start-up fissile 
+operation of \gls{SD-TMSR} for 60 years with different startup fissile 
 compositions and without any external feed of fissile $^{233}$U which we 
 assumed is unavailable. For that reason, five different types of initial 
-fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF were 
+fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SNF were 
 considered:
@@
 	\item Pu reactor-grade \cite{marka1993explosive};
-	\item transuranic (TRU) elements from LWR SF \cite{de2000scenarios};
+	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios};
 	\item $^{233}$U for comparison purpose \cite{ashraf2019whole_core}.
@@
 recovered from the spent fuel composition of commercial \gls{PWR} with the 
-average discharge burnup $33$ $GWd/t$ and after $10$ years of cooling before 
+average discharge burnup $33$ $GWd/tHM$ and after $10$ years of cooling before 
 reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
-isotopic compositions of \gls{TRU} was taken for the SF of UOX \gls{PWR} 
+isotopic compositions of \gls{TRU} was taken for the SNF of UOX \gls{PWR} 
 (after one use, no multi-recycling) with the average discharge $60$ 
-$GWd/t$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
-The molar composition of start-up fuel for all five cases is listed in 
-Table~\ref{tab:table4}. Meanwhile, the corresponding initial nuclei 
+$GWd/tHM$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
+The molar composition of startup fuel for all five cases is listed in 
+Table~\ref{tab:table4}. Additionally, the corresponding initial nuclei 
 inventories with different types of fuel are summarized in 
@@
 \begin{table}  %[!ht]
-	\caption{Initial heavy metal inventories (excluding $^{232}$Th) for 
+	\caption{Initial heavy metal inventories for 
 	different initial fissile loadings (g).}
@@
 		$^{245}$Cm		 &        & &&			2.51E+04	&   \\ \hline
-		Total            & 1.60E+07& 3.20E+07&1.13E+07&  2.51E+07&   1.30E+06  
+		Total$^{\ast}$           & 1.60E+07& 3.20E+07&1.13E+07&  2.51E+07&   1.30E+06  
 		\\
@@
 	\end{tabularx}
+\begin{tablenotes}
+	\small
+	\item $^{\ast}$ Excluding $^{232}$Th inventory.
+\end{tablenotes}
 \label{tab:table5}
@@
 the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
-$36$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
+$12$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
 provides many benefits for MSRs. For example, it would reduce the initial 
@@
 	\item After first depletion calculation step, we checked the total mass density of FPs and Pa in \texttt{FP-waste tank} and \texttt{pa-tank}, respectively.
-	\item A simple calculation yields the amount of Th and $^{233}$U that must be added during this cycle (mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa).
+	\item A simple calculation yields the amount of \gls{HM} that must be added during this cycle:
+	\subitem 3a. For thorium feed mechanism: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
+	\subitem 3b. For non-thorium feed mechanism: mass of \gls{HM} (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
 	\item Dividing this mass by time and inventory of refueling material gave the corresponding feed constant.
@@
 \section{Feed and extraction rates} \label{Feed-and-extraction-rates}
-In the present work, two different feed mechanisms are used. The first 
-mechanism allows continuous feed flow of thorium from Th stockpile, and 
+In the present work, two different feed mechanisms are used: (1) thorium feed mechanism and (2) non-thorium feed mechanism.
+The first mechanism allows continuous feed flow of thorium from Th stockpile, and 
 $^{233}$U from \texttt{pa-decay tank}. In contrast, the second mechanism 
@@
 
-where $\varepsilon_{e}$ is the removal efficiency. Equation \ref{Equ:1} gives 
+where $\varepsilon_{e}$ is the removal efficiency. Integration of equation \ref{Equ:1} gives 
 the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
@@
 and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
-the gaseous \gls{FPs} and non-dissolved metals was set to 30 seconds (removal 
+the gaseous \gls{FPs} and non-dissolved metals was set to 30s (removal 
 constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
@@
 equivalent to 5 m$^3$/d of chemical reprocessing rate 
-\cite{nuttin2005potential,li_optimization_2018}. The effective feed rates of 
+\cite{li_optimization_2018,nuttin2005potential}. The effective feed rates of 
 the heavy metals (HM) are changed during reactor operation to conserve the 
@@
 	\centering
-	\caption{The reprocessing table.} 
+	\caption{The reprocessing table \cite{ashraf2019whole_core}.} 
 	\vspace{1ex}

### 2019-10-25 paper/abstract.tex
After Tikhomirov's and Matthew's comments

@@
 \begin{abstract}
-Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation-resistance.
+Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation resistance.
 The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material.
-Since $^{233}$U does not exist in nature, it is required to examine other available fissile materials.
-This work investigated the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), Pu reactor-grade (a mixture of plutonium isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
-The \gls{MSR} burnup routine provided by SERPENT-2 has been used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}.
-The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U have been studied in the present work.
-Additionally, the neutron spectrum shift during the reactor operation was calculated.
-The results showed that the continuous flow of Pu reactor-grade helps transition to thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel.
+Since $^{233}$U does not exist in nature, We must examine other available fissile materials.
+This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), reactor-grade Pu (a mixture of Pu isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
+The \gls{MSR} burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}.
+The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U are studied in the present work.
+Additionally, the neutron spectrum shift during the reactor operation is calculated.
+The results show that the continuous flow of reactor-grade Pu helps transition to the thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel.
 Finally, using \gls{TRU} as initial fissile materials offers the possibility of operating the SD-TMSR for an extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.

### 2019-10-25 paper/conclusion.tex
After Tikhomirov's and Matthew's comments

@@
 Five different types of initial fissile loadings have been studied for 
-transitioning to the thorium fuel cycle in the \gls{SD-TMSR}. We 
+transitioning to the thorium fuel cycle in the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). We 
 adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
 feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
-performed with Pu reactor-grade, TRU, and $^{233}$U as initial fissile 
+performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
 materials. Additionally, the dynamics of the effective multiplication factor 
@@
 
-Results demonstrated that continuous flow of Pu reactor-grade allows the 
+Results demonstrate that continuous flow of reactor-grade Pu allows the 
 transition to the thorium fuel cycle in a relatively short time ($\approx$ 
@@
 
-Additionally, the neutron energy spectrum shift during the reactor operation 
+The neutron energy spectrum shift during the reactor operation 
 for the Pu and TRU cases is different from the $^{233}$U fueling scenario. 
-Indeed, the spectrum hardening for $^{233}$U initial fissile isotope during 
-operation, but softening for the Pu and TRU cases. Notably, the most 
+The spectrum hardens for the $^{233}$U initial fissile isotope during 
+operation, but softens for the Pu and TRU cases. Notably, the most 
 significant neutron energy spectrum shift was obtained for reactor-grade Pu 
@@
 temperature coefficient of reactivity is negative and relatively large in all 
-cases. For TRU case, the coefficient remained almost constant during 
+cases. For the TRU case, the coefficient remained almost constant during 
 operation: $-4.79\pm0.12$ $pcm/K$ and $-4.76\pm0.11$ $pcm/K$ for the initial 
@@
 code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
-Moreover, in further simulations, we intend to take into account the delayed 
+In further simulations, we intend to take into account the delayed 
 neutron precursor drift. The \gls{SD-TMSR} reactivity control system has not 
@@
 
-Lastly, an additional area to explore is the accident safety analysis which 
+An additional area to explore is the accident safety analysis which 
 requires high-fidelity multi-physics model of the \gls{SD-TMSR} with the 

### 2019-10-25 paper/results.tex
After Tikhomirov's and Matthew's comments

@@
 
-The thorium feed mechanism adopts continuous feed flow of external thorium (from Th stockpile) and 
-$^{233}$U from \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
+The thorium feed mechanism adopts continuous feed flow of external thorium from the thorium stockpile and 
+$^{233}$U from the \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
 in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
@@
 Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
-decreases sharply during the first 25 years of reactor operation for the first 
+decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
 four cases. $k_{eff}$ decreases as a result of depletion of the initial 
-fissile materials and production of poisonous fission products. Thus, the 
+fissile materials and production of poisonous fission products \gls{FPs}. Thus, the 
 reactor becomes subcritical relatively quickly for alternative startup 
-compositions ($\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
-years in the Pu reactor-grade case). The amount of $^{233}$U generated in 
-the \gls{SD-TMSR} is not enough to maintain the reactor criticality and 
+compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
+years in the reactor-grade Pu case. The amount of $^{233}$U generated in 
+the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is not enough to maintain the reactor criticality and 
 counteract parasitic neutron absorption. Nevertheless, 
@@
 \gls{SD-TMSR} for a lifetime-long period of time (Figure~\ref{fig:keff1} (U-233 case)). 
-Additionally, the molar fraction of the LEU and Pu reactor-grade in the initial fuel composition was increased
-more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and Pu reactor-grade cases)).
+Additionally, the molar fraction of the LEU and reactor-grade Pu in the initial fuel composition was increased
+more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and reactor-grade Pu cases)).
 Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.
@@
 The non-thorium feed mechanism allows continuous feed flow of 
-$^{233}$U from \texttt{Pa-decay tank} and external Heavy Metal (excluding Th). 
-Under the non-thorium feed mechanism, four different initial fissile materials were studied: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, and \gls{TRU}. The continuous feed of $^{233}$U 
-without $^{232}$Th will lead to supercritical reactor, thus the $^{233}$U case 
-is excluded from non-thorium feed mechanism study.
+$^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (excluding Th). 
+Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{LEU}, Pu mixed with \gls{LEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
+without $^{232}$Th will lead to a supercritical reactor, thus the $^{233}$U case 
+is excluded from the non-thorium feed mechanism study.
 The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
@@
 salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
-the Beginning Of Life (BOL). 
+the BOL. 
 Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
-during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both Pu reactor-grade and TRU case 
+during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both the reactor-grade Pu and TRU cases 
 show promising results relative to the other two cases (LEU and Pu+LEU) (see Figure~\ref{fig:keff2}). 
@@
 
-For the Pu reactor-grade case, the amount of $^{233}$U generated in the \gls{SD-TMSR} in addition to the external feed flow of Pu is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs.
+For the reactor-grade Pu case, the amount of $^{233}$U generated in the \gls{SD-TMSR}, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs.
 For the \gls{TRU} fuel salt, the amount of 
@@
 reactor for a long period of time ($\approx$ $40$ years) without any 
-external feed of $^{233}$U ($^{233}$U used only from \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
-because the \glspl{MA}\footnote{In the present work, the Minor Actinides 
-(MA) include Np, Am and Cm.} accumulating in the core as a result of 
+external feed of $^{233}$U ($^{233}$U used only from the \texttt{Pa-decay tank}). Nevertheless, $k_{eff}$ decreases with the burnup 
+because of the \glspl{MA}\footnote{In the present work, the minor actinides 
+(MA) include Np, Am, and Cm.} accumulating in the core as a result of 
 continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU 
-fuel are less attractive for non-thorium feed mechanism. The continuous LEU 
+fuel are less attractive for the non-thorium feed mechanism. The continuous LEU 
 feed increases the amount of fertile $^{238}$U and consequently, reduces the 
 feasibility of such fissile materials. According to the $k_{eff}$ 
-results, Pu reactor-grade and TRU are only alternative fissile materials that  
+results, reactor-grade Pu and TRU are the only alternative fissile materials that  
 can be used to startup and maintain operation of the \gls{SD-TMSR}.
 
-\subsection{Pu reactor-grade, TRU, and $^{233}$U initial fuel}
-In this section, the simulation of the SD-TMSR with Pu reactor-grade and TRU 
-fissile materials is discussed. Additionally, previously studied the $^{233}$U 
+\subsection{Reactor-grade Pu, TRU, and $^{233}$U initial fuel}
+In this section, the simulation of the SD-TMSR with reactor-grade Pu and TRU 
+fissile materials is discussed. Additionally, the previously studied $^{233}$U 
 case is listed for comparison \cite{ashraf2019whole_core}. 
-Figure~\ref{fig:refillCCC} demonstrates the dynamics of heavy metal refill 
+Figure~\ref{fig:refillCCC} demonstrates the dynamics of the heavy metal refill 
 rate during 60 \gls{EFPY} of the SD-TMSR operation. The heavy metal refill 
-rate was adjusted to maintain the reactor critical and the total fuel mass 
+rate was adjusted to maintain criticality and the total fuel mass 
 almost constant\footnote{The variation of the total fuel mass is less than 
-$0.1\%$} during the reactor operation. In the $^{233}$U case, the mean values of 
+$0.1\%$} during reactor operation. In the $^{233}$U case, the mean values of 
 $^{233}$U and $^{232}$Th refill rate are $1.77$ and $2.21$ $kg/d$, 
-respectively. Similarly, in the Pu reactor-grade case, the mean values of 
+respectively. Similarly, in the reactor-grade Pu case, the mean values of 
 $^{233}$U and Pu refill rate are $0.75$ and $2.75$ $kg/d$, respectively. For  
@@
 	\caption{Dynamics of heavy metal refill rate during 60 \gls{EFPY} of 
-		reactor operation. Solid lines for $^{233}$U case, dashed lines for Pu 
-		reactor-grade case, and dotted lines for TRU case.}
+		reactor operation. Solid lines for the $^{233}$U case, dashed lines for the
+		reactor-grade Pu case, and dotted lines for the TRU case.}
 	\label{fig:refillCCC}
@@
 
-Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC} demonstrate 
-the evolution of important isotopes for $^{233}$U, Pu and TRU cases 
+Figures~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC} demonstrate 
+the evolution of important isotopes for the $^{233}$U, Pu, and TRU cases 
 respectively. For the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}), the mass of Pa in the fuel salt is almost constant and reaches 
 $17.8$  $kg$ at the end of the operation time. 
-Additionally, the mass of Minor Actinides (MA) and Pu increases with time.
-The level of Pu in the fuel salt correlates with the mass of the MA.
-Moreover, MA needs more time to reach equilibrium than Pu.
+Additionally, the mass of minor actinides (MA) and Pu increases with time.
+The level of Pu in the fuel salt correlates with the mass of the MA; however, MA need more time to reach equilibrium than Pu.
 Uranium inventory increases during
-operation and reaches equilibrium after $\approx$ $27$ years. Figure~\ref{fig:inventoryCCCC} shows that refueling the core with Th helps 
+operation and reaches equilibrium after $\approx$ $27$ years. Figure~\ref{fig:inventoryCCCC} shows that refueling the core with thorium helps 
 maintain an almost constant inventory throughout the full operation time. 
-For Pu and TRU cases (Figure~\ref{fig:inventoryPu_TRUCCC}), the protactinium extraction time was selected equal 30s 
-to avoid poisoning the core. Therefore, 
-Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
+For the Pu and TRU cases (Figure~\ref{fig:inventoryPu_TRUCCC}), the Pa extraction time was selected to be 30 s 
+to avoid poisoning the core. Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
 is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
 isotopes for all three cases reach the equilibrium state after $\approx$ $30$ 
-years (see Figure~\ref{fig:inventoryCCCC} and ~\ref{fig:inventoryPu_TRUCCC}).
+years (see Figure~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC}).
 \begin{figure}
@@
 	\vspace{-0.4in}
-	\caption{Evolution of the important nuclides inventories for $^{233}$U 
+	\caption{Evolution of the important nuclides inventories for the $^{233}$U 
 		case (MA involves Np, Am, Cm) \cite{ashraf2019whole_core}.}
@@
 	\vspace{-0.5in}
-	\caption{Evolution of the important nuclides inventories for Pu 
-		reactor-grade case (solid lines) and for TRU case (dashed lines).}
+	\caption{Evolution of the important nuclides inventories for the 
+		reactor-grade Pu case (solid lines) and for the TRU case (dashed lines).}
 	\label{fig:inventoryPu_TRUCCC}
@@
 Figure~\ref{fig:Th232CC} illustrates the variation of thorium inventory in the 
-fuel salt for $^{233}$U, Pu reactor-grade and TRU cases. The thorium inventory 
+fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases. The thorium inventory 
 decreases in the $^{233}$U case by only $3.2$\% at the End Of Life (EOL) when the thorium 
-feed mechanism was applied. 
-In contrast, thorium total mass decreases significantly in Pu and TRU cases when the non-thorium 
-feed mechanism was applied. Thus, thorium mass decreases by $39.2$\% and 
-$37.96$\% for Pu reactor-grade and TRU cases, respectively.
+feed mechanism is applied. 
+In contrast, thorium total mass decreases significantly in the Pu and TRU cases when the non-thorium 
+feed mechanism is applied. Thus, thorium mass decreases by $39.21$\% and 
+$37.96$\% for the reactor-grade Pu and TRU cases, respectively.
 \begin{figure}
@@
 	\includegraphics[width=\textwidth]{Th232CC.png}
-	\caption{The variation of thorium mass in the fuel salt for $^{233}$U, Pu reactor-grade, and TRU cases.}
+	\caption{The variation of thorium mass in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:Th232CC}
@@
 Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt 
-for $^{233}$U, Pu reactor-grade and TRU cases. Notably, the mass of the 
-$^{233}$U reaches the equilibrium after $\approx$ $30$ years. Overall, the 
+for the $^{233}$U, reactor-grade Pu, and TRU cases. The mass of 
+$^{233}$U reaches equilibrium after $\approx$ $30$ years; overall, the 
 amount of $^{233}$U is sufficient to maintain criticality in 
@@
 	\includegraphics[width=\textwidth]{U233CC.png}
-	\caption{Mass of $^{233}$U in the fuel salt for $^{233}$U, Pu reactor-grade, and TRU cases.}
+	\caption{Mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:U233CC}
@@
 
-In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by HM (Pu and TRU) for 
+In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by heavy metals (Pu and TRU) for 
 criticality, which increases the Pu molar fraction (mole\%) in the molten salt. 
-According to the literature, the limit of Pu solubility in the FLiBe salt is 
+According to literature, the limit of Pu solubility in the FLiBe salt is 
 $\approx$ $4.0$ mole\% \cite{ignatiev2012progress,sood1975plutonium}. 
 Figure~\ref{fig:PusolubilityCC} represents the Pu fraction in the fuel salt 
-(mole\%) for $^{233}$U, Pu reactor-grade and TRU cases, respectively. In $^{233}$U and Pu reactor-grade cases, the Pu fraction increases 
+(mole\%) for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. In the $^{233}$U and reactor-grade Pu cases, the Pu fraction increases 
 slightly but still below its solubility limit. On the other hand, the Pu 
@@
 	\includegraphics[width=\textwidth]{PusolubilityCC.png}
-	\caption{The Pu fraction in the fuel salt (mole\%) for $^{233}$U, Pu reactor-grade, and TRU cases.}
+	\caption{The Pu fraction in the fuel salt (mole\%) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:PusolubilityCC}
@@
 Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
-operation for $^{233}$U, Pu reactor-grade and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
+operation for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
 zero. 
-Although all produced $^{233}$U was used to refuel the core, the reactor was subcritical after $40$ years of operation (Figure~\ref{fig:keff2}).
-In $^{233}$U and Pu reactor-grade cases, the net production of 
-$^{233}$U increases with burnup and reaches at the end of operation lifetime 
-about $1.77$ $t$ and $10$ $t$, respectively. As shown in 
+Although all produced $^{233}$U is used to refuel the core, the reactor is subcritical after $40$ years of operation (Figure~\ref{fig:keff2}).
+In the $^{233}$U and reactor-grade Pu cases, the net production of 
+$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$ at EOL, respectively. As shown in 
 Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
-$1.3$ $t$; this is sufficient to startup another \gls{SD-TMSR}. Similarly, 
+$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR}. Similarly, 
 one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
-after $\approx$ $4.5$ years if we applied the non-thorium feed mechanism on 
-the SD-TMSR that initially loaded by Pu reactor-grade alternative to 
-$^{233}$U. In addition, Figure~\ref{fig:NetCC} also shows that for $^{233}$U 
-case the net production of $^{233}$U during the first 455 days is negative, 
-thus about $175.28$ $kg$ of $^{233}$U must be added during this period. 
+after $\approx$ $4.5$ years if we apply the non-thorium feed mechanism on 
+the SD-TMSR that was initially loaded by reactor-grade Pu alternative to 
+$^{233}$U. In addition, Figure~\ref{fig:NetCC} shows that for the $^{233}$U 
+case the net production of $^{233}$U during the first 455 days is negative; 
+about $175.28$ $kg$ of $^{233}$U must be added during this period. 
 In conclusion, the thorium fuel cycle transition can be achieved by selecting the 
 proper feed mechanism and initial fissile material. 
-Specifically, applied non-thorium feed mechanism on 
-the SD-TMSR loaded by Pu reactor-grade allows the 
+Specifically, applying the non-thorium feed mechanism on 
+the SD-TMSR loaded by reactor-grade Pu allows the 
 transition to the thorium fuel cycle after $\approx$ 
-$4.5$ years. Additionally, applied thorium feed mechanism on 
+$4.5$ years. Additionally, applying the thorium feed mechanism on 
 the SD-TMSR loaded by $^{233}$U allows the 
-transition to the thorium fuel cycle after $26$ years of operation. 
+transition to the thorium fuel cycle after $\approx$ $26$ years of operation. 
 The comparison between the two feed mechanisms with different types of initial 
@@
 	\includegraphics[width=\textwidth]{NetCC.png}
-	\caption{Net production of $^{233}$U during burnup period (60 \gls{EFPY}) for $^{233}$U, Pu reactor-grade, and TRU cases.}
+	\caption{Net production of $^{233}$U during the burnup period (60 \gls{EFPY}) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:NetCC}
@@
 			\hline
-			Feed mechanism & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) & Pu 
-			reactor-grade & \gls{TRU}& $^{233}$U \\
+			Feed mechanism & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) &  
+			reactor-grade Pu & \gls{TRU}& $^{233}$U \\
 			\hline
@@
 Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
-lethargy for full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
-MeV for the $^{233}$U, Pu reactor-grade, and TRU cases at BOL and EOL. In $^{233}$U 
+lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
+MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In the $^{233}$U 
 case, at the EOL, the neutron spectrum is harder than at BOL due to the 
-accumulation of the Pu and other strong thermal neutron absorbers in the fuel 
-salt. For Pu reactor-grade and TRU cases, during the reactor operation, the 
+accumulation of Pu and other strong thermal neutron absorbers in the fuel 
+salt. For the reactor-grade Pu and TRU cases, during reactor operation, the 
 fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
-(see Figure~\ref{fig:U233CC}), the neutron spectrum softens and becomes 
-similar to a initial thermal spectrum of $^{233}$U fueled \gls{SD-TMSR}.
+(see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
+similar to the initial thermal spectrum of a $^{233}$U fueled \gls{SD-TMSR}.
  \begin{figure}
@@
  			\vspace{-0.4in}
- 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for $^{233}$U, Pu reactor-grade, and TRU cases.}
+ 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
  	\label{fig:spectrumFLUX110vC}
@@
 	\item Fuel salt temperature (Doppler Effect) rising from 900 to 1000 K 
-	(first row  in Table ~\ref{tab:tcoe}).
+	(first row  in Table~\ref{tab:tcoe}).
 	\item Fuel salt density decreasing from 3.3 to 3.233 g/cm$^3$ 

### 2019-10-25 paper/introduction.tex

@@
-\section{Introduction}
-The \gls{GIF} has defined eight technology goals for the next generation
+\section{Introduction} \label{Introduction}
+The \gls{GIF} defines eight technological goals for the next generation
 nuclear systems.
-These goals have been defined in four broad areas: safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}.
-The \gls{MSR} has many advantages that consistent
-with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online
-reprocessing and refueling, excellent neutron economy and operation near
+These goals are defined in four broad areas: safety and reliability, non-proliferation and physical protection, economics, and sustainability \cite{doe2002technology}.
+The \gls{MSR} has many advantages that agree
+with \gls{GIF}'s goals, like: liquid fuel, inherent safety, online
+reprocessing and refueling, excellent neutron economy, and operation near
 atmospheric
 pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}.
-Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV
+Thus, the \gls{GIF} selected the \gls{MSR} as one of the promising Generation-IV
 reactors \cite{doe2002technology,pioro2016handbook}.
-In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl).
-This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
-circulates through the core and allows transferring fission heat from reactor
-core to \glspl{IHX}.
+In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl);
+this liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
+circulates through the core and allows fission heat to transfer from the reactor
+core to intermediate heat exchanger.
 
-The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250
-MW$_{th}$) was introduced by the \gls{CAS} \cite{li_optimization_2018}. The
+The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) 2,250
+MW$_{th}$ was introduced by the Chinese Academy of Sciences \cite{li_optimization_2018}. The
 SD-TMSR
@@
 fuel cycle. In the SD-TMSR the fissile and fertile elements are integrated
-into the same salt. In addition, the active core is divided into two zones,
+into the same salt. The active core is divided into two zones;
 the radius of the fuel channels in the outer zone is modified to be larger
@@
 	merle2004scenarios,rosenthal1970molten}. This design assumes that we have
-fissile $^{233}$U inventory to startup new \glspl{MSR}. But $^{233}$U does not
-exist in the Earth's crust and can be produced from fertile $^{232}$Th only in
-the nuclear reactor. Therefore, it is required to examine alternative fissile
-materials (e.g., $^{235}$U) to replace the $^{233}$U in the startup fuel
+fissile $^{233}$U inventory to start up new \glspl{MSR}. However, $^{233}$U does not
+exist in the Earth's crust and can only be produced from fertile $^{232}$Th in 
+specific nuclear facilities. Therefore, we examine alternative fissile
+materials to replace the $^{233}$U in the startup fuel
 composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel
@@
 time\footnote{Time required to produce enough amount of $^{233}$U to trigger a
-	new SD-TMSR.} of $^{233}$U because in this case all startup fissile material
+	new SD-TMSR.} of $^{233}$U because in this case, all startup fissile material
 is being substituted by newly produced $^{233}$U.
 
-Betzler \emph{et al.} (2016), discussed the simulation of the startup of a MSBR unit
+Betzler \emph{et al.} (2016) discussed the simulation of the startup of a \gls{MSBR} unit
 cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent nuclear fuel (SNF) as initial
 fissile materials \cite{betzler2016modeling}. They concluded that the 
-plutonium vector extracted from LWR SNF is the best alternative source to 
-$^{233}$U because it has high ratio of fissile isotopes
-\cite{betzler2016modeling}. Zou \emph{et al.} (2018), introduced two approaches for
-the thorium fuel cycle transition in \gls{TMSR}: (1) in-core transition and 
+Pu vector extracted from LWR SNF is the best alternative source to 
+$^{233}$U because it has a high ratio of fissile isotopes
+\cite{betzler2016modeling}. Zou \emph{et al.} (2018) introduced two approaches for
+the thorium fuel cycle transition in the \gls{TMSR}: (1) in-core transition and 
 (2) ex-core transition. In the first approach, the TMSR is launched with 
@@
 $^{233}$U bred from thorium is rerouted into the core to maintain criticality. 
-In contrast, the second approache tends to store produced $^{233}$U out of the 
-core until there is enough amount to start a new TMSR \cite{zou2018transition}.
-Additionally, Zou \emph{et al.} (2018), studied the transitioning to thorium fuel
-cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU}
-as startup fuel. They concluded that the transition to thorium fuel cycle can
-be achieved in thermal smTMSR with a proper fuel fraction 
+In contrast, the second approach tends to store produced $^{233}$U out of the 
+core until there is enough to start a new TMSR \cite{zou2018transition}.
+Zou \emph{et al.} (2018) studied the transitioning to thorium fuel
+cycle in a small modular Thorium-based Molten Salt Reactor (smTMSR) using \gls{TRU}
+as startup fuel. They concluded that the transition to the thorium fuel cycle can
+be achieved in a thermal smTMSR with a proper fuel fraction 
 \cite{zou2018preliminary}.
 
-Heuer \emph{et al.} (2014), discussed the transition characteristics of the \gls{MSFR}
-under different launching scenarios (e.g., enriched uranium and TRU) they concluded that starting the thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.
+Heuer \emph{et al.} (2014) discussed the transition characteristics of the \gls{MSFR}
+under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.
 
-Indeed, there are various researches that revolve around starting the
+There are various researches that revolve around starting the
 \glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
@@
 	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
-	fiorina2013investigation}, while little focus on
+	fiorina2013investigation}, while few focus on
 thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
-	zou2018transition,zou2018preliminary}. Nevertheless, simulating the operation of the \gls{SD-TMSR} concept with other
-fissile materials (except $^{233}$U) was not studied before. Therefore,
+	zou2018transition,zou2018preliminary}. Simulating the operation of the \gls{SD-TMSR} concept with other
+fissile materials (except $^{233}$U) has not been studied before. Therefore,
 the main objective of the present paper is to discuss the simulation of the
@@
 different initial fissile materials and without any external feed of $^{233}$U
-to achieve the thorium fuel cycle transition. We investigated five different
-initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, Pu reactor-grade, \gls{TRU} from LWR SNF and $^{233}$U \cite{de2000scenarios}. Moreover, two different feed mechanisms were selected:
+to achieve the thorium fuel cycle transition. We investigate five different
+initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U \cite{de2000scenarios}. Two different feed mechanisms were selected:
 
 \begin{itemize}
-	\item Thorium feed mechanism: continuous feed flow of thorium from Th stockpile and $^{233}$U from \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
+	\item Thorium feed mechanism: continuous feed flow of thorium from the thorium stockpile and $^{233}$U from the \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
 \cite{betzler2016modeling}.
-	\item Non-thorium feed mechanism: continuous injection of Heavy Metal (HM) (excluding Th) and simultaneously feed of all or fraction of $^{233}$U from \texttt{Pa-decay tank}.
+	\item Non-thorium feed mechanism: continuous injection of heavy metal (excluding Th) and simultaneous feed of all or fraction of $^{233}$U from the \texttt{Pa-decay tank}.
 \end{itemize}
 
-All calculations presented in the present paper were performed using SERPENT-2 version 2.1.30 \cite{leppanen2014serpent}.
-We used the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling.
+All calculations presented in this paper are performed using SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}.
+We use the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling.
 SERPENT-2 uses an internal calculation routine for solving the set of Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}.
@@
 
-This present paper is organized as follows: after an introduction about 
-\gls{MSR} systems, the model description is discussed in section \ref{Model-description}. 
-Methodology and tools is descried in section \ref{Methodology-and-tools}. Extraction and feed mechanisms 
-are addressed in section  \ref{Feed-and-extraction-rates}. Section \ref{Results-and-discussion} focuses on the results and discussion. 
-Finally, section \ref{Conclusion} highlights the conclusions.
+This paper is organized as follows: section \ref{Introduction} introduces \gls{MSR} systems, section \ref{Model-description} discusses the model description, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Feed-and-extraction-rates} addresses extraction and feed mechanisms, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.
 

### 2019-10-25 paper/methods.tex

@@
 \subsection{Geometry}
-The \gls{SD-TMSR} design model was introduced by the \gls{CAS} as a part of  
+The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design model was introduced by the Chinese Academy of Sciences as a part of  
 the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based 
@@
 \cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
-design of \gls{SD-TMSR} is inspired by \gls{MSBR} 
-\cite{robertson_conceptual_1971} after some modification in the geometry to 
-control the positive temperature coefficient in MSBR. The \gls{SD-TMSR} core 
-geometry was described in details by Li \emph{et al.} 
-\cite{li_optimization_2018}.
+design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
+\cite{robertson_conceptual_1971} after modifying the geometry to 
+control the positive temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
+geometry is described in detail by Li \emph{et al.} 
+\cite{li_optimization_2018};
 Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the 
@@
 equal to 460 cm. Assemblies of graphite\footnote{We choose graphite density of 
-$2.3$ g/cm$^3$, to validate our results against results in the literature 
+$2.3$ g/cm$^3$, to validate our results against results in literature 
 \cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the 
-core. The side length of the graphite hexagonal prism was optimized in 
-\cite{li_optimization_2018} and found to be 7.5 cm. The liquid fuel circulates 
-continuously through the fuel channels that pierces the graphite hexagonal 
+core. The optimal side length of the graphite hexagonal prism is found to be 7.5 cm \cite{li_optimization_2018}. The liquid fuel circulates 
+continuously through the fuel channels that pierce the graphite hexagonal 
 prisms. The core is divided into two different zones to enhance 
-Th/$^{233}$U breeding performance. The radius of the fuel channels in the 
+Th/$^{233}$U breeding performance; the radii of the fuel channels in the 
 outer and inner zone are 5 and 3.5 cm, respectively. The axial and radial 
 graphite reflectors surround the core to minimize neutron leakage and 
-maximize flux in the core. The reflectors are surrounded by B${_4}$C cylinder 
-that acts as a radiation shielding. The \gls{SD-TMSR} pressure vessel holds 
-the fuel salt, graphite elements, reflector, shielding, \gls{IHX} and made of Ni-based (hastelloy N) alloy. The main 
+maximize flux in the core. The reflectors are surrounded by a B${_4}$C cylinder 
+that acts as radiation shielding. The \gls{SD-TMSR} pressure vessel holds 
+the fuel salt, graphite elements, reflector, shielding, intermediate heat exchanger, and is made of a Ni-based (hastelloy N) alloy. The main 
 characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.
@@
 \begin{table}  %[!ht]
-	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}}
+	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
 	\vspace{0.1in}
@@
 		Fuel density at 900 K, g/cm$^3$		  		& 3.3 \\
-		Fuel dilatation coefficient, g/(cm$^3$ $.$K)  &  -6.7$\times$10$^{-4}$ \\
+		Fuel dilatation coefficient, g/(cm$^3$$.$K)  &  -6.7$\times$10$^{-4}$ \\
 		Graphite density, g/cm$^3$             	    & 2.3	\\  
@@
 compositions and without any external feed of fissile $^{233}$U which we 
-assumed is unavailable. For that reason, five different types of initial 
-fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SNF were 
-considered:
+assume is unavailable. For that reason, five different types of initial 
+fissile materials are considered based on \gls{LEU}, Pu, and \gls{TRU} from Light Water
+Reactor (LWR) spent nuclear fuel (SNF):
 \begin{enumerate}[label=(\alph*)]
-	\item low-enriched uranium (LEU) (19.79\%);
-	\item Pu mixed with \gls{LEU} (19.79\%);
-	\item Pu reactor-grade \cite{marka1993explosive};
-	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios};
-	\item $^{233}$U for comparison purpose \cite{ashraf2019whole_core}.
+	\item low-enriched uranium (LEU) (19.79\%),
+	\item Pu mixed with \gls{LEU} (19.79\%),
+	\item reactor-grade Pu \cite{marka1993explosive},
+	\item transuranic (TRU) elements from LWR SNF \cite{de2000scenarios}, and
+	\item $^{233}$U for comparison \cite{ashraf2019whole_core}.
 \end{enumerate}
 
-The reactor-grade plutonium and \gls{TRU} composition are summarized in 
+The reactor-grade Pu and \gls{TRU} compositions are summarized in 
 Table~\ref{tab:table2} and ~\ref{tab:table3}, respectively.
@@
 \begin{table}  %[!ht]
-	\caption{Reactor-grade plutonium vector (wt.\%) \cite{marka1993explosive}}
+	\caption{Reactor-grade Pu vector (wt.\%) \cite{marka1993explosive}.}
 	\vspace{0.1in}
@@
 \begin{table}  %[!ht]
-	\caption{\gls{TRU} vector (wt.\%) \cite{de2000scenarios}}
+	\caption{\gls{TRU} vector (wt.\%) \cite{de2000scenarios}.}
 	\vspace{0.1in}
@@
 
-For reactor-grade plutonium case, the composition was taken for plutonium 
-recovered from the spent fuel composition of commercial \gls{PWR} with the 
-average discharge burnup $33$ $GWd/tHM$ and after $10$ years of cooling before 
+For the reactor-grade Pu case, the composition is taken for Pu 
+recovered from the SNF composition of a commercial \gls{PWR} with an 
+average discharge burnup of $33$ $GWd/tHM$ and after $10$ years of cooling before 
 reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
-isotopic compositions of \gls{TRU} was taken for the SNF of UOX \gls{PWR} 
-(after one use, no multi-recycling) with the average discharge $60$ 
-$GWd/tHM$ burnup, and after $5$ years of cooling \cite{de2000scenarios}. 
+isotopic compositions of \gls{TRU} are taken for the SNF of uranium oxide \gls{PWR} 
+(after one use, no multi-recycling) with an average discharge of $60$ 
+$GWd/tHM$ burnup and after $5$ years of cooling \cite{de2000scenarios}. 
 The molar composition of startup fuel for all five cases is listed in 
@@
 		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) 
-		& Pu reactor-grade & \gls{TRU}& $^{233}$U \\
+		&  reactor-grade Pu & \gls{TRU}& $^{233}$U \\
 		\hline
@@
 		\hline
-		Nuclide & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) & Pu 
-		reactor-grade & \gls{TRU}& $^{233}$U \\	\hline
+		Nuclide & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) &  
+		reactor-grade Pu & \gls{TRU}& $^{233}$U \\	\hline
 		$^{232}$Th       &6.24E+07 & 4.67E+07 &   6.75E+07			& 5.44E+07	& 7.69E+07    \\ 
@@
 
-Simulation of Liquid-fueled Molten Salt Reactor (MSR) systems requires 
+Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
 computational software that must support online fuel salt reprocessing and 
@@
 transport and burnup code.} \cite{leppanen2014serpent} is used to simulate the 
-full-core of the SD-TMSR with different types of initial fuel. The extension 
+full-core of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with different types of initial fuel. The extension 
 of SERPENT accounts for continuous online reprocessing and refueling 
-\cite{aufiero2013extended}. ENDF-VII.0 cross-section library was used for all 
+\cite{aufiero2013extended}. The ENDF-VII.0 cross section library was used for all 
 calculations in this work. The results demonstrate full-core runs of 
-$1.25\times 10^7$ neutron history per depletion step. The full burnup time of 
+$1.25\times 10^7$ neutron histories per depletion step. The full burnup time of 
 the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
@@
 
-As shown in Figure~\ref{fig:flow}, after launched the input file, an advanced 
+As shown in Figure~\ref{fig:flow}, after launching the input file, we solve the Bateman equation using an advanced 
 matrix exponential solution based on the Chebyshev Rational Approximation 
-Method (CRAM) \cite{isotalo2016improving} used to solve the Bateman equation. 
-Then, the system extracted gaseous \gls{FPs} and other materials 
-(non-dissolved metals, lanthanides, and soluble metals except Pu) with 
-suitable removal rate\footnote{The extraction rate depends on the type of 
+Method \cite{isotalo2016improving}. 
+Then, the system extracts gaseous \gls{FPs} and other materials 
+(non-dissolved metals, lanthanides, and soluble metals except Pa) with 
+a suitable removal rate\footnote{The extraction rate depends on the type of 
 poison and its impact on the neutron
-economy.}. This can be done by set the 
+economy.}. This is done by setting the 
 flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
@@
 \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
-soluble metals except protactinium).}. Specifically, protactinium was removed 
-from the fuel with a certain flow rate into the external tank, 
-\texttt{pa-decay tank}, to decay and produce $^{233}$U\footnote{The 
+soluble metals except protactinium).}. Specifically, Pa is removed 
+from the fuel with a certain flow rate into the 
+\texttt{Pa-decay tank} to decay and produce $^{233}$U\footnote{The 
 $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
@@
 and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup 
-routine provided by SERPENT-2 allows changes the flow rates ($mflow$) of the 
-isotopes during reactor operation \cite{aufiero2013extended}. Specifically, we have to determine the mass flow ($mflow$), which is the rate by 
+routine provided by SERPENT-2 allows changes to the flow rates ($mflow$) of the 
+isotopes during reactor operation \cite{aufiero2013extended}. Specifically, we have to determine the flow rate ($mflow$), which is the rate by 
 which elements or nuclides are transferred between materials. After that, the 
-transfer rates should be connected to materials with a reprocessing scheme. 
+flow rates must be connected to materials with a reprocessing scheme. 
 Finally, we have to link the reprocessing schemes to depletion histories. In 
-the present work, we adjusted the transfer rates of fresh fuel to maintain core 
+the present work, we adjust the transfer rates of fresh fuel to maintain core 
 criticality and to keep fuel salt inventory constant during burnup. The feed constant calculation procedures are summarized as follows:
 \begin{enumerate}
-	\item The simulation started without any injection of refueling materials (i.e. with only removing of FPs and Pa).
-	\item After first depletion calculation step, we checked the total mass density of FPs and Pa in \texttt{FP-waste tank} and \texttt{pa-tank}, respectively.
-	\item A simple calculation yields the amount of \gls{HM} that must be added during this cycle:
+	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
+	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-tank}, respectively.
+	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
 	\subitem 3a. For thorium feed mechanism: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
-	\subitem 3b. For non-thorium feed mechanism: mass of \gls{HM} (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
-	\item Dividing this mass by time and inventory of refueling material gave the corresponding feed constant.
+	\subitem 3b. For non-thorium feed mechanism: mass of (HM) (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
+	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
 \end{enumerate}
-The cycle calculation ran iteratively until the burnup reached the desired worth.
+The cycle calculation runs iteratively until the burnup reaches the desired worth.
 
@@
 In the present work, two different feed mechanisms are used: (1) thorium feed mechanism and (2) non-thorium feed mechanism.
-The first mechanism allows continuous feed flow of thorium from Th stockpile, and 
-$^{233}$U from \texttt{pa-decay tank}. In contrast, the second mechanism 
-continuously injects Heavy Metal (HM) (excluding Th) and simultaneously feeds  
-all or part of produced $^{233}$U from \texttt{Pa-decay tank}. The fission 
-products act as poisons in the MSRs; they negatively impacting the reactivity. 
+The first mechanism allows continuous feed flow of thorium from the thorium stockpile and 
+$^{233}$U from the \texttt{Pa-decay tank}. In contrast, the second mechanism 
+continuously injects heavy metal (HM) (excluding Th) and simultaneously feeds  
+all or part of produced $^{233}$U from the \texttt{Pa-decay tank}. The fission 
+products \gls{FPs} act as poisons in the MSRs; they negatively impact the reactivity. 
 Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
@@
 and summarized in Table~\ref{tab:table6}. The effective reprocessing time for 
-the gaseous \gls{FPs} and non-dissolved metals was set to 30s (removal 
+the gaseous \gls{FPs} and non-dissolved metals was set to 30 s (removal 
 constant $\lambda_{e}$ = $-0.0333$ $s^{-1}$), because such elements must be 
-extracted promptly and continuously via gas removal system. In contrast, 
-extracting the soluble \gls{FPs}, lanthanides, and protactinium can be done by 
-the chemical reprocessing (i.e. fluorination and reduction reaction). 
+extracted promptly and continuously via a gas removal system. In contrast, 
+extracting the soluble \gls{FPs}, lanthanides, and Pa is done by 
+chemical reprocessing (i.e. fluorination and reduction reaction). 
 Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
@@
 $\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
-equivalent to 5 m$^3$/d of chemical reprocessing rate 
+equivalent to a chemical reprocessing rate of 5 m$^3$/d 
 \cite{li_optimization_2018,nuttin2005potential}. The effective feed rates of 
 the heavy metals (HM) are changed during reactor operation to conserve the 
-total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, Pu reactor-grade and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9} and \ref{tab:table10} in Appendix.
+total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9}, and \ref{tab:table10} in Appendix.
 
@@
 			\hline
-			Gaseous \gls{FPs} and non-dissolved metals  &  H, He, N, O, Ne, Ar, Kr, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te, Xe, Lu, Hf, Ta, W, Re, Os, Ir, Pt, Au and Rn.		&	30s	&  -3.333E-02 \\
+			Gaseous \gls{FPs} and non-dissolved metals  &  H, He, N, O, Ne, Ar, Kr, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te, Xe, Lu, Hf, Ta, W, Re, Os, Ir, Pt, Au, and Rn.		&	30 s	&  -3.333E-02 \\
 			\hline
 			Lanthanides and other soluble \gls{FPs}     & 
-			Zn, Ga, Ge, As, Se, Br, Rb, Sr, Y, Zr, Cd, In, Sn, I, Cs, Ba, La, Ce, Pr, Nd, Pm, Sm, Eu, Gd, Tb, Dy, Ho, Er, Tm and Yb. & 10.599 d (5 m$^3$/d) &  -1.092E-06 \\
+			Zn, Ga, Ge, As, Se, Br, Rb, Sr, Y, Zr, Cd, In, Sn, I, Cs, Ba, La, Ce, Pr, Nd, Pm, Sm, Eu, Gd, Tb, Dy, Ho, Er, Tm, and Yb. & 10.599 d (5 m$^3$/d) &  -1.092E-06 \\
 			\hline

### 2019-10-25 paper/methods.tex
minor changes

@@
 	\subitem 3a. For thorium feed mechanism: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
-	\subitem 3b. For non-thorium feed mechanism: mass of (HM) (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
+	\subitem 3b. For non-thorium feed mechanism: mass of the heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
 	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.

### 2019-10-25 paper/conclusion.tex
Matt's comments implemented in Andrei's part

@@
 
-Five different types of initial fissile loadings have been studied for 
-transitioning to the thorium fuel cycle in the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR). We 
-adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
-feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
+Five different types of initial fissile loadings are considered to investigate 
+transitioning to the thorium fuel cycle in the SD-TMSR. We adopted two 
+different feed mechanisms: thorium feed mechanism and non-thorium feed 
+mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
 performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 

### 2019-10-25 paper/results.tex
minor changes
Matt's comments implemented in Andrei's part

@@
 Figure~\ref{fig:spectrumFLUX110vC} represents the neutron flux per unit 
-lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 10 
-MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In the $^{233}$U 
-case, at the EOL, the neutron spectrum is harder than at BOL due to the 
-accumulation of Pu and other strong thermal neutron absorbers in the fuel 
-salt. For the reactor-grade Pu and TRU cases, during reactor operation, the 
-fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
+lethargy for a full-core SD-TMSR model in the energy range from 10$^{-8}$ to 
+10 MeV for the $^{233}$U, reactor-grade Pu, and TRU cases at BOL and EOL. In 
+the $^{233}$U case, at the EOL, the neutron spectrum is harder than at BOL due 
+to the accumulation of Pu and other strong thermal neutron absorbers in the 
+fuel salt. For the reactor-grade Pu and TRU cases, during reactor operation, 
+the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope 
 (see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
@@
 \subsection{Neutron flux}
-Figures~\ref{fig:fast_flux}, \ref{fig:thermal_flux} show the radial 
+Figures~\ref{fig:fast_flux} and \ref{fig:thermal_flux} show the radial 
 distribution of fast (energy range between 0.625 eV and 20 MeV) and thermal 
@@
 different initial fissile materials in the fuel salt ($^{233}$U, reactor-grade 
-plutonium, TRU) at startup and at equilibrium (after $\approx 30$ years of 
-operation). Actinides evolution and poisonous fission product accumulation 
-for various initial fissile compositions demonstrated the different effects on 
-the SD-TMSR neutronics performance. For the $^{233}$U case, the thermal neutron 
-flux is suppressed at the equilibrium because fissile $^{233}$U in the core is 
-being substituted with heavier fissile actinides: $^{235}$U, $^{239}$Pu, and 
-$^{241}$Pu. This is in good agreement with results in the literature 
+Pu, TRU) at startup and at equilibrium (after $\approx 30$ years of 
+operation). Actinides' evolution and poisonous fission product accumulation 
+for various initial fissile compositions demonstrates the different effects on 
+the SD-TMSR neutronics performance. For the $^{233}$U case, the thermal 
+neutron flux is suppressed at equilibrium because fissile $^{233}$U in the 
+core is being substituted with heavier fissile actinides: $^{235}$U, 
+$^{239}$Pu, and $^{241}$Pu. This agrees with results in literature 
 \cite{rykhlevskii2019modeling, ashraf2019whole_core}.
@@
 
-Opposite behavior was observed for the Pu reactor-grade and TRU cases. For 
-these cases, the thermal neutron flux is increasing during operation while 
-fast neutron flux is decreasing. Fissile plutonium nuclides (generate 
-relatively hard spectrum) from initial fuel salt composition is gradually 
-substituted with the $^{233}$U (generates relatively soft spectrum), produced 
-from the fertile $^{232}$Th. During reactor operation, the $^{233}$U becomes 
-primary fissile isotope, which leads to the neutron spectrum softening of the 
-reactor. 
+Opposite behavior is observed for the reactor-grade Pu and TRU cases. For  
+these cases, the thermal neutron flux increases during operation while fast 
+neutron flux decreases. Fissile Pu nuclides (generate relatively hard 
+spectrum) from initial fuel salt composition are gradually substituted with  
+$^{233}$U (generates relatively soft spectrum), produced from fertile 
+$^{232}$Th. During reactor operation, $^{233}$U becomes the primary fissile 
+isotope, which softening the neutron spectrum of the reactor. 
 \begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
@@
 
-Notably, more changes in thermal neutron flux shape and magnitude for the 
-$^{233}$U case were observed in the inner core zone ($R\lesssim150$) than 
-in the outer core zone. In contrast, for Pu reactor-grade and TRU cases, 
-significant changes were observed for thermal neutron flux in the outer core 
+More changes in thermal neutron flux shape and magnitude for the 
+$^{233}$U case are observed in the inner core zone ($R\lesssim150$) than 
+in the outer core zone. In contrast, for the reactor-grade Pu and TRU cases, 
+significant changes are observed for thermal neutron flux in the outer core 
 zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
 relatively large changes in thermal flux leakage from the core for the Pu and 
-TRU cases. Overall, the SD-TMSR core design was optimized for $^{233}$U 
-fissile isotope \cite{li_optimization_2018}; thus, the core geometry (e.g., 
-fuel channels lattice pitch) must be re-optimized for another type of fuel to 
-obtain better neutronics performance.
+TRU cases. The SD-TMSR core design was optimized for $^{233}$U  
+\cite{li_optimization_2018}; thus, the core geometry (e.g., channels lattice 
+pitch) must be re-optimized for another type of fuel to obtain better 
+neutronics performance.
 
@@
 The temperature coefficient of reactivity quantifies reactivity changes due to 
-temperature increase in the core and was calculated in this work as follows:
+temperature increase in the core and is calculated in this work as follows:
 \begin{align}
@@
 Table~\ref{tab:tcoe} summarizes temperature coefficients calculated for three 
-different initial fissile loads at the startup and at the equilibrium. By 
-propagating the $k_{eff}$ statistical error provided by SERPENT-2, 
-uncertainty for each temperature coefficient was calculated using formula:
+different initial fissile loads at startup and at equilibrium. By propagating 
+the $k_{eff}$ statistical error provided by SERPENT-2, uncertainty for each 
+temperature coefficient is calculated using the following formula:
 \begin{align}
@@
 \end{align}
-Notably, other sources of uncertainty are neglected, such as cross-section 
-measurement error and approximations inherent in the density dependence on 
-temperature.
+Other sources of uncertainty are neglected, such as cross-section measurement 
+error and approximations inherent in the density dependence on temperature.
 
-When the fuel salt temperature increases, the density of the salt decreases, 
-but at the same time, the total volume of fuel salt in the 
-core remains constant because it
-is bounded by the vessel. When the graphite 
-temperature increases, the density of
-graphite decreases, creating additional 
-space for the salt. The cross-section temperatures for the fuel and moderator 
-were changed from 900 to 1000 K to determine the temperature coefficients. 
-This work considered five different cases:
+When the fuel salt temperature increases, the density of the salt decreases; 
+however, the total volume of fuel salt in the core remains constant because it
+is bounded by the vessel. When the graphite temperature increases, the density 
+of graphite decreases, creating additional space for the salt. The 
+cross-section temperatures for the fuel and moderator were changed from 900 to 
+1000 K to determine the temperature coefficients. This work considers five 
+different cases:
 \begin{enumerate}
@@
 these three cases is unchanged because the fuel is a liquid. However, when 
-the graphite blocks heat up, both the density and the geometry changing due 
+the graphite blocks heat up, both the density and the geometry change due 
 to the thermal expansion of solid graphite. The graphite linear thermal 
 expansion is not a dominating factor \cite{li_optimization_2018}, and herein 
-we focus only on Doppler Effect for the moderator temperature coefficient.
+we focus only on the Doppler Effect for the moderator temperature coefficient.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The \gls{FTC} is negative for all considered fuel compositions due to thermal 
-Doppler broadening of the resonance capture cross-sections in the thorium. For the 
-$^{233}$U case, the \gls{FTC} decreases in magnitude by $-25\%$ due to neutron 
-spectrum hardening during the reactor operation. For Pu reactor-grade and TRU 
-cases, the \gls{FTC} becomes more negative at the equilibrium, by $+31\%$ and 
-$+14\%$, respectively. Spectrum softening for these fueling cases positively 
-affects the \gls{FTC} magnitude, and this effect seems to be proportional to 
-the spectrum shift.
+Doppler broadening of the resonance capture cross sections in the thorium. For 
+the $^{233}$U case, the \gls{FTC} decreases in magnitude by $25\%$ due to 
+neutron spectrum hardening during the reactor operation. For reactor-grade Pu 
+and TRU cases, the \gls{FTC} increases in magnitude at equilibrium, by $31\%$ 
+and $14\%$, respectively. Spectrum softening for these fueling cases 
+positively affects the \gls{FTC} magnitude, and this effect seems to be 
+proportional to the spectrum shift.
 
@@
 operation because of spectrum hardening with fuel depletion. For other cases, 
-the \gls{MTC} is negative and also decreasing in magnitude during the reactor 
+the \gls{MTC} is negative and also decreases in magnitude during reactor  
 operation. Finally, the total temperature coefficient of reactivity is 
@@
 during reactor operation due to spectral shift. Notably, the total temperature 
-coefficient is the most negative for the Pu reactor-grade case at startup, 
+coefficient is the most negative for the reactor-grade Pu case at startup, 
 which has the hardest neutron spectrum (Figure~\ref{fig:spectrumFLUX110vC}). 
-These coefficients agree with earlier estimates for SD-TMSR 
+These coefficients agree with earlier estimates for the SD-TMSR 
 \cite{li_optimization_2018, ashraf2019whole_core} and \gls{MSBR} 
-\cite{rykhlevskii2019modeling,  
-rykhlevskii_full-core_2017,robertson_conceptual_1971}.
+\cite{rykhlevskii2019modeling, rykhlevskii_full-core_2017,  
+robertson_conceptual_1971}.
 
@@
 reactivity remains relatively large and negative (in the range between $-2.59$ 
-and $-5.06$ pcm/K) comparing with the conventional \gls{PWR}, which has 
+and $-5.06$ pcm/K) compared to the conventional \gls{PWR}, which has 
 temperature coefficient of about $-1.71$ $pcm/^{\circ}F\approx -3.08$ $pcm/K$ 
-\cite{forget_integral_2018}), and allows excellent reactor stability and 
+\cite{forget_integral_2018}, and allows excellent reactor stability and 
 control. The additional analysis must be performed taking graphite moderator 
@@
 properties for the SD-TMSR graphite are not available in published literature. 
-Alternatively, relatively well-studied reactor graphite (e.g., AXQ graphite 
+Relatively well-studied reactor graphite (e.g., AXQ graphite 
 \cite{robertson_conceptual_1971}) can be considered as a candidate for the 
@@
 \begin{align}
-k_{eff} &= k_{inf} P_f  P_t = \eta f p \epsilon P_f P_t
+k_{eff} &= \eta f p \epsilon P_f P_t
 \intertext{where}
@@
 fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
-online reprocessing capabilities, all six factors have been calculated at the 
+online reprocessing capabilities, all six factors are calculated at the 
 beginning of the operation and after 30 years of operation. Neutron population 
@@
 neutron spectrum shift during operation. The thermal utilization factor (f) 
-remains almost constant during operation for $^{233}$U and TRU cases but 
-considerably declines for Pu case due to significant neutron spectrum 
+remains almost constant during operation for the $^{233}$U and TRU cases but 
+considerably declines for the Pu case due to significant neutron spectrum 
 softening.
@@
 probability ($p$), and fast fission factor ($\epsilon$) differ notably between 
-initial and equilibrium state for all three initial fissile materials. The 
-fast fission factor ($\epsilon$) is much larger at startup for Pu and TRU 
-cases because these initial fissile materials provided a much harder neutron 
-spectrum than $^{233}$U, and $\epsilon$ grows throughout the core's lifetime. 
-Conversely, the resonance escape probability decreases during reactor 
-operation. The thermal fission factor increases during reactor operation for 
-the $^{233}$U as initial fuel due to the accumulation of fissile plutonium 
-isotopes, which produce more neutrons per fission ($\nu$). The other two 
-scenarios demonstrated opposite behavior: plutonium isotopes with large 
-neutrons per fission production ($\nu$) are gradually substituted with the 
-$^{233}$U, which has lower $\nu$ \cite{sjostrand_cross_1960}. This six 
-factors' evolution agrees with previously determined evolution parameters for 
-a similar single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
+the initial and equilibrium state for all three initial fissile materials.  
+$\epsilon$ is much larger at startup for the Pu and TRU cases because these 
+initial fissile materials provide a much harder neutron spectrum than 
+$^{233}$U, and $\epsilon$ grows throughout the core's lifetime. Conversely, 
+$p$ decreases during reactor operation. The thermal fission factor ($\eta$)  
+increases during reactor operation for the $^{233}$U as initial fuel due to 
+the accumulation of fissile plutonium isotopes, which produce more neutrons 
+per fission ($\nu$). The other two scenarios demonstrate opposite behavior: 
+plutonium isotopes with large $\nu$ are gradually substituted with $^{233}$U, 
+which has a lower $\nu$ \cite{sjostrand_cross_1960}. This six factors' 
+evolution agrees with previously determined evolution parameters for a similar 
+single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
 rykhlevskii2019modeling, park_whole_2015}.

### 2019-10-25 paper/introduction.tex

@@
 circulates through the core and allows fission heat to transfer from the reactor
-core to intermediate heat exchanger.
+core to intermediate heat exchangers.
 

### 2019-10-25 paper/results.tex
Addressed issues

--- 2019-10-25 paper/results.tex
@@
 four cases. $k_{eff}$ decreases as a result of depletion of the initial 
-fissile materials and production of poisonous fission products \gls{FPs}. Thus, the 
+fissile materials and production of poisonous fission products (FPs). Thus, the 
 reactor becomes subcritical relatively quickly for alternative startup 
@@
 \end{align}
-Notably, other sources of uncertainty are neglected, such as cross-section 
+Notably, other sources of uncertainty are neglected, such as cross section 
 measurement error and approximations inherent in the density dependence on 
@@
 graphite decreases, creating additional 
-space for the salt. The cross-section temperatures for the fuel and moderator 
+space for the salt. The cross section temperatures for the fuel and moderator 
 were changed from 900 to 1000 K to determine the temperature coefficients. 
@@
 
-In the first case, the fuel temperature change only impacts cross-section 
+In the first case, the fuel temperature change only impacts cross section 
 temperature. In the second case, changes in the fuel temperature only impact 
@@
 The \gls{FTC} is negative for all considered fuel compositions due to thermal 
-Doppler broadening of the resonance capture cross-sections in the thorium. For the 
+Doppler broadening of the resonance capture cross sections in the thorium. For the 
 $^{233}$U case, the \gls{FTC} decreases in magnitude by $-25\%$ due to neutron 

### 2019-10-25 paper/conclusion.tex
Addressed issues

@@
 \section{Conclusion} \label{Conclusion}
-
-Five different types of initial fissile loadings are considered to investigate 
-transitioning to the thorium fuel cycle in the SD-TMSR. We adopted two 
-different feed mechanisms: thorium feed mechanism and non-thorium feed 
-mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
+Five different types of initial fissile loadings have been studied for 
+transitioning to the thorium fuel cycle in the Single-fluid Double-zone 
+Thorium-based Molten Salt Reactor (SD-TMSR). We 
+adopted two different feed mechanisms: thorium feed mechanism and non-thorium 
+feed mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
 performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 

### 2019-10-25 paper/results.tex

--- 2019-10-25 paper/results.tex
@@
 \end{align}
-Other sources of uncertainty are neglected, such as cross-section measurement 
+
+Other sources of uncertainty are neglected, such as cross section measurement 
 error and approximations inherent in the density dependence on temperature.
 
-When the fuel salt temperature increases, the density of the salt decreases; 
-however, the total volume of fuel salt in the core remains constant because it
-is bounded by the vessel. When the graphite temperature increases, the density 
-of graphite decreases, creating additional space for the salt. The 
-cross-section temperatures for the fuel and moderator were changed from 900 to 
-1000 K to determine the temperature coefficients. This work considers five 
-different cases:
+When the fuel salt temperature increases, the density of the salt decreases, 
+but at the same time, the total volume of fuel salt in the 
+core remains constant because it
+is bounded by the vessel. When the graphite 
+temperature increases, the density of
+graphite decreases, creating additional 
+space for the salt. The cross section temperatures for the fuel and moderator 
+were changed from 900 to 1000 K to determine the temperature coefficients. 
+This work considered five different cases:
 \begin{enumerate}

### 2019-11-17 paper/abstract.tex
Abstract edits except #23

@@
 Liquid-fueled \gls{MSR} systems represent advances in safety, economics, sustainability, and proliferation resistance.
-The \gls{MSR} has been designed to operate in Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material.
-Since $^{233}$U does not exist in nature, We must examine other available fissile materials.
-This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{LEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), reactor-grade Pu (a mixture of Pu isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
+The \gls{MSR} has been designed to operate with a Th/$^{233}$U fuel cycle with $^{233}$U used as startup fissile material.
+Since $^{233}$U does not exist in nature, we must examine other available fissile materials to start up these reactor concepts.
+This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{HALEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), reactor-grade Pu (a mixture of Pu isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
 The \gls{MSR} burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}.
-The effective multiplication factor, fuel salt composition evolution and net production of $^{233}$U are studied in the present work.
+The effective multiplication factor, fuel salt composition evolution, and net production of $^{233}$U are studied in the present work.
 Additionally, the neutron spectrum shift during the reactor operation is calculated.
 The results show that the continuous flow of reactor-grade Pu helps transition to the thorium fuel cycle within a relatively short time ($\approx$ $4.5$ years) compared to $26$ years for $^{233}$U startup fuel.
-Finally, using \gls{TRU} as initial fissile materials offers the possibility of operating the SD-TMSR for an extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
+Finally, using \gls{TRU} as the initial fuel materials offers the possibility of operating the SD-TMSR for an extended period of time ($\approx$ $40$ years) without any external feed of $^{233}$U.
 \end{abstract}
-
-%The SD-TMSR (2,250 MW$_{th}$) is a Single-fluid Double-zone Thorium-based Molten Salt Reactor.
-The active core of the SD-TMSR is divided into the inner zone (486 fuel tubes) and the outer zone (522 fuel tubes) to improve the Th-U breeding performance.
-The lack of computational reactor analysis software that deal with MSR cores prevents improvement.
-This work adopted the SERPENT-2 Monte Carlo code to analyze the whole core model of the SD-TMSR.
-Built-in SERPENT-2 capabilities simulated online reprocessing and refueling and calculated the multiplication factor and Breeding Ratio (BR).
-We found that the molten salt Temperature Coefficient of Reactivity $(\alpha$$_{T}$) was negative for initial and equilibrium states.
-This study investigated the variation of the multiplication factor, BR, and build-up of important nuclides in the core as a function of burn-up time.
-Under online reprocessing and refueling, we studied the variation of the reactivity during 60 years of reactor operation.
-The present work has introduced a feasible reprocessing scheme.
-In addition, it has investigated the neutron flux energy spectrum at initial and equilibrium state.
-%In conclusion, the full core of SD-TMSR was modeled and the net production of $^{233}$U was found to be positive.
-
-%Therefore, \gls{MSR} has been selected as one of the promising reactors by the \gls{GIF}.

### 2019-11-17 paper/introduction.tex
Introduction edits except #25

--- 2019-10-25 paper/introduction.tex
@@
 reactors \cite{doe2002technology,pioro2016handbook}.
-In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl);
+In \glspl{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl) \cite{betzler_impacts_2019};
 this liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly
 circulates through the core and allows fission heat to transfer from the reactor
-core to intermediate heat exchanger.
+core to intermediate heat exchangers.
 
@@
 is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
-fuel cycle. In the SD-TMSR the fissile and fertile elements are integrated
-into the same salt. The active core is divided into two zones;
+fuel cycle. In the SD-TMSR, the fissile and fertile elements are integrated
+into a single salt. To improve the breeding ratio, the active core is divided into two zones:
 the radius of the fuel channels in the outer zone is modified to be larger
-than the radius of the fuel channels in the inner zone to improve the breeding
-ratio \cite{nuttin2005potential,li_optimization_2018}.
+than the radius of the fuel channels in the inner zone \cite{nuttin2005potential,li_optimization_2018}.
 
@@
 cycle transition can be achieved after reaching the doubling
-time\footnote{Time required to produce enough amount of $^{233}$U to trigger a
-	new SD-TMSR.} of $^{233}$U because in this case, all startup fissile material
+time - time required to produce enough amount of $^{233}$U to trigger a
+	new SD-TMSR - of $^{233}$U because in this case, all startup fissile material
 is being substituted by newly produced $^{233}$U.
@@
 cycle in a small modular Thorium-based Molten Salt Reactor (smTMSR) using \gls{TRU}
-as startup fuel. They concluded that the transition to the thorium fuel cycle can
+as startup fuel. They concluded that the transition to a thorium fuel cycle can
 be achieved in a thermal smTMSR with a proper fuel fraction 
@@
 Heuer \emph{et al.} (2014) discussed the transition characteristics of the \gls{MSFR}
-under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible while closing the current fuel cycle and adopting stockpile incineration in MSRs for optimizing the long-term waste management \cite{heuer2014towards}.
+under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible in the MSFR while closing the current fuel cycle and optimizing the management of the long-term wastes.
+\cite{heuer2014towards}.
 
-There are various researches that revolve around starting the
-\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these
-researches focus on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
+Various previous works explore starting the
+\glspl{MSR} with fissile materials alternative to $^{233}$U. Many such publications have focused on the fast-spectrum \glspl{MSR} \cite{heuer2014towards,ashraf2019modeling,
 	ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019,
@@
 thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
-	zou2018transition,zou2018preliminary}. Simulating the operation of the \gls{SD-TMSR} concept with other
+	zou2018transition,zou2018preliminary}. For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other
 fissile materials (except $^{233}$U) has not been studied before. Therefore,
-the main objective of the present paper is to discuss the simulation of the
-\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with
-different initial fissile materials and without any external feed of $^{233}$U
-to achieve the thorium fuel cycle transition. We investigate five different
-initial fissile materials: \gls{LEU}, Pu mixed with \gls{LEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U \cite{de2000scenarios}. Two different feed mechanisms were selected:
+the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with
+various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
+initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U \cite{de2000scenarios}. Two different feed mechanisms were selected:
 
 \begin{itemize}
-	\item Thorium feed mechanism: continuous feed flow of thorium from the thorium stockpile and $^{233}$U from the \texttt{Pa-decay tank}\footnote{An imaginary tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
+	\item Thorium feed mechanism: continuous feed flow of thorium from the thorium stockpile and $^{233}$U from the \texttt{Pa-decay tank}\footnote{An external tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
 \cite{betzler2016modeling}.
-	\item Non-thorium feed mechanism: continuous injection of heavy metal (excluding Th) and simultaneous feed of all or fraction of $^{233}$U from the \texttt{Pa-decay tank}.
+	\item Non-thorium feed mechanism: continuous injection of the same initial heavy metals (excluding Th) and simultaneous feed of all or fraction of $^{233}$U from the \texttt{Pa-decay tank}.
 \end{itemize}
@@
 We use the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling.
-SERPENT-2 uses an internal calculation routine for solving the set of Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}.
-Additionally, SERPENT-2 allows us to conduct the burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.
+SERPENT-2 uses an internal calculation routine for solving the Bateman equations describing the changes in the material compositions caused by neutron-induced reactions and radioactive decay \cite{leppanen2014serpent}.
+Additionally, SERPENT-2 enables burnup calculations on computer clusters with multiple cores using distributed-memory MPI parallelization.
 

### 2019-11-18 paper/introduction.tex
Methods edits except #26

@@
 cycle transition can be achieved after reaching the doubling
-time - time required to produce enough amount of $^{233}$U to trigger a
-	new SD-TMSR - of $^{233}$U because in this case, all startup fissile material
+time $-$ time required to produce enough amount of $^{233}$U to trigger a
+	new SD-TMSR $-$ of $^{233}$U because in this case, all startup fissile material
 is being substituted by newly produced $^{233}$U.
@@
 This paper is organized as follows: section \ref{Introduction} introduces \gls{MSR} systems, section \ref{Model-description} discusses the model description, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Feed-and-extraction-rates} addresses extraction and feed mechanisms, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.
-
-%produce enough amount of $^{233}$U to start a new \gls{SD-TMSR}.
-%Therefore, the aim of this paper is to operate the \gls{SD-TMSR} for a long 
-%period of time with different initial fissile materials without external feed 
-%of $^{233}$U (that does not exist anywhere) to produce enough amount of 
-%$^{233}$U that is required to start a new \gls{SD-TMSR}.
-
-%The \gls{MSR} is the only liquid-fueled reactor that the \gls{GIF} has chosen 
-%as one of the six promising concepts 
-%\cite{doe2002technology,pioro2016handbook}. The reactor's liquid fuel 
-%distinguishes it from other nuclear reactors. \glspl{MSR} can operate 
-%extended 
-%time without shutdown for refueling with a superior neutron economy 
-%\cite{doe2002technology}. Introducing online reprocessing and refueling 
-%systems would ensure sustainability. In a \gls{MSR}, liquid fuel salt (e.g. a 
-%mixture of LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) circulates through the core 
-%and 
-%transports fission heat to the \glspl{IHX}. Finally, this type of reactor has 
-%a high conversion efficiency and a negative temperature coefficient.
-
-%Both thermal and fast \gls{MSR} concepts exist in the literature 
-%\cite{pioro2016handbook,engel1979development}. For thermal \glspl{MSR}, 
-%hexagonal graphite prisms act as moderators. In contrast, fast spectrum 
-%\glspl{MSR} lack moderators. A \gls{MSR} can breed in both cases, making them 
-%optimal for realizing a desirable Thorium-Uranium fuel cycle 
-%\cite{hargraves2010liquid}.
-
-%In the 1950s, \gls{ORNL} performed experiments that provided a basis for 
-%\gls{MSR} feasibility. In 1958, a 5 MW$_{th}$ homogeneous reactor experiment 
-%called HRE-2 utilized water-based liquid fuel to illustrate the intrinsic 
-%stability of homogeneous reactors. In the 1960s, \gls{ORNL} performed the 
-%\gls{MSRE} 
-%\cite{engel1979development,haubenreich1970experience,fiorinibasis,robertson1965msre}.
-% These experiments demonstrated the capability of circulating a liquid 
-%fluoride mixture without significant corrosion problems. Researchers used a 
-%nickel-based alloy (Hastelloy N) as structural material and controlled the 
-%fuel's oxidation by using a U$^{3+}$/U$^{4+}$ buffer. The experiment also 
-%tested the continuous reprocessing of liquid fuel. The results showed that 
-%introducing a noble gas system (i.e. gas bubbling system) during the fuel 
-%cycle helps extract gaseous fission products \cite{pioro2016handbook}.
-
-%\gls{ORNL} later researched the \gls{MSBR} \cite{rosenthal1970molten}. There 
-%were two types of \gls{MSBR}: the single-fluid molten salt reactor and the 
-%two-fluid molten salt reactor. While the single-fluid MSR dissolves fertile 
-%and fissile materials in the same salt, the two-fluid MSR physically 
-%separates 
-%them. The two-fluid MSR had a higher breeding performance than the 
-%single-fluid MSR. However, the single-fluid MSR can operate as an 
-%iso-breeding 
-%reactor as long as there is an efficient reprocessing system for the fuel 
-%salt 
-%\cite{rosenthal1970molten}.
-
-%Despite the success of the \gls{MSRE}, \gls{ORNL} halted work on the 
-%\gls{MSBR} in 1976. The \gls{Euratom} later revived the project. To enhance 
-%the breeding performance of the \gls{MSBR}, \gls{Euratom} introduced the idea 
-%of dividing the core into multiple zones of fuel channels with different 
-%radii 
-%\cite{nuttin2005potential}. The results showed that increasing the radii of 
-%the outer fuel channels relative to the inner radii improved the reactor's 
-%breeding and allowed it to out-perform the reactor with a single-zone core 
-%and 
-%large fuel channels \cite{nuttin2005potential}.
-
-%Later, fast spectrum MSRs were introduced. Several fast MSR designs include: 
-%\gls{MSFR}, \gls{EVOL} \cite{serp2014molten}, \gls{MOSART} 
-%\cite{boussier2012molten}, REBUS-3700 \cite{mourogov2006potentialities} and 
-%Molten Chloride Salt Fast Reactor \cite{taube1978fast}. \gls{GIF} has elected 
-%to further research \gls{MSFR} and \gls{MOSART} 
-%\cite{serp2014molten,boussier2012molten,locatelli2013generation,pettersen2016coupled}.
-% Both designs feature the fast-spectrum, Th-based fuel, and liquid fuel 
-%circulation. The \gls{MSFR} concept initially gained momentum at \gls{CNRS} 
-%in 
-%France, and the \gls{MOSART} concept is in progress in Russia.
-
-%Indeed, several challenges interfere with the commercial adoption of 
-%\gls{MSFR}. For example, large initial inventory of $^{233}$U and relatively 
-%long doubling time for $^{233}$U production. Moreover, material scientists 
-%must identify or create structural materials which have reasonable lifespan 
-%in 
-%extreme operational conditions (high temperature, large neutron flux, 
-%chemically aggressive salt). Finally, breeding of high-quiality fissile 
-%material in the \gls{MSFR} blanket rises significant nuclear 
-%non-proliferation 
-%concerns \cite{pettersen2016coupled,merle2009minimizing}.
-
-%The thermal MSR has priority due to the low inventory of initial fissile 
-%$^{233}$U and short doubling time for its production \cite{ZOU2015114}.
-%Nagy et al. studied the effect of core zoning on the breeding performance and 
-%graphite lifespan of a graphite-moderated MSR 
-%\cite{nagy2011new,nagy2012effects}. Li et al. divided the active core into 
-%two 
-%zones to improve the breeding performance \cite{li_optimization_2018}. The 
-%central zone is moderated, while the unmoderated outer zone acts as a 
-%subcritical fast spectrum zone \cite{li_optimization_2018}.
-
-%In 2011, the \gls{CAS} established the strategic project ``Future Advanced 
-%Nuclear Energy $-$ Thorium-based Molten Salt Reactor System (TMSR)". Since 
-%then, several studies aimed to improve the \gls{TMSR} to efficiently utilize 
-%the Th-U fuel cycle 
-%\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}.
-%Separately, we can highlight the issue of a closed Th-U fuel cycle in the 
-%thermal spectrum. A number of studies have shown the fundamental possibility 
-%of organizing such a cycle in a heavy-water reactor and referred to the 
-%limitation of the burn-up of solid fuels due to the accumulation of the 
-%fission products (FPs) 
-%\cite{dastur1995thorium,bergel2004mode,bergelson2008op}. The question of 
-%feasibility and parameters of a closed U-Th fuel cycle in a \gls{TMSR} 
-%reactor 
-%is relevant.
-
-%Liquid-fueled systems require specific neutron transport and depletion tools 
-%that capture online fuel reprocessing and refueling. Specifically, the 
-%circulation of the liquid fuel and the continuous feed or removal of elements 
-%(e.g. fissile material injection into and Fission Products (FPs) extraction 
-%from the fuel salt) are out-of-scope for most contemporary nuclear reactor 
-%physics software, which was originally written primarily to simulate 
-%solid-fueled reactors. The SERPENT-2 \cite{leppanen2014serpent} code 
-%extension 
-%takes into account the online fuel reprocessing and its effects on depletion 
-%calculations \cite{aufiero2013extended}.
-
-%The present paper aims to analyze the fuel depletion of the \gls{SD-TMSR} 
-%during 60 years reactor operation time using SERPENT-2. This work 
-%investigates 
-%the inventory of isotopes in the core to establish the advantages of the 
-%\gls{TMSR} concept applied to energy production (based on the thorium fuel 
-%cycle). All calculations presented in the present work were implemented using 
-%SERPENT-2 version 2.1.30. We adopted the built-in SERPENT-2 subroutine to 
-%simulate continuous online reprocessing and refueling in contrast with other 
-%batch-wise codes \footnote{In the batch-wise technique, the simulation stops 
-%at a certain time and restarts after removing of poisoning isotopes and 
-%addition of fissile and/or fertile materials.} (e.g. SaltProc 
-%\cite{rykhlevskii2019modeling} and MCNP6-PYTHON \cite{Jeong2016}).
-%SERPENT-2 allowed us to conduct burn-up calculations on computer clusters 
-%with multiple cores using distributed-memory MPI parallelization. The drift 
-%of 
-%the delayed neutron precursors is not examined in this paper.
-
-%The present paper is organized as follows: after a general introduction about 
-%\gls{MSR} systems, section 2 briefly presents the \gls{SD-TMSR}. Section 3 
-%focuses on the methodology and calculation tools used in this work. Fission 
-%products extraction modeling is described in section 4. Section 5 highlights 
-%the results and discussion. Finally, section 6 summarizes the conclusions.

### 2019-11-18 paper/methods.tex
Methods edits except #26

--- 2019-10-25 paper/methods.tex
@@
 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design model was introduced by the Chinese Academy of Sciences as a part of  
-the strategic project ``Future Advanced Nuclear Energy $-$ Thorium-based 
-Molten Salt Reactor System (TMSR)" in 2011 
-\cite{li_optimization_2018,jiang2012advanced,li2015analysis,li2017model}. The 
+the strategic project ``Thorium-based Molten-Salt Reactor(TMSR) nuclear energy system" 
+\cite{jiang2012advanced,li2015analysis,li_optimization_2018}. The 
 design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
 \cite{robertson_conceptual_1971} after modifying the geometry to 
-control the positive temperature coefficient in the MSBR. The \gls{SD-TMSR} core 
-geometry is described in detail by Li \emph{et al.} 
-\cite{li_optimization_2018};
-Figure~\ref{fig:ff} illustrates the quarter-core model configuration of the 
-\gls{SD-TMSR}. The active zone is a right cylinder with height and diameter 
+control the positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.} 
+described the \gls{SD-TMSR} core 
+geometry in \cite{li_optimization_2018,ashraf2019whole_core}. 
+Figure~\ref{fig:ff} illustrates the quarter-core view of the 
+\gls{SD-TMSR}.
+The active zone is a right cylinder with height and diameter 
 equal to 460 cm. Assemblies of graphite\footnote{We choose graphite density of 
@@
 \cite{li_optimization_2018,nuttin2005potential}.} hexagonal prisms fill the 
-core. The optimal side length of the graphite hexagonal prism is found to be 7.5 cm \cite{li_optimization_2018}. The liquid fuel circulates 
-continuously through the fuel channels that pierce the graphite hexagonal 
-prisms. The core is divided into two different zones to enhance 
+core. The optimal side length of the graphite hexagonal prism was found in previous work to be 7.5 cm \cite{li_optimization_2018}. The liquid fuel circulates 
+continuously through fuel channels that pierce the graphite hexagonal 
+prisms. Two radial zones divide the core to enhance 
 Th/$^{233}$U breeding performance; the radii of the fuel channels in the 
@@
 graphite reflectors surround the core to minimize neutron leakage and 
-maximize flux in the core. The reflectors are surrounded by a B${_4}$C cylinder 
-that acts as radiation shielding. The \gls{SD-TMSR} pressure vessel holds 
-the fuel salt, graphite elements, reflector, shielding, intermediate heat exchanger, and is made of a Ni-based (hastelloy N) alloy. The main 
+maximize flux in the core. B${_4}$C cylinder surrounds the reflectors and 
+acts as radiation shielding. The \gls{SD-TMSR} pressure vessel is made of a Ni-based (hastelloy N) alloy holds 
+the fuel salt, graphite elements, reflector, shielding, and intermediate heat exchanger. The main 
 characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{l | l}
+	\begin{tabularx}{\textwidth}{l | r}
 		\hline
@@
 17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (mixture of 
-thorium and other actinides). The aim of this paper is to simulate the  
-operation of \gls{SD-TMSR} for 60 years with different startup fissile 
+thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U).
+The aim of this paper is to simulate the  
+operation of the \gls{SD-TMSR} for 60 years with various startup fissile 
 compositions and without any external feed of fissile $^{233}$U which we 
 assume is unavailable. For that reason, five different types of initial 
-fissile materials are considered based on \gls{LEU}, Pu, and \gls{TRU} from Light Water
+fissile materials are considered based on \gls{HALEU}, Pu, and \gls{TRU} from Light Water
 Reactor (LWR) spent nuclear fuel (SNF):
 \begin{enumerate}[label=(\alph*)]
-	\item low-enriched uranium (LEU) (19.79\%),
-	\item Pu mixed with \gls{LEU} (19.79\%),
+	\item High Assay Low Enriched Uranium (HALEU) (19.79\%),
+	\item Pu mixed with \gls{HALEU} (19.79\%),
 	\item reactor-grade Pu \cite{marka1993explosive},
@@
 \end{enumerate}
-
+All types of initial fissile materials are fed as fluorides.
 The reactor-grade Pu and \gls{TRU} compositions are summarized in 
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{s s s s s}
+	\begin{tabularx}{\textwidth}{r r r r r}
 		\hline
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{s s s s s s s s s s}
+	\begin{tabularx}{\textwidth}{r r r r r r r r r r}
 		\hline
@@
 reprocessing \cite{oecd1989probabilistic,marka1993explosive}. Similarly, the 
-isotopic compositions of \gls{TRU} are taken for the SNF of uranium oxide \gls{PWR} 
+isotopic compositions of \gls{TRU} reflect the composition of the \gls{PWR} UOX SNF 
 (after one use, no multi-recycling) with an average discharge of $60$ 
@@
 Table~\ref{tab:table4}. Additionally, the corresponding initial nuclei 
-inventories with different types of fuel are summarized in 
+inventories with various fissile fuel options are summarized in 
 Table~\ref{tab:table5}.
@@
 		\hline
-		LiF&70&70&70&70&70\\
+		LiF&70.0&70.0&70.0&70.0&70.0\\
 		BeF$_2$&17.5&17.5&17.5&17.5&17.5\\
-		ThF$_4$&8.25&7.5&10.75&	8.65&12.3		\\
-		UF$_4$&4.25&4.75&&&	0.2		\\
+		ThF$_4$&8.25&7.50&10.75&	8.65&12.3		\\
+		UF$_4$&4.25&4.75&&&	0.20		\\
 		PuF$_3$&&0.25&1.75&&		\\
@@
 	\caption{Initial heavy metal inventories for 
-	different initial fissile loadings (g).}
+	various initial fissile loadings (kg).}
 	\vspace{0.1in}
@@
 		reactor-grade Pu & \gls{TRU}& $^{233}$U \\	\hline
-		$^{232}$Th       &6.24E+07 & 4.67E+07 &   6.75E+07			& 5.44E+07	& 7.69E+07    \\ 
+		$^{232}$Th       &6.24E+04 & 4.67E+04 &   6.75E+04			& 5.44E+04	& 7.69E+04    \\ 
 		$^{233}$U        &         & &        &       &  1.30E+06 \\
-		$^{235}$U        & 3.17E+06 &6.01E+06	&            &   & \\
-		$^{238}$U      	 &1.28E+07  &2.43E+07 &	&  &\\
-		$^{237}$Np	  	 &         && &1.58E+06	&    \\
-		$^{238}$Pu	  	 &         &1.60E+04	& 1.13E+05 & 6.78E+05	&   \\
-		$^{239}$Pu       &         &9.59E+05&6.76E+06& 1.15E+07&    \\
-		$^{240}$Pu       &         &3.99E+05& 2.82E+06&5.40E+06&  	\\  
-		$^{241}$Pu		 &         &1.60E+05&1.13E+06&2.69E+06&   \\
-		$^{242}$Pu		 &         &6.39E+04	&4.51E+05	& 1.68E+06& \\
-		$^{241}$Am		 &         &&& 8.53E+05 & \\
+		$^{235}$U        & 3.17E+03 &6.01E+03	&            &   & \\
+		$^{238}$U      	 &1.28E+04  &2.43E+04 &	&  &\\
+		$^{237}$Np	  	 &         && &1.58E+03	&    \\
+		$^{238}$Pu	  	 &         &1.60E+01	& 1.13E+02 & 6.78E+02	&   \\
+		$^{239}$Pu       &         &9.59E+02&6.76E+03& 1.15E+04&    \\
+		$^{240}$Pu       &         &3.99E+02& 2.82E+03&5.40E+03&  	\\  
+		$^{241}$Pu		 &         &1.60E+02&1.13E+03&2.69E+03&   \\
+		$^{242}$Pu		 &         &6.39E+01	&4.51E+02	& 1.68E+03& \\
+		$^{241}$Am		 &         &&& 8.53E+02 & \\
 		$^{242}$Am		 &         &&&  &\\
-		$^{243}$Am       &        & &&4.77E+05&\\
-		$^{244}$Cm		 &        & &&2.01E+05&  \\
-		$^{245}$Cm		 &        & &&			2.51E+04	&   \\ \hline
-		Total$^{\ast}$           & 1.60E+07& 3.20E+07&1.13E+07&  2.51E+07&   1.30E+06  
-		\\
+		$^{243}$Am       &        & &&4.77E+02&\\
+		$^{244}$Cm		 &        & &&2.01E+02&  \\
+		$^{245}$Cm		 &        & &&			2.51E+01	&   \\ 
 		\hline
 	\end{tabularx}
-\begin{tablenotes}
-	\small
-	\item $^{\ast}$ Excluding $^{232}$Th inventory.
-\end{tablenotes}
 \label{tab:table5}
@@
 Simulation of liquid-fueled Molten Salt Reactor (MSR) systems requires 
-computational software that must support online fuel salt reprocessing and 
+computational software that can support online fuel salt reprocessing and 
 refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 
-beta\footnote{SERPENT-2 is a 3D continuous energy Monte Carlo neutron 
-transport and burnup code.} \cite{leppanen2014serpent} is used to simulate the 
-full-core of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with different types of initial fuel. The extension 
+\footnote{SERPENT-2 is a 3D continuous energy Monte Carlo neutron 
+transport and burnup code.} \cite{leppanen2014serpent} simulates the 
+Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
 of SERPENT accounts for continuous online reprocessing and refueling 
@@
 $12$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
-provides many benefits for MSRs. For example, it would reduce the initial 
+provides many benefits for MSRs. For example, it has the potential to reduce the initial 
 fissile material inventory required to achieve criticality and improve the 
@@
 \begin{figure}[t!] % replace 't' with 'b' to \centering
-	\includegraphics[width=\textwidth]{flowch.png}
-	\caption{Flow chart of the calculation procedures.}
+	\includegraphics[width=\textwidth]{flowch1.png}
+	\caption{Flow chart of the calculation procedures (implemented by SERPENT-2).}
 	\label{fig:flow}
@@
 
-As shown in Figure~\ref{fig:flow}, after launching the input file, we solve the Bateman equation using an advanced 
+As shown in Figure~\ref{fig:flow}, after launching the input file, SERPENT solves the Bateman equation using an advanced 
 matrix exponential solution based on the Chebyshev Rational Approximation 
@@
 flow rate of gaseous \gls{FPs} and other materials from the fuel to the 
-\texttt{FP-waste tank}\footnote{An imaginary tank used to store the gaseous 
+\texttt{FP-waste tank}\footnote{An external tank used to store the gaseous 
 \gls{FPs} and the other materials (non-dissolved metals, lanthanides, and 
@@
 $\approx$ $27$ $d$.}. The produced $^{233}$U is used as a fresh fissile fuel 
-and the residual $^{233}$U is the net production of $^{233}$U. The MSR burnup 
-routine provided by SERPENT-2 allows changes to the flow rates ($mflow$) of the 
-isotopes during reactor operation \cite{aufiero2013extended}. Specifically, we have to determine the flow rate ($mflow$), which is the rate by 
+and the residual $^{233}$U (if exist) is the net production of $^{233}$U that required to start up a new SD-TMSR and achieve the transition to thorium fuel cycle. The MSR burnup 
+routine provided by SERPENT-2 allows changes to the mass flow rates ($mflow$) of the 
+isotopes during reactor operation \cite{aufiero2013extended}. Specifically, the SERPENT user should determine the mass flow rate ($mflow$), which is the rate by 
 which elements or nuclides are transferred between materials. After that, the 
 flow rates must be connected to materials with a reprocessing scheme. 
-Finally, we have to link the reprocessing schemes to depletion histories. In 
+The final step is to link the reprocessing schemes to depletion histories. In 
 the present work, we adjust the transfer rates of fresh fuel to maintain core 
-criticality and to keep fuel salt inventory constant during burnup. The feed constant calculation procedures are summarized as follows:
+criticality and to keep fuel salt mass constant during burnup. The continuous feed constant calculation procedures are summarized as follows:
 \begin{enumerate}
@@
 	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
-	\subitem 3a. For thorium feed mechanism: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
-	\subitem 3b. For non-thorium feed mechanism: mass of (HM) (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
+	\subitem 3a. \textbf{Thorium feed mechanism}: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
+	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of the heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
 	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
@@
 \section{Feed and extraction rates} \label{Feed-and-extraction-rates}
-In the present work, two different feed mechanisms are used: (1) thorium feed mechanism and (2) non-thorium feed mechanism.
+In the present work, two different feed mechanisms are used: (1) thorium and (2) non-thorium.
 The first mechanism allows continuous feed flow of thorium from the thorium stockpile and 
@@
 all or part of produced $^{233}$U from the \texttt{Pa-decay tank}. The fission 
-products \gls{FPs} act as poisons in the MSRs; they negatively impact the reactivity. 
+products (FPs) act as poisons in MSRs: they negatively impact the reactivity. 
 Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
@@
 $dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that 
-the \gls{MSR} extracts during time $dt$; thus \cite{nuttin2005potential}
+the \gls{MSR} extracts during time $dt$, thus \cite{nuttin2005potential}
 
@@
 
-where $\varepsilon_{e}$ is the removal efficiency. Integration of equation \ref{Equ:1} gives 
+where $\varepsilon_{e}$ is the removal efficiency \%. Integration of equation \ref{Equ:1} gives 
 the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
-is removed), where $\lambda_{e}=\varepsilon_{e}/T_{r}$. The removal constant 
+is removed), where $\lambda_{e}=\dfrac{{\varepsilon_{e}}}{{T}_{r}}$. The removal constant 
 $\lambda_{e}$ of gaseous and other fission products is precisely calculated 
@@
 extracted promptly and continuously via a gas removal system. In contrast, 
-extracting the soluble \gls{FPs}, lanthanides, and Pa is done by 
-chemical reprocessing (i.e. fluorination and reduction reaction). 
+chemical processes (i.e. fluorination and reduction) extract the soluble \gls{FPs}, lanthanides, and Pa.
 Therefore, the system reprocesses a specific amount of fuel salt daily. In the 
@@
 $\approx$10.59 days ($\lambda_{e}$ = $-1.092\times10^{-6}$ $s^{-1}$), which is 
-equivalent to a chemical reprocessing rate of 5 m$^3$/d 
-\cite{li_optimization_2018,nuttin2005potential}. The effective feed rates of 
+equivalent to a chemical reprocessing rate of 5 m$^3$/d chosen by Nuttin \emph{et al.} \cite{nuttin2005potential} and Li \emph{et al.} \cite{li_optimization_2018}. The effective feed rates of 
 the heavy metals (HM) are changed during reactor operation to conserve the 
-total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9}, and \ref{tab:table10} in Appendix.
+total fuel mass and criticality.
+The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9}, and \ref{tab:table10} in \ref{Appendix}.
 
@@
 	\vspace{1ex}
-	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4.5cm}|s|p{2cm}|}
+	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4.5cm}|p{2cm}|p{2cm}|}
 			\hline
-			\textbf{Reprocessing group}  & \textbf{Element} & \textbf{Reproc- essing time} & \textbf{Removal constant} $\lambda_{e}$ $[s^{-1}]$ \\
+			\textbf{Reprocessing group}  & \textbf{Element} & \textbf{Reprocessing time} & \textbf{Removal constant} $\lambda_{e}$ $[s^{-1}]$ \\
 			\hline
-			Gaseous \gls{FPs} and non-dissolved metals  &  H, He, N, O, Ne, Ar, Kr, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te, Xe, Lu, Hf, Ta, W, Re, Os, Ir, Pt, Au, and Rn.		&	30 s	&  -3.333E-02 \\
+			\raggedright Gaseous \gls{FPs} and non-dissolved metals  &  H, He, N, O, Ne, Ar, Kr, Nb, Mo, Tc, Ru, Rh, Pd, Ag, Sb, Te, Xe, Lu, Hf, Ta, W, Re, Os, Ir, Pt, Au, and Rn.		&	\raggedright 30 s	&  -3.333E-02 \\
 			\hline
-			Lanthanides and other soluble \gls{FPs}     & 
-			Zn, Ga, Ge, As, Se, Br, Rb, Sr, Y, Zr, Cd, In, Sn, I, Cs, Ba, La, Ce, Pr, Nd, Pm, Sm, Eu, Gd, Tb, Dy, Ho, Er, Tm, and Yb. & 10.599 d (5 m$^3$/d) &  -1.092E-06 \\
+			\raggedright Lanthanides and other soluble \gls{FPs}     & 
+			Zn, Ga, Ge, As, Se, Br, Rb, Sr, Y, Zr, Cd, In, Sn, I, Cs, Ba, La, Ce, Pr, Nd, Pm, Sm, Eu, Gd, Tb, Dy, Ho, Er, Tm, and Yb. & \raggedright 10.59 d (5 m$^3$/d) &  -1.092E-06 \\
 			\hline
-			Protactinium   & Pa  &  10.599 d (5 m$^3$/d)  &  -1.092E-06 \\
+			Protactinium   & Pa  & \raggedright 10.59 d (5 m$^3$/d)  &  -1.092E-06 \\
 			\hline

### 2019-11-18 paper/methods.tex
Results edits except #27

@@
 The general composition of the liquid fuel salt in this work is 70LiF - 
-17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (mixture of 
+17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (mixture of 
 thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U).
@@
 \begin{table}  %[!ht]
-	\caption{Composition of startup fuel (mole\%).}
+	\caption{Molar composition for startup fuel salts (mole\%).}
 	\vspace{0.1in}
@@
 		\hline
-		Fuel salt component& \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) 
+		Fuel salt component& \gls{LEU} (19.79 wt.\%) & Pu+enriched U (19.79 wt.\%) 
 		&  reactor-grade Pu & \gls{TRU}& $^{233}$U \\

### 2019-11-18 paper/results.tex
Results edits except #27

@@
 \section{Results and discussion} \label{Results-and-discussion}
-
-\subsection{Thorium feed mechanism}
-
-The thorium feed mechanism adopts continuous feed flow of external thorium from the thorium stockpile and 
-$^{233}$U from the \texttt{Pa-decay tank}. The molar fraction of the heavy metal 
+The molar fraction of the heavy metal (HM) 
 in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
@@
 the Beginning Of Life (BOL).
+\subsection{Thorium feed mechanism}
+The thorium feed mechanism continuously feeds thorium from the external stockpile and 
+$^{233}$U from the \texttt{Pa-decay tank}.
 Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
@@
 four cases. $k_{eff}$ decreases as a result of depletion of the initial 
-fissile materials and production of poisonous fission products (FPs). Thus, the 
+fissile materials and production of poisonous fission products (FPs). The amount of $^{233}$U generated in 
+the SD-TMSR is not enough to maintain the reactor criticality and 
+counteract parasitic neutron absorption. Thus, the 
 reactor becomes subcritical relatively quickly for alternative startup 
 compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
-years in the reactor-grade Pu case. The amount of $^{233}$U generated in 
-the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) is not enough to maintain the reactor criticality and 
-counteract parasitic neutron absorption. Nevertheless, 
-the continuous feed flow of thorium and $^{233}$U helps to operate the 
-\gls{SD-TMSR} for a lifetime-long period of time (Figure~\ref{fig:keff1} (U-233 case)). 
-Additionally, the molar fraction of the LEU and reactor-grade Pu in the initial fuel composition was increased
-more, consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (LEU and reactor-grade Pu cases)).
+years in the reactor-grade Pu case. For U-233 case, 
+the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
+\gls{SD-TMSR} for a 60 year lifetime (Figure~\ref{fig:keff1} (U-233 case)). 
+Additionally, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
+more.
+Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
 Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.
@@
 
-The non-thorium feed mechanism allows continuous feed flow of 
+The non-thorium feed mechanism continuously feeds 
 $^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (excluding Th). 
-Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{LEU}, Pu mixed with \gls{LEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
+Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
 without $^{232}$Th will lead to a supercritical reactor, thus the $^{233}$U case 
 is excluded from the non-thorium feed mechanism study.
-The molar fraction of the heavy metal in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
-Additionally, the initial fissile material fraction was increased for the four fuel 
-salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
-the BOL. 
 Figure~\ref{fig:keff2} shows the change of the effective multiplication factor 
 during 60 \gls{EFPY} of reactor operation for the non-thorium feed mechanism. Both the reactor-grade Pu and TRU cases 
-show promising results relative to the other two cases (LEU and Pu+LEU) (see Figure~\ref{fig:keff2}). 
+show promising results relative to the other two cases (HALEU and Pu+HALEU) (see Figure~\ref{fig:keff2}). 
 \begin{figure}
@@
 (MA) include Np, Am, and Cm.} accumulating in the core as a result of 
-continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the LEU and Pu+LEU 
-fuel are less attractive for the non-thorium feed mechanism. The continuous LEU 
+continuous TRU feed. As shown in Figure~\ref{fig:keff2}, the HALEU and Pu+HALEU 
+fuel are less attractive for the non-thorium feed mechanism. The continuous HALEU 
 feed increases the amount of fertile $^{238}$U and consequently, reduces the 
@@
 is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
-isotopes for all three cases reach the equilibrium state after $\approx$ $30$ 
+elements for all three cases reach the equilibrium state after $\approx$ $30$ 
 years (see Figure~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC}).
@@
 	\vspace{-0.4in}
-	\caption{Evolution of the important nuclides inventories for the $^{233}$U 
-		case (MA involves Np, Am, Cm) \cite{ashraf2019whole_core}.}
+	\caption{Evolution of important nuclide inventories for $^{233}$U 
+		startup fuel (MA involves Np, Am, Cm) \cite{ashraf2019whole_core}.}
 	\label{fig:inventoryCCCC}
@@
 	\vspace{-0.5in}
-	\caption{Evolution of the important nuclides inventories for the 
+	\caption{Evolution of important nuclide inventories for the 
 		reactor-grade Pu case (solid lines) and for the TRU case (dashed lines).}
@@
 	\includegraphics[width=\textwidth]{Th232CC.png}
-	\caption{The variation of thorium mass in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
+	\caption{Mass variation of all thorium isotopes in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:Th232CC}
@@
 In the non-thorium feed mechanism, the SD-TMSR is continuously refueled by heavy metals (Pu and TRU) for 
-criticality, which increases the Pu molar fraction (mole\%) in the molten salt. 
-According to literature, the limit of Pu solubility in the FLiBe salt is 
-$\approx$ $4.0$ mole\% \cite{ignatiev2012progress,sood1975plutonium}. 
-Figure~\ref{fig:PusolubilityCC} represents the Pu fraction in the fuel salt 
-(mole\%) for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. In the $^{233}$U and reactor-grade Pu cases, the Pu fraction increases 
+criticality, which increases the Pu mole concentration (\%) in the molten salt. 
+The Pu solubility in FLiBe is 
+$\approx$ $4.0$ \% \cite{ignatiev2012progress,sood1975plutonium}. 
+Figure~\ref{fig:PusolubilityCC} represents the Pu mole concentration variation in the fuel salt 
+for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. In the $^{233}$U and reactor-grade Pu cases, the Pu mole concentration increases 
 slightly but still below its solubility limit. On the other hand, the Pu 
-fraction in the molten salt loaded by TRU increases during operation and 
+mole concentration in the molten salt loaded by TRU increases during operation and 
 reaches the Pu solubility limit after $\approx$ $40$ years. This issue may 
@@
 	\includegraphics[width=\textwidth]{PusolubilityCC.png}
-	\caption{The Pu fraction in the fuel salt (mole\%) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
+	\caption{The Pu mole concentration in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:PusolubilityCC}
@@
 zero. 
-Although all produced $^{233}$U is used to refuel the core, the reactor is subcritical after $40$ years of operation (Figure~\ref{fig:keff2}).
+Although all produced $^{233}$U is used to refuel the core, the reactor is subcritical after $40$ years of operation (see Figure~\ref{fig:keff2}).
 In the $^{233}$U and reactor-grade Pu cases, the net production of 
-$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$ at EOL, respectively. As shown in 
-Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
+$^{233}$U increases with burnup and reaches about $1.77$ $t$ and $10$ $t$ at EOL, respectively. Figure~\ref{fig:NetCC} shows that for the $^{233}$U 
+case the net production of $^{233}$U during the first 455 days is negative; 
+about $175.28$ $kg$ of $^{233}$U must be added during this period. 
+As shown in Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
 $1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR}. Similarly, 
@@
 the SD-TMSR that was initially loaded by reactor-grade Pu alternative to 
-$^{233}$U. In addition, Figure~\ref{fig:NetCC} shows that for the $^{233}$U 
-case the net production of $^{233}$U during the first 455 days is negative; 
-about $175.28$ $kg$ of $^{233}$U must be added during this period. 
+$^{233}$U. 
+To avoid the nuclear weapons proliferation, we recommended stopping the SD-TMSR after producing the required $^{233}$U ($\approx$ $4.5$) and replacing the core fuel by Th/$^{233}$U fuel.
+
 In conclusion, the thorium fuel cycle transition can be achieved by selecting the 
@@
 transition to the thorium fuel cycle after $\approx$ $26$ years of operation. 
-The comparison between the two feed mechanisms with different types of initial 
-fuel is listed in Table~\ref{tab:comp_feeds}.
+The comparison between the two feed mechanisms with various initial fuel types 
+is listed in Table~\ref{tab:comp_feeds}.
 
@@
 	\includegraphics[width=\textwidth]{NetCC.png}
-	\caption{Net production of $^{233}$U during the burnup period (60 \gls{EFPY}) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
+	\caption{Net production of $^{233}$U with burnup (60 \gls{EFPY}) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
 	\label{fig:NetCC}
@@
  			\vspace{-0.4in}
- 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for the $^{233}$U, reactor-grade Pu, and TRU cases.}
+ 	\caption{The neutron flux energy spectrum at BOL (solid lines) and EOL (dashed lines) for 3 different initial 
+ 		fuel salt compositions (for all cases, the neutron flux
+ 		confidence intervals $\pm\sigma$ at BOL and EOL are $<1.0139$\% and $<0.6274$\%, respectively).}
  	\label{fig:spectrumFLUX110vC}
@@
 TRU cases. The SD-TMSR core design was optimized for $^{233}$U  
-\cite{li_optimization_2018}; thus, the core geometry (e.g., channels lattice 
+\cite{li_optimization_2018}, thus, the core geometry (e.g., channels lattice 
 pitch) must be re-optimized for another type of fuel to obtain better 
@@
 		Equil. \\ \hline
-		Fuel salt temperature&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
+		Fuel salt temperature ($\alpha_{D,fuel}$) &$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
 		\\ 
-		Fuel salt density&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
-		Total salt fuel&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
+		Fuel salt density ($\alpha_{l,fuel}$) &$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
+		Total salt fuel ($\alpha_{fuel})$ &$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
 		\hline
-		Graphite temperature&$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
+		Graphite temperature ($\alpha_{D,M}$) &$+1.45$&$+0.45$&$-2.68$&$-1.37$&$-1.44$&$-1.14$ 
 		\\	\hline
-		Total core&$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
+		Total core ($\alpha$) &$-1.77$&$-2.59$&$-6.54$&$-5.06$&$-4.79$&$-4.76$ \\ \hline
 	\end{tabularx}
@@
 \intertext{where}
-\eta     &= \mbox{thermal fission factor} \nonumber \\
+\eta     &= \mbox{neutron reproduction factor} \nonumber \\
 f        &= \mbox{thermal utilization factor} \nonumber \\
@@
 $^{233}$U, and $\epsilon$ grows throughout the core's lifetime. Conversely, 
-$p$ decreases during reactor operation. The thermal fission factor ($\eta$)  
+$p$ decreases during reactor operation. The neutron reproduction factor ($\eta$)  
 increases during reactor operation for the $^{233}$U as initial fuel due to 

### 2019-11-18 paper/conclusion.tex
Conclusion and future work edits except #28

--- 2019-10-25 paper/conclusion.tex
@@
 \section{Conclusion} \label{Conclusion}
-
-Five different types of initial fissile loadings are considered to investigate 
-transitioning to the thorium fuel cycle in the SD-TMSR. We adopted two 
-different feed mechanisms: thorium feed mechanism and non-thorium feed 
-mechanism. Lifetime-long depletion for the whole-core SD-TMSR model was 
+Five initial fissile loadings strategies have been studied for 
+transitioning to the thorium fuel cycle in the Single-fluid Double-zone 
+Thorium-based Molten Salt Reactor (SD-TMSR). We 
+adopted two different feed mechanisms: thorium and non-thorium. 
+This work determined that High Assay Low Enriched Uranium (HALEU), even with some Pu, is infeasible. 
+Full lifetime (60 year) depletion for the whole-core SD-TMSR model was 
 performed with reactor-grade Pu, TRU, and $^{233}$U as initial fissile 
@@
 of operating the SD-TMSR for an extended time ($\approx$ $40$ years) 
-without any external feed of $^{233}$U. Notably, the Pu molar fraction (mole\%) in 
-fuel salt was calculated and found to be below the solubility limit.
+without any external feed of $^{233}$U. Notably, the Pu mole concentration (\%) in 
+fuel salt was found to be below the solubility limit.
 
@@
 The spectrum hardens for the $^{233}$U initial fissile isotope during 
-operation, but softens for the Pu and TRU cases. Notably, the most 
+operation, but thermalizes for the Pu and TRU cases. Notably, the most 
 significant neutron energy spectrum shift was obtained for reactor-grade Pu 
@@
 
-We compared the operational and safety parameters of the \gls{SD-TMSR} for all 
-three startup fuels at both initial and equilibrium states. The total 
+We compared the operational and safety parameters of the \gls{SD-TMSR} for the 
+three promising startup fuels at both initial and equilibrium states. The total 
 temperature coefficient of reactivity is negative and relatively large in all 
@@
 and equilibrium states, respectively. For reactor-grade Pu, the coefficient 
-absolute value decreased from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
-60 years of operation. Finally, the six factors evolution during the operation 
-were calculated for all three cases, and these parameters can be used to 
-design the reactivity control system of the \gls{SD-TMSR}.
+evolved from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
+60 years of operation. Finally, the six factor evolution during the operation 
+was calculated for all three cases, providing a basis for designing the reactivity control system of the \gls{SD-TMSR}.
 
@@
 code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
-In further simulations, we intend to take into account the delayed 
+In further simulations, we intend to account for delayed 
 neutron precursor drift. The \gls{SD-TMSR} reactivity control system has not 
-been introduced in the literature yet. Thus, the control rods design and 
-configuration might be suggested in the nearest future.
+been introduced in the literature yet. Thus, the control rod design and 
+configuration may be suggested in the nearest future.
 
 An additional area to explore is the accident safety analysis which 
-requires high-fidelity multi-physics model of the \gls{SD-TMSR} with the 
+requires high-fidelity multi-physics simulation of the \gls{SD-TMSR} with the 
 coupled neutronics/thermal-hydraulics software, Moltres 
@@
 \gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in this work, 
-would be employed to generate problem-oriented nuclear data libraries for 
+will be employed to generate problem-oriented nuclear data libraries for 
 Moltres. The ultimate goal of this effort is to develop a 
-fast-running computational model for studying the dynamics behavior of generic 
-\glspl{MSR}, performing safety analysis for different accident scenarios and 
-optimizing design of various reactor concepts.
+fast-running computational model for studying the dynamic behavior of generic 
+\glspl{MSR}, performing safety analysis for different accident scenarios, and 
+optimizing the design of various reactor concepts.
 

### 2019-11-18 paper/results.tex
Conclusion and future work edits except #28

@@
 
-Table~\ref{tab:six_factor} summarizes the six factors for 3 different initial 
+Table~\ref{tab:six_factor} summarizes the six factor for 3 different initial 
 fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
-online reprocessing capabilities, all six factors are calculated at the 
+online reprocessing capabilities, six factor is calculated at the 
 beginning of the operation and after 30 years of operation. Neutron population 
@@
 \begin{table} [ht!]
-	\caption{Six factors for the SD-TMSR model for 3 different initial 
+	\caption{Six factor for the SD-TMSR model for 3 different initial 
 		fuel salt compositions at startup and equilibrium.}

### 2019-11-19 cover-letter/cover-letter.tex
Cover letter added

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Plain Cover Letter
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
% It was modified by Katy Huff
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%    PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage{graphicx}
%\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\usepackage{eso-pic,graphicx}

%--------------------------------------------------------------------------------------
%--------INPUT DATA
%--------------------------------------------------------------------------------------
\usepackage{xspace}
\newcommand{\StudentFirstName}{O.\xspace}
\newcommand{\StudentLastName}{Ashraf\xspace}
\newcommand{\RecipientName}{Prof. Mostafa Ghiaasiaan\xspace}
\newcommand{\RecipientAddress}{Executive Editor\\Annals of Nuclear Energy}
%\newcommand{\<++>}{<++>\xspace}

\begin{document}
	\AddToShipoutPictureBG*{\includegraphics[width=\paperwidth,height=\paperheight]{background.pdf}}

	%----------------------------------------------------------------------------------------
	%    ADDRESSEE SECTION
	%----------------------------------------------------------------------------------------

	\begin{letter}{\RecipientName\\
			\RecipientAddress\xspace}

		%-------------------------------------------------------------------------------
		%    YOUR NAME & ADDRESS SECTION
		%-------------------------------------------------------------------------------
		\address{O. Ashraf\\
			oabdelaziz@mephi.ru\\
			osama.ashraf@edu.asu.edu.eg\\
			Institute of Nuc. Physics and Eng.\\
			National Research Nuclear University\\
			Moscow, Russia, 115409}

		%-------------------------------------------------------------------------------
		%    LETTER CONTENT SECTION
		%-------------------------------------------------------------------------------

		\opening{To \RecipientName,}

		Please find enclosed a manuscript entitled: ``Various strategies for thorium fuel cycle transition in the SD-TMSR'' which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, 
		and Prof. Kathryn D. Huff) are submitting for publication as a research article 
		in Annals of Nuclear Energy. The presented manuscript is 100\% original and never been published in any form (symposia, conferences, etc).

		This manuscript investigates the fuel cycle and neutronics performance of the single-fluid double-zone thorium molten salt reactor (SD-TMSR) with different fissile material loadings at startup: High Assay Low Enriched Uranium (HALEU) (19.79\%), Pu mixed with HALEU (19.79\%), reactor-grade Pu, transuranic elements (TRU), and $^{233}$U, using SERPENT-2 Monte Carlo code. This manuscript provides feasible strategies for thorium fuel cycle transition in the SD-TMSR based on reactor-grade Pu and transuranic elements (TRU) results.

		Declarations of interest: none\\

		Thank you for your consideration of our work.

		Your quick response will be highly appreciated.

		\closing{Sincere regards,
			\includegraphics[height=1.5cm]{signature.png}\\
			\fromsig{O. Ashraf\\
				Assistant Teacher\\
				Institute of Nuc. Physics and Eng.\\
				National Research Nuclear University (MEPhI)}
		}

		%-------------------------------------------------------------------------------

	\end{letter}

\end{document}

### 2019-11-19 paper/abstract.tex
Cover letter added

@@
 Since $^{233}$U does not exist in nature, we must examine other available fissile materials to start up these reactor concepts.
-This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{HALEU} (19.79\%), Pu mixed with \gls{LEU} (19.79\%), reactor-grade Pu (a mixture of Pu isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
+This work investigates the fuel cycle and neutronics performance of the \gls{SD-TMSR} with different fissile material loadings at startup: \gls{HALEU} (19.79\%), Pu mixed with \gls{HALEU} (19.79\%), reactor-grade Pu (a mixture of Pu isotopes chemically extracted from \gls{PWR} \gls{SNF} with $33$ $GWd/tHM$ burnup), \gls{TRU} from \gls{LWR} \gls{SNF}, and $^{233}$U.
 The \gls{MSR} burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the \gls{SD-TMSR}.

### 2019-11-19 paper/introduction.tex
minor important changes

@@
 
-The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) 2,250
+The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
 MW$_{th}$ was introduced by the Chinese Academy of Sciences \cite{li_optimization_2018}. The
@@
 cycle transition can be achieved after reaching the doubling
-time $-$ time required to produce enough amount of $^{233}$U to trigger a
-	new SD-TMSR $-$ of $^{233}$U because in this case, all startup fissile material
+time of $^{233}$U $-$ time required to produce enough amount of $^{233}$U to trigger a
+	new SD-TMSR $-$ because in this case, all startup fissile material
 is being substituted by newly produced $^{233}$U.
@@
 Heuer \emph{et al.} (2014) discussed the transition characteristics of the \gls{MSFR}
-under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible in the MSFR while closing the current fuel cycle and optimizing the management of the long-term wastes.
-\cite{heuer2014towards}.
+under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible in the MSFR while closing the current fuel cycle and optimizing the management of the long-term wastes \cite{heuer2014towards}.
 
@@
 various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
-initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U \cite{de2000scenarios}. Two different feed mechanisms were selected:
+initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu \cite{marka1993explosive}, \gls{TRU} from LWR SNF \cite{de2000scenarios}, and $^{233}$U.
+Two different feed mechanisms were selected:
 
 \begin{itemize}
-	\item Thorium feed mechanism: continuous feed flow of thorium from the thorium stockpile and $^{233}$U from the \texttt{Pa-decay tank}\footnote{An external tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U.
-\cite{betzler2016modeling}.
-	\item Non-thorium feed mechanism: continuous injection of the same initial heavy metals (excluding Th) and simultaneous feed of all or fraction of $^{233}$U from the \texttt{Pa-decay tank}.
+	\item \textbf{Thorium feed mechanism}: continuous feed flow of thorium from the external stockpile and $^{233}$U from the \texttt{Pa-decay tank}\footnote{An external tank used to store protactinium extracted from the core.}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U \cite{betzler2016modeling}.
+	\item \textbf{Non-thorium feed mechanism}: continuous injection of external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}) and simultaneous feed of all or fraction of $^{233}$U from the \texttt{Pa-decay tank}.
 \end{itemize}
 
-All calculations presented in this paper are performed using SERPENT-2 version 2.1.31 \cite{leppanen2014serpent}.
+All calculations presented in this paper are performed using SERPENT-2 version 2.1.31\footnote{SERPENT-2 is a 3D continuous energy Monte Carlo neutron 
+	transport and burnup code.} \cite{leppanen2014serpent}.
 We use the MSR burnup routine provided by SERPENT-2 to simulate continuous online reprocessing and refueling.
@@
 
-This paper is organized as follows: section \ref{Introduction} introduces \gls{MSR} systems, section \ref{Model-description} discusses the model description, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Feed-and-extraction-rates} addresses extraction and feed mechanisms, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.
+This paper is organized as follows: section \ref{Model-description} discusses the model description, section \ref{Methodology-and-tools} describes methodology and tools, section \ref{Feed-and-extraction-rates} addresses extraction and feed mechanisms, section \ref{Results-and-discussion} focuses on the results and discussion, and section \ref{Conclusion} highlights the conclusions.

### 2019-11-19 paper/methods.tex
minor important changes

@@
 	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
-	SD-TMSR \cite{ashraf2019Preliminary}.}
+	SD-TMSR.}
 	\label{fig:ff}
@@
 \subsection{Fuel composition}
-The general composition of the liquid fuel salt in this work is 70LiF - 
+The general composition of the startup liquid fuel salt in this work is 70LiF - 
 17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (mixture of 
-thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU} from LWR SNF, and $^{233}$U).
+thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}, and $^{233}$U).
 The aim of this paper is to simulate the  
@@
 		\hline
-		Fuel salt component& \gls{LEU} (19.79 wt.\%) & Pu+enriched U (19.79 wt.\%) 
+		Fuel salt component& \gls{HALEU} (19.79 wt.\%) & Pu+\gls{HALEU} (19.79 wt.\%) 
 		&  reactor-grade Pu & \gls{TRU}& $^{233}$U \\
@@
 		(TRU)F$_3$&&&	&3.85	&\\
+		\hline
+		Total HM &12.5&12.5&12.5&12.5&12.5\\
 		\hline
@@
 		\hline
-		Nuclide & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) &  
+		Nuclide & \gls{HALEU} (19.79\%) & Pu+\gls{HALEU} (19.79wt.\%) &  
 		reactor-grade Pu & \gls{TRU}& $^{233}$U \\	\hline
 		$^{232}$Th       &6.24E+04 & 4.67E+04 &   6.75E+04			& 5.44E+04	& 7.69E+04    \\ 
-		$^{233}$U        &         & &        &       &  1.30E+06 \\
+		$^{233}$U        &         & &        &       &  1.30E+03 \\
 		$^{235}$U        & 3.17E+03 &6.01E+03	&            &   & \\
@@
 computational software that can support online fuel salt reprocessing and 
-refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 
-\footnote{SERPENT-2 is a 3D continuous energy Monte Carlo neutron 
-transport and burnup code.} \cite{leppanen2014serpent} simulates the 
+refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
 Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
@@
 	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
-	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-tank}, respectively.
+	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
 	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
 	\subitem 3a. \textbf{Thorium feed mechanism}: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
-	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of the heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
+	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of external heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
 	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
@@
 In the present work, two different feed mechanisms are used: (1) thorium and (2) non-thorium.
-The first mechanism allows continuous feed flow of thorium from the thorium stockpile and 
+The first mechanism allows continuous feed flow of thorium from the external stockpile and 
 $^{233}$U from the \texttt{Pa-decay tank}. In contrast, the second mechanism 
-continuously injects heavy metal (HM) (excluding Th) and simultaneously feeds  
+continuously injects external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}) and simultaneously feeds  
 all or part of produced $^{233}$U from the \texttt{Pa-decay tank}. The fission 

### 2019-11-19 paper/results.tex
minor important changes

@@
 The molar fraction of the heavy metal (HM) 
-in the initial fuel was kept constant and equal to 12.5 mole\% for all cases. 
+in the initial fuel was kept constant and equal to 12.5 mole\% for all cases (see Table~\ref{tab:table4}). 
 Additionally, the initial fissile material fraction was increased for the five fuel 
@@
 the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
-\gls{SD-TMSR} for a 60 year lifetime (Figure~\ref{fig:keff1} (U-233 case)). 
+\gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1} (U-233 case)). 
 Additionally, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
@@
 The non-thorium feed mechanism continuously feeds 
-$^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (excluding Th). 
+$^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}).
 Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
@@
 \end{figure}
-
 For the reactor-grade Pu case, the amount of $^{233}$U generated in the \gls{SD-TMSR}, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs.
@@
 Figures~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC} demonstrate 
-the evolution of important isotopes for the $^{233}$U, Pu, and TRU cases 
+the evolution of important nuclide inventories for the $^{233}$U, Pu, and TRU cases 
 respectively. For the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}), the mass of Pa in the fuel salt is almost constant and reaches 
@@
 Figure~\ref{fig:NetCC} demonstrates the net production of $^{233}$U during 
-operation for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
+reactor operation for the $^{233}$U, reactor-grade Pu, and TRU cases, respectively. For the TRU case, the net production of $^{233}$U is almost 
 zero. 
@@
 			\hline
-			Feed mechanism & \gls{LEU} (19.79\%) & Pu+enriched U (19.79wt.\%) &  
+			Feed mechanism & \gls{HALEU} (19.79\%) & Pu+\gls{HALEU} (19.79wt.\%) &  
 			reactor-grade Pu & \gls{TRU}& $^{233}$U \\

### 2019-11-23 paper/introduction.tex
after Andrei's review

@@
 cycle transition can be achieved after reaching the doubling
-time of $^{233}$U $-$ time required to produce enough amount of $^{233}$U to trigger a
-	new SD-TMSR $-$ because in this case, all startup fissile material
+time of $^{233}$U (required time to produce enough $^{233}$U to start up a new unit) because in this case, all startup fissile material
 is being substituted by newly produced $^{233}$U.
@@
 
+$^{233}$U (in the \texttt{Pa-decay tank}) is contaminated with $^{232}$U, which produced from parasitic (n, 2n) reactions on $^{233}$U itself, or on $^{233}$Pa, or on $^{232}$Th.
+$^{208}$Tl a daughter of $^{232}$U emits intense $\gamma$-radiation and this makes $^{233}$U difficult to handle.
+Moreover, for nonproliferation reasons, $^{233}$U could be diluted with $^{238}$U which makes it impossible to use for nuclear weapons.
+
 All calculations presented in this paper are performed using SERPENT-2 version 2.1.31\footnote{SERPENT-2 is a 3D continuous energy Monte Carlo neutron 

### 2019-11-23 paper/methods.tex
after Andrei's review

@@
 	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
-	SD-TMSR.}
+	SD-TMSR \cite{ashraf2019whole_core}.}
 	\label{fig:ff}
@@
 all or part of produced $^{233}$U from the \texttt{Pa-decay tank}. The fission 
-products (FPs) act as poisons in MSRs: they negatively impact the reactivity. 
+products (FPs) act as poisons in nuclear reactors: they negatively impact the reactivity. 
 Therefore, \gls{FPs} must be extracted during reactor operation. Consider 
-$T_{r}$ as the time during which the total fuel salt is reprocessed and 
-$dN_{e}$ as the amount of particular element $e$ with inventory $N_{e}$ that 
-the \gls{MSR} extracts during time $dt$, thus \cite{nuttin2005potential}
+the \gls{MSR} extracts $dN_{e}$ amount of particular element $e$ during time $dt$, thus \cite{nuttin2005potential}:
+\begin{align}
+\dfrac{dN_{e}}{dt} &= N_{e}\dfrac{\varepsilon_{e}}{T_{r}}
+\label{Equ:1}
+\intertext{where}
+dN_{e} 	&= \mbox{the amount of particular element $e$} \nonumber \\
+dt   	&= \mbox{the extraction time of $dN_e$} \nonumber \\
+N_{e}  	&= \mbox{total inventory of element $e$} \nonumber \\
+\varepsilon_{e}	&= \mbox{the removal efficiency $\%$} \nonumber \\
+T_{r}	&= \mbox{the time during which the total fuel salt is reprocessed.} \nonumber
+\end{align}
 
-\begin{equation}
-\label{Equ:1}
-\dfrac{dN_{e}}{dt} = N_{e}\dfrac{\varepsilon_{e}}{T_{r}},	
-\end{equation}
-
-where $\varepsilon_{e}$ is the removal efficiency \%. Integration of equation \ref{Equ:1} gives 
-the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
+Integration of equation \ref{Equ:1} gives the removal constant $\lambda_{e}$ $[s^{-1}]$ (the rate at which the material 
 is removed), where $\lambda_{e}=\dfrac{{\varepsilon_{e}}}{{T}_{r}}$. The removal constant 

### 2019-11-24 paper/results.tex

@@
 the SD-TMSR that was initially loaded by reactor-grade Pu alternative to 
-$^{233}$U. 
-To avoid the nuclear weapons proliferation, we recommended stopping the SD-TMSR after producing the required $^{233}$U ($\approx$ $4.5$) and replacing the core fuel by Th/$^{233}$U fuel.
+$^{233}$U. For nonproliferation reasons, $^{233}$U could be diluted with $^{238}$U which makes it impossible to use for nuclear weapons.
 

### 2019-11-24 paper/introduction.tex
my part in #27

@@
 various initial fissile materials and without any external feed of $^{233}$U. We investigate five different
-initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu \cite{marka1993explosive}, \gls{TRU} from LWR SNF \cite{de2000scenarios}, and $^{233}$U.
+initial fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu \footnote{Reactor-grade Pu is a mixture of Pu isotopes chemically extracted from PWR SNF with 33 GWd/tHM burnup} \cite{marka1993explosive}, \gls{TRU} from LWR SNF \cite{de2000scenarios}, and $^{233}$U.
 Two different feed mechanisms were selected:

### 2019-11-25 paper/results.tex

@@
 Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
-Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.
+But the produced $^{233}$U is insufficient to keep the reactor critical and counteract parasitic neutron absorption.
+Therefore, $k_{eff}$ is decreased below 1.0, after $\approx$ $6$ years in the HALEU case and $\approx$ $12$ years in the reactor-grade Pu case.
 

### 2019-11-25 paper/results.tex
Greek letters for temperature coefficients in Table 8 fixed

@@
 		$\pm\sigma$ for all coefficients is between $0.11$ and $0.16$ pcm/K).}
-	\begin{tabularx}{\textwidth}{ p{0.27\textwidth} | X X  X X  X X } \hline
+	\begin{tabularx}{\textwidth}{ p{0.37\textwidth} | X X  X X  X X } \hline
 		\multirow{3}{*}{\shortstack{Reactivity coefficient \\ (pcm/K)}} 
@@
 		Equil. \\ \hline
-		Fuel salt temperature ($\alpha_{D,fuel}$) &$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
+		Fuel salt temperature ($\alpha_{D,F}$) 
+		&$-4.96$&$-5.26$&$-4.99$&$-3.12$&$-3.23$&$-1.97$ 
 		\\ 
-		Fuel salt density ($\alpha_{l,fuel}$) &$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
-		Total salt fuel ($\alpha_{fuel})$ &$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
+		Fuel salt density ($\alpha_{\rho,F}$) 
+		&$+1.49$&$+2.34$&$+1.54$&$-1.58$&$-0.37$&$-1.62$ \\
+		Total salt fuel ($\alpha_{F})$ 
+		&$-3.77$&$-2.83$&$-3.22$&$-4.23$&$-3.25$&$-3.69$ \\ 
 		\hline

### 2019-11-25 paper/results.tex
Uncertanties added to Table 9 and Future work shortened

@@
 		fuel salt compositions at startup and equilibrium.}
-	\begin{tabularx}{\textwidth}{ X | X X  X X  X X } \hline
-		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
-			material} \\ \cline{2-7}
+	\begin{tabularx}{\textwidth}{ X | X X  X X  X X | p{0.1\textwidth}} \hline
+		\multirow{3}{*}{Factor}  & \multicolumn{6}{c|}{Startup fissile 
+			material} & \multirow{3}{*}{$\pm\bar{\sigma}$} \\ 
+			\cline{2-7}
 		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
-		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
-		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
-		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31 \\ 
-		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
-		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15 \\
-		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
-		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
-		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
+		\multicolumn{2}{c|}{TRU} \\ \cline{2-7}
+		\space  & Initial & Equil & Initial & Equil & Initial & Equil & \space 
+		\\ \hline
+		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31&4.9E-4\\ 
+		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75&2.1E-4 \\
+		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15&4.6E-4 \\
+		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81&6.2E-4 \\
+		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99&1.7E-6 \\
+		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00&6.5E-11 \\ \hline
 	\end{tabularx}

### 2019-11-25 paper/results.tex
cite Ben's paper and rewrite the paragraph

--- 2019-11-25 paper/results.tex
@@
 \gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1} (U-233 case)).
-Additionally, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
-more.
-Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
-But the produced $^{233}$U is insufficient to keep the reactor critical and counteract parasitic neutron absorption.
-Therefore, $k_{eff}$ is decreased below 1.0, after $\approx$ $6$ years in the HALEU case and $\approx$ $12$ years in the reactor-grade Pu case.
+Notably, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
+more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
+For the HALEU fuel salt, the amount of $^{233}$U generated in the SD-TMSR after a few years is insufficient to counteract the absorption of the (non-fissile) $^{238}$U added at start-up after much of the original $^{235}$U is depleted.
+Consequently, the core becomes subcritical after $\approx$ $6$ years of operation.
+For the reactor-grade Pu fuel salt, the core becomes subcritical after $\approx$ $12$ years because the amount of $^{233}$U generated is not sufficient to counteract the neutron absorption in the non-fissile plutonium isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.
 
@@
 \subsection{Non-thorium feed mechanism}
-
 The non-thorium feed mechanism continuously feeds 

### 2019-11-25 paper/conclusion.tex

@@
 adopted two different feed mechanisms: thorium and non-thorium. 
-This work determined that High Assay Low Enriched Uranium (HALEU), even with some Pu, is infeasible. 
+This work determined that High Assay Low Enriched Uranium (HALEU), even mixed with Pu, is infeasible. 
 Full lifetime (60 year) depletion for the whole-core SD-TMSR model was 
@@
 code SaltProc \cite{rykhlevskii_arfc/saltproc_2018,rykhlevskii_milestone_2019}.
-In further simulations, we intend to account for delayed 
-neutron precursor drift. The \gls{SD-TMSR} reactivity control system has not 
-been introduced in the literature yet. Thus, the control rod design and 
-configuration may be suggested in the nearest future.
-
-An additional area to explore is the accident safety analysis which 
-requires high-fidelity multi-physics simulation of the \gls{SD-TMSR} with the 
-coupled neutronics/thermal-hydraulics software, Moltres 
-\cite{lindsay_introduction_2018}. The full-core SERPENT-2 model of the 
-\gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in this work, 
-will be employed to generate problem-oriented nuclear data libraries for 
-Moltres. The ultimate goal of this effort is to develop a 
+Additionally, the accident safety analysis using coupled 
+neutronics/thermal-hydraulics software, Moltres 
+\cite{lindsay_introduction_2018} will be performed. The full-core SERPENT-2 
+model of the \gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in 
+this work, will be employed to generate problem-oriented nuclear data 
+libraries for Moltres. The ultimate goal of this effort is to develop a 
 fast-running computational model for studying the dynamic behavior of generic 

### 2019-11-25 paper/results.tex
last version before submission

@@
 the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
-\gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1} (U-233 case)).
+\gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1}, U-233 case).
+
 Notably, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
@@
 $^{233}$U from the \texttt{Pa-decay tank} and external heavy metals (\gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}).
-Under the non-thorium feed mechanism, four different initial fissile materials are studied: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, and \gls{TRU}. The continuous feed of $^{233}$U 
+Under the non-thorium feed mechanism, only four different initial fissile materials are studied: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, and \gls{TRU}.
+The continuous feed of $^{233}$U
 without $^{232}$Th will lead to a supercritical reactor, thus the $^{233}$U case 
@@
 As shown in Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
-$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR}. Similarly, 
+$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR} (see Table~\ref{tab:table5}). Similarly, 
 one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 

### 2019-11-25 paper/introduction.tex

@@
 
-$^{233}$U (in the \texttt{Pa-decay tank}) is contaminated with $^{232}$U, which produced from parasitic (n, 2n) reactions on $^{233}$U itself, or on $^{233}$Pa, or on $^{232}$Th.
-$^{208}$Tl a daughter of $^{232}$U emits intense $\gamma$-radiation and this makes $^{233}$U difficult to handle.
-Moreover, for nonproliferation reasons, $^{233}$U could be diluted with $^{238}$U which makes it impossible to use for nuclear weapons.
+$^{233}$U is contaminated with $^{232}$U, which produced from parasitic (n,2n) reactions in $^{233}$Pa, or in $^{232}$Th, or in $^{233}$U itself.
+$^{208}$Tl a daughter of $^{232}$U emits intense $\gamma$-radiation and this makes $^{233}$U undesirable for nuclear weapons.
+Moreover, for nonproliferation reasons, bred $^{233}$U could be diluted with $^{238}$U to produce denatured fuel, which not suitable for nuclear weapons \cite{dolan2017molten}.
 

### 2019-11-25 paper/methods.tex

@@
 		Thermal power, MW$_{th}$          				&  2,250  \\ 
-		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_4$ \\
+		Fuel salt components                            & LiF-BeF$_2$-(\gls{HM})F$_N$ \\
 		Fuel composition, mole\%                        & 70-17.5-12.5    \\
@@
 \end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%\begin{figure}[t!] % replace 't' with 'b' to \centering
-%	\hspace{+0.65in}
-%	\includegraphics[width=\textwidth]{core.png}
-%	\caption{Plan view of SD-TMSR core.}
-%	\label{fig:core}
-%\end{figure}
 
@@
 17.5BeF$_2$ - 12.5(HM)F$_N$ mole\%, where HM is the heavy metal (mixture of 
-thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}, and $^{233}$U).
+thorium and one of these fissile materials: \gls{HALEU}, Pu mixed with \gls{HALEU}, reactor-grade Pu, \gls{TRU}, and $^{233}$U), and $N$ is dependent on the chosen fissile material and the thermochemical state of the liquid fuel salt.
+
 The aim of this paper is to simulate the  
@@
 
-\begin{table}  %[!ht]
+\begin{table} % [!ht]
+	\centering
 	\caption{Reactor-grade Pu vector (wt.\%) \cite{marka1993explosive}.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{r r r r r}
+	\begin{tabularx}{\textwidth}{|X |X |X| X| X|}
 		\hline
@@
 		\hline
-		 1.3&60.3&24.3&9.1&5 \\
+		 1.3 &60.3&24.3&9.1&5 \\
 		\hline
@@
 
-\begin{table}  %[!ht]
+\begin{table} %  [!ht]
+	\centering
 	\caption{\gls{TRU} vector (wt.\%) \cite{de2000scenarios}.}
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{r r r r r r r r r r}
+	\begin{tabularx}{\textwidth}{|X| X| X| X| X| X| X| X| X| X|}
 		\hline
@@
 		\hline
-		Nuclide & \gls{HALEU} (19.79\%) & Pu+\gls{HALEU} (19.79wt.\%) &  
+		Nuclide & \gls{HALEU} (19.79 wt.\%) & Pu+\gls{HALEU} (19.79 wt.\%) &  
 		reactor-grade Pu & \gls{TRU}& $^{233}$U \\	\hline
@@
 from the fuel with a certain flow rate into the 
-\texttt{Pa-decay tank} to decay and produce $^{233}$U\footnote{The 
+\texttt{Pa-decay tank} to decay and produce $^{233}$U \footnote{The 
 $^{233}$Pa is removed and left to decay into $^{233}$U with $\tau_{1/2}$ 
@@
 the heavy metals (HM) are changed during reactor operation to conserve the 
-total fuel mass and criticality.
-The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table~\ref{tab:table8}, \ref{tab:table9}, and \ref{tab:table10} in \ref{Appendix}.
+total fuel mass and criticality. The effective feed rates for Th/$^{233}$U, reactor-grade Pu, and TRU cases are listed in Table A.1, A.2, and A.3 in \ref{Appendix}.
 
@@
 	\vspace{1ex}
-	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4.5cm}|p{2cm}|p{2cm}|}
+	\begin{tabularx}{\textwidth}{|p{2.3cm}|p{4cm}|p{2.2cm}|p{1.9cm}|}
 			\hline
@@
 \end{table}
-
-%\begin{table}[ht!]
-%	\centering
-%	\caption{The refueling table.} 
-%	\vspace{1ex}
-%	\begin{tabularx}{\textwidth}{|p{1.5cm}|b|p{1.9cm}|}
-%		\hline
-%		\textbf{Nuclide} & \textbf{Feed rate} & \textbf{Feed constant$^{\star}$} $\lambda_{e}$ $[s^{-1}]$ \\
-%		\hline
-%		$^{232}$Th        &  1.842 [Kg/day], first 90 [d] & 1.500E-09 \\
-%		&  2.511 [Kg/day], from 90 to 1550 [d] & 		2.045E-09 \\
-%		&  2.456 [Kg/day], from 1550 to 3010 [d] & 		2.000E-09 \\
-%		&  2.321 [Kg/day], from 3010 to 5930 [d]& 		1.890E-09	\\
-%		&  2.241 [Kg/day], from 5930 to 7390 [d] &		1.825E-09	\\
-%		&  2.186 [Kg/day], from 7390 to 12500 [d] &		1.780E-09	\\
-%		&  2.118 [Kg/day], from 12500 to 15420 [d] &	1.725E-09	\\
-%		&  2.136 [Kg/day], from 15420 to 18340 [d]&		1.740E-09		\\
-%		&  2.063 [Kg/day], from 18340 to 21900 [d]&		1.680E-09	 \\ 
-%		\hline
-%		$^{233}$U & 2.619 [Kg/day], first 90 [d]	&   6.400E-09  \\
-%		& 2.009 [Kg/day],  form 90 to 1550 [d] &	4.910E-09 \\
-%		& 1.944 [Kg/day], from 1550 to 3010 [d] &	4.750E-09 \\
-%		& 1.826 [Kg/day],  from 3010 to 5930 [d] &	4.460E-09 \\
-%		& 1.811 [Kg/day],  from 5930 to 7390[d] &	4.425E-09 \\
-%		& 1.744 [Kg/day], from 7390 to 12500 [d] &	4.260E-09 \\
-%		& 1.699 [Kg/day], from 12500 to 18340 [d]	& 4.150E-09 \\
-%		& 1.657 [Kg/day], from 18340 to 21900 [d]	& 4.050E-09 \\
-%		\hline
-%	\end{tabularx}
-%	\begin{tablenotes}
-%		\small
-%		\item  $^{\star}$ Feed constant is the mass fraction of fissile nuclide ($^{232}$Th or $^{233}$U) transferred from the external storage to the core per second.
-%	\end{tablenotes}
-%	\label{tab:table3}
-%\end{table}

### 2020-02-03 paper/revisions/review-responses.tex
add review-responses and highlights files

%
% Copyright 2007, 2008, 2009 Elsevier Ltd
%
% This file is part of the 'Elsarticle Bundle'.
% ---------------------------------------------
%
% It may be distributed under the conditions of the LaTeX Project Public
% License, either version 1.2 of this license or (at your option) any
% later version.  The latest version of this license is in
%    http://www.latex-project.org/lppl.txt
% and version 1.2 or later is part of all distributions of LaTeX
% version 1999/12/01 or later.
%
% The list of all files belonging to the 'Elsarticle Bundle' is
% given in the file `manifest.txt'.
%

% Template article for Elsevier's document class `elsarticle'
% with numbered style bibliographic references
% SP 2008/03/01
%
%
%
% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%
%
%\documentclass[preprint,12pt]{elsarticle}
\documentclass[answers,11pt]{exam}

% \documentclass[preprint,review,12pt]{elsarticle}

% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
% for a journal layout:
% \documentclass[final,1p,times]{elsarticle}
% \documentclass[final,1p,times,twocolumn]{elsarticle}
% \documentclass[final,3p,times]{elsarticle}
% \documentclass[final,3p,times,twocolumn]{elsarticle}
% \documentclass[final,5p,times]{elsarticle}
% \documentclass[final,5p,times,twocolumn]{elsarticle}

% if you use PostScript figures in your article
% use the graphics package for simple commands
% \usepackage{graphics}
% or use the graphicx package for more complicated commands
\usepackage{graphicx}
% or use the epsfig package if you prefer to use the old commands
% \usepackage{epsfig}

% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
% The amsthm package provides extended theorem environments
% \usepackage{amsthm}
\usepackage{amsmath}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
% for the whole article with \linenumbers after \end{frontmatter}.
\usepackage{lineno}

% I like to be in control
\usepackage{placeins}

% natbib.sty is loaded by default. However, natbib options can be
% provided with \biboptions{...} command. Following options are
% valid:

%   round  -  round parentheses are used (default)
%   square -  square brackets are used   [option]
%   curly  -  curly braces are used      {option}
%   angle  -  angle brackets are used    <option>
%   semicolon  -  multiple citations separated by semi-colon
%   colon  - same as semicolon, an earlier confusion
%   comma  -  separated by comma
%   numbers-  selects numerical citations
%   super  -  numerical citations as superscripts
%   sort   -  sorts multiple citations according to order in ref. list
%   sort&compress   -  like sort, but also compresses numerical citations
%   compress - compresses without sorting
%
% \biboptions{comma,round}

% \biboptions{}

% Katy Huff addtions
\usepackage{xspace}
\usepackage{color}

\usepackage{multirow}
\usepackage[hyphens]{url}

\usepackage[acronym,toc]{glossaries}
\include{acros}

\makeglossaries

%\journal{Annals of Nuclear Energy}

\begin{document}

%\begin{frontmatter}

% Title, authors and addresses

% use the tnoteref command within \title for footnotes;
% use the tnotetext command for the associated footnote;
% use the fnref command within \author or \address for footnotes;
% use the fntext command for the associated footnote;
% use the corref command within \author for corresponding author footnotes;
% use the cortext command for the associated footnote;
% use the ead command for the email address,
% and the form \ead[url] for the home page:
%
% \title{Title\tnoteref{label1}}
% \tnotetext[label1]{}
% \author{Name\corref{cor1}\fnref{label2}}
% \ead{email address}
% \ead[url]{home page}
% \fntext[label2]{}
% \cortext[cor1]{}
% \address{Address\fnref{label3}}
% \fntext[label3]{}

\title{Strategies for thorium fuel cycle transition in the SD-TMSR\\
\large Response to Review Comments}
\author{O. Ashraf, Andrei Rykhlevskii, G. V. Tikhomirov, Kathryn D. Huff}

% use optional labels to link authors explicitly to addresses:
% \author[label1,label2]{<author name>}
% \address[label1]{<address>}
% \address[label2]{<address>}

%\author[uiuc]{Kathryn Huff}
%        \ead{kdhuff@illinois.edu}
%  \address[uiuc]{Department of Nuclear, Plasma, and Radiological Engineering,
%        118 Talbot Laboratory, MC 234, Universicy of Illinois at
%        Urbana-Champaign, Urbana, IL 61801}
%
% \end{frontmatter}
\maketitle
\section*{Review General Response}
We would like to thank the reviewers for their detailed assessment of
this paper. Your suggestions, clarifications, and comments have resulted in 
changes which certainly improved the paper.

\begin{questions}
        \section*{Reviewer 1}

        \question This work investigates the fuel cycle and neutronics performance of the Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with different fissile material based on an extended SERPENT-2 code. The whole paper states clearly.

        \begin{solution}
                Thank you very much for these comments. We appreciate your detailed review, which has certainly improved the paper. The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
        \end{solution}

        %---------------------------------------------------------------------

        \question In the SD-TMSR burnup calculation, how are the depletion regions and burnup time step defined?
        \begin{solution}

        \end{solution}

        %---------------------------------------------------------------------
        \question During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere. In other words, during one burnup step, the fission reactions occur in only part of the time (depends on the ratio of time taken in fuel salt passing reactor core and external loop), and nuclides' decay or other reactions occur in the whole burnup step time. Have you considered this in SERPENT calculation?  
        \begin{solution}

        \end{solution}

        %---------------------------------------------------------------------

        \section*{Reviewer 2}

        %---------------------------------------------------------------------
        \question Strategies for thorium fuel cycle transition by employing different startup fissile material and feed mechanisms were investigated for the single-fluid double-zoned thorium-based molten salt reactor (SD-TMSR) in this study, and some specific conclusions were obtained. While, realizing thorium fuel cycle transition by using different startup fissile material has already been well studied in the previous studies for different types of MSR, including SD-TMSR. The motivation (e.g., improvement from previous studies) for conducting this study is not clear. In addition, some statements in the paper are inaccurate and more interpretations should be provided to explain some obtained results. Therefore, a major revision is required to improve the manuscript.

        \begin{solution}
                Thank you for these kind comments. Your suggestions have 
                certainly improved the paper. 
        \end{solution}

        %---------------------------------------------------------------------

        \question SD-TMSR concept development does not correctly described in the section "introduction", where it states that the SD-TMSR was introduced by the Chinese Academy of Sciences. Actually, SD-TMSR concept was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) (see Ref.: Tech. Rep. ORNL-4541). In addition, the study of reference 7 which was cited to illustrate SD-TMSR concept actually adopted the single-flow single-zone MSR rather than SD-TMSR.

        \begin{solution}

        \end{solution}

        %---------------------------------------------------------------------

        \question The authors did not conduct a sufficient literature survey on the fuel cycle transition studies for the SD-TMSR concept. Cui. et al., have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) (see Ref.: Transition toward thorium fuel cycle in a molten salt reactor by using plutonium, NUCL SCI TECH (2017) 28:152; Possible scenarios for the transition to thorium fuel cycle in molten salt reactor by using enriched uranium. Progress in Nuclear Energy 104 (2018) 75-84). The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except U-233) has not studied before" in page 3 is therefore inaccurate.
        \begin{solution}
                Thank you for your helpful review.  
        \end{solution}

        %---------------------------------------------------------------------

        \question More details should be provided to illustrate the heavy metal addition for the thorium feed mechanism and non-thorium feed mechanism in page 11. It is hard to understand why the mass of Th / external heavy metals (excluding Th) is approximately equal to the mass of extracted Pa.
        \begin{solution}
               Thank you for these kind comments. Your suggestions have certainly improved the paper.
        \end{solution}

        %--------------------------------------------------------------------

        \question Phenomenons presented in Figure 3 that K-eff for the case of Pu+HALEU firstly increases and then decreases, and the time to become subcritical for the case of reactor-grade Pu is longest (except the case of U-233) should be explained.
        \begin{solution}
                 Thank you for your kind review.  
        \end{solution}

        %--------------------------------------------------------------------
        \question In page 19, why the Pa extraction time was selected to be 30s since Pa is neither the gaseous FPs nor the non-dissolved metals?
        \begin{solution}

        \end{solution}

        %--------------------------------------------------------------------
        \question For Figure 9, it is inaccurate to state that the mass of U-233 reaches equilibrium after ~30 years, apparently from the figure, we can observe that the mass of U-233 for three of the cases still increase/decrease after 30 years.

        \begin{solution}
                Thank you for the excellent point. The whole statement has been modified to read:

        \end{solution}

        %--------------------------------------------------------------------
        \question Regarding to Figure 10, reasons should be provided to explain why the time achieving Pu solubility limit for the case of TRU is shorter than that of the case of reactor-grade Pu.
        \begin{solution}
                 This has now been clarified in the text.
        \end{solution}

        %--------------------------------------------------------------------
        \question It is hard to understand that the neutron spectrum of TRU case at BOL is softer than U-233 case since TRU has a greater amount of thermal neutron absorbers and the fissile material is dominated by Pu which would generate hard neutron spectrum.

        \begin{solution}
                 Thank you for the 
        \end{solution}

        %--------------------------------------------------------------------
        \question More details should be provided to explain the radial neutron flux distribution for the cases of Pu reactor-grade and TRU presented in Fig.13 and 14. For both the radial fast and thermal neutron flux change from BOL to EOL, why it is much larger for Pu reactor-grade case compared with TRU case. In addition, the state "In contrast, for the reactor-grade Pu and TRU cases, significant changes are observed for thermal neutron flux in the outer core zone and reactor" is inaccurate, apparently from Figure 14, it can be seen that the Pu reactor-grade (initial) case has a small change in the outer core zone and reflector.
        \begin{solution}
                Thanks  
        \end{solution}

        %--------------------------------------------------------------------
        \question Regarding to the FTC for three different cases, reasons should be provided to explain why spectrum softening will positively affects the FTC since generally harder neutron spectrum would benefit FTC.
        \begin{solution}
                Thank  
        \end{solution}

        %--------------------------------------------------------------------
        \question It seems unclear why (what is the purpose) to conduct the study of six factor analysis.
        \begin{solution}
                 Thanks  
        \end{solution}

        %--------------------------------------------------------------------
        \question Making the full definition for abbreviation through the whole paper is not necessary, such as SD-TMSR, first time is enough.

        \begin{solution}
                Thank you for your insightful comment.
        \end{solution}

        %--------------------------------------------------------------------

\end{questions}
\bibliographystyle{elsarticle-num}
\bibliography{../2019-Scenarios}
\end{document}

%
% End of file `elsarticle-template-num.tex'.

### 2020-02-03 paper/highlights/highlights.tex
add review-responses and highlights files

\documentclass[review]{elsarticle}

\usepackage{lineno}
\usepackage{xspace}
\modulolinenumbers[5]

\journal{Annals of Nuclear Energy}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

%%%% packages and definitions (optional)
\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF
\usepackage{hhline}
\usepackage{amsmath}

%\usepackage[demo]{graphicx}
%\usepackage{caption}
%\usepackage{subcaption}

\usepackage{booktabs}
\usepackage{threeparttable, tablefootnote}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}
\newcolumntype{x}{>{\hsize=.25\hsize}X}

\graphicspath{ {figures/} }

% tikz %
\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

% hyperref %
\usepackage[hidelinks]{hyperref}

\begin{document}
\begin{frontmatter}
\title{Strategies for thorium fuel cycle transition in the SD-TMSR}
\end{frontmatter}
\section*{Highlights}
\begin{itemize}
       \item  
       \item  
       \item 
       \item  
       \item  
\end{itemize}
\end{document}

### 2020-02-03 paper/methods.tex

@@
 	\caption{$XZ$ (a) and $XY$ (b) section of the quarter-core model of the 
-	SD-TMSR \cite{ashraf2019whole_core}.}
+	SD-TMSR \cite{ashraf2019Preliminary}.}
 	\label{fig:ff}
@@
 \begin{table}  %[!ht]
-	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018}.}
+	\caption{The main characteristics of the SD-TMSR \cite{li_optimization_2018,ashraf2019whole_core}.}
 	\vspace{0.1in}
@@
 	\centering
-	\caption{The reprocessing table \cite{ashraf2019whole_core}.} 
+	\caption{The reprocessing table \cite{ashraf2019whole_core,ashraf2019Preliminary}.} 
 	\vspace{1ex}

### 2020-02-04 paper/revisions/review-responses.tex
solve issue #34^C

@@
         \begin{solution}
+        		  Thank you for the excellent point.
+
+        		  About depletion regions definition: we used depletion mode 1 in Serpent-2 (i.e.
+burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.
+The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.
+
+        		  About burnup time step definition: it is time interval given in days.
+During burnup time step the SD-TMSR should be critical and total fuel mass is almost constant (dm $\leq$ 0.1\%).
+We started our calculations by 30 days' time step but we do not find significant changes in K$_{eff}$ when we increased the time step to 365 days.
+The maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for the following calculations.
 
@@
         \begin{solution}
+		          Thank you for your insightful comment.
+We usually use total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input.
+Moreover, we should reduce power density accordingly because fission takes place only in the core.
+In our calculations, we introduce the total power instead of power density and SERPENT automatically divides total power by total fuel volume.
 
@@
         \begin{solution}
-                Thank you for these kind comments. Your suggestions have 
-                certainly improved the paper. 
+                Thank you very much for these comments.
+We appreciate your detailed review, which has certainly improved the paper.
+The manuscript has been enhanced and more detail is described regarding these changes in the specific comment responses below.
         \end{solution}

### 2020-02-04 cover-letter/cover-letter.tex
solve issue #34^C

@@
 
-		Please find enclosed a manuscript entitled: ``Various strategies for thorium fuel cycle transition in the SD-TMSR'' which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, 
+		Please consider our revised manuscript, ``Strategies for thorium fuel cycle transition in the SD-TMSR'', which I and my coauthors (Mr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, 
 		and Prof. Kathryn D. Huff) are submitting for publication as a research article 
-		in Annals of Nuclear Energy. The presented manuscript is 100\% original and never been published in any form (symposia, conferences, etc).
+		in Annals of Nuclear Energy.
 
-		This manuscript investigates the fuel cycle and neutronics performance of the single-fluid double-zone thorium molten salt reactor (SD-TMSR) with different fissile material loadings at startup: High Assay Low Enriched Uranium (HALEU) (19.79\%), Pu mixed with HALEU (19.79\%), reactor-grade Pu, transuranic elements (TRU), and $^{233}$U, using SERPENT-2 Monte Carlo code.
-This manuscript provides feasible strategies for thorium fuel cycle transition in the SD-TMSR based on reactor-grade Pu and transuranic elements (TRU) results.
+		We appreciate the interest that the editors and reviewers have taken in our manuscript and the constructive suggestions they have given.
+We have addressed the major concerns of the reviewers.
+It is our belief that the manuscript is substantially improved after making the suggested edits.
 
-		Declarations of interest: none\\
+		Following this letter is the detailed response to reviewers. We included the 
+	    answers in the manuscript. Changes made in the manuscript are marked using track changes.
 
-		Thank you for your consideration of our work.
+		%Declarations of interest: none\\
 
-		Your quick response will be highly appreciated.
+		Thank you again for consideration of our revised manuscript.
 

### 2020-02-04 paper/methods.tex
solve issue #34^C

@@
 calculations in this work. The results demonstrate full-core runs of 
-$1.25\times 10^7$ neutron histories per depletion step. The full burnup time of 
+$1.25\times 10^7$ neutron histories per depletion step.
+During depletion step the SD-TMSR should be critical and total fuel mass is almost constant (dm $\leq$ 0.1\%).
+We started our calculations by 30 days' time step but we do not find significant changes in K$_{eff}$ when we increased the time step to 365 days.
+The maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for the following calculations.
+The full burnup time of 
 the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
-$12$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
+$12$ $pcm$. 
+During the molten salt reactor operation, part of fuel salt flows outside of reactor core then the fission reaction is not happened in external loop, however the decay reactions happens everywhere.
+We use total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input.
+Moreover, we should reduce power density accordingly because fission takes place only in the core.
+In our calculations, we introduce the total power instead of power density and SERPENT automatically divides total power by total fuel volume.
+
+The online extraction of \gls{FPs} and other neutron absorbers 
 provides many benefits for MSRs. For example, it has the potential to reduce the initial 

### 2020-02-04 paper/revisions/review-responses.tex
Answer reviewer 1

--- 2020-02-03 paper/revisions/review-responses.tex
@@
 
+        		  Thank you for the excellent point.
+
+        		  About depletion regions definition: we used depletion mode 1 in SERPENT-2 (i.e.
+burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.
+The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.
+
+        		  About burnup time step definition: it is time interval given in days.
+During burnup time step, the SD-TMSR core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%).
+We started our calculations by 30 days' time step but we do not find significant changes in K$_{eff}$ when we increased the time step to 365 days.
+The maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for all simulation in this work.
+
+        		  We changed the paragraph as follows:\\
+        		  The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.
+We used depletion mode 1 in SERPENT-2 (i.e.
+burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.
+
+        		  We changed the paragraph as follows:\\
+        		  During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%).
+To determine the appropriate depletion step size, we conducted a time step refinement study.
+We started with $\Delta t=30$days and gradually increased the depletion time step until the error in K$_{eff}$ became significant.
+For $\Delta t=1$year the maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.
+
         \end{solution}
@@
 
+		          Thank you for your insightful comment.
+We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input.
+Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.
+
+		          We changed the paragraph as follows:\\    
+		          During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere.
+We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input.
+Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.
         \end{solution}

### 2020-02-04 paper/methods.tex
Answer reviewer 1

--- 2020-02-03 paper/methods.tex
@@
 calculations in this work. The results demonstrate full-core runs of
-$1.25\times 10^7$ neutron histories per depletion step. The full burnup time of 
+$1.25\times 10^7$ neutron histories per depletion step.
+During the depletion step, the core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%).
+To determine the appropriate depletion step size, we conducted a time step refinement study.
+We started with $\Delta t=30$days and gradually increased the depletion time step until the error in K$_{eff}$ became significant.
+For $\Delta t=1$year the maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.
+The full burnup time of 
 the SD-TMSR was 60 years with statistical error in $k_{eff}$ equal to $\pm$ 
-$12$ $pcm$. The online extraction of \gls{FPs} and other neutron absorbers 
+$12$ $pcm$. 
+During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere.
+We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input.
+Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.
+
+The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.
+We used depletion mode 1 in Serpent-2 (i.e.
+burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.
+
+The online extraction of \gls{FPs} and other neutron absorbers 
 provides many benefits for MSRs. For example, it has the potential to reduce the initial 

### 2020-02-04 paper/revisions/review-responses.tex
solve issue #35

@@
         \begin{solution}
+                 Thank you for catching this. The whole statement has been modified to read:\\
+                 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
+                 MW$_{th}$ was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.
+
+                 Thank you for catching this. Reference 7 has been removed from the paragraph.
 
@@
                 Thank you for your helpful review.
+The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except$^{233}$U) has not studied before" in page 3, has been removed.
+
+                Also, the mentioned references have been added as following:\\
+                Cui \emph{et al.} (2017-2018) have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) \cite{cui2017transition,cui2018possible}.
+
         \end{solution}
@@
         \begin{solution}
-               Thank you for these kind comments. Your suggestions have certainly improved the paper.
+               Thank you for the comment.
+Actually, in page 11, we mention that the mass of Th / external heavy metals (excluding Th) is approximately equal to the mass of extracted Fission products (FPs) and not Pa.
+Because in both feed mechanisms (thorium and non-thorium) we continually added $^{233}$U and the mass of$^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decay to $^{233}$U after $\approx$ 27 d).
+To keep the total fuel mass almost constant, the mass of Th/ external heavy metals (excluding Th) must be equal to the mass of extracted FPs.
+               Moreover, we rewrite the paragraph in page 11 to address this thought:\\
+               \begin{enumerate}
+               	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
+               	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
+               	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
+               	\subitem 3a. \textbf{Thorium feed mechanism}: mass of $^{233}$U $\approx$ mass of extracted Pa and mass of Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
+               	\subitem 3b.
+\textbf{Non-thorium feed mechanism}: mass of $^{233}$U $\approx$ mass of extracted Pa and mass of heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
+               	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
+               \end{enumerate}
+
         \end{solution}

### 2020-02-04 paper/introduction.tex
solve issue #35

@@
 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
-MW$_{th}$ was introduced by the Chinese Academy of Sciences \cite{li_optimization_2018}. The
-SD-TMSR
-is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
+MW$_{th}$ was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.
+The SD-TMSR is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
 fuel cycle. In the SD-TMSR, the fissile and fertile elements are integrated
@@
 the radius of the fuel channels in the outer zone is modified to be larger
-than the radius of the fuel channels in the inner zone \cite{nuttin2005potential,li_optimization_2018}.
+than the radius of the fuel channels in the inner zone \cite{li_optimization_2018}.
 
@@
 core until there is enough to start a new TMSR \cite{zou2018transition}.
+
+Cui \emph{et al.} (2017-2018) have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) \cite{cui2017transition,cui2018possible}.
+
 Zou \emph{et al.} (2018) studied the transitioning to thorium fuel
@@
 thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
-	zou2018transition,zou2018preliminary}. For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other
-fissile materials (except $^{233}$U) has not been studied before. Therefore,
+	zou2018transition,zou2018preliminary}. Therefore,
 the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with

### 2020-02-04 paper/introduction.tex
revmove definition for SD-TMSR

@@
 	zou2018transition,zou2018preliminary}. Therefore,
-the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the \gls{SD-TMSR} with
+the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the SD-TMSR with
 various initial fissile materials and without any external feed of $^{233}$U. We investigate five different

### 2020-02-04 paper/methods.tex
revmove definition for SD-TMSR

@@
 refueling \cite{serp2014molten}. In this work, SERPENT-2 version 2.1.31 \cite{leppanen2014serpent} simulates the 
-Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) full-core with various initial fuel types. This extension 
+SD-TMSR full-core with various initial fuel types. This extension 
 of SERPENT accounts for continuous online reprocessing and refueling 

### 2020-02-04 paper/results.tex
revmove definition for SD-TMSR

@@
 Additionally, the initial fissile material fraction was increased for the five fuel 
-salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
+salt compositions until the SD-TMSR reactor was sufficiently critical at 
 the Beginning Of Life (BOL).
@@
 the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
-\gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1}, U-233 case).
+SD-TMSR for a full lifetime (60 year) (Figure~\ref{fig:keff1}, U-233 case).
 
@@
 \end{figure}
-For the reactor-grade Pu case, the amount of $^{233}$U generated in the \gls{SD-TMSR}, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs.
+For the reactor-grade Pu case, the amount of $^{233}$U generated in the SD-TMSR, in addition to the external feed flow of Pu, is sufficient to maintain the reactor criticality and counteract the neutron absorption in the initial non-fissile isotopes and FPs.
 For the \gls{TRU} fuel salt, the amount of 
@@
 results, reactor-grade Pu and TRU are the only alternative fissile materials that  
-can be used to startup and maintain operation of the \gls{SD-TMSR}.
+can be used to startup and maintain operation of the SD-TMSR.
 
@@
 As shown in Figure~\ref{fig:NetCC}, for the $^{233}$U case, after 26 years the net production of $^{233}$U reaches 
-$1.3$ $t$; this is sufficient to start up another \gls{SD-TMSR} (see Table~\ref{tab:table5}). Similarly, 
+$1.3$ $t$; this is sufficient to start up another SD-TMSR (see Table~\ref{tab:table5}). Similarly, 
 one can see that the same amount of $^{233}$U ($1.3$ $t$) can be achieved 
@@
 (see Figure~\ref{fig:U233CC}); the neutron spectrum softens and becomes 
-similar to the initial thermal spectrum of a $^{233}$U fueled \gls{SD-TMSR}.
+similar to the initial thermal spectrum of a $^{233}$U fueled SD-TMSR.
  \begin{figure}

### 2020-02-05 paper/revisions/review-responses.tex
After Andrei's review

--- 2020-02-04 paper/revisions/review-responses.tex
@@
         \begin{solution}
+                 Thank you for catching this. The whole statement has been modified to read:\\
+                 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
+                 MW$_{th}$ was proposed for the first time by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.
+
+                 Thank you for catching this. Reference 7 has been removed from the paragraph.
 
@@
                 Thank you for your helpful review.
+The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except$^{233}$U) has not studied before" in page 3, has been removed.
+
+                Also, the mentioned references have been added as following:\\
+                Cui \emph{et al.} (2017-2018) used an in-house developed tool to study the thorium fuel cycle transition based on MSBR by employing enriched uranium and Pu as the startup fissile materials.
+Two scenarios, a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario, were investigated to achieve the fuel cycle transition.
+Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% concentration of $^{235}$U (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel by applying 60 days of chemical reprocessing \cite{cui2017transition,cui2018possible}.
+
         \end{solution}
@@
         \begin{solution}
-               Thank you for these kind comments. Your suggestions have certainly improved the paper.
+               Thank you for the comment.
+Actually, in page 11, we mention that the mass of Th / external heavy metals is approximately equal to the mass of extracted Fission products (FPs) and not Pa.
+Because in both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d).
+To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.
+
+               Moreover, we rewrite the paragraph in page 11 to address this thought:\\
+               \begin{enumerate}
+               	\item The simulation starts without injecting refueling materials (i.e. only removing FPs and Pa).
+               	\item After the first depletion calculation step, we check the total mass density of FPs and Pa in the \texttt{FP-waste tank} and \texttt{Pa-decay tank}, respectively.
+               	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
+               	\subitem 3a.
+\textbf{Thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
+               	\subitem 3b.
+\textbf{Non-thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
+               	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant (1/s).
+               \end{enumerate}
+               In both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d).
+To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.
+
         \end{solution}
@@
         \begin{solution}
-                Thank you for your insightful comment.
+                Thank you for the information. The full definition for abbreviation through the whole paper has been removed as requested.
         \end{solution}

### 2020-02-05 paper/conclusion.tex

@@
 Five initial fissile loadings strategies have been studied for 
-transitioning to the thorium fuel cycle in the Single-fluid Double-zone 
-Thorium-based Molten Salt Reactor (SD-TMSR). We 
+transitioning to the thorium fuel cycle in the SD-TMSR. We 
 adopted two different feed mechanisms: thorium and non-thorium. 

### 2020-02-05 paper/introduction.tex

@@
 The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
-MW$_{th}$ was proposed by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.
+MW$_{th}$ was proposed for the first time by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.
 The SD-TMSR is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
@@
 
-Cui \emph{et al.} (2017-2018) have made an extensive study on fuel cycle transition for SD-TMSR by employing LEU and Pu as the startup fissile materials and two transition modes (in-core transition and ex-core transition) \cite{cui2017transition,cui2018possible}.
+Cui \emph{et al.} (2017-2018) used an in-house developed tool to study the thorium fuel cycle transition based on MSBR by employing enriched uranium and Pu as the startup fissile materials.
+Two scenarios, a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario, were investigated to achieve the fuel cycle transition.
+Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% concentration of $^{235}$U (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel by applying 60 days of chemical reprocessing \cite{cui2017transition,cui2018possible}.
 
@@
 thermal-spectrum \glspl{MSR} \cite{betzler2016modeling,
-	zou2018transition,zou2018preliminary}. Therefore,
-the main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the SD-TMSR with
+	zou2018transition,zou2018preliminary}.
+The main objective of the present paper is to establish feasible strategies for thorium fuel cycle transition in the SD-TMSR with
 various initial fissile materials and without any external feed of $^{233}$U. We investigate five different

### 2020-02-05 paper/methods.tex

@@
 	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
-	\subitem 3a. \textbf{Thorium feed mechanism}: mass of Th $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
-	\subitem 3b. \textbf{Non-thorium feed mechanism}: mass of external heavy metals (excluding Th) $\approx$ mass of extracted FPs and mass of $^{233}$U $\approx$ mass of extracted Pa.
-	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant.
+	\subitem 3a.
+\textbf{Thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
+	\subitem 3b.
+\textbf{Non-thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
+	\item Dividing this mass by time and inventory of refueling material gives the corresponding feed constant (1/s).
 \end{enumerate}
-The cycle calculation runs iteratively until the burnup reaches the desired worth.
+In both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d).
+To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.
 

### 2020-02-06 paper/revisions/review-responses.tex
Comments from Reviewer 2 (6)

@@
         \begin{solution}
-                Thank you for the excellent point. The whole statement has been modified to read:
+                Thank you for the excellent point. The statement has been removed from the text.
+                Moreover, we rewrite the paragraph to address this thought:\\
+                Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.
+For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ 1.7 $t$ at the EOL.
+For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ 35 and 45 years for Pu and TRU cases, respectively, decreases.
+The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt.
+Hard neutron spectrum converts more $^{233}$U from $^{232}$Th.
+For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th).
+However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.
 

### 2020-02-06 paper/results.tex
Comments from Reviewer 2 (6)

@@
 
-Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt 
-for the $^{233}$U, reactor-grade Pu, and TRU cases. The mass of 
-$^{233}$U reaches equilibrium after $\approx$ $30$ years; overall, the 
-amount of $^{233}$U is sufficient to maintain criticality in 
-the three cases.
+Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.
+For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL.
+For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases.
+The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt.
+Hard neutron spectrum converts more $^{233}$U from $^{232}$Th.
+For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th).
+However, for $^{233}$U case, the neutron spectrum is hardened at EOL due to the accumulation of Pu isotopes.
+
 \begin{figure}

### 2020-02-06 paper/revisions/review-responses.tex
Answer q 7 and 8

@@
                 Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.
-For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ 1.7 $t$ at the EOL.
-For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ 35 and 45 years for Pu and TRU cases, respectively, decreases.
+For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL.
+For reactor-grade Pu and TRU cases, the mass of $^{233}$U firstly, increases and after $\approx$ $35$ and $45$ years for Pu and TRU cases, respectively, decreases.
 The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt.
@@
                  This has now been clarified in the text.
+                 We rewrite the paragraph to address this thought:\\
+                 Notably, for TRU case, the time achieving Pu solubility limit is shorter than that for reactor-grade Pu case.
+The reason for this is the relatively high concentration of Pu in the initial heavy metal for the TRU-started SD-TMSR ($\approx$ $29.26$ \% compared with $14.31$ \% for Pu-started SD-TMSR, see Table 5).
+
         \end{solution}
@@
         \begin{solution}
-                 Thank you for the 
+                 We appreciate your detailed review. 
+                 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U.
+$^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b).
+Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
+
+                 The following paragraph has been added to the manuscript.\\
+                 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U.
+$^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b).
+Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
+
         \end{solution}

### 2020-02-06 paper/results.tex

@@
 HM initial inventory \cite{zou2018transition}.
+Notably, for TRU case, the time achieving Pu solubility limit is shorter than that for reactor-grade Pu case.
+The reason for this is the relatively high concentration of Pu in the initial heavy metal for the TRU-started SD-TMSR ($\approx$ $29.26$ \% compared with $14.31$ \% for Pu-started SD-TMSR, see Table~\ref{tab:table5}).
+
 \begin{figure}
@@
 similar to the initial thermal spectrum of a $^{233}$U fueled SD-TMSR.
+The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U.
+$^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b).
+Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
  \begin{figure}

### 2020-02-06 paper/revisions/review-responses.tex
Comments from Reviewer 2 (4)

@@
         \begin{solution}
-                 Thank you for your kind review.
+                 Thank you for your insightful comment. Phenomenons presented in Figure 3 have been described in the manuscript.
+
+                 The following paragraph has been added to the manuscript.\\
+                 For Pu+HALEU case, K${_eff}$ firstly increases during the first $\approx$ $3$ EFPY and after that decreases.
+This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the fission power until the transition to Th/$^{233}$U fuel cycle.
+Figure~\ref{fig:diffPuAll811} shows the variation of fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) during reactor operation.
+For TRU and reactor-grade Pu, the fissile plutonium isotopes are depleted, during operating (the fissile material is dominated by Pu in these cases).
+For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium.
+Therefore, the mass of fissile plutonium increases during operating but its value still relatively low.
+For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ 3 EFPY and then decreases.
+The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, K${_eff}$ increases during the first $\approx$ 3 years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
+
+                 The following paragraph has been added to the manuscript.\\
+                 Figure~\ref{fig:keff1} shows that the decrease in K${_eff}$ for reactor-grade Pu case occurs at a much later operating time than for other cases, this is because of the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
+Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.
+
         \end{solution}
@@
                  We appreciate your detailed review.
-                 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U.
-$^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b).
-Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
 

### 2020-02-06 paper/results.tex
Comments from Reviewer 2 (4)

@@
 Consequently, the core becomes subcritical after $\approx$ $6$ years of operation.
-For the reactor-grade Pu fuel salt, the core becomes subcritical after $\approx$ $12$ years because the amount of $^{233}$U generated is not sufficient to counteract the neutron absorption in the non-fissile plutonium isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.
+
+For Pu+HALEU case, K${_eff}$ firstly increases during the first $\approx$ $3$ EFPY and after that decreases.
+This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the fission power until the transition to Th/$^{233}$U fuel cycle.
+Figure~\ref{fig:diffPuAll811} shows the variation of fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) during reactor operation.
+For TRU and reactor-grade Pu, the fissile plutonium isotopes are depleted, during operating (the fissile material is dominated by Pu in these cases).
+For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium.
+Therefore, the mass of fissile plutonium increases during operating but its value still relatively low.
+For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ 3 EFPY and then decreases.
+The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, K${_eff}$ increases during the first $\approx$ 3 years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
+
+Figure~\ref{fig:keff1} shows that the decrease in K${_eff}$ for reactor-grade Pu case occurs at a much later operating time than for other cases, this is because of the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
+Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{diffPuAll811.png}
+		\vspace{-0.5in}
+	\caption{The variation of relative mass of fissile Pu ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) during reactor operation.} 
+	\label{fig:diffPuAll811}
+\end{figure}
 

### 2020-02-07 paper/revisions/review-responses.tex
Comments from Reviewer 2 (4) after Andrei's review

--- 2020-02-06 paper/revisions/review-responses.tex
@@
         \begin{solution}
-                 Thank you for your kind review.
+                 Thank you for your insightful comment. Phenomenons presented in Figure 3 have been described in the manuscript.
+
+                 The following paragraph has been added to the manuscript.\\
+                 For Pu+HALEU case, K${_eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
+This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle.
+Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor operation.
+For TRU and reactor-grade Pu, the fissile plutonium isotopes are gradually depleted, during operating (the fissile material is dominated by Pu in these cases).
+For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium.
+Therefore, the mass of fissile plutonium increases during operating but its value still relatively low.
+For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases.
+The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, K${_eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
+
+                 The following paragraph has been added to the manuscript.\\
+                 Figure~\ref{fig:keff1} shows that the decrease in K${_eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
+Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.
+
         \end{solution}

### 2020-02-07 paper/results.tex

--- 2020-02-06 paper/results.tex
@@
 Consequently, the core becomes subcritical after $\approx$ $6$ years of operation.
-For the reactor-grade Pu fuel salt, the core becomes subcritical after $\approx$ $12$ years because the amount of $^{233}$U generated is not sufficient to counteract the neutron absorption in the non-fissile plutonium isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.
+
+For Pu+HALEU case, K${_eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
+This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle.
+Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor operation.
+For TRU and reactor-grade Pu, the fissile plutonium isotopes are gradually depleted, during operating (the fissile material is dominated by Pu in these cases).
+For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium.
+Therefore, the mass of fissile plutonium increases during operating but its value still relatively low.
+For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases.
+The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, K${_eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
+
+Figure~\ref{fig:keff1} shows that the decrease in K${_eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
+Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{diffPuAll811.png}
+		\vspace{-0.5in}
+	\caption{The variation of relative mass of fissile Pu ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) during reactor operation.} 
+	\label{fig:diffPuAll811}
+\end{figure}
 

### 2020-02-08 paper/revisions/review-responses.tex
Comments from Reviewer 2 (main)

@@
 
+                The works described in \cite{cui2017transition} and
+                \cite{cui2018possible} are most similar to the work
+                presented in this paper. However, a few major differences
+                follow: (1) Cui \emph{et al.} employed an in-house developed tool which is based on SCALE6.1 for depletion simulations while this work used SERPENT-2; (2) in current work we investigated different initial loading cases (HALEU, Pu+HALEU, reactor-grade Pu, TRU and $^{233}$U) while Cui \emph{et al.} studied enriched uranium and Pu as the startup fissile materials; (3) we adopted the SD-TMSR model optimized by Li \emph{et al.} \cite{li_optimization_2018} which is different than the model adopted by Cui \emph{et al.}, in current model, the radii of the fuel channels in the outer and inner zone are 5 and 3.5 cm, respectively, while in Cui \emph{et al.} model, all fuel channels have the same radius 2.03 cm, also the side length of the graphite hexagonal prism is different in two models (7.5 instead of 10 cm in Cui model), also, total salt volume, density and composition are different than those used in our study; (4) Cui \emph{et al.} studied the highly enriched uranium (e$>$90), while we excluded it due to the unavailability of this material for use as an initial reactor fuel (non-proliferation issues) and because the performance of this material is expected to be similar to $^{233}$U; (5) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle transition: a (B\&B) scenario and a Pre-breeding scenario, while we adopting different approach by introducing two different feed mechanisms: thorium and non-thorium feed mechanism.
+
+                In more detail, in Cui's scenarios, the amount of Th is kept constant.
+$^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality.
+In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor.
+Thus, the criticality of the core is maintained by refueling external fissile material.
+
+                In current work, in thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the Pa-decay tank into the core.
+The excess $^{233}$U (if exist) is stored outside the core.
+In non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the Pa-decay tank.
+Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm $\leq$ 0.1\%).
+In non-thorium feed mechanism, the amount of Th decreases during reactor operation, while it is constant in thorium feed mechanism.
+
         \end{solution}

### 2020-02-08 paper/introduction.tex
Comments from Reviewer 2 (main)

@@
 
-Cui \emph{et al.} (2017-2018) used an in-house developed tool to study the thorium fuel cycle transition based on MSBR by employing enriched uranium and Pu as the startup fissile materials.
-Two scenarios, a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario, were investigated to achieve the fuel cycle transition.
-Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% concentration of $^{235}$U (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel by applying 60 days of chemical reprocessing \cite{cui2017transition,cui2018possible}.
-
 Zou \emph{et al.} (2018) studied the transitioning to thorium fuel
@@
 under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible in the MSFR while closing the current fuel cycle and optimizing the management of the long-term wastes \cite{heuer2014towards}.
+
+Cui \emph{et al.} (2017-2018) used an in-house developed tool to study the thorium fuel cycle transition based on MSBR by employing enriched uranium and Pu as the startup fissile materials.
+Two scenarios, a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario, were investigated to achieve the fuel cycle transition.
+Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% concentration of $^{235}$U (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel by applying 60 days of chemical reprocessing \cite{cui2017transition,cui2018possible}.
+
+The works described in \cite{cui2017transition} and
+\cite{cui2018possible} are most similar to the work
+presented in this paper. However, a few major differences
+follow: (1) Cui \emph{et al.} employed an in-house developed tool which is based on SCALE6.1 for depletion simulations while this work used SERPENT-2; (2) in current work we investigated different initial loading cases (HALEU, Pu+HALEU, reactor-grade Pu, TRU and $^{233}$U) while Cui \emph{et al.} studied enriched uranium and Pu as the startup fissile materials; (3) we adopted the SD-TMSR model optimized by Li \emph{et al.} \cite{li_optimization_2018} which is different than the model adopted by Cui \emph{et al.}, in current model, the radii of the fuel channels in the outer and inner zone are 5 and 3.5 cm, respectively, while in Cui \emph{et al.} model, all fuel channels have the same radius 2.03 cm, also the side length of the graphite hexagonal prism is different in two models (7.5 instead of 10 cm in Cui model), also, total salt volume, density and composition are different than those used in our study; (4) Cui \emph{et al.} studied the highly enriched uranium (e$>$90), while we excluded it due to the unavailability of this material for use as an initial reactor fuel (non-proliferation issues) and because the performance of this material is expected to be similar to $^{233}$U; (5) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle transition: a (B\&B) scenario and a Pre-breeding scenario, while we adopting different approach by introducing two different feed mechanisms: thorium and non-thorium feed mechanism.
+
+In more detail, in Cui's scenarios, the amount of Th is kept constant.
+$^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality.
+In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor.
+Thus, the criticality of the core is maintained by refueling external fissile material.
+
+In current work, in thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the Pa-decay tank into the core.
+The excess $^{233}$U (if exist) is stored outside the core.
+In non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the Pa-decay tank.
+Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm $\leq$ 0.1\%).
+In non-thorium feed mechanism, the amount of Th decreases during reactor operation, while it is constant in thorium feed mechanism.
 

### 2020-02-09 paper/introduction.tex
Comments from Reviewer 2 (main) after Andrei's review

--- 2020-02-05 paper/introduction.tex
@@
 under different launching scenarios (e.g., enriched uranium and TRU); they concluded that starting the thorium fuel cycle is feasible in the MSFR while closing the current fuel cycle and optimizing the management of the long-term wastes \cite{heuer2014towards}.
+
+Cui \emph{et al.} (2017-2018) analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
+Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.
+
+The research effort described in \cite{cui2017transition} and
+\cite{cui2018possible} is most similar to the work
+presented in this paper. However, a few major differences
+are: (1) we used built-in truly continuous fuel depletion capabilities in
+SERPENT-2 \cite{aufiero2013extended} while Cui \emph{et al.} employed an in-house tool named MSR
+Reprocessing Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE and employs a batch-wise approach (the burnup simulation stops at a given time and restarts with a new liquid fuel composition after removal of discarded materials and addition of fissile/fertile materials); (2) we investigated different initial loading cases (HALEU, Pu+HALEU, reactor-grade Pu, TRU and $^{233}$U) while Cui \emph{et al.} studied only uranium and Pu as the startup fissile materials; (3) we adopted the SD-TMSR core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which is different from the MSBR-like model adopted by Cui \emph{et al.}; (4) Cui \emph{et al.} studied the high-enriched uranium (e$>$90) while we excluded it due to the unavailability of this material for use as an initial reactor fuel (non-proliferation issues) and because the performance of this material is expected to be similar to $^{233}$U; (5) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle transition: a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario while we adopting different approach by introducing two different feed mechanisms: thorium and non-thorium feed mechanism.
+
+In more detail, in current work, the radii of the fuel channels in the outer and inner zone are 5 and 3.5 cm, respectively, while in Cui \emph{et al.} work, all fuel channels have the same radius 2.03 cm, also, the side length of the graphite hexagonal prism is different in both models (7.5 instead of 10 cm in Cui model), total salt volume, density, and composition are different than those used in our study.
+In Cui's scenarios, the amount of Th is kept constant.
+$^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality.
+In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor.
+Thus, the criticality of the core is maintained by refueling external fissile material.
+In current work, using the thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the \texttt{Pa-decay tank} into the core.
+The excess $^{233}$U (if exist) is stored outside the core.
+In the non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the \texttt{Pa-decay tank}.
+Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm$_{total fuel}$ $\leq$ 0.1\%).
+In the non-thorium feed mechanism, the amount of Th decreases during reactor operation while it is constant in the thorium feed mechanism.
 

### 2020-02-10 paper/revisions/review-responses.tex

--- 2020-02-07 paper/revisions/review-responses.tex
@@
 
-                Also, the mentioned references have been added as following:\\
-                Cui \emph{et al.} (2017-2018) used an in-house developed tool to study the thorium fuel cycle transition based on MSBR by employing enriched uranium and Pu as the startup fissile materials.
-Two scenarios, a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario, were investigated to achieve the fuel cycle transition.
-Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% concentration of $^{235}$U (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel by applying 60 days of chemical reprocessing \cite{cui2017transition,cui2018possible}.
+                The following paragraphs have been added to the manuscript.\\
+                Cui \emph{et al.} (2017-2018) analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
+Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.
+
+                The research effort described in \cite{cui2017transition} and
+                \cite{cui2018possible} is most similar to the work
+                presented in this paper. However, a few major differences
+                are: (1) we used built-in truly continuous fuel depletion capabilities in
+                SERPENT-2 \cite{aufiero2013extended} while Cui \emph{et al.} employed an in-house tool named MSR
+                Reprocessing Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE and employs a batch-wise approach (the burnup simulation stops at a given time and restarts with a new liquid fuel composition after removal of discarded materials and addition of fissile/fertile materials); (2) we investigated different initial loading cases (HALEU, Pu+HALEU, reactor-grade Pu, TRU and $^{233}$U) while Cui \emph{et al.} studied only uranium and Pu as the startup fissile materials; (3) we adopted the SD-TMSR core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which is different from the MSBR-like model adopted by Cui \emph{et al.}; (4) Cui \emph{et al.} studied the high-enriched uranium (e$>$90) while we excluded it due to the unavailability of this material for use as an initial reactor fuel (non-proliferation issues) and because the performance of this material is expected to be similar to $^{233}$U; (5) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle transition: a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario while we adopting different approach by introducing two different feed mechanisms: thorium and non-thorium feed mechanism.
+
+                In more detail, in current work, the radii of the fuel channels in the outer and inner zone are 5 and 3.5 cm, respectively, while in Cui \emph{et al.} work, all fuel channels have the same radius 2.03 cm, also, the side length of the graphite hexagonal prism is different in both models (7.5 instead of 10 cm in Cui model), total salt volume, density, and composition are different than those used in our study.
+In Cui's scenarios, the amount of Th is kept constant.
+$^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality.
+In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor.
+Thus, the criticality of the core is maintained by refueling external fissile material.
+                In current work, using the thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the \texttt{Pa-decay tank} into the core.
+The excess $^{233}$U (if exist) is stored outside the core.
+In the non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the \texttt{Pa-decay tank}.
+Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm$_{total fuel}$ $\leq$ 0.1\%).
+In the non-thorium feed mechanism, the amount of Th decreases during reactor operation while it is constant in the thorium feed mechanism.
 

### 2020-02-10 paper/revisions/review-responses.tex
Comments from Reviewer 2 (5)

@@
 During burnup time step, the SD-TMSR core was maintained critical and total fuel mass was almost constant (dm $\leq$ 0.1\%).
-We started our calculations by 30 days' time step but we do not find significant changes in K$_{eff}$ when we increased the time step to 365 days.
-The maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for all simulation in this work.
+We started our calculations by 30 days' time step but we do not find significant changes in $k_{eff}$ when we increased the time step to 365 days.
+The maximum change in $k_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for all simulation in this work.
 
@@
 To determine the appropriate depletion step size, we conducted a time step refinement study.
-We started with $\Delta t=30$days and gradually increased the depletion time step until the error in K$_{eff}$ became significant.
-For $\Delta t=1$year the maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.
+We started with $\Delta t=30$days and gradually increased the depletion time step until the error in $k_{eff}$ became significant.
+For $\Delta t=1$year the maximum change in $k_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.
 
@@
                  The following paragraph has been added to the manuscript.\\
-                 For Pu+HALEU case, K${_eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
+                 For Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
 This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle.
@@
 For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases.
-The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, K${_eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
+The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
 
                  The following paragraph has been added to the manuscript.\\
-                 Figure~\ref{fig:keff1} shows that the decrease in K${_eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
+                 Figure~\ref{fig:keff1} shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
 Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.
@@
         \begin{solution}
+                  Thank you for the question.
+Specifically, Pa is removed from the fuel by chemical reprocessing into the \texttt{Pa-decay tank} to decay and produce $^{233}$U.
+The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U.
+Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
+The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time.
+Also, a relatively large amount of $^{233}$U can be obtained when we applied RP = $30$ $s$ against $10.59$ $d$.
+The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup.
+Therefore, we selected the RP = $30$ $s$.
+This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years).
+For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~\ref{fig:keff2}).
 
+                  The following paragraph has been added to the manuscript.\\
+                  The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U.
+Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
+The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time.
+Also, a relatively large amount of $^{233}$U can be obtained when we applied RP = $30$ $s$ against $10.59$ $d$.
+The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup.
+Therefore, we selected the RP = $30$ $s$.
+This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years).
+For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~\ref{fig:keff2}).
         \end{solution}

### 2020-02-11 paper/results.tex

@@
 
-For Pu+HALEU case, K${_eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
+For Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
 This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle.
@@
 For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases.
-The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, K${_eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
+The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
 
-Figure~\ref{fig:keff1} shows that the decrease in K${_eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
+Figure~\ref{fig:keff1} shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
 Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted \cite{betzler2016modeling}.
@@
 maintain an almost constant inventory throughout the full operation time.
-For the Pu and TRU cases (Figure~\ref{fig:inventoryPu_TRUCCC}), the Pa extraction time was selected to be 30 s 
-to avoid poisoning the core. Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
+
+The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U.
+Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
+The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time.
+Also, a relatively large amount of $^{233}$U can be obtained when we applied RP = $30$ $s$ against $10.59$ $d$.
+The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup.
+Therefore, we selected the RP = $30$ $s$.
+This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ $40$ years).
+For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~\ref{fig:keff2}).
+
+Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
 is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
@@
 years (see Figure~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC}).
+
 \begin{figure}
@@
 \end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{Keff_U2332.png}
+	\vspace{-0.5in}
+	\caption{The effect of Reprocessing Period (RP) on the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.}
+	\label{fig:Keff_U2332}
+\end{figure}
+
 \begin{figure}

### 2020-02-11 paper/highlights/highlights.tex
Highlights and minor changes

@@
 \begin{itemize}
-       \item  
-       \item  
-       \item 
-       \item  
-       \item  
+	\item Five initial fissile loadings have been studied for transitioning to the thorium fuel cycle in the SD-TMSR.
+	\item The MSR burnup routine provided by SERPENT-2 is used to simulate the online reprocessing and refueling in the SD-TMSR.
+	\item The dynamics of $k_{eff}$, major isotopes mass, and essential safety parameters have been investigated.
+	\item The neutron energy spectrum shift during the reactor operation was calculated.
+	\item Temperature coefficient of reactivity evolution during SD-TMSR operation are investigated.
 \end{itemize}

### 2020-02-12 paper/results.tex

@@
 	\centering
+	\includegraphics[width=\textwidth]{keff1.png}
+	\vspace{-0.5in}
+	\caption{The change of the effective multiplication factor during 60 \gls{EFPY} of reactor operation for thorium feed mechanism (confidence interval $\pm\sigma$ is shaded).} 
+	\label{fig:keff1}
+\end{figure}
+
+\begin{figure}
+	\centering
 	\includegraphics[width=\textwidth]{diffPuAll811.png}
@@
 	\label{fig:diffPuAll811}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{keff1.png}
-	\vspace{-0.5in}
-	\caption{The change of the effective multiplication factor during 60 \gls{EFPY} of reactor operation for thorium feed mechanism (confidence interval $\pm\sigma$ is shaded).} 
-	\label{fig:keff1}
 \end{figure}
@@
 Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
-is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
+is relatively low when compared with Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
 elements for all three cases reach the equilibrium state after $\approx$ $30$ 
@@
 reactivity remains relatively large and negative (in the range between $-2.59$ 
-and $-5.06$ pcm/K) compared to the conventional \gls{PWR}, which has 
+and $-5.06$ pcm/K) compared with the conventional \gls{PWR}, which has 
 temperature coefficient of about $-1.71$ $pcm/^{\circ}F\approx -3.08$ $pcm/K$ 

### 2020-02-17 paper/revisions/review-responses.tex
Reviewer 2 comments 9-11 addressed #47 #38

@@
         		  We changed the paragraph as follows:\\
+
         		  The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.
@@
 
-		          Thank you for your insightful comment.
-We used total fuel salt inventory in the primary loop to define the fuel material in the SERPENT input.
-Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.
+		          Thank you for your insightful comment. We used total fuel 
+		          salt inventory in the primary loop to define the fuel 
+		          material in the SERPENT input. Moreover, we accordingly 
+		          adjusted power density in SERPENT burnup calculations 
+		          because fission takes place only in the core region.
+		          We changed the paragraph as follows:\\
 
-		          We changed the paragraph as follows:\\    
 		          During the molten salt reactor operation, part of fuel salt flows outside of the reactor core then the fission reaction has not happened in the external loop, however, the decay reactions happen everywhere.
@@
         \begin{solution}
-                 Thank you for catching this. The whole statement has been modified to read:\\
+                 Thank you for catching this. The whole statement has been 
+                 modified to read:\\
+
                  The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
@@
         \begin{solution}
-                Thank you for your helpful review.
-The state "For the SD-TMSR concept, simulating the fissile core startup and fuel cycle transition with other fissile materials (except$^{233}$U) has not studied before" in page 3, has been removed.
+                Thank you for your helpful review. The state "For the SD-TMSR 
+                concept, simulating the fissile core startup and fuel cycle 
+                transition with other fissile materials (except$^{233}$U) has 
+                not studied before" in page 3, has been removed. 
+                The following paragraphs have been added to the manuscript.\\
 
-                The following paragraphs have been added to the manuscript.\\
                 Cui \emph{et al.} (2017-2018) analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
@@
         \begin{solution}
-               Thank you for the comment.
-Actually, in page 11, we mention that the mass of Th / external heavy metals is approximately equal to the mass of extracted Fission products (FPs) and not Pa.
-Because in both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d).
-To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.
+               Thank you for the comment. Actually, in page 11, we mention 
+               that the mass of Th / external heavy metals is approximately 
+               equal to the mass of extracted Fission products (FPs) and not 
+               Pa. Because in both feed mechanisms (thorium and non-thorium) 
+               we continuously added $^{233}$U and the mass of injected 
+               $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa 
+               decays to $^{233}$U after $\approx$ 27 d). To keep the total 
+               fuel mass almost constant, for \textbf{thorium feed mechanism}, 
+               the mass of injected Th must be equal to the mass of extracted 
+               FPs and for \textbf{non-thorium feed mechanism}, the mass of 
+               injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade 
+               Pu, or TRU) must be equal to the mass of extracted FPs.
+               Moreover, we rewrite the paragraph in page 11 to address this 
+               thought:\\
 
-               Moreover, we rewrite the paragraph in page 11 to address this thought:\\
                \begin{enumerate}
@@
         \begin{solution}
-                 Thank you for your insightful comment. Phenomenons presented in Figure 3 have been described in the manuscript.
+                 Thank you for your insightful comment. Phenomenons presented 
+                 in Figure 3 have been described in the manuscript.
+                 The following paragraph has been added to the manuscript.\\
 
-                 The following paragraph has been added to the manuscript.\\
                  For Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
@@
                  The following paragraph has been added to the manuscript.\\
+
                  Figure~\ref{fig:keff1} shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
@@
                   The following paragraph has been added to the manuscript.\\
+
                   The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U.
@@
                 Moreover, we rewrite the paragraph to address this thought:\\
+
                 Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.
@@
                  We rewrite the paragraph to address this thought:\\
+
                  Notably, for TRU case, the time achieving Pu solubility limit is shorter than that for reactor-grade Pu case.
@@
                  We appreciate your detailed review.                   
+                 The following paragraph has been added to the manuscript:\\
 
-                 The following paragraph has been added to the manuscript.\\
                  The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U.
@@
         %--------------------------------------------------------------------
-        \question More details should be provided to explain the radial neutron flux distribution for the cases of Pu reactor-grade and TRU presented in Fig.13 and 14.
-For both the radial fast and thermal neutron flux change from BOL to EOL, why it is much larger for Pu reactor-grade case compared with TRU case.
-In addition, the state "In contrast, for the reactor-grade Pu and TRU cases, significant changes are observed for thermal neutron flux in the outer core zone and reactor" is inaccurate, apparently from Figure 14, it can be seen that the Pu reactor-grade (initial) case has a small change in the outer core zone and reflector.
+        \question More details should be provided to explain the radial 
+        neutron flux distribution for the cases of Pu reactor-grade and TRU 
+        presented in Fig.13 and 14. For both the radial fast and thermal 
+        neutron flux change from BOL to EOL, why it is much larger for Pu 
+        reactor-grade case compared with TRU case. In addition, the state "In 
+        contrast, for the reactor-grade Pu and TRU cases, significant changes 
+        are observed for thermal neutron flux in the outer core zone and 
+        reactor" is inaccurate, apparently from Figure 14, it can be seen that 
+        the Pu reactor-grade (initial) case has a small change in the outer 
+        core zone and reflector. 
         \begin{solution}
-                Thanks  
+				Thank you for pointing it out. Figure 14 shows significant 
+				changes \textbf{during reactor operation} in the outer core 
+				zone for the Pu (green line) and almost no changes for the TRU 
+				(orange). In this paragraph, we comparing changes in the flux 
+				due to fuel salt depletion (initial vs equilibrium), but not 
+				with $r$ coordinate. However, we are agree that thermal flux 
+				drop in the reflector is more dramatic for the TRU (initial 
+				and equilibrium compositions) an the Pu (equilibrium) cases 
+				than for the U-233 case. We think it happens because of 
+				non-optimal geometry of the core for the Pu and TRU initial 
+				loading.			
+				The following paragraphs has been added to the manuscript for 
+				clarify this point:\\
+
+				Notably, the neutron flux change for both the fast and thermal 
+				energies is 
+				much larger for the reactor-grade Pu case than for TRU case 
+				(Figures~15 and 16). The 
+				reason is the 
+				much softer neutron spectrum for the TRU initial loading 
+				compared with the 
+				reactor-grade Pu as shown in 
+				Figure~14: peak thermal 
+				neutron flux is about 4 times larger for the TRU case. The 
+				neutron spectrum in 
+				the SD-TMSR core initially loaded by TRU is much softer than 
+				the reactor-grade 
+				Pu case and even than the U-233 case because $^{232}$Th 
+				inventory is the 
+				lowest for the TRU case: 54.4t instead of 67.5t  and 76.9t for 
+				the  
+				reactor-grade Pu and U-233 cases, respectively 
+				(Table~5). 
+				$^{232}$Th greatly affects the neutron energy spectrum due to 
+				its large 
+				absorption cross section in the thermal energy range and 
+				resonance region 
+				between $10^{-5}$ and $10^{-3}$. Finally, when the TRU and the 
+				reactor-grade 
+				Pu cases reached equilibrium fuel salt composition ($\approx 
+				30$ years after 
+				startup), the radial fast and thermal neutron flux 
+				distribution became similar 
+				in both shape and magnitude.
+
+				More changes in thermal neutron flux shape and magnitude 
+				during the reactor 
+				operation for the $^{233}$U case are observed in the inner 
+				core zone 
+				($R\lesssim150$) than in the outer core zone. In the outer 
+				core zone, 
+				significant changes during reactor operation are observed for 
+				the thermal 
+				neutron flux for the reactor-grade Pu case. In contrast, for 
+				the TRU case, it 
+				is almost negligible. Additionally, 
+				Figure~16 shows 
+				relatively significant changes in thermal flux leakage from 
+				the core for the 
+				Pu (equilibrium composition) and TRU (initial and equilibrium 
+				composition) 
+				cases. The SD-TMSR core design was optimized for $^{233}$U  
+				\cite{li_optimization_2018}; thus, the core geometry (e.g., 
+				channels lattice 
+				pitch) must be re-optimized for another type of fuel to obtain 
+				better 
+				neutronics performance.
         \end{solution}
@@
         \begin{solution}
-                Thank  
+                Thank you for your insightful comment.  Indeed, the Doppler 
+                effect coefficient ($\alpha_{D,F}$) is usually stronger for 
+                harder spectrum (see Table~8, ``Fuel salt temperature''), so, 
+                spectrum softening negatively affects $\alpha_{D,F}$ (it is 
+                decreasing by value but still negative). But we additionally 
+                considered the fuel salt density coefficient 
+                ($\alpha_{\rho,F}$), which is usually positive in thermal MSRs 
+                (e.g., $+1.09pcm/K$ for the \gls{MSBR}           
+                \cite{robertson_conceptual_1971}) and \textbf{softer} neutron 
+                spectrum benefit $\alpha_{\rho,F}$ \cite{li_effects_2018-1, 
+                rykhlevskii2019modeling}. More analysis on this topic:
+            Li, X., Ma, Y., Yu, C. et al. Effects of fuel salt composition on 
+            fuel salt temperature coefficient (FSTC) for an under-moderated 
+            molten salt reactor (MSR). NUCL SCI TECH 29, 110 (2018). 
+            https://doi.org/10.1007/s41365-018-0458-1.     
+	            The following paragraphs has been added to the manuscript:\\
+
+	            The \gls{FTC} is a combination of the Doppler effect 
+	            coefficient 
+	            ($\alpha_{D,F}$) and density coefficient ($\alpha_{\rho,F}$) 
+	            and significantly 
+	            affected by the neutron spectrum. Li \emph{et al.} reported 
+	            that 
+	            $\alpha_{D,F}$ in thermal \gls{MSR} is always negative and 
+	            increases by 
+	            magnitude when spectrum hardening (see Table~8, first raw). 
+	            In contrast, $\alpha_{\rho,F}$ is a combination of 
+	            moderator-to-fuel volume 
+	            ratio, absorption cross section of heavy metal, and the core 
+	            leakage. When the 
+	            fuel salt temperature increases, the salt becomes less dense, 
+	            causing a 
+	            reduction in the fuel concentration and the neutron spectrum 
+	            become softer. 
+	            Such spectrum softening is leading to a rise in macroscopic 
+	            absorption cross 
+	            section of the fissile isotopes. Moreover, the spectrum 
+	            softening may leads to 
+	            a larger fast fission reaction rate \cite{li_effects_2018-1}. 
+	            Thus, spectrum 
+	            softening positively affects the density coefficient 
+	            ($\alpha_{\rho,F}$): 
+	            $+1.54$ $pcm/K$ and $-1.58$ $pcm/K$ at the startup and 
+	            equilibrium for the 
+	            reactor-grade Pu case, respectively. More discussion about 
+	            effects of fuel 
+	            salt composition in the \gls{FTC} can be found elsewhere 
+	            \cite{li_effects_2018-1}.
         \end{solution}
@@
         \begin{solution}
-                 Thanks  
+                 Thank you for bringing our attention to the point. Usually, 
+                 six factor analysis helps to understand reasons of changes in 
+                 TCs and control rod worths during reactor operation. But in 
+                 this case, considering many various cases, such analysis is 
+                 outmoded.           
+                  The section has been removed from the manuscript completely.
         \end{solution}

### 2020-02-17 paper/results.tex
Reviewer 2 comments 9-11 addressed #47 #38

@@
 \end{figure}
+\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
+	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
+	\caption{Radial thermal neutron flux distribution for 3 different initial 
+		fuel salt compositions at startup and equilibrium (the thermal flux 
+		confidence interval $\pm\sigma<1.6$\% for all cases).}
+	\label{fig:thermal_flux}
+\end{figure}
 
@@
 isotope, which softening the neutron spectrum of the reactor.
-\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
-	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
-	\caption{Radial thermal neutron flux distribution for 3 different initial 
-		fuel salt compositions at startup and equilibrium (the thermal flux 
-		confidence interval $\pm\sigma<1.6$\% for all cases).}
-	\label{fig:thermal_flux}
-\end{figure}
 
-More changes in thermal neutron flux shape and magnitude for the 
-$^{233}$U case are observed in the inner core zone ($R\lesssim150$) than 
-in the outer core zone. In contrast, for the reactor-grade Pu and TRU cases, 
-significant changes are observed for thermal neutron flux in the outer core 
-zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
-relatively large changes in thermal flux leakage from the core for the Pu and 
-TRU cases. The SD-TMSR core design was optimized for $^{233}$U  
-\cite{li_optimization_2018}, thus, the core geometry (e.g., channels lattice 
+Notably, the neutron flux change for both the fast and thermal energies is 
+much larger for the reactor-grade Pu case than for TRU case 
+(Figures~\ref{fig:fast_flux} and \ref{fig:thermal_flux}). The reason is the 
+much softer neutron spectrum for the TRU initial loading compared with the 
+reactor-grade Pu as shown in Figure~\ref{fig:spectrumFLUX110vC}: peak thermal 
+neutron flux is about 4 times larger for the TRU case. The neutron spectrum in 
+the SD-TMSR core initially loaded by TRU is much softer than the reactor-grade 
+Pu case and even than the U-233 case because $^{232}$Th inventory is the 
+lowest for the TRU case: 54.4t instead of 67.5t  and 76.9t for the  
+reactor-grade Pu and U-233 cases, respectively (Table~\ref{tab:table5}). 
+$^{232}$Th greatly affects the neutron energy spectrum due to its large 
+absorption cross section in the thermal energy range and resonance region 
+between $10^{-5}$ and $10^{-3}$. Finally, when the TRU and the reactor-grade 
+Pu cases reached equilibrium fuel salt composition ($\approx 30$ years after 
+startup), the radial fast and thermal neutron flux distribution became similar 
+in both shape and magnitude.
+
+More changes in thermal neutron flux shape and magnitude during the reactor 
+operation for the $^{233}$U case are observed in the inner core zone 
+($R\lesssim150$) than in the outer core zone. In the outer core zone, 
+significant changes during reactor operation are observed for the thermal 
+neutron flux for the reactor-grade Pu case. In contrast, for the TRU case, it 
+is almost negligible. Additionally, Figure~\ref{fig:thermal_flux} shows 
+relatively significant changes in thermal flux leakage from the core for the 
+Pu (equilibrium composition) and TRU (initial and equilibrium composition) 
+cases. The SD-TMSR core design was optimized for $^{233}$U  
+\cite{li_optimization_2018}; thus, the core geometry (e.g., channels lattice 
 pitch) must be re-optimized for another type of fuel to obtain better 
@@
 When the fuel salt temperature increases, the density of the salt decreases, 
-but at the same time, the total volume of fuel salt in the 
-core remains constant because it
-is bounded by the vessel. When the graphite 
-temperature increases, the density of
-graphite decreases, creating additional 
-space for the salt. The cross section temperatures for the fuel and moderator 
-were changed from 900 to 1000 K to determine the temperature coefficients. 
+but at the same time, the total volume of fuel salt in the core remains 
+constant because it is bounded by the vessel. When the graphite temperature 
+increases, the density of graphite decreases, creating additional space for 
+the salt. The cross section temperatures for the fuel and moderator were 
+changed from 900 to 1000 K to determine the temperature coefficients. 
 This work considered five different cases:
@@
 and TRU cases, the \gls{FTC} increases in magnitude at equilibrium, by $31\%$ 
-and $14\%$, respectively. Spectrum softening for these fueling cases 
-positively affects the \gls{FTC} magnitude, and this effect seems to be 
-proportional to the spectrum shift.
+and $14\%$, respectively.
+
+The \gls{FTC} is a combination of the Doppler effect coefficient 
+($\alpha_{D,F}$) and density coefficient ($\alpha_{\rho,F}$) and significantly 
+affected by the neutron spectrum. Li \emph{et al.} reported that 
+$\alpha_{D,F}$ in thermal \gls{MSR} is always negative and increases by 
+magnitude when spectrum hardening (see Table~\ref{tab:tcoe}, first raw). 
+In contrast, $\alpha_{\rho,F}$ is a combination of moderator-to-fuel volume 
+ratio, absorption cross section of heavy metal, and the core leakage. When the 
+fuel salt temperature increases, the salt becomes less dense, causing a 
+reduction in the fuel concentration and the neutron spectrum become softer. 
+Such spectrum softening is leading to a rise in macroscopic absorption cross 
+section of the fissile isotopes. Moreover, the spectrum softening may leads to 
+a larger fast fission reaction rate \cite{li_effects_2018-1}. Thus, spectrum 
+softening positively affects the density coefficient ($\alpha_{\rho,F}$): 
+$+1.54$ $pcm/K$ and $-1.58$ $pcm/K$ at the startup and equilibrium for the 
+reactor-grade Pu case, respectively. More discussion about effects of fuel 
+salt composition in the \gls{FTC} can be found elsewhere 
+\cite{li_effects_2018-1}.
 
@@
 SD-TMSR concept.
-
-\subsection{Six factor analysis}
-The effective multiplication factor can be expressed as follows:
-\begin{align}
-k_{eff} &= \eta f p \epsilon P_f P_t
-\intertext{where}
-\eta     &= \mbox{neutron reproduction factor} \nonumber \\
-f        &= \mbox{thermal utilization factor} \nonumber \\
-p        &= \mbox{resonance escape probability} \nonumber \\
-\epsilon &= \mbox{fast fission factor} \nonumber \\
-P_f      &= \mbox{fast non-leakage probability} \nonumber \\
-P_t      &= \mbox{thermal non-leakage probability.} \nonumber
-\end{align}
-
-Table~\ref{tab:six_factor} summarizes the six factor for 3 different initial 
-fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
-online reprocessing capabilities, six factor is calculated at the 
-beginning of the operation and after 30 years of operation. Neutron population 
-and number of active/inactive cycles were selected to obtain $k_{eff}$ 
-statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
-probabilities remain constant regardless of initial fissile material and 
-neutron spectrum shift during operation. The thermal utilization factor (f) 
-remains almost constant during operation for the $^{233}$U and TRU cases but 
-considerably declines for the Pu case due to significant neutron spectrum 
-softening.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{table} [ht!]
-	\caption{Six factor for the SD-TMSR model for 3 different initial 
-		fuel salt compositions at startup and equilibrium.}
-	\begin{tabularx}{\textwidth}{ X | X X  X X  X X | p{0.1\textwidth}} \hline
-		\multirow{3}{*}{Factor}  & \multicolumn{6}{c|}{Startup fissile 
-			material} & \multirow{3}{*}{$\pm\bar{\sigma}$} \\ 
-			\cline{2-7}
-		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
-		\multicolumn{2}{c|}{TRU} \\ \cline{2-7}
-		\space  & Initial & Equil & Initial & Equil & Initial & Equil & \space 
-		\\ \hline
-		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31&4.9E-4\\ 
-		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75&2.1E-4 \\
-		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15&4.6E-4 \\
-		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81&6.2E-4 \\
-		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99&1.7E-6 \\
-		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00&6.5E-11 \\ \hline
-	\end{tabularx}
-	\label{tab:six_factor}
-\end{table}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In contrast, the neutron reproduction factor ($\eta$), resonance escape 
-probability ($p$), and fast fission factor ($\epsilon$) differ notably between 
-the initial and equilibrium state for all three initial fissile materials.  
-$\epsilon$ is much larger at startup for the Pu and TRU cases because these 
-initial fissile materials provide a much harder neutron spectrum than 
-$^{233}$U, and $\epsilon$ grows throughout the core's lifetime. Conversely, 
-$p$ decreases during reactor operation. The neutron reproduction factor ($\eta$)  
-increases during reactor operation for the $^{233}$U as initial fuel due to 
-the accumulation of fissile plutonium isotopes, which produce more neutrons 
-per fission ($\nu$). The other two scenarios demonstrate opposite behavior: 
-plutonium isotopes with large $\nu$ are gradually substituted with $^{233}$U, 
-which has a lower $\nu$ \cite{sjostrand_cross_1960}. This six factors' 
-evolution agrees with previously determined evolution parameters for a similar 
-single-fluid double-zone \gls{MSBR} \cite{ashraf2019whole_core, 
-rykhlevskii2019modeling, park_whole_2015}.

### 2020-02-17 paper/revisions/review-responses.tex

@@
         \begin{solution}
-				Thank you for pointing it out. Figure 14 shows significant 
-				changes \textbf{during reactor operation} in the outer core 
-				zone for the Pu (green line) and almost no changes for the TRU 
-				(orange). In this paragraph, we comparing changes in the flux 
-				due to fuel salt depletion (initial vs equilibrium), but not 
-				with $r$ coordinate. However, we are agree that thermal flux 
+				Thank you for pointing it out. In this paragraph, we comparing 
+				changes in the flux due to fuel salt depletion (initial vs 
+				equilibrium), but not with $r$ coordinate. Figure 14 shows 
+				significant changes \textbf{during reactor operation} in the 
+				outer core zone for the Pu (green line) and almost no changes 
+				for the TRU (orange). However, we are agree that thermal flux 
 				drop in the reflector is more dramatic for the TRU (initial 
-				and equilibrium compositions) an the Pu (equilibrium) cases 
+				and equilibrium compositions) and the Pu (equilibrium) cases 
 				than for the U-233 case. We think it happens because of 
@@
 				Notably, the neutron flux change for both the fast and thermal 
-				energies is 
-				much larger for the reactor-grade Pu case than for TRU case 
-				(Figures~15 and 16). The 
-				reason is the 
-				much softer neutron spectrum for the TRU initial loading 
-				compared with the 
-				reactor-grade Pu as shown in 
-				Figure~14: peak thermal 
-				neutron flux is about 4 times larger for the TRU case. The 
-				neutron spectrum in 
-				the SD-TMSR core initially loaded by TRU is much softer than 
-				the reactor-grade 
-				Pu case and even than the U-233 case because $^{232}$Th 
-				inventory is the 
-				lowest for the TRU case: 54.4t instead of 67.5t  and 76.9t for 
-				the  
-				reactor-grade Pu and U-233 cases, respectively 
-				(Table~5). 
-				$^{232}$Th greatly affects the neutron energy spectrum due to 
-				its large 
+				energies is much larger for the reactor-grade Pu case than for 
+				TRU case (Figures~15 and 16). The reason is the much softer 
+				neutron spectrum for the TRU initial loading compared with the 
+				reactor-grade Pu as shown in Figure~14: peak thermal neutron 
+				flux is about 4 times larger for the TRU case. The neutron 
+				spectrum in the SD-TMSR core initially loaded by TRU is much 
+				softer than the reactor-grade Pu case and even than the U-233 
+				case because $^{232}$Th inventory is the lowest for the TRU 
+				case: 54.4t instead of 67.5t and 76.9t for the reactor-grade  
+				Pu and U-233 cases, respectively (Table~5). $^{232}$Th greatly 
+				affects the neutron energy spectrum due to its large 
 				absorption cross section in the thermal energy range and 
-				resonance region 
-				between $10^{-5}$ and $10^{-3}$. Finally, when the TRU and the 
-				reactor-grade 
-				Pu cases reached equilibrium fuel salt composition ($\approx 
-				30$ years after 
+				resonance region between $10^{-5}$ and $10^{-3}$. Finally, 
+				when the TRU and the reactor-grade Pu cases reached 
+				equilibrium fuel salt composition ($\approx 30$ years after 
 				startup), the radial fast and thermal neutron flux 
-				distribution became similar 
-				in both shape and magnitude.
+				distribution became similar in both shape and magnitude.
 
 				More changes in thermal neutron flux shape and magnitude 
-				during the reactor 
-				operation for the $^{233}$U case are observed in the inner 
-				core zone 
-				($R\lesssim150$) than in the outer core zone. In the outer 
-				core zone, 
-				significant changes during reactor operation are observed for 
-				the thermal 
+				during the reactor operation for the $^{233}$U case are 
+				observed in the inner core zone ($R\lesssim150$) than in the 
+				outer core zone. In the outer core zone, significant changes 
+				during reactor operation are observed for the thermal 
 				neutron flux for the reactor-grade Pu case. In contrast, for 
-				the TRU case, it 
-				is almost negligible. Additionally, 
-				Figure~16 shows 
-				relatively significant changes in thermal flux leakage from 
-				the core for the 
-				Pu (equilibrium composition) and TRU (initial and equilibrium 
-				composition) 
-				cases. The SD-TMSR core design was optimized for $^{233}$U  
+				the TRU case, it is almost negligible. Additionally, 
+				Figure~16 shows relatively significant changes in thermal flux 
+				leakage from the core for the Pu (equilibrium composition) and 
+				TRU (initial and equilibrium composition) cases. The SD-TMSR 
+				core design was optimized for $^{233}$U  				
 				\cite{li_optimization_2018}; thus, the core geometry (e.g., 
-				channels lattice 
-				pitch) must be re-optimized for another type of fuel to obtain 
-				better 
-				neutronics performance.
+				channels lattice pitch) must be re-optimized for another type 
+				of fuel to obtain better neutronics performance.
         \end{solution}
@@
 	            The \gls{FTC} is a combination of the Doppler effect 
-	            coefficient 
-	            ($\alpha_{D,F}$) and density coefficient ($\alpha_{\rho,F}$) 
-	            and significantly 
-	            affected by the neutron spectrum. Li \emph{et al.} reported 
-	            that 
+	            coefficient ($\alpha_{D,F}$) and density coefficient 
+	            ($\alpha_{\rho,F}$) and significantly affected by the neutron 
+	            spectrum. Li \emph{et al.} reported that 	            
 	            $\alpha_{D,F}$ in thermal \gls{MSR} is always negative and 
-	            increases by 
-	            magnitude when spectrum hardening (see Table~8, first raw). 
-	            In contrast, $\alpha_{\rho,F}$ is a combination of 
-	            moderator-to-fuel volume 
-	            ratio, absorption cross section of heavy metal, and the core 
-	            leakage. When the 
-	            fuel salt temperature increases, the salt becomes less dense, 
-	            causing a 
-	            reduction in the fuel concentration and the neutron spectrum 
-	            become softer. 
-	            Such spectrum softening is leading to a rise in macroscopic 
-	            absorption cross 
-	            section of the fissile isotopes. Moreover, the spectrum 
-	            softening may leads to 
+	            increases by magnitude when spectrum hardening (see Table~8, 
+	            first raw). In contrast, $\alpha_{\rho,F}$ is a combination of 
+	            moderator-to-fuel volume ratio, absorption cross section of 
+	            heavy metal, and the core leakage. When the fuel salt 
+	            temperature increases, the salt becomes less dense, 
+	            causing a reduction in the fuel concentration and the neutron 
+	            spectrum become softer. Such spectrum softening is leading to 
+	            a rise in macroscopic absorption cross section of the fissile 
+	            isotopes. Moreover, the spectrum softening may leads to 
 	            a larger fast fission reaction rate \cite{li_effects_2018-1}. 
-	            Thus, spectrum 
-	            softening positively affects the density coefficient 
-	            ($\alpha_{\rho,F}$): 
-	            $+1.54$ $pcm/K$ and $-1.58$ $pcm/K$ at the startup and 
-	            equilibrium for the 
+	            Thus, spectrum softening positively affects the density 
+	            coefficient ($\alpha_{\rho,F}$): $+1.54$ $pcm/K$ and $-1.58$ 
+	            $pcm/K$ at the startup and equilibrium for the 
 	            reactor-grade Pu case, respectively. More discussion about 
-	            effects of fuel 
-	            salt composition in the \gls{FTC} can be found elsewhere 
+	            effects of fuel salt composition in the \gls{FTC} can be found 
+	            elsewhere 
 	            \cite{li_effects_2018-1}.

### 2020-02-17 paper/revisions/review-responses.tex
minor changes + references to figures and tables

@@
 This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle.
-Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor operation.
+Figure~4 shows the variation in fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor operation.
 For TRU and reactor-grade Pu, the fissile plutonium isotopes are gradually depleted, during operating (the fissile material is dominated by Pu in these cases).
@@
 
-                 Figure~\ref{fig:keff1} shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
+                 Figure~3 shows that the decrease in $k_{eff}$ for reactor-grade Pu case occurs at the much later operating time than for other cases because the neutron spectrum in the reactor-grade Pu initial core is hardened; more $^{232}$Th is being converted to $^{233}$U.
 Nevertheless, this amount of the $^{233}$U is not enough to counteract the neutron absorption in the non-fissile Pu isotopes after much of the $^{239}$Pu and $^{241}$Pu is depleted.
@@
 The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U.
-Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
+Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
 The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time.
@@
 This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years).
-For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~\ref{fig:keff2}).
+For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~5).
 
@@
                   The target is to maintain the core criticality for a long period of time without any external feed of $^{233}$U.
-Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
+Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
 The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time.
@@
 This produces $^{233}$U in the \texttt{Pa-decay tank} barely enough to operate the TRU-started SD-TMSR for a long period of time ($\approx$ 40 years).
-For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~\ref{fig:keff2}).
+For reactor-grade Pu case, the produced $^{233}$U is sufficient to maintain the core criticality within the 60-years of operation (see Figure~5).
         \end{solution}
@@
 
-                Figure~\ref{fig:U233CC} demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.
+                Figure~11 demonstrates the mass of $^{233}$U in the fuel salt for the $^{233}$U, reactor-grade Pu, and TRU cases.
 For $^{233}$U case, the mass of $^{233}$U increases with operating time and reaches $\approx$ $1.7$ $t$ at the EOL.
@@
                  The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U.
-$^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b).
-Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
+$^{232}$Th has a very high absorption cross section in the thermal region ($\approx$ $10^2$ b).
+Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~14).
 
@@
 				changes in the flux due to fuel salt depletion (initial vs 
-				equilibrium), but not with $r$ coordinate. Figure 14 shows 
+				equilibrium), but not with $r$ coordinate. Figure 15 shows 
 				significant changes \textbf{during reactor operation} in the 
@@
 				loading.
-				The following paragraphs has been added to the manuscript for 
+
+				The following paragraphs have been added to the manuscript for 
 				clarify this point:\\
@@
 				case because $^{232}$Th inventory is the lowest for the TRU 
-				case: 54.4t instead of 67.5t and 76.9t for the reactor-grade  
+				case: $54.4$ $t$ instead of $67.5$ $t$ and $76.9$ $t$ for the reactor-grade  
 				Pu and U-233 cases, respectively (Table~5). $^{232}$Th greatly 
@@
                 ($\alpha_{\rho,F}$), which is usually positive in thermal MSRs 
-                (e.g., $+1.09pcm/K$ for the \gls{MSBR}           
+                (e.g., $+ 1.09 pcm/K$ for the \gls{MSBR}           
                 \cite{robertson_conceptual_1971}) and \textbf{softer} neutron 
@@
             https://doi.org/10.1007/s41365-018-0458-1.
-	            The following paragraphs has been added to the manuscript:\\
+
+	            The following paragraphs have been added to the manuscript:\\
 

### 2020-02-17 paper/methods.tex
minor changes + references to figures and tables

@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{|X |X |X| X| X|}
+	\begin{tabularx}{\textwidth}{X X X X X}
 		\hline
@@
 		\hline
-		 1.3 &60.3&24.3&9.1&5 \\
+		$ $ $ $ $ $ $ $ $ $1.3 &$ $ $ $ $ $60.3&$ $ $ $ $ $24.3&$ $ $ $ $ $ $ $ $ $9.1&$ $ $ $ $ $ $ $ $ $ $ $ $ $5 \\
 		\hline
@@
 	\vspace{0.1in}
-	\begin{tabularx}{\textwidth}{|X| X| X| X| X| X| X| X| X| X|}
+	\begin{tabularx}{\textwidth}{X X X X X X X X X X}
 		\hline
@@
 		\hline
-		6.3&2.7&45.9&21.5&10.7&6.7&3.4&1.9&0.8&0.1 \\
+		$ $ $ $ $ $ $ $ $ $6.3&$ $ $ $ $ $ $ $ $ $2.7& $ $ $ $ $ $45.9& $ $ $ $ $ $21.5& $ $ $ $ $ $10.7&$ $ $ $ $ $ $ $ $ $6.7&$ $ $ $ $ $ $ $ $ $3.4&$ $ $ $ $ $ $ $ $ $1.9&$ $ $ $ $ $ $ $ $ $$ $0.8&$ $ $ $ $ $ $ $ $ $0.1 \\
 		\hline
@@
 		$^{241}$Am		 &         &&& 8.53E+02 & \\
-		$^{242}$Am		 &         &&&  &\\
 		$^{243}$Am       &        & &&4.77E+02&\\

### 2020-02-24 paper/conclusion.tex
minor changes

@@
 
-We compared the operational and safety parameters of the \gls{SD-TMSR} for the 
+We compared the operational and safety parameters of the SD-TMSR for the 
 three promising startup fuels at both initial and equilibrium states. The total 
@@
 evolved from $-6.54\pm0.16$ $pcm/K$ to $-4.79\pm0.12$ during 
-60 years of operation. Finally, the six factor evolution during the operation 
-was calculated for all three cases, providing a basis for designing the reactivity control system of the \gls{SD-TMSR}.
+60 years of operation.
 
@@
 \cite{lindsay_introduction_2018} will be performed. The full-core SERPENT-2 
-model of the \gls{SD-TMSR} and equilibrium fuel salt compositions, obtained in 
+model of the SD-TMSR and equilibrium fuel salt compositions, obtained in 
 this work, will be employed to generate problem-oriented nuclear data 

### 2020-02-24 paper/introduction.tex
minor changes

@@
 
-Cui \emph{et al.} (2017-2018) analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
+Cui \emph{et al.} analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
 Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.
@@
 
-In more detail, in current work, the radii of the fuel channels in the outer and inner zone are 5 and 3.5 cm, respectively, while in Cui \emph{et al.} work, all fuel channels have the same radius 2.03 cm, also, the side length of the graphite hexagonal prism is different in both models (7.5 instead of 10 cm in Cui model), total salt volume, density, and composition are different than those used in our study.
+Comparing with Cui \emph{et al.}, we used different geometry, volumes, densities, and fuel salt compositions.
 In Cui's scenarios, the amount of Th is kept constant.

### 2020-02-24 paper/methods.tex
minor changes

@@
 \subsection{Geometry}
-The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) design model was introduced by the Chinese Academy of Sciences as a part of  
+The SD-TMSR design model was introduced by the Chinese Academy of Sciences as a part of  
 the strategic project ``Thorium-based Molten-Salt Reactor(TMSR) nuclear energy system" 
 \cite{jiang2012advanced,li2015analysis,li_optimization_2018}. The 
-design of the \gls{SD-TMSR} is inspired by the \gls{MSBR} 
+design of the SD-TMSR is inspired by the \gls{MSBR} 
 \cite{robertson_conceptual_1971} after modifying the geometry to 
 control the positive moderator temperature coefficient in the MSBR. Li \emph{et al.} and Ashraf \emph{et al.} 
-described the \gls{SD-TMSR} core 
+described the SD-TMSR core 
 geometry in \cite{li_optimization_2018,ashraf2019whole_core}. 
 Figure~\ref{fig:ff} illustrates the quarter-core view of the 
-\gls{SD-TMSR}.
+SD-TMSR.
 The active zone is a right cylinder with height and diameter 
@@
 maximize flux in the core. B${_4}$C cylinder surrounds the reflectors and 
-acts as radiation shielding. The \gls{SD-TMSR} pressure vessel is made of a Ni-based (hastelloy N) alloy holds 
+acts as radiation shielding. The SD-TMSR pressure vessel is made of a Ni-based (hastelloy N) alloy holds 
 the fuel salt, graphite elements, reflector, shielding, and intermediate heat exchanger. The main 
-characteristics of the \gls{SD-TMSR} are listed in Table~\ref{tab:table1}.
+characteristics of the SD-TMSR are listed in Table~\ref{tab:table1}.
 
@@
 The aim of this paper is to simulate the  
-operation of the \gls{SD-TMSR} for 60 years with various startup fissile 
+operation of the SD-TMSR for 60 years with various startup fissile 
 compositions and without any external feed of fissile $^{233}$U which we 
@@
 To determine the appropriate depletion step size, we conducted a time step refinement study.
-We started with $\Delta t=30$days and gradually increased the depletion time step until the error in K$_{eff}$ became significant.
-For $\Delta t=1$year the maximum change in K$_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.
+We started with $\Delta t=30$ days and gradually increased the depletion time step until the error in K$_{eff}$ became significant.
+The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.
 The full burnup time of 
@@
 Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.
+But we did not consider processes, such as decay, which occurs outside of the core.
+Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in \cite{zhang2018review}.
 
-The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.
-We used depletion mode 1 in Serpent-2 (i.e.
-burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.
+The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump.
+We used the depletion mode 1 in SERPENT-2 (i.e.
+burn 1), which means that the fuel material is treated as a single depletion zone.
 

### 2020-02-25 paper/revisions/review-responses.tex

@@
 
-        		  About depletion regions definition: we used depletion mode 1 in SERPENT-2 (i.e.
-burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.
-The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.
+        		  About depletion regions definition: we used the depletion mode 1 in SERPENT-2 (i.e. burn 1), which means that the fuel material
+        		  is treated as a single depletion zone. The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump.
 
@@
 We started our calculations by 30 days' time step but we do not find significant changes in $k_{eff}$ when we increased the time step to 365 days.
-The maximum change in $k_{eff}$ was $\leq$ 0.02\%), therefore we adopted 365-day as a time step for all simulation in this work.
+The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.
 
@@
 
-        		  The fuel is liquid -it well- mixed all the time due to turbulent flow and mixing in the pump.
-We used depletion mode 1 in SERPENT-2 (i.e.
-burn 1), this means that the fuel material is not divided and all occurrences of it are treated as a single depletion zone.
+        		  The liquid fuel is well-mixed all the time due to turbulent flow and mixing in the pump.
+We used the depletion mode 1 in SERPENT-2 (i.e.
+burn 1), which means that the fuel material is treated as a single depletion zone.
 
@@
 To determine the appropriate depletion step size, we conducted a time step refinement study.
-We started with $\Delta t=30$days and gradually increased the depletion time step until the error in $k_{eff}$ became significant.
-For $\Delta t=1$year the maximum change in $k_{eff}$ was $\leq$ 0.02\%), therefore we adopted a constant, 365-day-long time step for all simulation in this work.
+We started with $\Delta t=30$ days and gradually increased the depletion time step until the error in $k_{eff}$ became significant.
+The difference in $k_{eff}$ between $\Delta t=1$ year and $\Delta t=30$ days was $\leq$ 0.02\%; thus, we adopted a constant, 365-day-long time step for all simulation in this work.
 
@@
 		          because fission takes place only in the core region.
+But we did not consider processes, such as decay, which occurs outside of the core.
+Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in Zhang et al.
+(2018) \cite{zhang2018review}.
+
 		          We changed the paragraph as follows:\\
@@
 Moreover, we accordingly adjusted power density in SERPENT burnup calculations because fission takes place only in the core region.
+But we did not consider processes, such as decay, which occurs outside of the core.
+Also, the drift of the delayed neutron precursors is not examined in this paper, but discussion about this can be found in \cite{zhang2018review}.
         \end{solution}
@@
         \begin{solution}
-                Thank you for your helpful review. The state "For the SD-TMSR 
+                Thank you for your helpful review. The statement "For the SD-TMSR 
                 concept, simulating the fissile core startup and fuel cycle 
@@
                 not studied before" in page 3, has been removed. 
-                The following paragraphs have been added to the manuscript.\\
+                The following paragraphs have been added to the manuscript:\\
 
-                Cui \emph{et al.} (2017-2018) analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
+                Cui \emph{et al.} analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
 Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.
-
 The research effort described in \cite{cui2017transition} and
@@
 
-                In more detail, in current work, the radii of the fuel channels in the outer and inner zone are 5 and 3.5 cm, respectively, while in Cui \emph{et al.} work, all fuel channels have the same radius 2.03 cm, also, the side length of the graphite hexagonal prism is different in both models (7.5 instead of 10 cm in Cui model), total salt volume, density, and composition are different than those used in our study.
+                Comparing with Cui \emph{et al.}, we used different geometry, volumes, densities, and fuel salt compositions.
 In Cui's scenarios, the amount of Th is kept constant.
@@
                Pu, or TRU) must be equal to the mass of extracted FPs.
-               Moreover, we rewrite the paragraph in page 11 to address this 
-               thought:\\
+               We rewrite the paragraph on page 11 to clarify this point:\\
 
@@
                  in Figure 3 have been described in the manuscript.
-                 The following paragraph has been added to the manuscript.\\
+                 The following paragraph and additional Figure~4 has been added to the manuscript:\\
 
@@
 For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases.
-The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
-
-                 The following paragraph has been added to the manuscript.\\
+The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.\\
 
@@
 Figure~8 shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
-The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time.
-Also, a relatively large amount of $^{233}$U can be obtained when we applied RP = $30$ $s$ against $10.59$ $d$.
+The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime.
+Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$.
 The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup.
@@
 
-                  The following paragraph has been added to the manuscript.\\
+                  The following paragraph and additional Figure~8 has been added to the manuscript:\\
 
@@
                 Thank you for the excellent point. The statement has been removed from the text.
-                Moreover, we rewrite the paragraph to address this thought:\\
+                Moreover, we rewrite the paragraph to clarify this point:\\
 
@@
 The neutron spectrum shift during operating affects the inventory of $^{233}$U in the fuel salt.
-Hard neutron spectrum converts more $^{233}$U from $^{232}$Th.
+Harder neutron spectrum enhance $^{233}$U breeding from $^{232}$Th.
 For the reactor-grade Pu and TRU cases, during operating, the fissile Pu is depleted and the $^{233}$U becomes the major fissile isotope; the neutron spectrum softens (low conversation of $^{233}$U from $^{232}$Th).
@@
                  This has now been clarified in the text.
-                 We rewrite the paragraph to address this thought:\\
+                 We rewrite the paragraph to clarify this point:\\
 
@@
                 ($\alpha_{\rho,F}$), which is usually positive in thermal MSRs 
-                (e.g., $+ 1.09 pcm/K$ for the \gls{MSBR}           
+                (e.g., $+1.09$ $pcm/K$ for the \gls{MSBR}           
                 \cite{robertson_conceptual_1971}) and \textbf{softer} neutron 

### 2020-02-25 paper/results.tex
Osama comments addressed

@@
 Figure~\ref{fig:Keff_U2332} shows how Reprocessing Period (RP) affects the $k_{eff}$ and amount of $^{233}$U in the \texttt{Pa-decay tank} for the TRU-started SD-TMSR.
-The fast extraction of Pa from the core (RP = $30$ $s$) leads to long operating time.
-Also, a relatively large amount of $^{233}$U can be obtained when we applied RP = $30$ $s$ against $10.59$ $d$.
+The faster extraction of Pa from the core (RP = $30$ $s$) is required to achieve suitable core lifetime.
+Also, the greater production of $^{233}$U can be obtained with RP = $30$ $s$ instead of $10.59$ $d$.
 The RP equal to $10.59$ $d$ is not suitable for TRU and reactor-grade Pu cases because additional $^{233}$U was required to supply the core after startup.
@@
 The neutron spectrum of TRU case at BOL is softer than $^{233}$U case because $^{232}$Th inventory is much lower for the TRU case: $54.4$ $t$ instead of $76.9$ $t$ for the $^{233}$U.
-$^{232}$Th has a very high absorption cross section in the thermal region ($\approx10^2 $b).
+$^{232}$Th has a very high absorption cross section in the thermal region ($\approx$ $10^2$ b).
 Moreover, $^{232}$Th has resonance region between $10^{-5}$ and $10^{-3}$ which justify relatively low energy of neutrons for the TRU case in this energy range (see Figure~\ref{fig:spectrumFLUX110vC}).
@@
 Pu case and even than the U-233 case because $^{232}$Th inventory is the 
-lowest for the TRU case: 54.4t instead of 67.5t  and 76.9t for the  
+lowest for the TRU case: $54.4$ $t$ instead of $67.5$ $t$ and $76.9$ $t$ for the  
 reactor-grade Pu and U-233 cases, respectively (Table~\ref{tab:table5}). 

### 2020-02-25 paper/revisions/review-responses.tex
Edits after meeting with Huff

@@
         \begin{solution}
-                 Thank you for catching this. The whole statement has been 
+                 Thank you for catching this. Just small correction: this ORNL 
+                 concept was called \emph{Molten Salt Breeder Reactor (MSBR)}. 
+                 The whole statement has been 
                  modified to read:\\
@@
                  The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
-                 MW$_{th}$ was proposed for the first time by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.
+                 MW$_{th}$ was proposed for the first time by ORNL as early as 
+                 in the 1960s, which was called Molten Salt Breeder Reactor 
+                 (MSBR) \cite{robertson_conceptual_1971}.
 
@@
 
-                Cui \emph{et al.} analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
-Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.
                 The research effort described in \cite{cui2017transition} and
                 \cite{cui2018possible} is most similar to the work
-                presented in this paper. However, a few major differences
-                are: (1) we used built-in truly continuous fuel depletion capabilities in
-                SERPENT-2 \cite{aufiero2013extended} while Cui \emph{et al.} employed an in-house tool named MSR
-                Reprocessing Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE and employs a batch-wise approach (the burnup simulation stops at a given time and restarts with a new liquid fuel composition after removal of discarded materials and addition of fissile/fertile materials); (2) we investigated different initial loading cases (HALEU, Pu+HALEU, reactor-grade Pu, TRU and $^{233}$U) while Cui \emph{et al.} studied only uranium and Pu as the startup fissile materials; (3) we adopted the SD-TMSR core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which is different from the MSBR-like model adopted by Cui \emph{et al.}; (4) Cui \emph{et al.} studied the high-enriched uranium (e$>$90) while we excluded it due to the unavailability of this material for use as an initial reactor fuel (non-proliferation issues) and because the performance of this material is expected to be similar to $^{233}$U; (5) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle transition: a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario while we adopting different approach by introducing two different feed mechanisms: thorium and non-thorium feed mechanism.
+                presented in this paper. Cui \emph{et al.} analyzed the fuel 
+                transition from 
+                enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the 
+                MSBR-like design. Cui 
+                \emph{et al.} found that the fuel transition can be achieved 
+                by using: (1) 
+                enriched uranium with greater than 40\% enrichment 
+                \cite{cui2018possible}; (2) 
+                Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel 
+                \cite{cui2017transition, 
+                	cui2018possible}.
 
-                Comparing with Cui \emph{et al.}, we used different geometry, volumes, densities, and fuel salt compositions.
-In Cui's scenarios, the amount of Th is kept constant.
-$^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality.
-In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor.
-Thus, the criticality of the core is maintained by refueling external fissile material.
-                In current work, using the thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the \texttt{Pa-decay tank} into the core.
-The excess $^{233}$U (if exist) is stored outside the core.
-In the non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the \texttt{Pa-decay tank}.
-Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm$_{total fuel}$ $\leq$ 0.1\%).
-In the non-thorium feed mechanism, the amount of Th decreases during reactor operation while it is constant in the thorium feed mechanism.
+                However, a few major differences follow: 
+                (1) Cui \emph{et al.} employed an in-house tool named MSR 
+                Reprocessing 
+                Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE 
+                and employs a 
+                batch-wise approach while we used built-in truly continuous 
+                fuel depletion 
+                capabilities in SERPENT-2 \cite{aufiero2013extended}; 
+                (2) Cui \emph{et al.} studied a high-enriched uranium ($>$40\% 
+                of $^{235}$U) 
+                and plutonium partitioned from light water reactors spent fuel 
+                as the startup 
+                fissile materials while we considered different loading cases: 
+                HALEU, Pu 
+                mixed with HALEU, reactor-grade plutonium, TRU and $^{233}$U;
+                (3) we adopted the SD-TMSR core geometry optimized by Li 
+                \emph{et al.} 
+                \cite{li_optimization_2018} which is different from the 
+                MSBR-like geometry by 
+                Mathieu \emph{et al.} \cite{mathieu_possible_2009} adopted by 
+                Cui \emph{et 
+                	al.}; 
+                (4) Cui \emph{et al.} introduced two scenarios for thorium 
+                fuel cycle 
+                transition: a Breeding and Burning (B\&B) scenario and a 
+                Pre-breeding scenario 
+                while we adopting different approach by introducing two 
+                different feed 
+                mechanisms: thorium and non-thorium.
+
+                Comparing with Cui \emph{et al.}, we used different reactor 
+                design (geometry, 
+                volumes, densities, fuel salt compositions) and computation 
+                method (continuous 
+                online reprocessing instead of batch-wise approach). In Cui's 
+                scenarios, the 
+                amount of thorium is kept constant. $^{233}$U is fed only in 
+                (B\&B) scenario 
+                and extra fissile materials would have to be added into the 
+                core if the 
+                produced $^{233}$U is not enough to maintain the reactor 
+                criticality. In the 
+                Pre-breeding scenario, all the $^{233}$U produced from the 
+                decay of the 
+                extracted $^{233}$Pa stored outside the core until it reaches 
+                the required 
+                startup mass for a new reactor. Thus, the criticality of the 
+                core is 
+                maintained by refueling external fissile material. In the 
+                current work, using 
+                the thorium feed mechanism, we simultaneously feed thorium and 
+                all or fraction 
+                of produced $^{233}$U from the \texttt{Pa-decay tank} into the 
+                core. The 
+                excess $^{233}$U (if exists) is stored outside the core. In 
+                the non-thorium 
+                feed mechanism, we continuously inject external heavy metals 
+                (HALEU, Pu mixed 
+                with HALEU, reactor-grade Pu, or TRU) and fraction of produced 
+                $^{233}$U from 
+                the \texttt{Pa-decay tank}. For the non-thorium mechanism, we 
+                feed a part of 
+                produced $^{233}$U because in some cases (e.g., TRU) refueling 
+                only external 
+                heavy metals failed to maintain the core criticality 
+                (limitation is 
+                dm$_{salt}$ $\leq$ 0.1\%).
 
@@
                fuel mass almost constant, for \textbf{thorium feed mechanism}, 
-               the mass of injected Th must be equal to the mass of extracted 
-               FPs and for \textbf{non-thorium feed mechanism}, the mass of 
-               injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade 
-               Pu, or TRU) must be equal to the mass of extracted FPs.
-               We rewrite the paragraph on page 11 to clarify this point:\\
+               the mass of injected thorium must be equal to the mass of 
+               extracted FPs and for \textbf{non-thorium feed mechanism}, the 
+               mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, 
+               reactor-grade Pu, or TRU) must be equal to the mass of 
+               extracted FPs. We rewrite the paragraph on page 11 to clarify 
+               this point:\\
 
@@
                	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
-               	\subitem 3a.
-\textbf{Thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
+               	\subitem 3a. \textbf{Thorium feed mechanism}: mass of injected 
+               	$^{233}$U $\approx$ mass of extracted Pa and mass of injected 
+               	$^{232}$Th $\approx$ mass of extracted FPs to maintain the 
+               	total fuel mass constant.
                	\subitem 3b.
@@
                \end{enumerate}
-               In both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d).
-To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.
+               In both feed mechanisms (thorium and non-thorium) we 
+               continuously added $^{233}$U and the mass of injected $^{233}$U 
+               is equal to the mass of extracted Pa ($^{233}$Pa decays to 
+               $^{233}$U after $\approx$ 27 d). To keep the total fuel mass 
+               almost constant, for \textbf{thorium feed mechanism}, the mass 
+               of injected thorium must be equal to the mass of extracted FPs 
+               and for \textbf{non-thorium feed mechanism}, the mass of 
+               injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade 
+               Pu, or TRU) must be equal to the mass of extracted FPs.
 
@@
 
-                 For Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
-This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle.
-Figure~4 shows the variation in fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor operation.
-For TRU and reactor-grade Pu, the fissile plutonium isotopes are gradually depleted, during operating (the fissile material is dominated by Pu in these cases).
-For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium.
-Therefore, the mass of fissile plutonium increases during operating but its value still relatively low.
-For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases.
-The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.\\
+                 For the Pu+HALEU case, $k_{eff}$ firstly increases during the 
+                 first $\approx$ $3$ EFPY and then gradually decreases. This 
+                 is due to the conversion of $^{238}$U from HALEU into fissile 
+                 plutonium, which often produces the majority of the neutrons 
+                 until the transition to Th/$^{233}$U fuel cycle. Figure~4 
+                 shows the variation in fissile plutonium isotopes ($^{239}$Pu 
+                 , $^{241}$Pu, and $^{243}$Pu) inventory during reactor 
+                 operation. For TRU and reactor-grade Pu, the fissile 
+                 plutonium isotopes are gradually depleted, during operating 
+                 (the fissile material is dominated by Pu in these cases). For 
+                 the HALEU case, the fissile material is dominated by 
+                 $^{235}$U, 
+                 however, $^{238}$U is converted into fissile plutonium. 
+                 Therefore, the mass of fissile plutonium increases during 
+                 operating but its value still relatively low. For the 
+                 Pu+HALEU case, the mass of the fissile plutonium isotopes 
+                 increases 
+                 within the first $\approx$ $3$ EFPY and then decreases. The 
+                 reactivity from the produced Pu is much greater than the 
+                 depletion of the initial reactivity (due to the depletion of 
+                 initial fissile isotopes), consequently, $k_{eff}$ increases 
+                 during the first $\approx$ $3$ years and then decreases; the 
+                 amount of $^{233}$U generated in the Pu+HALEU case is 
+                 insufficient to maintain the reactor criticality and 
+                 counteract neutron absorption in non-fissile isotopes.\\
 
@@
         \begin{solution}
-				Thank you for pointing it out. In this paragraph, we comparing 
-				changes in the flux due to fuel salt depletion (initial vs 
-				equilibrium), but not with $r$ coordinate. Figure 15 shows 
+				Thank you for pointing it out. 
+				At the EOL the fuel salt composition is more or less the same 
+				(``equilibrium'' composition), hence, both fast and thermal 
+				fluxes looks very similar for plutonium and TRU cases.
+				At the BOL, this difference is caused by different $^{232}$Th 
+				inventory at BOL for Pu reactor-grade (67.5t) and TRU (54.4t). 
+				 $^{232}$Th is a strong absorber in the thermal and 
+				 intermediate energy range, so, it causes such a significant  
+				 difference in the flux: reactor-grade Pu composition provides 
+				 much harder spectrum (see Figure~14) at BOL.
+
+                Figure 15 shows 
 				significant changes \textbf{during reactor operation} in the 
@@
 				The following paragraphs have been added to the manuscript for 
-				clarify this point:\\
+				clarification:\\
 
@@
 				neutron flux for the reactor-grade Pu case. In contrast, for 
-				the TRU case, it is almost negligible. Additionally, 
+				the TRU case, thermal neutron flux change in the outer core 
+				zone  is almost negligible. Additionally, 
 				Figure~16 shows relatively significant changes in thermal flux 
@@
 				\cite{li_optimization_2018}; thus, the core geometry (e.g., 
-				channels lattice pitch) must be re-optimized for another type 
+				channel lattice pitch) must be re-optimized for another type 
 				of fuel to obtain better neutronics performance.

### 2020-02-25 paper/results.tex
Edits after meeting with Huff

--- 2020-02-17 paper/results.tex
@@
 Notably, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
-more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)).
+more. Consequently, the initial $k_{eff}$ for these cases increased (see 
+Figure~\ref{fig:keff1} for HALEU and reactor-grade Pu cases).
 For the HALEU fuel salt, the amount of $^{233}$U generated in the SD-TMSR after a few years is insufficient to counteract the absorption of the (non-fissile) $^{238}$U added at start-up after much of the original $^{235}$U is depleted.
@@
 
-For Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ $3$ EFPY and then gradually decreases.
-This is due to the conversion of $^{238}$U from HALEU into fissile plutonium, which often produces the majority of the neutrons until the transition to Th/$^{233}$U fuel cycle.
-Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor operation.
-For TRU and reactor-grade Pu, the fissile plutonium isotopes are gradually depleted, during operating (the fissile material is dominated by Pu in these cases).
-For HALEU case, the fissile material is dominated by $^{235}$U, however, $^{238}$U is converted into fissile plutonium.
-Therefore, the mass of fissile plutonium increases during operating but its value still relatively low.
-For Pu+HALEU case, the mass of the fissile plutonium isotopes increases within the first $\approx$ $3$ EFPY and then decreases.
-The reactivity from the produced Pu is much greater than the depletion of the initial reactivity (due to the depletion of initial fissile isotopes), consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is insufficient to maintain the reactor criticality and counteract neutron absorption in non-fissile isotopes.
+For the Pu+HALEU case, $k_{eff}$ firstly increases during the first $\approx$ 
+$3$ EFPY and then gradually decreases. This is due to the conversion of 
+$^{238}$U from HALEU into fissile plutonium, which often produces the majority 
+of the neutrons until the transition to Th/$^{233}$U fuel cycle. 
+Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium 
+isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor 
+operation. For TRU and reactor-grade Pu, the fissile plutonium isotopes are 
+gradually depleted, during operating (the fissile material is dominated by Pu 
+in these cases). For the HALEU case, the fissile material is dominated by 
+$^{235}$U, however, $^{238}$U is converted into fissile plutonium. Therefore, 
+the mass of fissile plutonium increases during operating but its value still 
+relatively low. For the Pu+HALEU case, the mass of the fissile plutonium 
+isotopes 
+increases within the first $\approx$ $3$ EFPY and then decreases. The 
+reactivity from the produced Pu is much greater than the depletion of the 
+initial reactivity (due to the depletion of initial fissile isotopes), 
+consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and 
+then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is 
+insufficient to maintain the reactor criticality and counteract neutron 
+absorption in non-fissile isotopes.
 
@@
 significant changes during reactor operation are observed for the thermal 
-neutron flux for the reactor-grade Pu case. In contrast, for the TRU case, it 
-is almost negligible. Additionally, Figure~\ref{fig:thermal_flux} shows 
+neutron flux for the reactor-grade Pu case. In contrast, for the TRU case, 
+thermal neutron flux change in the outer core zone is almost negligible. 
+Additionally, Figure~\ref{fig:thermal_flux} shows 
 relatively significant changes in thermal flux leakage from the core for the 
@@
 cases. The SD-TMSR core design was optimized for $^{233}$U  
-\cite{li_optimization_2018}; thus, the core geometry (e.g., channels lattice 
+\cite{li_optimization_2018}; thus, the core geometry (e.g., channel lattice 
 pitch) must be re-optimized for another type of fuel to obtain better 

### 2020-02-25 paper/results.tex
Addressing Osama's comments

@@
 cases. The SD-TMSR core design was optimized for $^{233}$U  
-\cite{li_optimization_2018}; thus, the core geometry (e.g., channel lattice 
+\cite{li_optimization_2018}; thus, the core geometry (e.g., the channel lattice 
 pitch) must be re-optimized for another type of fuel to obtain better 

### 2020-02-25 paper/results.tex
Addressing Osama's comments

@@
 Pu case and even than the U-233 case because $^{232}$Th inventory is the 
-lowest for the TRU case: 54.4t instead of 67.5t and 76.9t for the  
+lowest for the TRU case: $54.4$ $t$ instead of $67.5$ $t$ and $76.9$ $t$ for the  
 reactor-grade Pu and U-233 cases, respectively (Table~\ref{tab:table5}). 

### 2020-02-25 paper/results.tex
Update paper/results.tex

@@
 initial reactivity (due to the depletion of initial fissile isotopes), 
-consequently, $k_{eff}$ increases during the first $\approx$ $3$ years and 
+consequently, $k_{eff}$ increases during the first $\approx$ $3$ EFPY and 
 then decreases; the amount of $^{233}$U generated in the Pu+HALEU case is 

### 2020-02-25 paper/introduction.tex

@@
 
-The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with a thermal power of 2,250
-MW$_{th}$ was proposed for the first time by ORNL as early as in the 1960s, which was called Molten salt breeding reactor (MSBR) \cite{robertson_conceptual_1971}.
+The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR) with 
+a thermal power of 2,250 MW$_{th}$ was proposed for the first time by ORNL as 
+early as in the 1960s, which was called Molten Salt Breeder Reactor (MSBR) 
+\cite{robertson_conceptual_1971}.
 The SD-TMSR is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U
@@
 
-Cui \emph{et al.} analyzed the fuel transition from enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design.
-Cui \emph{et al.} found that the fuel transition can be achieved by using: (1) enriched uranium with greater than 40\% enrichment, which rises the proliferation concerns; (2) Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition,cui2018possible}.
-
 The research effort described in \cite{cui2017transition} and
 \cite{cui2018possible} is most similar to the work
-presented in this paper. However, a few major differences
-are: (1) we used built-in truly continuous fuel depletion capabilities in
-SERPENT-2 \cite{aufiero2013extended} while Cui \emph{et al.} employed an in-house tool named MSR
-Reprocessing Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE and employs a batch-wise approach (the burnup simulation stops at a given time and restarts with a new liquid fuel composition after removal of discarded materials and addition of fissile/fertile materials); (2) we investigated different initial loading cases (HALEU, Pu+HALEU, reactor-grade Pu, TRU and $^{233}$U) while Cui \emph{et al.} studied only uranium and Pu as the startup fissile materials; (3) we adopted the SD-TMSR core geometry optimized by Li \emph{et al.} \cite{li_optimization_2018} which is different from the MSBR-like model adopted by Cui \emph{et al.}; (4) Cui \emph{et al.} studied the high-enriched uranium (e$>$90) while we excluded it due to the unavailability of this material for use as an initial reactor fuel (non-proliferation issues) and because the performance of this material is expected to be similar to $^{233}$U; (5) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle transition: a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario while we adopting different approach by introducing two different feed mechanisms: thorium and non-thorium feed mechanism.
+presented in this paper. Cui \emph{et al.} analyzed the fuel transition from 
+enriched $^{235}$U/Th and Pu/Th to $^{233}$U/Th for the MSBR-like design. Cui 
+\emph{et al.} found that the fuel transition can be achieved by using: (1) 
+enriched uranium with greater than 40\% enrichment \cite{cui2018possible}; (2) 
+Pu from LWR (burn-up of 60 GWd/t) spent nuclear fuel \cite{cui2017transition, 
+cui2018possible}.
 
-Comparing with Cui \emph{et al.}, we used different geometry, volumes, densities, and fuel salt compositions.
-In Cui's scenarios, the amount of Th is kept constant.
-$^{233}$U is fed only in (B\&B) scenario and extra fissile materials would have to be added into the core if the produced $^{233}$U is not enough to maintain the reactor criticality.
-In the Pre-breeding scenario, all the $^{233}$U produced from the decay of the extracted $^{233}$Pa stored outside the core until it reaches the required startup mass for a new reactor.
-Thus, the criticality of the core is maintained by refueling external fissile material.
-In current work, using the thorium feed mechanism, we simultaneously feed Th and all or part of produced $^{233}$U from the \texttt{Pa-decay tank} into the core.
-The excess $^{233}$U (if exist) is stored outside the core.
-In the non-thorium feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) and part of produced $^{233}$U from the \texttt{Pa-decay tank}.
-Here we feed a part of produced $^{233}$U because in some cases (e.g., TRU) refueling only external heavy metals failed to maintain the core criticality (limitation is dm$_{total fuel}$ $\leq$ 0.1\%).
-In the non-thorium feed mechanism, the amount of Th decreases during reactor operation while it is constant in the thorium feed mechanism.
+However, a few major differences follow: 
+(1) Cui \emph{et al.} employed an in-house tool named MSR Reprocessing 
+Sequence (MSR-RS) \cite{ZOU2015114} which couples with SCALE and employs a 
+batch-wise approach while we used built-in truly continuous fuel depletion 
+capabilities in SERPENT-2 \cite{aufiero2013extended}; 
+(2) Cui \emph{et al.} studied a high-enriched uranium ($>$40\% of $^{235}$U) 
+and plutonium partitioned from light water reactors spent fuel as the startup 
+fissile materials while we considered different loading cases: HALEU, Pu 
+mixed with HALEU, reactor-grade plutonium, TRU and $^{233}$U;
+(3) we adopted the SD-TMSR core geometry optimized by Li \emph{et al.} 
+\cite{li_optimization_2018} which is different from the MSBR-like geometry by 
+Mathieu \emph{et al.} \cite{mathieu_possible_2009} adopted by Cui \emph{et 
+al.}; 
+(4) Cui \emph{et al.} introduced two scenarios for thorium fuel cycle 
+transition: a Breeding and Burning (B\&B) scenario and a Pre-breeding scenario 
+while we adopting different approach by introducing two different feed 
+mechanisms: thorium and non-thorium.
+
+Comparing with Cui \emph{et al.}, we used different reactor design (geometry, 
+volumes, densities, fuel salt compositions) and computation method (continuous 
+online reprocessing instead of batch-wise approach). In Cui's scenarios, the 
+amount of thorium is kept constant. $^{233}$U is fed only in (B\&B) scenario 
+and extra fissile materials would have to be added into the core if the 
+produced $^{233}$U is not enough to maintain the reactor criticality. In the 
+Pre-breeding scenario, all the $^{233}$U produced from the decay of the 
+extracted $^{233}$Pa stored outside the core until it reaches the required 
+startup mass for a new reactor. Thus, the criticality of the core is 
+maintained by refueling external fissile material. In the current work, using 
+the thorium feed mechanism, we simultaneously feed thorium and all or fraction 
+of produced $^{233}$U from the \texttt{Pa-decay tank} into the core. The 
+excess $^{233}$U (if exists) is stored outside the core. In the non-thorium 
+feed mechanism, we continuously inject external heavy metals (HALEU, Pu mixed 
+with HALEU, reactor-grade Pu, or TRU) and fraction of produced $^{233}$U from 
+the \texttt{Pa-decay tank}. For the non-thorium mechanism, we feed a part of 
+produced $^{233}$U because in some cases (e.g., TRU) refueling only external 
+heavy metals failed to maintain the core criticality (limitation is 
+dm$_{salt}$ $\leq$ 0.1\%).
 

### 2020-02-25 paper/methods.tex

@@
 	\item A simple calculation yields the amount of heavy metal that must be added during this cycle:
-	\subitem 3a.
-\textbf{Thorium feed mechanism}: mass of injected $^{233}$U $\approx$ mass of extracted Pa and mass of injected Th $\approx$ mass of extracted FPs to maintain the total fuel mass constant.
+	\subitem 3a. \textbf{Thorium feed mechanism}: mass of injected $^{233}$U 
+	$\approx$ mass of extracted Pa and mass of injected $^{232}$Th $\approx$ 
+	mass of extracted FPs to maintain the total fuel mass constant.
 	\subitem 3b.
@@
 \end{enumerate}
-In both feed mechanisms (thorium and non-thorium) we continuously added $^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d).
-To keep the total fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of injected Th must be equal to the mass of extracted FPs and for \textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of extracted FPs.
+In both feed mechanisms (thorium and non-thorium) we continuously added 
+$^{233}$U and the mass of injected $^{233}$U is equal to the mass of extracted 
+Pa ($^{233}$Pa decays to $^{233}$U after $\approx$ 27 d). To keep the total 
+fuel mass almost constant, for \textbf{thorium feed mechanism}, the mass of 
+injected thorium must be equal to the mass of extracted FPs and for 
+\textbf{non-thorium feed mechanism}, the mass of injected fuel (i.e., HALEU, 
+Pu mixed with HALEU, reactor-grade Pu, or TRU) must be equal to the mass of 
+extracted FPs.
 

### 2020-02-25 paper/results.tex

@@
 Figure~\ref{fig:diffPuAll811} shows the variation in fissile plutonium 
-isotopes ($^{239}$Pu , $^{241}$Pu, and $^{243}$Pu) inventory during reactor 
+isotopes ($^{239}$Pu, $^{241}$Pu, and $^{243}$Pu) inventory during reactor 
 operation. For TRU and reactor-grade Pu, the fissile plutonium isotopes are 
